### 2014-08-27 domino-study_hri15.tex
Raw content drop out of Julia's thesis
Result diagrams are missing.

\documentclass{sig-alternate}

% UTF8 support
\usepackage[utf8x]{inputenc}

\usepackage{subfig}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{multirow}

\newcommand{\eg}{{\textit{e.g.~}}}
\newcommand{\etal}{{\textit{et al.~}}}
\newcommand{\ie}{{\textit{i.e.~}}}

%
% --- Author Metadata here ---
\conferenceinfo{10th ACM/IEEE International Conference on Human-Robot Interaction}{2015 Portland, USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{\LARGE \bf
How Children Perceive and Interact with a Robot that Behaves Unexpectedly - The Domino Experiment
}

%%% HRI 2015 -> double-blind review process

%\numberofauthors{1} 
%\author{
%\alignauthor
%Julia Fink, S\'{e}verin Lemaignan, Pierre Dillenbourg\\
%%\titlenote{Dr.~Trovato insisted his name be first.}
%       \affaddr{Computer-Human Interaction in Learning and Instruction Lab (CHILI)}\\
%       \affaddr{Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL)}\\
%       \affaddr{CH-1015 Lausanne}\\
%       \affaddr{Switzerland}\\
%       \email{firstname.lastname@epfl.ch}
%}
%
%\additionalauthors{Additional authors: 
%Francesco Mondada, LSRO, EPFL, francesco.mondada@epfl.ch 
%}
%

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{I.2.9}{Artificial Intelligence}{Robotics}[commercial robots and applications]

%\terms{Theory}

\keywords{anthropomorphism; children; engagement; human-robot interaction; mental models of robot behavior; wizard-of-oz}

\section{Introduction}

In the previous study, we investigated how children interact and relate to
Ranger. We found that manipulating the robot's behavior (\textit{proactive vs.
reactive}) can result in a different interaction style with the robot
(\textit{playful vs. task-oriented}). Generally, the robot was able to motivate
children to tidy up by putting their toys into the box.

However, the observed engagement and motivation may be due to an initial
fascination for the robot which is likely to fade out over time. Sustaining
interaction beyond novelty in HRI is challenging, and in child-robot
interaction, in particular. Also in the Roomba Study, we saw that initially,
children were fascinated by Roomba and played with it (even though this robot is
not made to encourage children to interact with it) but most of the children
lost their fascination soon and engaged less in using or playing with the robot.
Previous work comes to a similar conclusion. For instance, a study with the Pleo
robot in family homes showed that children interacted less with the robot after
some time \cite{fernaeus_how_2010}. We can expect a similar trend with Ranger.
This makes it important to explore possibilities of how to sustain children's
interaction with Ranger. The question is, how we can enhance children's interest
in Ranger so that they still engage with it after some time, and still feel
motivated by the robot to tidy up. Can we achieve this without increasing the
complexity and cost of the robot too much, keeping in mind the affordability of
the robot and its prospective deployment in a domestic environment?

In this chapter, we present a study that explores possibilities of sustaining
children's engagement with Ranger by manipulating the robot's behavior in such
way that it appears \textit{unexpected} to the children. We examine how
different variations of robot behavior impact children's interaction with Ranger
and their perception of it (\eg in terms of attributing intention and cognitive
abilities to the robot).

Using a playful domino game as the interaction scenario, we refer to this study
hereafter as the \textbf{``Domino Study''}.

\section{Scope and Research Goals}

\textbf{Engagement} is a metric that has been extensively used and studied both
in HRI and interactions with other agent-like systems. It has been defined from
several perspectives. For example \cite{sidner_where_2004} define engagement as
\textit{``the process by which two (or more) participants establish, maintain
and end their perceived connections''}. A definition of long-term engagement is
proposed by \cite{bickmore_maintaining_2010}: \textit{``the degree of
involvement a user chooses to have with a system over time''}.

Different possibilities to foster engagement (both short- and long-term
engagement) in HRI have been explored, in particular with social robots. A lot
of research has moved toward creating sophisticated emotional models which cause
complex robot behavior. Some other work
\cite{bickmore_maintaining_2010,short_no_2010} has shown that there can be much
simpler ways to enhance engagement.

\cite{bickmore_maintaining_2010} describe a series of longitudinal studies on
engagement with an agent-like system. They demonstrated that user engagement
with an interface agent can be increased using relatively simple techniques and
manipulations that make the agent more life-like and human. For instance, when
the agent showed variations in its behavior, participants were more engaged and
reported a desire to continue interacting with the agent.

Similarly, more looking at short-term engagement, \cite{short_no_2010} found
that a simple manipulation of the robot's behavior can lead to greater
engagement. The authors let participants play several rounds of the
rock-paper-scissors game with the robot (the playfulness of the scenario seems
important). When the robot was cheating from time to time, participants tended
to ascribe intention to the robot what in turn led to greater engagement in how
they were interacting with the robot. The mechanism behind the cheating action
that the robot showed, was that participants did not expect this behavior from
the robot. The authors suggest that \textit{``any deviation from expected
operation is sufficient to create a greater degree of engagement in the
interaction.''} Moreover, \cite[p.~225]{short_no_2010} proposed that
\textit{``many interactions can be improved by the introduction of such simple
behaviors, and that this should be exploited by designers in HRI. Bringing human
and robot together to perform a simple, repetitive, familiar task and then
having the robot behave unexpectedly can increase engagement and mental state
attribution without complex behavioral or mechanical additions.''}
\cite{leite_long-term_2013} studied the long-term engagement of children with a
chess playing robot that adapted its behavior to the children and showed empathy
toward them. She found that empathetic robots are more likely to engage users in
the long-term and they proposed several guidelines for designing such artificial
companions. Our aim for the ``Domino Study'' is however less ambitious than
creating a long-term robot companion. We are still at an early stage of the
development and are using a remote controlled prototype as we did in the
previous study. What we would like to achieve in this study is to find out how
we can enhance children's experience with the robot so that they do not find it
repetitive and boring to interact with Ranger. In general, repetitiveness is
likely to decrease a user's motivation to continue using a system
\cite{bickmore_establishing_2005}.

\section{Related Work}

\subsection{Motivation and Contributions}

The overall motivation of this study is to explore ways of fostering engagement and sustaining children's interest in the robot. Ultimately, the robotic box Ranger aims to motivate children to tidy up, and engagement with the robot is a prerequisite for this: \textit{``Engagement is crucial, because it is typically a prerequisite for other system objectives: If a user stops interaction with a system, then it cannot have any further impact''} \cite[p.~648]{bickmore_maintaining_2010}.

The question is how can we extend children's interest in the robot and sustain their engagement? This question is related to the \textit{novelty effect} which is commonly observed in human-robot interaction. Engagement beyond novelty is challenging to achieve, and optimally a long-term study should be used to investigate the interaction over time. With the current Ranger prototype which is operated by a human Wizard, a longitudinal study in a natural setting was not feasible at this point of time.\footnote{While we were planning this study, a second version of the Ranger prototype was under development. However, we wanted to take any opportunity to study children's interaction with the Ranger in more detail, and therefore set up another short-term study that would focus on a specific aspect of the interaction.} Although we see it as a limitation, most of the HRI studies that investigated engagement and attributions of intentionality to a robot were short-term studies but nevertheless produced relevant results that can encourage future research. Also the Domino Study is a short-term investigation and does not directly look at long-term usage but rather addresses the question of engagement with the robot, which in turn is a pre-requisite for long-term engagement.\\

We studied the effect of three different types of unexpected robot behavior (sometimes also labeled as \textit{misbehavior}) by means of a short-term interaction study in a controlled lab-setting.

If we are able to show that the robot's variation of behavior can improve short-term engagement, it is likely that this also leads to improvement in long-term engagement \cite{bickmore_maintaining_2010}.

\begin{figure}[!h] 
    \centering 
    \includegraphics[width=0.5\columnwidth]{domino_header.png} 
    \caption[How do Children Interact with a Robot that Behaves
    Unexpectedly?]{\small \textbf{How do children perceive and interact with a
    robot that behaves unexpectedly?} In an interaction study in the lab, 26
    children aged 4-5 years played with a robot that behaved unexpectedly from time
    to time. We studied children's engagement with the robot and their attributions
    of intentionality to it.}

    \label{fig:domino-header} 
\end{figure}

\subsection{Research Questions and Hypotheses}

In the Domino Study, we analyze child-robot interaction with a robot that shows
unexpected behavior. In a playful scenario which was set up in a laboratory
environment (Figure~\ref{fig:domino-setup}), 26 children aged 4-5 years were
assembling a domino game together. Each group consisted of two children and the
Ranger robot, which was used to transport domino tiles between the two children.

Ranger usually behaved correctly (expected behavior), coming over to a child
after being called and delivering the domino tile to the other child. However,
in pre-defined rounds Ranger showed unexpected behavior, when a child called the
robot. We defined three different types of \textit{misbehavior} that were tested
in a between-subjects study design:

\begin{itemize}

    \item The robot makes a \textbf{mistake}: When called by the child to come
        over, the robot goes wrong but recognizes its mistake and repairs. We
        expect this to be perceived as \textit{``to err is human''}, and assume
        increased attributions of human-likeness to the robot.\footnote{The
        attribution of human-likeness to a robot is labeled as
        \textit{anthropomorphism}, and we will hereafter sometimes use ``attribute
        intention'' and ``anthropomorphize'' synonymously.}

    \item The robot gets \textbf{lost}: When called by the child to come over,
        the robot goes wrong, without any observable reason, and remains at the
        wrong location. We expect this to be perceived as a bug or system error
        which causes the robot to not work correctly, and assume few
        attributions of human-likeness to the robot.

    \item The robot \textbf{disobey}: When called by the child to come over, the
        robot shows the intention to not obey by literally ``shaking its head'',
        which should reflect the negative reply to the child's request. The
        robot then goes to a wrong location and remains there while it continues
        to shake its head (this cue is not used in the lost behavior). We expect
        the disobey behavior to be perceived as the robot having an
        \textit{``own will''}, and we assume this leads to increased
        attributions of human-likeness (intention) to the robot.

\end{itemize}

We analyzed children's reaction focusing on two main aspects. On one hand,
children's \textbf{behavior} (their reactions) toward the unexpected robot
behavior was studied in terms of \textbf{active engagement} with the robot. On
the other hand, we analyzed children's \textbf{perception} of the robot in term
of \textbf{anthropomorphism} -- the attribution of human-like characteristics,
such as cognitive abilities and the ability to show intentions. We assumed that
in general a robot that behaves unexpectedly from time to time can promote
engagement and lead children to attribute intention to it. \cite{short_no_2010}
found that participants anthropomorphize a cheating robot more than a robot that
always behaves fairly, and also evaluate the interaction as more engaging. Based
on the related work we formulate the following two hypotheses:

\begin{description}

    \item[Hypothesis 1:] Children show more engagement toward a robot that
        behaves unexpectedly from time to time compared to a robot that always
        behaves correctly (within subjects variable).

    \item[Hypothesis 2:] Children perceive a robot that shows intention or
        cognitive abilities as more human-like than a robot that appears to have
        a system error, \ie the disobeying robot and the robot that makes a
        mistake will be more anthropomorphized than the robot that gets lost
        (between subjects variable).

\end{description}

Our research questions deal with both children's observable behavior and their
perception of the robot. We would also like to explore the relation between
these two aspects, related to the attribution of human-like characteristics to
the robot. The motivation behind this is to find out whether
\textit{anthropomorphism} cannot only be measured as a specific type of
perception but also as an observable behavior in the interaction itself. Thus,
we would like to take a first step in bringing things together and develop an
\textbf{index of anthropomorphism} that considers both children's perception and
interaction aspects (qualitatively). Previous work suggests that a social
relation to a robot (we view anthropomorphism as a specific type of social
relation) reflects an increased engagement and can be effective in sustaining
interaction. Consequently, we hypothesize a positive correlation between the
anthropomorphic perception of the robot and the amount of engagement in the
interaction.

%\subsection{Engagement}

%\subsection{Unexpected Robot Behavior}

\section{Method and Procedure}

\subsection{Description of the Scenario}

The basic idea of the interaction scenario was that there are two children who
play domino together, with the help of the robotic box Ranger. The scenario
setup is displayed in Figure~\ref{fig:domino-setup}. The challenge is that the
tiles of the domino are distributed in the room, hidden behind three beanbags,
and while one child -- \textit{the searcher} -- searches for the right tile, the
other child -- \textit{the receiver} -- is asked to stay in a play tent. There
is a ``river'' (play carpet) in between the two children that we told them they
cannot cross and therefore they need the robot to transport the domino tiles
between them.

We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
pictures of comic farm animals: cow, sheep, hen, donkey, duck, pig, rabbit. The
pictures were taken from a commercially available domino game adapted to the age
of the children (produced by Djeco, advised age 3+).

To start the game (divided in several \textit{runs} that correspond each to the
delivery and assembling of one domino tile), there is already one domino tile in
front of the tent, where \textit{the receiver} child stays and assembles the
domino chain. \textit{The receiver} child asks \textit{the searcher} child for a
specific tile, \eg a tile with a donkey, \textit{the searcher} searches for the
respective tile, sits down on the next beanbag, and asks the robot to come over.
The Ranger robot is first located next to the tent, then, when called by the
\textit{searcher} it starts moving, crosses the river carpet, and comes over to
the \textit{searcher} on the beanbag. The \textit{searcher} child puts the
domino tile into the robotic box, and the robot then goes back to \textit{the
receiver} child in the tent. Then, \textit{the receiver} takes out the domino
tile from the robot, and puts the two tiles together. The first \textit{run} is
over, and a new \textit{run} starts, when \textit{the receiver} asks \textit{the
searcher} for the next domino tile.

\subsection{Manipulation of Robot Behavior}
\label{sec:domino-manipulation}

We used the same prototype as in the previous study, and Ranger was again
controlled by a human Wizard, who was in the same room (see
Figure~\ref{fig:domino-setup}). This was to ensure that the Wizard could see
children's interaction and hear their commands to the robot without any delay.
Following a pre-defined script, the robot showed a behavior as presented in the
following list.

\begin{figure}[!b] 
    \centering 
    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
    \caption[Study Setup of the Playroom in the Lab]{\small \textbf{Study setup
    of the playroom in the lab (schematic top view)}. We configured one of the
    rooms in the lab to a playroom with a children's tent from IKEA, in which one of
    the children is located (referred to as \textit{the receiver} or ``the child in
    the tent''). A play carpet with a river on it is used as an imaginary barrier
    between the two children. The other child, referred to as \textit{the searcher}
    (or ``the child on the beanbag'') is asked to remain ``on the other side of the
    river'' in the area with the 3 beanbags, behind which each 3 domino tiles are
    distributed (displayed as black stars). In the back of the room, there is a
    camera to record the interaction scenario, and right next to it in the corner,
    there is the Wizard control station: a table with a laptop computer. As some
    parents stayed in the room during the interaction study, they are asked to sit
    on the chairs placed in the back of the room. The board next to the door is not
    used during the experiment, it is simply an accessory. The solid green arrows,
    show the robot's path for the \textit{correct} behavior. The blue dashed arrow
    visualizes a possible \textit{lost} path, where the Ranger stops and remains at
    a wrong stop (denoted by the blue cross). The yellow arrows reflect a possible
    \textit{mistake} path, where the robot goes wrong but then turns toward the
    searcher child (U-turn), and then comes straight over to the searcher. The red
    dashed arrow visualizes a possible \textit{disobey} path where the robot goes
    wrong, then turns toward the child but remains at the wrong stop (red cross).
    The different audio and visual cues that the robot uses during the different
    paths are explained in the text.}

    \label{fig:domino-setup} 
\end{figure}

The \textbf{correct} robot behavior:

\begin{itemize}

    \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
        and shows green light pattern (Figure~\ref{fig:domino-put},
        page~\pageref{fig:domino-put}, the light pattern is still yellow here
        indicating that Ranger ``reached'' the child; the green light pattern
        was shown slightly after the putting was done)

    \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
        sound and shows green light pattern (Figure~\ref{fig:domino-remove},
        page~\pageref{fig:domino-remove}).

        %	\item \emph{Box is touched or petted:} Ranger ``blushes'' with pink
        %	light around the area of the box's ``cheeks''

        %	\item \emph{Box is kicked or mistreated:} Ranger makes a
        %	``disturbance'' sound and the box moves backward

    \item \emph{Robot is called by one of the children:} When one of the
        children called the robot saying something like \textit{``Robot come
        here!''}, the robot starts moving toward the child
        (Figure~\ref{fig:domino-call}, page~\pageref{fig:domino-call}). Ranger
        does not react to any other verbal commands.

    \item \emph{Robot reaches one of the children:} When in front of one of the
        children who should either put or remove a domino tile, Ranger stops and
        shows yellow light, if no reaction, Ranger also makes a wiggle-like move
        (Figure~\ref{fig:domino-show}, page~\pageref{fig:domino-show}).

\end{itemize}

\begin{figure*}[!b]
  \centering

  \subfloat[call]
  {\label{fig:domino-call}
  \includegraphics[height=4cm]{domino-call.png}} 
  \subfloat[put]
  {\label{fig:domino-put}
  \includegraphics[height=4cm]{domino-put.png}}
  \subfloat[remove]
  {\label{fig:domino-remove}
  \includegraphics[height=4cm]{domino-remove.png}}

  \bigskip

  \subfloat[explore]
  {\label{fig:domino-explore}
  \includegraphics[height=4cm]{domino-explore.png}}
  \subfloat[gesture]
  {\label{fig:domino-gesture}
  \includegraphics[height=4cm]{domino-gesture.png}}
  \subfloat[misuse]
  {\label{fig:domino-misuse}
  \includegraphics[height=4cm]{domino-misuse.png}}

  \bigskip

  \subfloat[show]
  {\label{fig:domino-show}
  \includegraphics[height=4cm]{domino-show.png}}
  \subfloat[touch]
  {\label{fig:domino-touch}
  \includegraphics[height=4cm]{domino-touch.png}}   
  \subfloat[look at experimenter]
  {\label{fig:domino-look}
  \includegraphics[height=4cm]{domino-look.png}}\\

  \caption[Children's Interactions with the Robot and the Feedback of the
  Robot]{\small \textbf{Children's interactions with the robot and the feedback
  of the robot.} Apart from \textit{talking} to the robot, which is not
  displayed here, there were nine main interactions, which are explained in the
  respective paragraph on how children's behavior was coded in the videos
  (page~\pageref{sec:domino-coding}). The robot showed feedback to some of the
  children's actions: \textit{call, put} and \textit{remove} (top row), as
  explained in the text.}

  \label{fig:domino-actions}
\end{figure*}

Most of the time when the sender child (on one of the beanbags, see
Figure~\ref{fig:domino-setup}, page~\pageref{fig:domino-setup}) calls the robot,
it correctly goes right over to the beanbag where the child sits (bold green
arrows in Figure~\ref{fig:domino-setup}). It starts from its starting position
next to the tent, crosses the play carpet with the ``river'' and then goes to
the respective beanbag. During some specific \textit{runs} however, the robot
behaves unexpectedly (dashed arrows in Figure~\ref{fig:domino-setup}). There
were three different \textbf{manipulations} of the robot behavior:

\begin{itemize}

    \item \textbf{Mistake:} The sender child calls Ranger. The robot goes until
        it is on the carpet, stops, turns, and goes wrong (see yellow path in
        Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns
        its ``face'' toward the sender child, and ``blushes'' red around its
        ``cheeks'' (as if it recognizes its wrong position,
        Figure~\ref{fig:domino-mistake}, page~\pageref{fig:domino-mistake}).
        Then, Ranger goes correctly over to the sender child. The
        \textit{mistake} behavior is \textit{robot-repaired}, as no
        human-intervention is needed.

    \item \textbf{Lost:} After being called, Ranger goes until it is on the
        carpet. There, it stops, turns, and goes wrong (see blue path in
        Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
        with its ``face'' turned away from the child, and it blinks in yellow
        light (the same as when in front of a child) (see
        Figure~\ref{fig:domino-lost}, page~\pageref{fig:domino-lost}). Ranger
        remains waiting at the wrong position until the experimenter tells the
        child to go over to the robot to put the domino tile. The \textit{lost}
        behavior is \textit{human-repaired}, as it needs human-intervention.

    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
        carpet. Then, it shows \textit{disobeying} behavior: It stops, makes red
        light all over its surface and produces a repeated ``disturbance''
        sound. It turns, and goes to a wrong position (see red path in
        Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its
        ``face'' toward the sender child (Figure~\ref{fig:domino-disobey},
        page~\pageref{fig:domino-disobey}). In addition to the red blinking,
        Ranger makes a slow wiggle-like move, and remains waiting at the wrong
        position until the experimenter tells the child to go over to the robot
        to put the domino tile. Also the \textit{disobey} behavior is
        \textit{human-repaired}.

\end{itemize}

\begin{figure}[!t]
  \centering
\subfloat[mistake]
  {\label{fig:domino-mistake}
  \includegraphics[height=5cm]{domino-mistake.png}}
  \subfloat[lost]
  {\label{fig:domino-lost}
  \includegraphics[height=5cm]{domino-lost.png}}
  \subfloat[disobey]
  {\label{fig:domino-disobey}
  \includegraphics[height=5cm]{domino-disobey.png}}

  \caption[The Three Robot Misbehaviors]{\small \textbf{The three robot
  misbehaviors.}}

  \label{fig:domino-misbehavior}
\end{figure}

On its way back to the tent, Ranger always goes correctly. After the sender
child has put a domino tile, Ranger automatically turns and goes over to the
tent (the receiver child does not even need to call the robot).

%\paragraph{Time points of robot misbehavior}

After several correct runs, we assumed that children expect consistent robot
behavior. When the robot then does something unexpected, children are likely to
be positively surprised. A similar effect has been observed in a study with a
robot that was cheating from time to time \cite{short_no_2010}.

It may be that children interpret the unexpected robot behavior as a failure.
But we do not want them to lose trust in the robot, contrary, the unexpected
robot behavior should have a positive effect and promote engagement. We tried to
avoid a negative influence by timing the robot misbehavior not at the very
beginning and very end of the interaction, because it has been shown that early
and late robot failures negatively impact trust
\cite{desai_effects_2012,desai_impact_2013}. Desai et al. suggest that users
should all start and end with a working system. Consequently, we placed several
unexpected robot behaviors around the middle of the interaction, as shown in
Table~\ref{tab:domino-second}.

Also \cite{short_no_2010} decided to follow this pattern when introducing
unexpected robot behavior. In their study with a robot that cheated, from the 20
rounds of the rock-paper-scissors game, the robot cheated three times in the
middle: on the 4th, 8th and 15th round. The authors adjusted the interaction
length so that the spacing and timing of the cheating was preserved.

In our study, there were 14 runs in total. 5 runs were used to set the baseline
and in those 5 runs the robot always behaved correctly. Then, in the 9 remaining
runs, the robot showed misbehavior at the $3^{rd}$ and $4^{th}$ run as well as
at the $7^{th}$ and $8^{th}$ run (see Tables~\ref{tab:domino-first} and
\ref{tab:domino-second} on page \pageref{tab:domino-first}).

\subsubsection{Scenario Description}

\subsubsection{Manipulation of Robot Behavior}

\subsubsection{Semi-structured Interviews with Children}

\subsubsection{Participants}

Overall, there were 13 pairs of children (n=26) participating in the interaction
study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45). In 11 of the
pairs, children were friends who knew each other from kindergarten, nursery
school or because they lived in the same neighborhood. 2 of the pairs were
composed of brother and sister.

Table~\ref{tab:domino-sample} (page~\pageref{tab:domino-sample}) gives an
overview.

\begin{table}[H]
%\vspace{1 cm}
\captionof{table}[Domino Study Participants]{\small \textbf{Overview of the 13 groups (n = 26 children) that participated in the Domino Study.} The \textit{scenario duration} is the time that children spent interacting with the robot. The time duration of the short interviews is not included here. The \textit{anthropomorphism index} is a score that we developed and which measures how far children anthropomorphize the robot during the interaction study and the interview (see Section~\ref{sec:domino-anth-score}). The last row of the table gives the overview of the sample including the Mean age (M), the average scenario duration and average anthropomorphism index.}
\label{tab:domino-sample}       % Give a unique label
\centering
\footnotesize

\begin{tabular}{lllll}
\hline\noalign{\smallskip}
	\multirow{3}{*}{\textbf{group}} & \multirow{3}{*}{\textbf{children (age)}} & \multirow{3}{*}{\textbf{relation}} & \textbf{scenario} & \textbf{anthropomorphism} \\
	 & & & \textbf{duration} & \textbf{index} \\
	 & & & (min:sec) & points / \% \\
\noalign{\smallskip}\hline\hline\noalign{\smallskip}

	mistake1 & boy (4) & friends & 19:01 & 5.75 / 36~\% \\ 
	& boy (4) & & & \\ 
\noalign{\smallskip} \hline \noalign{\smallskip}

	mistake2 & boy (5) & friends & 15:28 & 10 / 63~\% \\
	& boy (4.5) & & & \\ 
\noalign{\smallskip} \hline \noalign{\smallskip}

	mistake3 & boy (4) & family & 15:24 & 8 / 50~\% \\ 
	& girl (4) & & & \\ 
\noalign{\smallskip} \hline \noalign{\smallskip}

	mistake4 & boy (4.5) & friends & 13:23 & 8 / 50~\% \\ 
	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \hline \noalign{\smallskip}

	lost1 & boy (4.5) & family & 17:08 & 8.75 / 55~\% \\ 
	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}

	lost2 & boy (5) & friends & 16:43 & 8.75 / 55~\% \\
	& boy (4.5) & & & \\  
\noalign{\smallskip} \hline \noalign{\smallskip}

	lost3 & girl (4.5) & friends & 15:01 & 7.5 / 47~\% \\ 
	& girl (4.5) & & &  \\ \noalign{\smallskip} \hline \noalign{\smallskip}

	lost4 & boy (5) & friends & 13:04 & 8.25 / 52~\% \\
	& girl (4) & & & \\ 
\noalign{\smallskip} \hline \hline \noalign{\smallskip}

	disobey1 & boy (4.5) & friends & 13:37 & 3.75 / 23~\% \\
	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}

	disobey2 & boy (4.5) & friends & 17:37 & 3.25 / 20~\% \\ 
	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}

	disobey3 & boy (5.5) & friends & 17:38 & 10.25 / 64~\% \\ 
	& boy (5.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}

	disobey4 & girl (4) & friends & 14:46 & 4.5 / 28~\% \\
	& girl (4) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}

	disobey5 & boy (4) & friends & 16:25 & 10.75 / 67~\%  \\
	& boy (4) & & & \\
\noalign{\smallskip} \hline \hline \noalign{\smallskip}

	13 groups & M age 4.46 & 2 family & 15:47 & M 7.5 / 47~\% \\ 
	26 children & 16 boys, 10 girls & 11 friends & & (SD 2.5 points) \\	
\noalign{\smallskip}\hline

\end{tabular}
\end{table}

\subsubsection{Course of the Study}

We recruited pairs of children (4-5 years old, who knew each other) to play a
``collaborative domino game with a robot''. We distributed flyers in the campus
kindergarten, sent out mails to pre-schools in town, and made a posting on an
online-blog that targets parents in Lausanne.

Participants were invited to come to our lab for a playful child-robot
interaction study that would last 60 min at most. Parents (or guardians) brought
their children and could either stay in the arranged play room or go to the
cafeteria in the same building. During the study, two experimenters were
present.

\begin{itemize}

    \item \textbf{Introduction and pre-interview ($\sim$5~min):} One of the
        experimenters introduced the study to the parents and asked them to sign
        a consent form. The other experimenter briefed children by explaining
        them the domino game and conducting the pre-interview (questions about
        previous experience with robots, and their expectations)\footnote{The
        interview questions for all three short-interviews are given in
        Table~\ref{tab:domino-questions} and the original French version can be
        found in the Appendix (page~\pageref{apx:domino-interview}).}. At the end of the
        pre-interview we introduced the Ranger box (first hidden under the wizard table)
        and explained that it was there to transport the domino tiles between them.

    \item \textbf{First interaction phase ($\sim$10~min):} In all 5 runs the
        robot behaves correctly, as displayed in Table \ref{tab:domino-first}.
        This first interaction phase was the same across all three conditions.
        It serves to familiarize children with the situation, the robot, and the
        game. We can assume that children expect consistent robot behavior
        afterwards.

\begin{table}[H]
\captionof{table}[First Interaction Phase (5 Runs with Correct Robot Behavior)]{\small \textbf{First interaction phase.} The robot behaved correctly~(v) in all five runs.}
\label{tab:domino-first}       % Give a unique label
\centering
\footnotesize
\begin{tabular}{lccccc}
\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
	&  run 1.1 & run 1.2 & run 1.3 & run 1.4 & run 1.5  \\ 
\noalign{\smallskip}\hline\hline
	\textit{correct} & v & v & v & v & v  \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

    \item \textbf{First short interview ($\sim$5~min):} In this interview we
        asked children several questions to assess their first impression of
        Ranger, and how far they ascribe cognitive abilities and mental states
        to the correctly behaving robot. After this first interview, children
        switched their roles (beanbag / tent), so to create a balance.

    \item \textbf{Second interaction phase ($\sim$20~min):} In the 9 runs of the
        second phase, the robot alternated between behaving correctly and
        misbehaving, as displayed in Table \ref{tab:domino-second}.

\begin{table}[H]
\captionof{table}[Second Interaction Phase (9 Runs with Partly Robot Misbehavior)]{\small \textbf{Second interaction phase.} There are 9 runs in the second interaction phase. At some time points, namely runs 2.3, 2.4 and 2.7, 2.8., the robot showed the respective misbehavior~(x), according to the experimental group either \textit{mistake, lost} or \textit{disobey}. In the other runs, namely runs 2.1, 2.2. and 2.5, 2.6 and 2.9 the robot behaved correctly~(v).}
\label{tab:domino-second}       % Give a unique label
\centering
\footnotesize
\begin{tabular}{lccccccccc}
\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
	&  run 2.1 & run 2.2 & \textbf{run 2.3} & \textbf{run 2.4} & run 2.5 & run 2.6 & \textbf{run 2.7} & \textbf{run 2.8} & run 2.9 \\ 
\noalign{\smallskip}\hline\hline
	\textit{mistake} & v & v & \textbf{x} & \textbf{x} & v & v & \textbf{x} & \textbf{x} & v \\ 
	\textit{lost} & v & v & \textbf{x} & \textbf{x} & v & v & \textbf{x} & \textbf{x} & v \\ 
	\textit{disobey} & v & v & \textbf{x} & \textbf{x} & v & v & \textbf{x} & \textbf{x} & v \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

    \item \textbf{Second short interview ($\sim$5~min):} After this phase of
        interacting with the unexpectedly behaving robot, we conducted another
        short interview and a debriefing with the children. We mostly asked
        open-ended questions, concerning several topics, such as whether they
        noticed anything unusual in the robot behavior (manipulation check), and
        how far they ascribe cognitive abilities, mental states, and moral
        standing to the robot after it had shown unexpected behavior.

\end{itemize}

In the end, we thanked parents and children and each child received a little
gift (\eg a small puzzle or a coloring book). Some children made a drawing of
the robot, which may be an interesting qualitative evaluation tool for future
studies with young children.

%	when there was enough time (we set a time limit of 60 min as duration for the entire experiment), we asked children to draw the Ranger robot with which they had just played.

The study was set up as a between-subjects experiment with three conditions,
corresponding to the three types of robot misbehavior. Thus, in one group the
robot only showed one type of misbehavior during the second interaction phase.
There were each 4 groups in the \textit{mistake} and \textit{lost} condition,
and 5 groups in the \textit{disobey} condition (see
Table~\ref{tab:domino-sample}). We did not have a control condition in which the
robot always behaved correctly in all 14 runs. However, we consider the first 7
runs as reference for \textit{expected behavior} (runs 1.1-2.2), to compare
against the remaining 7 runs, reflecting \textit{unexpected behavior} (2.3-2.9,
manipulation phase with the 3 conditions). As such, we can carry out a
within-subjects analysis to investigate the difference between expected and
unexpected robot behavior. All interactions and interviews were video and
audio-recorded.

\subsection{Semi-structured Interviews with the Children}

It is not easy to interview young children. We have seen this in our previous
study. Children have a short attention span, we (the experimenters) are
strangers to them, and they are in an unfamiliar environment. The pre-interview
served to ``break the ice'' and during the first playful interaction phase, most
children familiarized themselves with the situation.

Also, children do not articulate themselves and understand questions like
adults. We tested our interview structure and the script in a pilot-study with
three young children, and were assisted in formulating our questions by a
pedagogue and father of four. This helped us adapting our language and
question-style to the 4-5 year old participants. We set up the interviews like a
casual conversation / discussion, so we did not separate the two children in
order to keep the situation natural. We used casual and informal language
adapted to the age of the children, and encouraged them to justify their answers
and tell us more details by asking, for example, \textit{How do you know ... ?}
or \textit{Tell me, what have you observed when ... ?}. We paid attention to not
``put words in children's mouth''. Consequently, though we re-phrased and
repeated some questions, we never forced children to give an answer, and
accepted when they said they would not know or when they did not respond at all.

\begin{table}[h]
%\vspace{1 cm}
\captionof{table}[Questions Used During the Interviews with Children]{\small \textbf{Questions used during the semi-structured interviews with children.} An ``X'' indicates if the question was used in the pre-interview (\textit{pre}), in the \textit{first} short interview (after the 5 runs in which the robot behaved correctly) or in the \textit{second} short interview (after the 9 runs in which the robot sometimes showed unexpected behavior). The Ranger robot toy box is abbreviated with ``R''. (The original French version of the interview script is in the Appendix, page~\pageref{apx:domino-interview}.)}
\label{tab:domino-questions}       % Give a unique label
\centering
\footnotesize
\begin{tabular}{lcccl}
\hline\noalign{\smallskip}
	\textbf{question} & \textbf{pre} & \textbf{first} & \textbf{second} & \textbf{construct} \\
\noalign{\smallskip}\hline\hline\noalign{\smallskip}

	How do you imagine a robot? & X & & & \multirow{3}{*}{expectation} \\
	What could it look like? & X & & & \\
	Have you ever seen a robot before? & X & & & \\
\noalign{\smallskip} \hline \noalign{\smallskip}

	When you first saw R, what did you think? &  & X & & \multirow{4}{*}{impression} \\
	Is R a robot? How do you know? & & X & & \\
	Did you expect R would come over to you when you call it? & & X & & \\
	What happened when you put the domino tile in the box? & & X & & \\
\noalign{\smallskip} \hline \noalign{\smallskip}

	Do you think R could go out the door all by itself? & & X & & \multirow{4}{*}{ascribe intention} \\	
	Does R always obey / come over to you? & & X & X & \\
	Could R do something silly? & & X & X & \\
	Why did R not come over to you when you called it? & & & X & \\
\noalign{\smallskip} \hline \noalign{\smallskip}

	Here is a domino tile. Do you think R can see it? & & X & X & \multirow{2}{*}{ascribe cognitive abilities} \\
	When I say \textit{``Hello R!''}, do you think R can hear it? & & X & X & \\	
\noalign{\smallskip} \hline \noalign{\smallskip}

	Does R have feelings? Can R be happy or sad sometimes? & & & X & ascribe emotional state \\
\noalign{\smallskip} \hline \noalign{\smallskip}

	Do you like R? Why (not)? & & & X & \multirow{3}{*}{social acceptance} \\
	What do you (not) like about it? & & & X & \\
	Would you like to have R at home? & & & X & \\	
\noalign{\smallskip} \hline \noalign{\smallskip}

	Could R be your friend? Why (not)? & & & X & companionship\\
\noalign{\smallskip} \hline \noalign{\smallskip}

	Assume you go on a holiday for two weeks. Is it alright & & & \multirow{2}{*}{X} & \multirow{2}{*}{ascribe moral standing}\\
	~~to leave R alone at home? Why (not)? & & &  & \\	
\noalign{\smallskip}\hline

\end{tabular}
\end{table}

We generally needed to keep the interviews as short as possible. In designing
our interview script and selecting relevant questions, we took inspiration from
previous work on child-robot interaction and children's perception of robots
\cite{kahn_jr._robotic_2006,weiss_i_2009,leite_influence_2013}. For instance, we
applied and adapted some of the ``constructs'' and example questions from the
questionnaires used in \cite{kahn_jr._robotic_2006} and \cite{weiss_i_2009}. The
authors evaluated children's perception of the robotic dog AIBO after the
children had played with the robot. A ``construct'' addresses a specific factor
(topic) that can be measured by several questions. For instance, the construct
``cognitive abilities'' (called ``cognition'' in \cite{weiss_i_2009}) considers
the robot's ability to hear and to see (perceptual skills), as attributed by the
children. The construct ``moral standing'' and the respective question was taken
from \cite{kahn_jr._robotic_2006}.\footnote{According to
\cite{kahn_jr._robotic_2006}, \textit{moral} refers to considerations based on
an artifact's physical or psychological welfare, and virtue (whether the
artifact deserves care). An attribution of moral standing reflects, for
instance, that the robot engenders moral regard, is morally responsible,
blameworthy, has rights or deserves respect.}			Similarly, we grouped
questions according to specific constructs that they evaluate (see
Table~\ref{tab:domino-questions}). This was an adaption and extension of the
questions and constructs used in previous work.\\

With several recurring questions in the first and second interview, we wanted to
see the differences in children's perception of the correctly behaving and
unexpectedly behaving robot. We planned to use these two interviews as a
within-subject measurement, however, this did not work out very well because
children's responses were not always accurate, not comparable one by one, and
children did not always give an answer.

%	Even when children reply that they do not know, this is interesting. Then we either do not ask a good question or they are really uncertain about it.

Similar to how we processed interviews in the previous studies, we qualitatively
transcribed interviews, \ie we did not craft a full word-by-word transcript but
noted down any statement that was useful and relevant. This was organized in a
spreadsheet, so to obtain an overview of the different replies to a question.
The interviews were analyzed in a qualitative manner.

\subsubsection{Measurements, Coding and Data Analysis}

We have obtained two main types of data. On one hand, as just described, we can
analyze children's verbal statements concerning their \textbf{perception of the
robot} (captured in the audio recorded interviews). On the other hand, what we
describe in the following paragraphs, we can do a quantitative and qualitative
analysis of \textbf{children's behavior toward the robot} (captured in the video
recordings). Furthermore, we can investigate how far these two types of data can
be used to understand children's engagement in the interaction and how far they
anthropomorphize the robot. We would like to develop a toolkit that considers
both children's perception and interaction, in order to measure anthropomorphism
(as a special type of human-like engagement with the robot).

\paragraph{Coding children's behavior in the videos}	
\label{sec:domino-coding}

Similar to the coding scheme we used in the Ranger study
(Chapter~\ref{chap:Ranger-fieldstudy}), we annotated children's behavior in the
videos. Snapshots of the actions, along with the robot's feedback are shown in
Figure~\ref{fig:domino-actions}, page~\pageref{fig:domino-actions}. For the
segmentation of behavior we also used the same method as in the Ranger study. We
coded 10 different actions:

\begin{itemize}

    \item \textbf{Explore (ex)}: when children actively try to find out what the
        robot is doing (\eg by looking under the box); attentively watch or
        observe the robot (\eg attentively waiting for the box to show a
        reaction); experiment with the robot to figure out how it works (\eg put
        hands in front or inside of the box to see what happens);

    \item \textbf{Misuse (mis)}: when children kick the robot, poke it in its
        ``eye'', try to climb on or inside the box, drive / push the robot
        around, stop the robot's wheels with a foot;\\

    \item \textbf{Put domino (put)}: when a domino tile is put inside the box;

    \item \textbf{Remove domino (rem)}: when a domino tile is removed from the
        box;

    \item \textbf{Gesture (ges)}: when gestures are used to communicate /
        interact with the robot (\eg pointing gestures, waving at the robot);

    \item \textbf{Touch (touch)}: when the box is touched (\eg petted or
        caressed);

    \item \textbf{Show (show)}: when a child shows something to the robot (\eg
        by holding a domino tile in front of its eyes);

    \item \textbf{Call (call)}: when a child calls the robot to come over;

    \item \textbf{Talk (talk)}: when a child directly talks to the robot (using
        direct speech) besides calling the robot;

    \item \textbf{Look (look)}:	when a child looks at the experimenter due to
        confusion caused by the robot; look is not coded when the experimenter
        asks a question to the child;

\end{itemize}

The actions \textit{put, remove} and \textit{call} were ``requested'' actions
because the scenario required them and children were asked to carry them out.
Hence, these actions are not relevant to be analyzed quantitatively. The other
actions \textit{explore, misuse, gesture, touch, show, talk} and \textit{look}
are spontaneous actions that were not requested but arose in the interaction.
Hence, these actions are interesting to study, and they can further be used to
analyze \textbf{engagement}.

\subsubsection{Analyzing engagement with Ranger}

%	\textbf{Engagement} is a key metric in social HRI. In general, there are two
%	types of engagement: emotional and behavioral engagement.  efficacy of
%	various social characteristics (emotion, dialogue, personality \etc) can be
%	measured for capturing attention (acquisition time) and holding interest
%	(duration) \citep{steinfeld_common_2006}.

%	In a long-term interaction study with 8-9 year old children,
%	\cite{leite_long-term_2013} was measuring engagement through video
%	observations (by analyzing the amount of time that children spent looking at
%	the robot), interviews, and questionnaires. The interviews were
%	semi-structured, containing initial yes-or-no questions followed by
%	open-ended questions that allowed children to justify and elaborate their
%	answers.
%We have chosen a similar approach: in video observations we coded the action
%\textit{explore}, which includes carefully watching the robot. We also
%conducted short-term interviews with the 4-5 year old children, however,
%questionnaires were not feasible with this age group.

There are different possibilities to measure engagement in HRI, depending on the
specific research question and context. Metrics to measure behavioral engagement
in the interaction include, for instance, conversation analysis (\eg used in
\cite{short_no_2010}) or general attention analysis. These can be studied by
analyzing interaction videos in terms of head movement, eye tracking and gesture
/ body movement analysis (\eg in \cite{sidner_explorations_2005}).
Post-measurements to measure emotional engagement can be questionnaires that try
to assess constructs like the perceived presence and involvement in the
interaction. An example is the \textit{Interactive Experience Questionnaire}
(originally developed by \cite{lombard_measuring_2000}) of which adapted
versions were used in
\cite{kidd_effect_2004,bainbridge_effect_2008,short_no_2010}.

A mix of several methods has been used in a long-term interaction study with 8-9
year old children, \cite{leite_long-term_2013}. The author measured engagement
through video observations (by analyzing the amount of time that children spent
looking at the robot), interviews, and questionnaires. The interviews were
semi-structured, containing initial yes-or-no questions followed by open-ended
questions that allowed children to justify and elaborate their answers. We have
chosen a similar approach that considers both children's behavioral and
emotional engagement.

%	: in video observations we coded several ``engagement actions
%	\textit{explore}, which includes carefully watching the robot. We also
%	conducted short-term interviews with the 4-5 year old children, however,
%	questionnaires were not feasible with this age group.

With 4-5 year old children, however, we cannot use rating scales to ask them
about constructs as abstract as social presence or how much they felt involved
in the interaction. Here, we rely mostly on video analysis to quantify
engagement. Several of the aforementioned coded actions
(Section~\ref{sec:domino-coding}) can reflect engagement: \textit{explore,
misuse, gesture, touch, show,} and \textit{talk}. Also, \textit{look} at the
experimenter can be considered as engagement in the interaction: We assume that
children look at the experimenter when they are surprised and seek for help.
This behavior reflects that they want to make sense of the robot's behavior and
that they notice it as ``strange''. Further, we can take into account how they
refer to Ranger and describe the robot (as well as their experience) in the
interviews. We describe the combination of the two types of data in the next
paragraphs.

\paragraph{Engagement reflected in the perception of the robot}

We assume that active reasoning about Ranger reflects engagement (or interest in
the robot). But how do we identify whether children, 4-5 years old, reason about
a robot, its cognitive abilities, intentions or mental states, rather than
viewing it as a machine stepping through a task? As \cite{short_no_2010}
mentioned: \textit{``It is not easy to measure the attribution of mental
state.''} Asking \textit{``How much does the robot think?''} is not sufficient.
Short et al. proposed to rely more on subtle cues in the participants' behavior
and responses. The nature of participants' responses to open-ended question
about the robot's behavior (whether they noticed anything unusual and what) can
give insight into their attributions of mental state to the robot.

%	In \cite{short_no_2010}, a speech analysis revealed that participants used
%	more active voice verbs to describe the behavior of the cheating robot
%	compared to the robot that behaved fairly at all times. The authors
%	interpret that a use of active voice implies action in choice, and
%	attributions of mental state to the robot.

In terms of children's perception of Ranger, we used some of the questions
presented in Table~\ref{tab:domino-questions} to assess how far they
anthropomorphize the robot. As an indication for anthropomorphism we take
questions in the constructs \textit{ascribe intention, ascribe cognitive
abilities, ascribe emotional state}, and \textit{ascribe moral standing}.

\paragraph{Engagement reflected in the interaction}

As previously mentioned, from the 10 types of actions that were coded in the
videos, we cannot consider all of them as reflecting engagement with Ranger.
Since we asked children from our side to \textit{call} the robot, as well as to
\textit{put} and \textit{remove} domino tiles, these three actions were
excluded. Finally, we consider the following 7 actions as \textbf{engagement
actions}: \textit{explore, misuse, gesture, touch, show, talk}.\footnote{In
several figures of the ``engagement actions'' later on, \textit{explore} is
excluded from the visualization because it was too prominent and differences in
the other actions would not be observable. The huge proportion of
\textit{explore} suggests that this category needs to be refined in future
studies.}

\paragraph{Anthropomorphism index}
\label{sec:domino-anth-score}

To account for the fact that anthropomorphism arises in an interaction, we try
to bring both children's perception of the robot (post-measurement) and their
behavior toward it (in-the-moment measurement) together. By doing so, we would
like to obtain a qualitative \textbf{anthropomorphism index}. We quantify the
index by giving 1 point for each anthropomorphic perception of the robot (max.
13 points) and for specific kinds of human-like behavior toward the robot (max.
3 points). The index included the following aspects:\\ \\

\textbf{Perception: \textit{(max. 13 points)}}
\begin{itemize}
	\item Ascribe \textbf{mental states / feelings} to Ranger: \textit{0-4 points}\\
	(2 points for agreeing that Ranger can be happy or sad; 2 points for attributing Ranger with hunger or tiredness)
	\item Ascribe \textbf{cognitive abilities / intention} to Ranger: \textit{0-4 points}\\ 
	(each 0.5 points for ascribing seeing and hearing ability; 1 point for agreeing that Ranger can go out the door by itself; 1 point for disagreeing that Ranger always obeys; 1 point for agreeing that Ranger can do something silly)
	\item Ascribe \textbf{sociality / companionship} to Ranger: \textit{1 point}\\ 
	(1 point for agreeing that Ranger can be a friend)
	\item Ascribe \textbf{moral standing} to Ranger: \textit{1 point}\\ (1 point for disagreeing that Ranger be left alone at home)
	\item Other \textbf{anthropomorphic statements}: \textit{0-3 points}\\ 
	(1 point for anthropomorphic reason for Ranger's misbehavior; 2 points for anthropomorphic reason for not leaving Ranger alone) 
\end{itemize}

\textbf{Behavior: \textit{(max. 3 points)}}
\begin{itemize}
	\item Use of \textbf{direct speech} toward Ranger: \textit{1 point}\\
	(\textit{calling} the robot to come over is not considered)
	\item Use of \textbf{polite formulations} toward Ranger: \textit{1 point}\\ 
	(\eg saying \textit{``thank you Ranger''} or \textit{``please Ranger ...''} or \textit{``goodbye''})
	\item Use of \textbf{social or pointing gestures} toward Ranger: \textit{1 point}\\ 
	(\eg waving at the robot, nodding)
\end{itemize}

There are certainly limitations to this scoring scheme. For instance, the
balance between perception and behavior aspects is questionable (13 to 3
points). Also, we did not consistently assign 1 point to each item, but assigned
points between 0.5 and 2 points. We did this because we found that different
items reflect a higher level of anthropomorphic perception of the robot than
others (for instance, ascribing the ability to see an hear was suggested by our
study setup, and we cannot be sure that it really reflects anthropomorphism).
There are possibilities of refinement of this scoring scheme. For instance, a
more systematic weighting procedure and the identification of all relevant
factors would be an interesting future achievement. We could introduce a formula
to calculate the anthropomorphism index \textit{$\alpha$} by taking the sum of
the various items ($x_1, x_2, x_3...$) and different weights ($a, b, c ...$) to
balance them: $\alpha$ \textit{=} $a x_1$ \textit{+} $b x_2$ \textit{+} $c x_3
...$~. Machine learning techniques could be used to optimize such a calculation
of the anthropomorphism index.

\section{Findings}

There are two main types of findings: 1) related to the interaction of the
children with the robot and 2) related to the perception of the robot. This
section is organized accordingly. We then bring both types of data together by
building the \textit{anthropomorphism index}.

\subsection{Interaction}

\paragraph{Scenario and run duration}

In total, there was more than 5~hours of video material obtained from the
13~groups. The video material consisted of around 3.5~hours of the two
interaction phases and 1.5~hours of interviews. The interaction analysis
considers only the video parts that correspond to the \textit{scenario
duration}, which starts when the receiver child in the tent asks the searcher
child for the first domino tile, and it stops when the receiver child puts
together the last domino to the chain. The scenario duration is split in two
interaction phases, as described in Section \ref{sec:domino-course-study}, with
a pause in the middle, that corresponds to the first interview. On average, the
first interaction phase with 5 runs of the always correctly behaving robot
lasted 5~min~34~sec. The second interaction phase with 9 runs and the partly
misbehaving robot lasted on average 10~min~14~sec. Overall, the scenario
duration (all 14 runs) varied between 13~min~04~sec and 19~min~01~sec (average
15~min~47~sec, SD~=~1~min~50~sec). The condition had no significant impact on
the scenario duration (F(2,23)=.18, p=.835).\\

When looking at the average duration of each run, it is not a surprise that the
runs in which the robot misbehaved (2.3-2.4 and 2.7-2.8) lasted longer
(M~=~71~sec, SD~=~16~sec) than the runs in which the robot behaved correctly
(M~=~54~sec, SD~=~16~sec). Overall, for the runs with the correctly behaving
robot, there is a tendency that the average duration of the run decreases over
time ($M_{run1.1}$~=~73~sec, $M_{run2.9}$~=~42~sec). This suggests that children
familiarize themselves with the playful task and the robot and react more
promptly to it.

\paragraph{Interaction}

%\begin{figure}[!h]
%  \centering
%\subfloat[total number (count, \%)]    
%    {\label{fig:domino-action-count}\includegraphics[height=5cm]{domino_actions-pie.pdf}}
%%  \hspace{0.3cm}
%\subfloat[annotation duration, (\%)]    
%    {\label{fig:domino-action-time}\includegraphics[height=5cm]{domino_duration-pie.pdf}}
%
%  \caption[Total Number and Duration of Children's Actions with Ranger]{\small \textbf{Children's actions with Ranger.} (a) shows the total number of the counted actions that were annotated in the videos, (b) shows the total annotation duration percentage of these actions (the total duration of all coded actions are considered as 100\%, not the duration of the scenario).}
%  \label{fig:domino-actions-pie}
%\end{figure}

After having coded children's actions in the video, we obtained 2354 distinct
actions which summed up to a total annotation duration of 145 minutes. On
average, one child accounted for 92 actions (SD=23). The average number of
actions carried out per child was less in the \textit{disobey} condition
(average 75 actions) than in the \textit{lost} (average 98 actions) and
\textit{mistake} (average 102 actions) condition. The overall distribution of
the count of actions and the duration of the total annotation time per action is
shown in Figure~\ref{fig:domino-actions-pie}. We see that even more than in the
previous study, \textbf{children explored the robot} (52~\% of the actions,
making up 76~\% of the total annotation duration). Exploring includes carefully
watching the robot or actively trying to find out how it works. For instance,
one boy (4 years, group \texttt{lost1}) clapped his hands and waved in front of
Ranger's eyes; then he told the experimenter \textit{``No, it cannot hear and it
doesn't see me!''}.\\

Overall, the interactions with the robot were less varied than in the previous
study. We assume this was because the scenario was not as open but fairly well
structured and probably even more constrained (compared to the previous study
which was carried out in children's own rooms).

%	Also, children were asked to remain in the tent and around the beanbag, so
%	they could not freely interact with Ranger, as it was possible in the field
%	study. This constraint is alright because the Domino Study does not openly
%	explore interactions but focuses on children's reaction to the misbehaving
%	robot.

Besides \textit{explore}, children engage mostly in the actions required by the
scenario (Figure~\ref{fig:domino-actions-pie}): \textit{call} (12~\%),
\textit{put} (8~\%) and \textit{remove} (8~\%). Another 8~\% of the actions were
\textit{look} at the experimenter, which suggests that children were seeking for
help or reinforcement sometime. The remaining 12~\% of actions are attributed to
\textit{touch} (5~\%), \textit{talk} (4~\%) and \textit{gesture} (3~\%).

%\begin{figure}[!b] 
%\centering 
%\includegraphics[width=0.99\columnwidth]{domino-time-all.pdf} 
%\caption[Number and Type of Actions for Each Run]{\small \textbf{Number and type of actions for each run} (average for one child per minute). Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9). The first 7 runs correspond to the \textit{expected phase}, the second 7 runs correspond to the \textit{unexpected phase}. Especially during run 2.3, the first time when the robot showed an unexpected behavior, children tended to \textit{look} more at the experimenter. During the unexpected phase, also \textit{talk} and \textit{gesture} seem to be increased. The specific values comparing the expected and unexpected phases overall are presented in Table \ref{tab:domino-conditions}, page~\pageref{tab:domino-conditions}.}
%\label{fig:domino-time-all} 
%\end{figure}

When visualizing the average count of \textbf{actions for each run} (see
Figure~\ref{fig:domino-time-all}), we can see that over time, the total number
of actions does \textit{not} decrease. While interacting with the expected
behaving robot, there is a peak in run 2.1 which may be due to the fact that
children switched roles before that run. During the interaction with the
unexpected behaving robot, there are peaks in runs 2.3, the first run in which
the robot misbehaved, and a small peak in run 2.9, the very last run. This last
peak may be due to the fact that we told children this was the last run, and as
most children did not want to stop playing with the robot. Hence, they tended to
show some extra engagement, by increasing their use of \textit{gestures} and
\textit{talking} to the robot, for instance.

The key question is: how was the interaction impacted by the three
\textbf{different robot misbehaviors}?
Figure~\ref{fig:domino-time-condition-one} shows how the number of actions
evolved from run to run by condition. Overall, children tended to interact
slightly less with the \textit{disobeying} robot (the actions are normalized,
\ie they show an average per child per minute). This difference can be observed
during all the runs (and has also been found concerning children's engagement
with the robot, see next paragraphs). We are not sure how to interpret this. We
have to assume that interaction differences between the groups and further
individual differences between the children are the reason. We come back to
individual differences in the interaction later.

%\begin{figure}[!h] 
%\centering 
%\includegraphics[width=0.9\columnwidth]{domino-actions-perrun.pdf} 
%\caption[Total Number of Actions for Each Run per Condition]{\small \textbf{Total number of actions for each run per condition} (average for one child per minute). Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9). Especially during run 2.3, the first time when the robot showed an unexpected behavior, children interact more with the robot, as well as during run 2.7 when the robot misbehaved again after two correct runs. Another increase of actions is during the very last run.}
%\label{fig:domino-time-condition-one} 
%\end{figure}		
%

When comparing children's interaction with the robot between the
\textit{expected} phase and the \textit{unexpected} phase, the differences
between the conditions and the effect of the robot's misbehavior in general,
become clearer. Table~\ref{tab:domino-conditions} gives an overview. It compares
the number of actions in the expected and unexpected phase for the different
robot behaviors (average per child). The only two actions that were
significantly impacted by the different robot manipulations were
\textit{explore} and \textit{look}. As these two actions are considered to
reflect engagement, we will come back to these differences in the next
paragraphs on engagement with the robot. Overall, the values indicate that
children interacted on average more with the robot in the \textit{lost} and
\textit{mistake} condition. Also, in most cases, the values are higher in the
unexpected phase than in the expected phase. Consequently, children interacted
more during the phase with the misbehaving robot than during the phase when the
robot always behaved correctly. (Statistical tests to compare the effect of the
three different robot behaviors are provided in the following paragraphs,
concerning the \textit{``engagement actions''}, which are subset of all the
interactions.)

\begin{table*}[H]
\captionof{table}[Actions with the Three Robot Misbehaviors in Expected and Unexpected Phase.]{\small \textbf{Comparison of actions with the three robot misbehaviors in the expected and unexpected phase}. This table is based on n~=~2354 counted actions, and shows the average scores per child for the different actions by robot behavior condition. The first line in each double-row shows the values for the expected (exp) phase, in the second line are the values for the unexpected (unexp) phase. For instance, a value of 5.13 for \textit{call} in the expected phase, means that a child called the robot on average 5 times during the expected phase. Italic numbers indicate higher value when comparing the values of the expected and unexpected phase within the condition. Bold numbers indicate highest values when comparing the three different conditions.}
\label{tab:domino-conditions}       % Give a unique label
\centering
\footnotesize
\begin{tabular}{lcccccccccc}
\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
	 & \textbf{call} & \textbf{explore} & \textbf{gesture} & \textbf{look} & \textbf{misuse} & \textbf{put} & \textbf{remove} & \textbf{show} & \textbf{talk} & \textbf{touch} \\ 
	 & exp & exp & exp & exp & exp & exp & exp & exp & exp & exp \\
	 & unexp & unexp & unexp & unexp & unexp & unexp & unexp & unexp & unexp & unexp \\
\noalign{\smallskip}\hline\hline

	\textit{mistake} & \textbf{5.13} & \textbf{26.25} & 0.63 & 3.63 & 0.00 & \textit{\textbf{3.88}} & 3.00 & 0.00 & 0.50 & \textit{\textbf{3.00}} \\
	(n=813) & \textit{6.50} & \textit{\textbf{31.75}} & \textit{\textbf{2.50}} & \textit{4.38} & \textit{0.25} & \textbf{3.50} & \textit{\textbf{3.63}} & \textit{\textbf{0.38}} & \textit{2.25} & \textbf{2.63} \vspace{0.2cm} \\

	\textit{lost} & 3.63 & 25.00 & 0.63 & \textbf{3.88} & 0.00 & 3.50 & \textbf{3.50} & \textit{\textbf{0.50}} & 0.38 & 0.75 \\
	 (n=787) & \textit{\textbf{6.88}} & \textit{31.38} & \textit{1.75} & \textit{\textbf{6.88}} & 0.00 & \textbf{3.50} & 3.50 & 0.00 & \textit{1.75} & \textit{1.00} \vspace{0.2cm} \\

	\textit{disobey} & 5.00 & 12.00 & \textbf{1.30} & 1.20 & \textbf{0.10} & \textit{3.70} & \textit{\textbf{3.50}} & 0.10 & \textbf{2.50} & \textit{2.90} \\
	(n=754) & \textit{6.70} & \textit{19.50} & \textit{1.40} & \textit{2.70} & \textit{\textbf{0.80}} & 3.40 & 3.40 & \textit{0.20} & \textit{\textbf{3.00}} & 2.00 \\

\noalign{\smallskip}\hline
\end{tabular}
\end{table*}

\paragraph{Engagement with the robot}	
\label{sec:domino-engagement}

In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
here. As mentioned before, the findings here do not directly address the issues
of long-term usage but concern short-term \textit{engagement}, which is a
pre-requisite for long-term usage.

The huge proportion of \textit{explore} actions (52~\% of all coded actions)
already suggests that children were generally engaged in the interaction, and
most of the time carefully observed what the robot did. When considering the
actions \textit{explore, gesture, look, misuse, show, talk}, and \textit{touch}
as \textbf{engagement actions}, 1699 of the 2354 actions reflected engagement
(72~\%). This indicates that overall children were very engaged in the
interaction with the robot. Furthermore, data suggests that the robot in the
\textit{mistake} and \textit{lost} condition were more engaging for children
(each 75~\% of the actions reflected engagement) than the robot in the
\textit{disobey} condition (66~\% reflected engagement). The statistical
analysis supports this: An ANOVA indicates that there was a significant effect
of robot behavior on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
indicate that the mean score for \textit{explore} in the \textit{disobey}
condition is significantly different from the score in the \textit{mistake} and
\textit{lost} condition. This suggests that children explored the disobeying
robot less\footnote{It is surprising that the disobeying robot was explored
less. One may assume that the disobeying robot might better attract children's
attention because it faces the searcher child and uses fairly strong audio and
light cues as compared to the other behaviors.} (for the average values, see
Table~\ref{tab:domino-conditions}). For \textit{look}, the only significant
difference is found between the mean scores of \textit{lost} and
\textit{disobey}. Data suggests that when the robot is lost, children look more
often at the experimenter than when the robot disobeys. The other actions were
not found to differ significantly between the robot behavior conditions.

Overall, was there an effect on engagement when the robot misbehaved? We compare
children's engagement during the interaction phase with the expected robot
behavior and during the interaction phase with the unexpectedly behaving robot.
A statistical analysis revealed a significant difference between the average of
engagement actions carried out during the first 7 runs (correct robot behavior)
and during the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1,
p=.03). Figure~\ref{fig:domino-engagement-condition} shows the values for
engagement actions in the three conditions, comparing the expected and
unexpected phase. In all three conditions, children carried out more engagement
actions with the unexpectedly behaving robot. No interaction effect was found
between the two phases of interaction (expected / unexpected) and condition
(F(2,36)=1.2, p=.31). In general, this finding supports our first hypothesis:
children show more engagement toward a robot that behaves unexpectedly from time
to time compared to a robot that always behaves correctly.

It is, however, unclear why children engaged less with the disobeying robot (as
mentioned before), especially also in the \textit{expected} phase (see
Figure~\ref{fig:domino-engagement-condition}). In this phase, the robot did not
disobey but always behaved correctly as in the other two conditions. There were
no robot behavior differences between the conditions. We have to assume that the
effect is due to individual and group variations of children's behavior. These
individual variations would probably be less observable in the data if the
sample size would have been bigger.

%\begin{figure}[!t] 
%\centering 
%\includegraphics[width=0.5\columnwidth]{domino-engagement-condition.pdf} 
%\caption[Engagement Actions in Expected and Unexpected Phase]{\small \textbf{Average number of engagement actions in expected and unexpected phase.} In all three behavior conditions, children engage more in the unexpected phase. In general, the \textit{lost} and \textit{mistake} misbehavior are more engaging than the \textit{disobeying} behavior.} 
%\label{fig:domino-engagement-condition} 
%\end{figure}

Looking into detail, how did engagement change from run to run?
Figure~\ref{fig:domino-time-active} shows the average engagement actions
(without explore) for each run. How can we explain these variations? During the
\textit{first interaction phase} with the \textit{expected behavior}, we observe
small variations. Then, with the first \textit{unexpected robot behavior} in run
2.3, there is a huge peak in the engagement actions, which can again be observed
in run 2.5, slightly in run 2.7, and then again in the last run 2.9. These runs
correspond exactly to when the robot changed its behavior form correct to
incorrect and \textit{vice versa}. It appears that children are quite sensitive
to these variations and spontaneously respond to it. But as mentioned before, we
have to note that the huge peak of engagement actions in the last run may be due
to the fact that children knew this was going to be the last round.

%\begin{figure}[!h] 
%\centering 
%\includegraphics[width=0.99\columnwidth]{domino-time-active.pdf} 
%\caption[Engagement Actions for Each Run]{\small \textbf{Engagement actions for each run} (without explore). Average for one child per minute.}
%\label{fig:domino-time-active} 
%\end{figure}

The picture is unclear, when looking at how engagement evolved from run to run
in the three different conditions (see Appendix
Figure~\ref{fig:domino-time-condition},
page~\pageref{fig:domino-time-condition}). Both within the respective conditions
and when comparing them, there are variations that are difficult to make sense
of and we cannot give a clear interpretation how these variances may be related
to the respective robot misbehavior. We have to assume that the fairly small
sample size of 8-10 children per condition and the huge differences in
children's individual interaction style is the reason for these strange
variations.

Overall, our data suggest that the robot that gets lost and does a mistake
engage in a similar way but that the disobeying robot elicits less engagement.
This was verified by computing an average value for the \textit{engagement
actions}. This average expresses how many engagement actions one child did per
minute. The general engagement action values of the \textit{mistake} (5.66) and
\textit{lost} (5.41) condition are higher than the value of the \textit{disobey}
(3.48) condition. This shows again, that the disobeying robot was less engaging
for the children. A possible interpretation of this result is, that the
disobeying robot frustrated children or was perceived more negatively than the
other two manipulations.

%\begin{figure}[!h]
%  \centering
%\subfloat[disobey3, boy S15]    
%    {\label{fig:domino-diff-group1}\includegraphics[height=4cm]{domino-disobey3_S15.pdf}}
%%  \hspace{0.3cm}
%\subfloat[disobey3, boy S16]    
%    {\label{fig:domino-diff-group2}\includegraphics[height=4cm]{domino-disobey3_S16.pdf}}\\
%%  \hspace{0.3cm}
%\subfloat[mistake1, boy S5]    
%    {\label{fig:domino-same-group1}\includegraphics[height=4cm]{domino-mistake1_S5.pdf}}
%%  \hspace{0.3cm}
%\subfloat[mistake1, boy S6]    
%    {\label{fig:domino-same-group2}\includegraphics[height=4cm]{domino-mistake1_S6.pdf}}    
%    
%  \caption[Individual Differences in Interacting with the Robot]{\small \textbf{Individual differences in interacting with the robot}. The top row with figures a) and b) shows the group \texttt{disobey3} that consisted of two boys. We consider this group as not aligned in their interaction with the robot. While the boy S16 in figure b) talks a lot the robot and also touches it frequently and uses gestures during the first runs, the other boy S15 in figure a) does not do so at all. The bottom row with figures c) and d) shows the group \texttt{mistake1} that also consisted of two boys. We consider this group as fairly aligned in their interaction with the robot. Both children tend to touch the robot and look at the experimenter.}
%  \label{fig:domino-individual-differences}
%\end{figure}

\paragraph{Individual differences}

In fact, we visualized engagement actions for each child (see examples in
Figure~\ref{fig:domino-individual-differences}), and found very different
interaction styles between them, both on a pair and on an individual level. In a
few groups, children were ``aligned'' (homogeneous) in their behavior. For
instance, if one child started to talk to the robot, the other child would do
the same. Mimicking or mirroring the behavior of others is common among young
children. We consider a group as aligned when they engaged with the robot in a
similar way. This was the case in some of the groups. In some other groups,
there were differences between the two children, for instance one child hardly
showed engagement actions while the other one was more engaged. Or there was one
child who dominated the interaction while the other may have had a more
introvert personality.

With a small sample size, individual differences have a quite strong impact in
the data-set and it makes statements about the influence of the robot behavior
as a variable difficult. For instance, we found more \textit{misuse} behavior in
the \textit{disobeying} condition (Figure~\ref{fig:domino-time-disobey-active},
page~\pageref{fig:domino-time-disobey-active}) than in the other conditions. One
may assume that this is due to the robot's strong disobeying behavior. However,
there were two boys who had a rough interaction style and reacted almost
aggressively toward the disobeying robot. No other children showed this strong
reaction.

We did not find a statistically significant effect of gender on any of the
actions. There are however some \textbf{qualitative gender differences} that are
noteworthy. Boys generally seemed to interact more with the robot: they
\textit{explored} it more (M=52.0, SD=16.0) than girls did (M=38.7, SD=17.8);
boys \textit{talked} more (M=5.19, SD=9.0) to the robot than girls (M=1.0,
SD=2.2); they \textit{called} the robot more often (M=12.75, SD=5.9) than girls
(M=8.8, SD=5.9), used more \textit{gestures} toward the robot (M=3.6, SD=4.5)
than girls (M=1.4, SD=2.0) and boys were they only ones who showed some few
\textit{misuse} actions. Contrary, girls more often touched the robot (M=5.2,
SD=6.0) than boys did (M=3.6, SD=3.5), and slightly more often looked to the
experimenter (M=7.8, SD=7.4) than boys (M=6.8, SD=4.1). Interestingly, we had
found similar but also non-significant gender differences in the Ranger Study
(Chapter~\ref{chap:Ranger-fieldstudy}): boys had used more gestures toward the
robot, while girls had more often touched the robot. Despite the fact that in
both cases the differences are not significant, we can interpret that boys and
girls interact differently with Ranger.

\paragraph{Summary}

It is not easy to draw a clear conclusion about children's interaction with the
robot, especially not when comparing the three different conditions. There were
huge variations in the data, due to children's different interaction styles and
their individuality. Overall, the analysis showed that children were generally
engaged in the interaction with Ranger. Most of the time, they explored the
robot, by watching it carefully or trying to find out how it works, for
instance. During the course of the experiment, the amount of actions did not
decrease (over the whole experiment) but was sustained by the manipulation of
robot behavior. Children were significantly more engaged in the interaction
phase with the unexpected robot behavior, compared to the phase in which the
robot behaved correctly. The increase of looking at the experimenter in run~2.3
shows that children were surprised when they saw the robot doing something
unexpected. Concerning the different robot misbehaviors, the \textit{mistake}
and \textit{lost} robot behavior appear to be more effective to trigger (and
possibly sustain) interaction than the \textit{disobey} behavior. Children's
high engagement (increased use of gestures and direct speech to the robot) in
the last run of the experiment may reflect their wish to continue playing with
the robot.

\subsection{Perception}

In this section, we analyze how children perceived the robot. This may help
understand why they tended to be less engaged with the disobeying robot. This
section is organized along the different constructs that were assessed in the
interviews with the children. An overview of the questions used during the
interviews is given in Table~\ref{tab:domino-questions},
page~\pageref{tab:domino-questions}.

Overall, we gathered more than 1.5~hours of video- and audio-recorded interview
material. The duration of both the first and second interview together varied
between 5-11~min, with an average duration of 7~min~49~sec. The second interview
(M=280~sec, SD=70~sec) usually lasted slightly longer than the first one
(M=189~sec, SD=39~sec).

%\hl{(probably check for gender differences in children's responses)}

\paragraph{Expectations and robot-likeness}

In the pre-interview, some of the children said that they had seen a robot
before. This may be due to the fact that several participants (their parents)
were recruited around the campus of our Institute of Technology. Some children
mentioned they had seen a robot at EPFL's \textit{``robotic festival''}, a
public event at which robots are demonstrated and robotic workshops are
organized. We asked children how they imagine a robot and how a robot could look
like (Figure~\ref{fig:domino-imagine}). 10 children did not respond to this
question which can be explained by the fact that this was the very first
question we asked them and the whole situation was still new to them. However,
from the 16 children who provided an answer, 10 mentioned that for them, a robot
has some human-like properties: it either looks like a human (has a body, arms,
hands, legs, feet, or a head) or it can walk, grasp, search for things, or even
set the table. 5 of the children had no clear concept of what a robot is.

%\begin{figure}[!h]
%  \centering
%	\subfloat[]    
%    {\label{fig:domino-imagine}\includegraphics[width=4.75cm]{domino-imagine.pdf}}
%%    \hspace{0.2cm}
%	\subfloat[]    
%    {\label{fig:domino-robot}\includegraphics[width=4.75cm]{domino-robot.pdf}}
%%	\hspace{0.2cm}
%	\subfloat[]	
%	{\label{fig:domino-ranger-how}\includegraphics[width=4.75cm]{domino-ranger-how.pdf}}
%  \caption[Expectations and Robot-likeness or Ranger]{\small \textbf{Expectations of robots in general and robot-likeness of Ranger.} When children had to justify why they thought Ranger is a robot (c), multiple answers were possible, we received 21 answers from 12 children.} 
%  \label{fig:domino-expectations}
%\end{figure}

\paragraph{First impression of Ranger}

Asked whether Ranger was a robot (see Figure~\ref{fig:domino-robot}), children
were not sure how to reply, and some hesitated or did not provide an answer at
all. In general, it was not easy for children to decide whether Ranger was a
robot or not because only a few of them had a clear concept of a robot in mind.
9 children did not give an answer at all. Some children mentioned they had had
different expectations (those who had a human-like image of a robot). From those
who replied, 5 children did not find that Ranger is a robot because it has no
arms or legs and because its eyes are not real. However the majority of the
respondents (12 of 17) was convinced of the opposite, namely that Ranger is a
robot. According to them (see Figure~\ref{fig:domino-ranger-how}) Ranger is a
robot because it is able to move by itself, it has eyes, it is able to transport
things, and because it has feelings (expressed by the light and sound cues).

\paragraph{Manipulation check}

Before going into details about differences in the perception of the robot due
to the different misbehaviors, we need to check whether children noticed the
manipulations of the robot behavior, and how they interpreted them. Did they
perceive and classify the different misbehaviors, \textit{mistake, lost} and
\textit{disobey}, as we intended?  As stated in the beginning of the chapter, we
had hypothesized that the \textit{disobey} behavior is perceived as the robot
intentionally not doing what it should do. The \textit{mistake} behavior was
intended to show that the robot can do a mistake but is aware of it and able to
repair its mistake, which should also lead to some perception of intentionality.
Contrary, we expected that the \textit{lost} condition is perceived as a
malfunction or bug of the robot.  In the second interview, after the robot had
misbehaved, we asked children whether the robot always did what they wanted it
to do. Most children disagreed and said they noticed something strange. However,
there were some children who gave a positive answer, suggesting that they found
the robot always did what they wanted it to do. This was a surprise. Had they
not noticed the robot's misbehavior? Why not? On one hand, we found that
children sometimes gave contradictory replies when asked the same question
twice. This is difficult to interpret. On the other hand, children may have a
general tendency to please adults \cite{leite_long-term_2013}, and it could be
the case that some were too shy to tell us that the robot did something strange.

%\begin{figure}[!h]
%\centering
%  \includegraphics[height=6cm]{domino-why-misbehavior.pdf}   
%\caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible to the question why the robot did not come over, and we received 37 answers. This question shows that children did not necessarily interpret the misbehavior in the way we had assumed.}
%  \label{fig:domino-why-misbehavior}
%\end{figure}

We nevertheless asked children why they thought the robot had not always come
over to them. 4 of the children did not reply. The remaining ones gave a variety
of reasons (Figure~\ref{fig:domino-why-misbehavior}). The most common answer (9
of 37 replies) was that the robot is somehow \textit{unpredictable} in what it
is doing and that it could go \textit{no matter where}\footnote{We translated
children's answers from French to English. For some expressions the meaning and
connotation of an expression may not be the same. We understand \textit{``partir
dans tous les senses''} as ``to go off in all possible directions'' and hence
interpret this reflects viewing the robot as being unpredictable.} because
\textit{``with robots you have these kind of problems, they do no matter what''}
(boy (5), \texttt{lost4}). 8 replies concerned \textit{technical problems}
(including \textit{broken parts}), suggesting that children perceived the
misbehavior as unintended by the robot. 2 of the children who had interacted
with the disobeying robot said Ranger was \textit{angry}, which none of the
children in other conditions replied (these were not the two boys who reacted
aggressively). Several children ascribed intentionality to Ranger explaining
that it \textit{did not want to continue} carrying domino tiles or that it
\textit{made a mistake / did something silly}\footnote{We understood
\textit{``faire une bêtise''} as ``to do a silly thing'' in the sense of making
a mistake.}.

%\hl{(put some more quotes of the children, maybe even in French)}

Overall, we can notice that not all children perceived the misbehavior of the
robot as we had intended and we have to keep this in mind while interpreting the
data. Also \cite{leite_long-term_2013} found in her study that when children did
not understand an action of the robot, they tended to view it as a mistake,
rather than interpreting the robot's behavior as a deliberative action.

%	\textit{``the supportive behavior ``Play Bad Move'' was not completely
%	understood as a deliberative action of the robot, but rather as a
%	mistake''}.

In our case, it is not easy to make a clear statement about how each of the
manipulations was perceived by the children.  Similar to how people reacted to
the cheating robot in the study of \cite{short_no_2010}, most children showed
surprise, were amused, sometimes confused, or occasionally slightly angry (\eg
two boys tended to shout to the robot after it had disobeyed). The
\textit{disobeying} robot seemed to evoke the strongest reactions, partly with a
negative implication: later three of the children in this condition stated they
would not accept Ranger as a friend \textit{because it did not always come over
when they asked it to come over}. \cite{short_no_2010} described a similar
implication of the robot cheating behavior: participants made unfavorable
character attributions to the cheating robot, so the robot's actions affected
perceptions of the robot as ``fair'' and ``honest''.

%	\cite{short_no_2010} found that participants often had an emotional reaction
%	to the robot's behavior and made unfavorable character attributions to the
%	cheating robot. The robot's actions affected perceptions of the robot as
%	``fair'' and ``honest''. Qualitatively, the authors found that participants'
%	reactions in the verbal cheat case tended more towards confusion, while
%	their reactions to the action cheat were more exaggerated, showing surprise,
%	amusement, and occasionally anger.

%	\cite{short_no_2010} found that participants who saw the action cheat
%	mentioned cheating, while the participants who saw the verbal cheat
%	frequently described it as a mistake or malfunction, while only sometimes
%	calling it cheating.

%\begin{figure}[!h]
%\centering
%  \subfloat[]
%  {\label{fig:domino-hear}
%  \includegraphics[height=5.5cm]{domino-hear.pdf}}
%  \subfloat[]
%  {\label{fig:domino-see}
%  \includegraphics[height=5.5cm]{domino-see.pdf}}   
%\caption[Attribution of Cognitive Skills to Ranger]{\small \textbf{Attribution of cognitive skills to Ranger.} These two questions were asked both in the first interview, after children had interacted with the correctly behaving robot, and in the second interview, after children had interacted with the unexpectedly behaving robot (three conditions). A comparison of the answers (first-second) can reveal to what extent the respective misbehavior of the robot impacted children's attribution of cognitive abilities. (Note that there were 10 participants in the disobey condition and each 8 participants in the mistake and lost condition. Consequently, here and in the following visualizations, we need to be careful as the bars are based on counting answers.) The three bars on the right side of each diagram are a split-up of the \textit{``all''} bar of the second time children were asked.}
%  \label{fig:domino-cognition}
%\end{figure}

\paragraph{Attributions of cognitive abilities (perceptual skills)}

To assess how far children ascribed low-level cognitive abilities to the robot,
we asked them whether they believed Ranger is able to hear and see
(Figure~\ref{fig:domino-cognition}). Also these questions were asked both in the
first and the second interview. First, the majority of children replied
positively, saying that Ranger can hear (15) and can see (19). We asked them to
justify their answer in both cases (\textit{``How do you know?''}). Those
ascribing cognitive abilities answered, for instance: \textit{``It can see
because it is looking right at me.''} (girl (4), \texttt{disobey4}) or
\textit{``The only thing it can hear is when you say `come here'.''} (boy (5),
\texttt{mistake2}). Those who answered negatively added, for instance:
\textit{``It cannot see because the eyes are not real.''} (girl (4.5),
\texttt{disobey1}); \textit{``It cannot hear because it doesn't have ears.''}
(boy (4), \texttt{mistake4}); and surprisingly two 4-year old children mentioned
that Ranger is not able to hear because it does not have a \textit{mouth}. It
seems that for some younger children the concepts of speaking and hearing are
both related to a mouth. From those two questions, we can summarize that after
children had interacted with the \textbf{correctly behaving robot} the majority
does \textbf{ascribe cognitive abilities} to the robot.\\

After they had interacted with the misbehaving robot, some children responded
differently. Now 11 children (first 15) answered Ranger can hear, and 15
children (first 19) responded it can see. 2 children in the \textit{mistake}
condition consistently changed their opinion for both hearing and seeing
abilities. The other changes were not consistent for both senses and partly even
contradicting. There was no clear tendency, and also we cannot say whether the
different conditions had a different impact. We can note that also to the
\textbf{unexpectedly behaving robot} children tend to \textbf{ascribe cognitive
abilities} but slightly less than before. It seems that initially the
attribution of cognitive abilities is due to the robot's physical design (\eg
eyes) and that the manipulation of the robot's behavior does not substantially
change this perception (only for few children).

%\begin{figure}[h]
%\centering
%  \subfloat[]
%  {\label{fig:domino-obey}
%  \includegraphics[height=5.8cm]{domino-obey.pdf}}
%  \subfloat[]
%  {\label{fig:domino-silly}
%  \includegraphics[height=5.8cm]{domino-silly.pdf}}   
%\caption[Attribution of Intention to Ranger]{\small \textbf{Attribution of intention to Ranger.} Similar as before, children were asked these questions twice. Concerning question (a), there are no remarkable differences in children's responses given in the \textit{first} and \textit{second} interview. Children tend to think Ranger does always obey to them, even after it misbehaved (\textit{second} part). There is however a small difference in the responses visualized in graph (b). After the robot misbehaved, 8 children think the robot could do something silly whereas first, only 3 children answered like this.}
%  \label{fig:domino-intention}
%\end{figure}

\paragraph{Attributions of intention}

One of the central points of this study was to investigate to what degree
children attribute intention and cognitive abilities to the robot.  In the first
interview after children had interacted with the correctly behaving robot we
asked three questions to assess how far they ascribe \textbf{intention} to it
(see questionnaire items in Table~\ref{tab:domino-questions},
page~\pageref{tab:domino-questions}). One of these questions was whether they
believed Ranger could go out the door by itself. They majority of 16 children
answered negatively, which suggests that they initially do not ascribe intention
to the robot. The two other questions were whether Ranger would always obey and
whether Ranger could do a silly thing (Figure~\ref{fig:domino-intention}). These
two questions were asked again later after children had interacted with the
unexpectedly behaving robot.

%	With these recurring questions we wanted to see whether children had changed
%	their mind in terms of ascribing intention to Ranger (and whether the
%	unexpected robot behavior had caused this effect). This comparison turned
%	out to be difficult, however.

Overall, in the first interview 12 of the 26 children believed Ranger does
always obey to them. Asked whether Ranger could do something silly, the great
majority of 21 children replied negatively. We can summarize that after children
had interacted with the \textbf{correctly behaving robot} the majority does
\textbf{not ascribe intention} to the robot.

After they had interacted with the misbehaving robot, we asked children again.
Now, still 11 children (previously 12) believed Ranger would always obey to
them. When analyzing the answers of each child separately, there were 2 children
in the \textit{disobey} condition that changed their answer from \textit{yes} to
\textit{no}; however also 1 child in the \textit{lost} condition that switched
their answer in the opposite way (strangely). There was a more remarkable change
when asking children whether Ranger could do something silly. In the second
interview, 8 children (previously~3) answered Ranger could do something silly. 1
child in the \textit{disobey} condition had changed their answer, and each 2 in
the \textit{mistake} and \textit{lost} condition.

Overall, it it interesting to note that children tend to ascribe cognitive
abilities to the robot, like the ability to see and hear but not intention. We
interpret that children may perceive the robot as being able to process sensory
information but that it is not able to make decisions on its own. We can
summarize that even with the \textbf{unexpectedly behaving robot} children do
\textbf{not necessarily ascribe intention} to the robot. The unexpected robot
behavior impacted only some children's attributions of intention to the robot.
It seemed that some children did not interpret the robot's misbehavior as
intentional but more like a technical problem or mistake. For instance, even
after the robot misbehaved by \textit{disobeying}, the majority of the children
in this condition was still convinced that the robot could not do a silly thing
(Figure~\ref{fig:domino-silly}).

\paragraph{Attributions of emotional state and perceived companionship}

We examined whether children attributed \textbf{feelings} to the robot by asking
them (once at the end of the experiment) if they thought that Ranger can feel
happy or sad sometimes (Figure~\ref{fig:domino-feelings}). The great majority of
children (21 of 26) gave a positive answer. Only 2 children who had interacted
with the \textit{disobeying} robot did not believe that Ranger has feelings and
another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
all. Overall, data suggests that \textbf{children attributed emotional states}
to the robot. Asked for more details, several children answered that it is
through its colors and sounds that the robot shows a feeling. Most children said
that they could make the robot feel happy by playing with it and putting a
domino tile inside the box. This may also be a reflection of their own feelings,
projected on the robot.  More than half of the children (14 of 26) agreed Ranger
can be their friend. We did not ask about what being a friend means to them but
as children generally liked playing with the robot, this may be linked to each
other. We can note that children \textbf{ascribe feelings to the robot and
partly accept that it can be a ``friend''}.

%\begin{figure}[!h]
%\centering
% \subfloat[]
%  {\label{fig:domino-feelings}
%  \includegraphics[height=5cm]{domino-feelings.pdf}}
% \subfloat[]
%  {\label{fig:domino-friend}
%  \includegraphics[height=5cm]{domino-friend.pdf}}
%\caption[Attribution of Emotional State and Perceived Companionship]{\small \textbf{Attributions of emotional state and perceived companionship}.}
%  \label{fig:domino-feelings-companion}
%\end{figure}

\paragraph{Attributions of moral standing}

Inspired from the questionnaire used by \cite{kahn_jr._robotic_2006}, we asked
children if it would be alright to leave Ranger alone at home (\eg during two
weeks when they go on a vacation) (Figure~\ref{fig:domino-leave}). The great
majority of 20 children responded negatively. Asked why, children gave a variety
of answers that we classified into 7 categories
(Figure~\ref{fig:domino-leave-why}). With 5 replies, the most common answer was
that the robot ``could do something silly''. Some other children simply answered
they would like to take it with them. Others were afraid that the Ranger ``would
not find its way'' or ``may be taken away by someone''. 2 children believed
Ranger is sad when left alone and 1 child responded the robot would try to
escape. This shows that some children really ascribed emotions or an ``own
will'' to the robot.  We can summarize that children generally \textbf{ascribe
moral standing to the robot}, meaning that it is an entity that deserves some
kind of respect and care.

%\begin{figure}[!h] \centering \subfloat[] {\label{fig:domino-leave}
%\includegraphics[height=5cm]{domino-leave.pdf}} \subfloat[]
%{\label{fig:domino-leave-why}
%\includegraphics[height=5cm]{domino-leave-why.pdf}} \caption[Attribution of
%Moral Standing]{\small \textbf{Attributions of moral standing}. We asked
%children whether it was alright to leave Ranger alone at home if they go on a
%2-week vacation (a). Multiple answers (open-ended) were allowed when asked to
%justify their answer (b).} \label{fig:domino-leave-alone} \end{figure}

\paragraph{Acceptance of Ranger}

It does not come as a surprise that children showed great fascination for the
robot and the domino game (we cannot clearly separate these two things). Only
those children whose expectations of the robot were not met, seemed to be
skeptical. Asked if they like Ranger, 16 children gave a positive reply and
there was no negative response, however 10 children did not answer this
question. Also, 18 of the children answered they would like to have Ranger at
home. Still 5 children gave a negative reply and 3 did not provide an answer at
all.

%\begin{figure}[!h]
%\centering
% \subfloat[]
%  {\label{fig:domino-like}
%  \includegraphics[height=5cm]{domino-like.pdf}}
% \subfloat[]
%  {\label{fig:domino-leave-athome}
%  \includegraphics[height=5cm]{domino-athome.pdf}}
%\caption[Acceptance of Ranger]{\small \textbf{Acceptance of Ranger}.}
%  \label{fig:domino-acceptance}
%\end{figure}

\paragraph{Summary}

In general, children tended to associate a robot with some human-like design and
characteristics, and they were hence not sure whether Ranger counts as a robot.
According to the children, Ranger's ability to move and its moving eyes however
suggest it is a robot.

Their perception of Ranger shows that they commonly ascribed some human-like
characteristics to the robot, such as emotional states or cognitive abilities,
and that they also tend to view it as a social entity (\eg by ascribing moral
standing, and accepting it as a friend). But children do not necessarily ascribe
intention and own reasoning to the robot. This suggests that anthropomorphism is
not something discrete being either \textit{there} or \textit{not there}; it may
rather exist in several variations or levels. (We explore social engagement and
anthropomorphism in more detail in the next section and come back to it in the
Conclusions Chapter of this thesis.)

Concerning the manipulation of the robot behavior, most (but not all) children
recognized something strange and agreed that the robot did \textit{``no matter
what''}. The different types of misbehavior were not clearly interpreted as we
had intended. The robot's behavior was mostly perceived as
\textit{``unpredictable''}. Qualitatively, it seemed that the
\textit{disobeying} robot had a stronger impact on children's perception of the
robot than the other two behaviors \textit{mistake} and \textit{lost}.
Generally, children like Ranger and most said that they would like to play with
it at home.\\

%Also \cite{leite_long-term_2013} reported that when the iCat (the robot used in
%the study) said something that children were not expecting, the most salient
%affective expression was surprise.  6 out of the 16 children who took part in
%the study talked to the robot from the first until the last week of
%interaction. The most frequent words that children said to the robot were
%``thank you''. (we also observed this in the Domino Study)

\subsection{Anthropomorphism Index and Social Engagement with Ranger}

The anthropomorphism index expresses to what extent children engaged with Ranger
in a human-like way, both in terms of their behavior toward the robot and their
perception of the robot. We mostly present findings on a pair (group) level but
also look at differences between children in one group.

As described in Section \ref{sec:domino-anth-score}
(page~\pageref{sec:domino-anth-score}), the anthropomorphism index considers on
one hand whether children behaved toward the robot in a human-like way. The
behavioral aspects refer to a qualitative analysis of the interaction, and not
to the counts of actions annotated in the video material. These qualitative
aspects included use of direct speech toward the robot, use of social pointing
gestures (\eg waving or nodding), and use of polite formulations. For instance,
several children said \textit{``thank you''} when Ranger brought a domino tile
to them or used a polite formulation when calling Ranger: \textit{``Robot,
please come over!''}\footnote{These forms of politeness that children use when
talking to a robot have also been observed by \cite{leite_long-term_2013}.}. If
a child was using such formulations, he or she was assigned 1 point, and at the
end, the sum of these points formed the anthropomorphism index. On the other
hand, the anthropomorphism index considers to what degree children perceive the
robot as human-like. These results have been mostly presented in the previous
section (\eg attribution of feelings to the robot).

To obtain the anthropomorphism index for a pair, we first calculated the index
per child and then took the average of the two children in one group.  The group
indexes varied between 3.25 and 10.75 points with an average of 7.5 points
(SD~=~2.5), which is 47~\% of the maximum possible index of 16 points. Similar
to the individually different interaction styles of the children, there were
also variations in terms of to what extent they anthropmorphized Ranger. In 7 of
the 13 groups, the anthropomorphism indexes for both children were similar
(difference less than 1.5 points), which means that both children
anthropomorphized the robot to a similar degree. This agreement among children
happened for both higher and lower indexes. In 6 of the 13 groups, the
anthropomorphism indexes varied in more than 2 points, which means that one of
the children anthropomorphized the robot more than the other one. This is an
interesting finding.

On an overall average, Ranger was moderately anthropomorphized by the
children.\footnote{However, as our developed anthropomorphism score is relative,
we cannot really make a claim about what a difference of \textit{+} or \textit{-
1} point means.} 8 of the 13 groups had an index of 8 or higher.
Table~\ref{tab:domino-anth-score} shows that of those groups, 3 were in the
\textit{mistake} condition, 3 in the \textit{lost} condition and 2 in the
\textit{disobey} condition. Also, the mean index of anthropomorphism in the
three conditions varied, with the \textit{mistake} and \textit{lost} condition
leading to a higher index than the \textit{disobey} condition.	This finding
suggests that the disobeying robot was less anthropomorphized than the other two
robot behaviors, which speaks against our second hypothesis. We had expected
that the disobeying behavior is perceived as an intentional action which we
assumed would lead to increased anthropomorphism. This was not the case. The
slight difference between the \textit{lost} and \textit{mistake} robot was also
expected in the opposite direction. It could be that the robot's
``helplessness'' led to this. With the lost robot, children looked more often at
the experimenter than in the other condition (see
Table~\ref{tab:domino-conditions}, page~\pageref{tab:domino-conditions}), which
suggests that they could not fully make sense of the robot's behavior. The fact
of not being able to understand (and hence predict) a robot's behavior is likely
to increase anthropomorphism.\footnote{One of the cognitive / psychological
explanations for anthropomorphism is that people want to make sense of something
they do not understand and then tend to anthropomorphize this something (human
traits are a good source of making attributions because this is what people
understand best -- themselves and other humans). For more details the reader may
refer to \cite{epley_seeing_2007}.}

\begin{table}[ht!]
\label{tab:domino-anth-score}       % Give a unique label
\centering
\footnotesize
\begin{tabular}{lccc}
\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
	& \multirow{2}{*}{M} & \multirow{2}{*}{SD} & count of groups with \\ 
	& & & with index above 8 \\
\noalign{\smallskip}\hline\hline
	\textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
	\textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
	\textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
\noalign{\smallskip}\hline
\end{tabular}
\caption{\textbf{Anthropomorphism index.} The maximum possible index was 16. The \textit{lost} robot elicits the highest index, which suggests that it is anthropomorphized more. Contrary to our hypothesis, data suggests that the \textit{disobeying} robot is anthropomorphized less but the \textit{lost} robot more.}
\end{table}

But to what extent is the human-like interaction related to perceiving the robot
as human-like? Do children who interact a lot and are probably more engaged with
the robot also perceive the robot as more human-like? This was what we
hypothesized. Data suggests the opposite, however. As shown in
Figure~\ref{fig:domino-anthropo-interaction}, we found a significant
\textit{negative} correlation between the count of engagement actions (per
group) and the qualitative anthropomorphism index (r(11)=-0.56, p=.05).

%	(b=-.05, t(11)=-2.22, p=.048).

The overall model with the count of engagement actions (per group) predicts a
significant proportion of the qualitative anthropomorphism index (adjusted
R$^2$=.25, F(1,11)=4.9, p=.05). This means that the more a group showed
engagement in the interaction, the less they anthropomorphized the robot. This
is a key results, which was against our initial assumption. How can we interpret
this? It may be that children who interact more with the robot understand better
how it works, they are more familiar with it, and as such the robot appears less
``mystical'' to them, so there is not a big need to anthropomorphize it. On the
contrary, the cluster of groups that do not interact much but anthropomorphize
the robot more, is quite homogeneous. The negative correlation between the
number of engagement actions and the anthropomorphism index suggests that
children who interact more with the robot tend to anthropomorphize it less. This
implies that anthropomorphism could fade out after some time (or rather after
some interaction). This evokes the question how far anthropomorphism (as a
special kind of social engagement) really helps in sustaining interaction. This
is a critical point because most of the short-term investigations suggest that
anthropomorphic design and human social cues emitted by a robot foster
engagement and acceptance. What if this is not true for continued interaction,
and thus for the long-term?  We have to be careful about our interpretation, due
to the small sample size with which we obtained these findings. We suggest to
investigate the aspect further in future research.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\columnwidth]{domino-correlation.pdf}

    \caption[Correlation of Anthropomorphic Perception of the Robot and
    Interaction]{\small \textbf{Correlation of anthropomorphic perception of the
    robot and engagement actions.} A scatter plot of the count of engagement
    actions (without explore) and the \textit{anthropomorphic perception} (score per
    group) shows a negative correlation. The score for the anthropomorphic
    perception (\textit{y-axis}) does not take into account the behavioral aspect of
    the anthropomorphism index, as this is part of the interaction
    (\textit{x-axis}).  There seem to be two clusters of groups: those who interact
    more with the robot and anthropomorphize it less, and those who interact less
    but anthropomorphize the robot more.}

    \label{fig:domino-anthropo-interaction}
\end{figure}

Our data on the anthropomorphism index also suggest \textbf{qualitative gender
differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
SD=2.4). (Interestingly, as it was mentioned before, boys interacted slightly
more with the robot than girls; though not significantly. This is
counter-intuitive concerning the negative correlation between amount of
interaction with the robot and anthropomorphism tendency.) It would be
interesting to investigate in more detail whether boys are more prone to
anthropomophize a robot than girls.\footnote{Findings presented in
\cite{schermerhorn_robot_2008} suggested similar gender differences. In their
study, males tended to think of the robot as more human-like and accordingly
showed more ``social facilitation'' than females, who perceived the robot as
more machine-like.}

%	\hl{(is this consistent with previous work?)}

\paragraph{Summary}

The established \textit{anthropomorphism index} suggests that children tend to
conditionally anthropomorphize the robot. Higher indexes of anthropomorphism
were found in the \textit{lost} and \textit{mistake} condition which was against
our hypothesis. Interestingly, data suggests a significant negative correlation
of engagement and anthropomorphism index. It appears that groups who interacted
more with the robot perceived it as less-humanlike. This raises the question to
what extent anthropomorphic perceptions of a robot can last over time, and with
increasing interaction experience.

\section{Discussion}

\subsection{Engagement and Anthropomorphism}

\section{Conclusions}

We found that in a playful scenario where 4-5 year old children play domino
together with a robot, the robot seems to be more engaging when it shows some
misbehavior compared to when it always behaves as expected.\footnote{However, we
cannot say if this effect holds also after novelty has worn off.} Different
types of misbehavior appear to have a different effect on children's interaction
and their perception of human-likeness in the robot. A \textit{disobeying} robot
may be perceived more negatively than a robot that makes a \textit{mistake} or
gets \textit{lost}. This may lead to attributions of negative personality to the
robot and children may be less motivated to continue interacting. Such effect
would be against our idea to promote long-term engagement. A similar conclusion
was drawn by \cite{short_no_2010}, in their study of a cheating robot:
Participants sympathized with a robot that \textit{verbally} cheated but they
behaved punitively towards a robot that cheated \textit{in its actions}.  Thus,
the effect depends on the type of misbehavior that the robot shows. With some
``lighter'' misbehavior, children may show helping-behavior and increase their
engagement, whereas using some ``stronger'' misbehavior, may lead children to
see the robot as being unpredictable and they could lose trust in it.

In general, any difference in robot behavior may have a strong effect on
children's perception of the robot, and can powerfully shape how they relate to
it: \textit{``The attribution of mental state to a robotic partner has dramatic
consequences for the relationship between robot and human. A friend has mental
state, a vacuum cleaner does not''} \cite[p.~225]{short_no_2010}.  From what we
have seen in the Domino Study, we have a rough estimate of how children react
and relate to a robot that behaves unexpectedly from time to time. They are
mostly surprised, laugh at the robot, and they tend to be more engaged and
playful. However, they are also confused and cannot really make sense of the
robot's strange behavior. We also cannot clearly say whether children perceived
the unexpected robot behavior entirely as a malfunction (something that happens
to a machine) or as being intended and based on a motivation (something related
to a social entity). Children stated both, when asked why the robot had
misbehaved. Some referred to \textit{``a technical problem''} while others said
the robot \textit{``is tired''} or it \textit{``doesn't want to carry domino
tiles any more but rather go on a tour outside''}. Maybe our manipulations were
not as clearly designed as we expected. There is always some freedom in how
things are interpreted -- especially with young children.  Certainly more work
needs to be done to investigate which robot behavior is most beneficial for
young children and can promote their engagement and motivation to interact with
Ranger over extended periods of time.

%	Whereas a cheating opponent is acting out of a desire to win the game, a
%	malfunction, on the other hand, is entirely accidental, and could be the
%	fault of physical design or faulty programming, and can even occur entirely
%	without involvement on the part of the robot. \textit{``A malfunction is
%	something that happens to a machine, while a social entity that can cheat
%	has motivations and desires.'' Short et al.}

\subsection{Limitations}

This study and the results have several limitations.  First, we did not have a
real control group in which the robot always behaved correctly. Instead, we took
the first interaction phase as a reference for how children interact with the
correctly behaving robot.  Also, the sample size of 13 groups was small. There
were  variations in the data due to the individual differences of children. More
data could have allowed for a better comparison between the conditions.  With
the manipulation of the robot behavior we were able to surprise children.
However, it is questionable how often the same type of behavior manipulation
leads to surprise. Moreover, our experiment was a short-term interaction study
while we try to make statements about how to sustain long-term engagement. This
is critical but not unusual. Long-term HRI studies with young children are
extremely rare as they are difficult to set up as well as time and resource
consuming \cite{leite_long-term_2013}. Nevertheless, we could have probably
improved our study by setting up several short interaction sessions spreading
over several weeks. At the end of each session we could have asked whether
children want to play again with the robot. Such a study could have helped to
investigate the long-term interaction with the robot and the impact of the
behavioral variances.

\subsection{Lessons Learned}

One of the lessons learned is that it is difficult to set up a controlled lab
study with young children. Children are not like adults who patiently
participate in a 45-minutes experiment and then get some reward in the end. On
one hand, an experiment with children should not be boring for them, but on the
other hand, you would like to seriously collect some data. A lot of the
challenges we experienced are also described in \cite{ros_child-robot_2011}. One
of the most difficult parts turned out to be the interviews with the children.
We need to be careful to not over interpret some of their answers. Some children
seem to not have a clear opinion and partly contradict themselves. These answers
are not easy to interpret. An interview script including the questions need to
be designed very carefully, and should definitely be tested beforehand with the
respective age group.

Overall, it appears that when trying to study something in more detail, such as
the manipulation of robot behavior, 4-5 year old children may be too young. But
when trying to evaluate a more general approach, the design of a prototype, or
an interaction scenario, children are a very good choice. They say things as
they are and react very naturally, when compared to adults, who may reply more
socially desired.

\paragraph{Summary}

In this study, we investigated the effect of unexpected robot behavior on
children's engagement in interacting with Ranger and on their perception of the
robot.  Our first hypothesis finds support: children show more engagement toward
a robot that behaves unexpectedly from time to time. Further, different types of
unexpected behavior may have a different effect, and therefore the behavior
manipulation needs to be designed with care.
We did not find support for our second hypothesis which stated that children
perceive a robot showing intention or cognitive abilities as more human-like
than a robot that appears to have a system error. This may be due to the study
setup and the fact that children did not interpret the robot misbehavior in the
conceived way. Our findings seem to suggest the contrary to our hypothesis. A
robot that appeared to do a \textit{mistake} or to be \textit{lost} was more
anthropomorphized than a robot that \textit{disobeyed}. But again, as children
may have misinterpreted these robot behaviors we cannot be sure about this
result.

Another outcome of this study is the initial development and first tryout of an
\textbf{anthropomorphism index}. This index considers both behavioral and
perception aspects and is able to indicate lower and higher levels of
anthropomorphism along this continuous index. At the moment, there is no such
index available that quantifies anthropomorphism along a scale and there is no
technique that combines behavior and perception. We may raise a discussion about
this in Chapter~\ref{chap:conclusion}.  In the future, we will need to refine
and improve this scale. For instance, we need to identify the specific factors
that should be included as measurement points in such a scale, for both aspects
(behavior and perception). Also, we need to think about how to balance the two
aspects appropriately. Probably, also characteristics of the person, the robot,
and the situation need to be considered.

\nocite{johnson_detecting_2003}

\section*{Acknowledgments}

This research was supported by the Swiss National Science Foundation through the
National Centre of Competence in Research Robotics.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv}
\bibliography{domino}

\balancecolumns

\end{document}

### 2014-09-04 domino-study_hri15.tex
Added all missing figures in Julia's original paper

@@
 
-%\begin{figure}[!h]
-%  \centering
-%\subfloat[total number (count, \%)]    
-%    {\label{fig:domino-action-count}\includegraphics[height=5cm]{domino_actions-pie.pdf}}
-%%  \hspace{0.3cm}
-%\subfloat[annotation duration, (\%)]    
-%    {\label{fig:domino-action-time}\includegraphics[height=5cm]{domino_duration-pie.pdf}}
-%
-%  \caption[Total Number and Duration of Children's Actions with Ranger]{\small \textbf{Children's actions with Ranger.} (a) shows the total number of the counted actions that were annotated in the videos, (b) shows the total annotation duration percentage of these actions (the total duration of all coded actions are considered as 100\%, not the duration of the scenario).}
-%  \label{fig:domino-actions-pie}
-%\end{figure}
+\begin{figure}[!h]
+  \centering
+\subfloat[total number (count, \%)]    
+    {\label{fig:domino-action-count}\includegraphics[height=5cm]{domino_actions-pie.pdf}}
+%  \hspace{0.3cm}
+\subfloat[annotation duration, (\%)]    
+    {\label{fig:domino-action-time}\includegraphics[height=5cm]{domino_duration-pie.pdf}}
+
+  \caption[Total Number and Duration of Children's Actions with Ranger]{\small \textbf{Children's actions with Ranger.} (a) shows the total number of the counted actions that were annotated in the videos, (b) shows the total annotation duration percentage of these actions (the total duration of all coded actions are considered as 100\%, not the duration of the scenario).}
+  \label{fig:domino-actions-pie}
+\end{figure}
 
@@
 
-%\begin{figure}[!b] 
-%\centering 
-%\includegraphics[width=0.99\columnwidth]{domino-time-all.pdf} 
-%\caption[Number and Type of Actions for Each Run]{\small \textbf{Number and type of actions for each run} (average for one child per minute).
+\begin{figure}[!b] 
+\centering 
+\includegraphics[width=0.99\columnwidth]{domino-time-all.pdf} 
+\caption[Number and Type of Actions for Each Run]{\small \textbf{Number and type of actions for each run} (average for one child per minute).
 Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9).
@@
 The specific values comparing the expected and unexpected phases overall are presented in Table \ref{tab:domino-conditions}, page~\pageref{tab:domino-conditions}.}
-%\label{fig:domino-time-all} 
-%\end{figure}
+\label{fig:domino-time-all} 
+\end{figure}
 
@@
 
-%\begin{figure}[!h] 
-%\centering 
-%\includegraphics[width=0.9\columnwidth]{domino-actions-perrun.pdf} 
-%\caption[Total Number of Actions for Each Run per Condition]{\small \textbf{Total number of actions for each run per condition} (average for one child per minute).
+\begin{figure}[!h] 
+\centering 
+\includegraphics[width=0.9\columnwidth]{domino-actions-perrun.pdf} 
+\caption[Total Number of Actions for Each Run per Condition]{\small \textbf{Total number of actions for each run per condition} (average for one child per minute).
 Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9).
@@
 Another increase of actions is during the very last run.}
-%\label{fig:domino-time-condition-one} 
-%\end{figure}		
-%
+\label{fig:domino-time-condition-one} 
+\end{figure}
 
@@
 
-%\begin{figure}[!t] 
-%\centering 
-%\includegraphics[width=0.5\columnwidth]{domino-engagement-condition.pdf} 
-%\caption[Engagement Actions in Expected and Unexpected Phase]{\small \textbf{Average number of engagement actions in expected and unexpected phase.} In all three behavior conditions, children engage more in the unexpected phase.
+\begin{figure}[!t] 
+\centering 
+\includegraphics[width=0.5\columnwidth]{domino-engagement-condition.pdf} 
+\caption[Engagement Actions in Expected and Unexpected Phase]{\small \textbf{Average number of engagement actions in expected and unexpected phase.} In all three behavior conditions, children engage more in the unexpected phase.
 In general, the \textit{lost} and \textit{mistake} misbehavior are more engaging than the \textit{disobeying} behavior.}
-%\label{fig:domino-engagement-condition} 
-%\end{figure}
+\label{fig:domino-engagement-condition} 
+\end{figure}
 
@@
 
-%\begin{figure}[!h] 
-%\centering 
-%\includegraphics[width=0.99\columnwidth]{domino-time-active.pdf} 
-%\caption[Engagement Actions for Each Run]{\small \textbf{Engagement actions for each run} (without explore). Average for one child per minute.}
-%\label{fig:domino-time-active} 
-%\end{figure}
+\begin{figure}[!h] 
+\centering 
+\includegraphics[width=0.99\columnwidth]{domino-time-active.pdf} 
+\caption[Engagement Actions for Each Run]{\small \textbf{Engagement actions for each run} (without explore). Average for one child per minute.}
+\label{fig:domino-time-active} 
+\end{figure}
 
@@
 
-%\begin{figure}[!h]
-%  \centering
-%\subfloat[disobey3, boy S15]    
-%    {\label{fig:domino-diff-group1}\includegraphics[height=4cm]{domino-disobey3_S15.pdf}}
-%%  \hspace{0.3cm}
-%\subfloat[disobey3, boy S16]    
-%    {\label{fig:domino-diff-group2}\includegraphics[height=4cm]{domino-disobey3_S16.pdf}}\\
-%%  \hspace{0.3cm}
-%\subfloat[mistake1, boy S5]    
-%    {\label{fig:domino-same-group1}\includegraphics[height=4cm]{domino-mistake1_S5.pdf}}
-%%  \hspace{0.3cm}
-%\subfloat[mistake1, boy S6]    
-%    {\label{fig:domino-same-group2}\includegraphics[height=4cm]{domino-mistake1_S6.pdf}}    
-%    
-%  \caption[Individual Differences in Interacting with the Robot]{\small \textbf{Individual differences in interacting with the robot}.
-The top row with figures a) and b) shows the group \texttt{disobey3} that consisted of two boys.
-We consider this group as not aligned in their interaction with the robot.
-While the boy S16 in figure b) talks a lot the robot and also touches it frequently and uses gestures during the first runs, the other boy S15 in figure a) does not do so at all.
-The bottom row with figures c) and d) shows the group \texttt{mistake1} that also consisted of two boys.
-We consider this group as fairly aligned in their interaction with the robot.
-Both children tend to touch the robot and look at the experimenter.}
-%  \label{fig:domino-individual-differences}
-%\end{figure}
+\begin{figure}[!h]
+    \centering
+    \subfloat[disobey3, boy S15]    
+    {\label{fig:domino-diff-group1}\includegraphics[height=4cm]{domino-disobey3_S15.pdf}}
+    %  \hspace{0.3cm}
+    \subfloat[disobey3, boy S16]    
+    {\label{fig:domino-diff-group2}\includegraphics[height=4cm]{domino-disobey3_S16.pdf}}\\
+    %  \hspace{0.3cm}
+    \subfloat[mistake1, boy S5]    
+    {\label{fig:domino-same-group1}\includegraphics[height=4cm]{domino-mistake1_S5.pdf}}
+    %  \hspace{0.3cm}
+    \subfloat[mistake1, boy S6]    
+    {\label{fig:domino-same-group2}\includegraphics[height=4cm]{domino-mistake1_S6.pdf}}
+
+    \caption[Individual Differences in Interacting with the Robot]{\small
+        \textbf{Individual differences in interacting with the robot}. The top row
+        with figures a) and b) shows the group \texttt{disobey3} that consisted of two
+        boys. We consider this group as not aligned in their interaction with the
+        robot. While the boy S16 in figure b) talks a lot the robot and also touches
+        it frequently and uses gestures during the first runs, the other boy S15 in
+        figure a) does not do so at all. The bottom row with figures c) and d) shows
+        the group \texttt{mistake1} that also consisted of two boys. We consider this
+        group as fairly aligned in their interaction with the robot. Both children
+        tend to touch the robot and look at the experimenter.}
+
+    \label{fig:domino-individual-differences}
+\end{figure}
 
@@
 
-%\begin{figure}[!h]
-%  \centering
-%	\subfloat[]    
-%    {\label{fig:domino-imagine}\includegraphics[width=4.75cm]{domino-imagine.pdf}}
-%%    \hspace{0.2cm}
-%	\subfloat[]    
-%    {\label{fig:domino-robot}\includegraphics[width=4.75cm]{domino-robot.pdf}}
-%%	\hspace{0.2cm}
-%	\subfloat[]	
-%	{\label{fig:domino-ranger-how}\includegraphics[width=4.75cm]{domino-ranger-how.pdf}}
-%  \caption[Expectations and Robot-likeness or Ranger]{\small \textbf{Expectations of robots in general and robot-likeness of Ranger.} When children had to justify why they thought Ranger is a robot (c), multiple answers were possible, we received 21 answers from 12 children.}
-%  \label{fig:domino-expectations}
-%\end{figure}
+\begin{figure}[!h]
+    \centering
+    \subfloat[] {
+        \label{fig:domino-imagine}
+        \includegraphics[width=4.75cm]{domino-imagine.pdf}
+    }
+    %    \hspace{0.2cm}
+    \subfloat[] {
+        \label{fig:domino-robot}
+        \includegraphics[width=4.75cm]{domino-robot.pdf}
+    }
+    %	\hspace{0.2cm}
+    \subfloat[]	{
+        \label{fig:domino-ranger-how}
+        \includegraphics[width=4.75cm]{domino-ranger-how.pdf}
+    }
+    \caption[Expectations and Robot-likeness or Ranger]{\small
+    \textbf{Expectations of robots in general and robot-likeness of Ranger.}
+    When children had to justify why they thought Ranger is a robot (c), multiple
+    answers were possible, we received 21 answers from 12 children.}
+
+    \label{fig:domino-expectations}
+\end{figure}
 
@@
 
-%\begin{figure}[!h]
-%\centering
-%  \includegraphics[height=6cm]{domino-why-misbehavior.pdf}   
-%\caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible to the question why the robot did not come over, and we received 37 answers.
-This question shows that children did not necessarily interpret the misbehavior in the way we had assumed.}
-%  \label{fig:domino-why-misbehavior}
-%\end{figure}
+\begin{figure}[!h]
+    \centering
+    \includegraphics[height=6cm]{domino-why-misbehavior.pdf}   
+    \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
+    to the question why the robot did not come over, and we received 37 answers.
+    This question shows that children did not necessarily interpret the misbehavior
+    in the way we had assumed.}
+
+    \label{fig:domino-why-misbehavior}
+\end{figure}
 
@@
 
-%\begin{figure}[!h]
-%\centering
-%  \subfloat[]
-%  {\label{fig:domino-hear}
-%  \includegraphics[height=5.5cm]{domino-hear.pdf}}
-%  \subfloat[]
-%  {\label{fig:domino-see}
-%  \includegraphics[height=5.5cm]{domino-see.pdf}}   
-%\caption[Attribution of Cognitive Skills to Ranger]{\small \textbf{Attribution of cognitive skills to Ranger.} These two questions were asked both in the first interview, after children had interacted with the correctly behaving robot, and in the second interview, after children had interacted with the unexpectedly behaving robot (three conditions).
-A comparison of the answers (first-second) can reveal to what extent the respective misbehavior of the robot impacted children's attribution of cognitive abilities.
-(Note that there were 10 participants in the disobey condition and each 8 participants in the mistake and lost condition.
-Consequently, here and in the following visualizations, we need to be careful as the bars are based on counting answers.) The three bars on the right side of each diagram are a split-up of the \textit{``all''} bar of the second time children were asked.}
-%  \label{fig:domino-cognition}
-%\end{figure}
+\begin{figure}[!h]
+    \centering
+    \subfloat[]{
+        \label{fig:domino-hear}
+        \includegraphics[height=5.5cm]{domino-hear.pdf}
+    }
+    \subfloat[] {
+        \label{fig:domino-see}
+        \includegraphics[height=5.5cm]{domino-see.pdf}
+    }
+    \caption[Attribution of Cognitive Skills to Ranger]{\small
+    \textbf{Attribution of cognitive skills to Ranger.} These two questions were
+    asked both in the first interview, after children had interacted with the
+    correctly behaving robot, and in the second interview, after children had
+    interacted with the unexpectedly behaving robot (three conditions). A comparison
+    of the answers (first-second) can reveal to what extent the respective
+    misbehavior of the robot impacted children's attribution of cognitive abilities.
+    (Note that there were 10 participants in the disobey condition and each 8
+    participants in the mistake and lost condition. Consequently, here and in the
+    following visualizations, we need to be careful as the bars are based on
+    counting answers.) The three bars on the right side of each diagram are a
+    split-up of the \textit{``all''} bar of the second time children were asked.}
+
+    \label{fig:domino-cognition}
+\end{figure}
 
@@
 
-%\begin{figure}[h]
-%\centering
-%  \subfloat[]
-%  {\label{fig:domino-obey}
-%  \includegraphics[height=5.8cm]{domino-obey.pdf}}
-%  \subfloat[]
-%  {\label{fig:domino-silly}
-%  \includegraphics[height=5.8cm]{domino-silly.pdf}}   
-%\caption[Attribution of Intention to Ranger]{\small \textbf{Attribution of intention to Ranger.} Similar as before, children were asked these questions twice.
-Concerning question (a), there are no remarkable differences in children's responses given in the \textit{first} and \textit{second} interview.
-Children tend to think Ranger does always obey to them, even after it misbehaved (\textit{second} part).
-There is however a small difference in the responses visualized in graph (b).
-After the robot misbehaved, 8 children think the robot could do something silly whereas first, only 3 children answered like this.}
-%  \label{fig:domino-intention}
-%\end{figure}
+\begin{figure}[h]
+    \centering
+    \subfloat[] {
+        \label{fig:domino-obey}
+        \includegraphics[height=5.8cm]{domino-obey.pdf}
+    }
+    \subfloat[] {
+        \label{fig:domino-silly}
+        \includegraphics[height=5.8cm]{domino-silly.pdf}
+    }
+    \caption[Attribution of Intention to Ranger]{\small \textbf{Attribution of
+    intention to Ranger.} Similar as before, children were asked these questions
+    twice. Concerning question (a), there are no remarkable differences in
+    children's responses given in the \textit{first} and \textit{second} interview.
+    Children tend to think Ranger does always obey to them, even after it misbehaved
+    (\textit{second} part). There is however a small difference in the responses
+    visualized in graph (b). After the robot misbehaved, 8 children think the robot
+    could do something silly whereas first, only 3 children answered like this.}
+
+    \label{fig:domino-intention}
+\end{figure}
 
@@
 
-%\begin{figure}[!h]
-%\centering
-% \subfloat[]
-%  {\label{fig:domino-feelings}
-%  \includegraphics[height=5cm]{domino-feelings.pdf}}
-% \subfloat[]
-%  {\label{fig:domino-friend}
-%  \includegraphics[height=5cm]{domino-friend.pdf}}
-%\caption[Attribution of Emotional State and Perceived Companionship]{\small \textbf{Attributions of emotional state and perceived companionship}.}
-%  \label{fig:domino-feelings-companion}
-%\end{figure}
+\begin{figure}[!h]
+    \centering
+    \subfloat[]
+    {   \label{fig:domino-feelings}
+        \includegraphics[height=5cm]{domino-feelings.pdf}}
+    \subfloat[]
+    {   \label{fig:domino-friend}
+        \includegraphics[height=5cm]{domino-friend.pdf}}
+    \caption[Attribution of Emotional State and Perceived Companionship]{\small
+    \textbf{Attributions of emotional state and perceived companionship}.}
+
+    \label{fig:domino-feelings-companion}
+\end{figure}
 
@@
 
-%\begin{figure}[!h] \centering \subfloat[] {\label{fig:domino-leave}
-%\includegraphics[height=5cm]{domino-leave.pdf}} \subfloat[]
-%{\label{fig:domino-leave-why}
-%\includegraphics[height=5cm]{domino-leave-why.pdf}} \caption[Attribution of
-%Moral Standing]{\small \textbf{Attributions of moral standing}. We asked
-%children whether it was alright to leave Ranger alone at home if they go on a
-%2-week vacation (a). Multiple answers (open-ended) were allowed when asked to
-%justify their answer (b).} \label{fig:domino-leave-alone} \end{figure}
+\begin{figure}[!h]
+    \centering 
+    \subfloat[] {
+        \label{fig:domino-leave}
+        \includegraphics[height=5cm]{domino-leave.pdf}
+    } 
+    \subfloat[] {
+        \label{fig:domino-leave-why}
+        \includegraphics[height=5cm]{domino-leave-why.pdf}
+    } 
+    \caption[Attribution of Moral Standing]{\small \textbf{Attributions of moral
+        standing}. We asked children whether it was alright to leave Ranger
+        alone at home if they go on a 2-week vacation (a). Multiple answers
+        (open-ended) were allowed when asked to justify their answer (b).}
+
+    \label{fig:domino-leave-alone} 
+\end{figure}
 
@@
 
-%\begin{figure}[!h]
-%\centering
-% \subfloat[]
-%  {\label{fig:domino-like}
-%  \includegraphics[height=5cm]{domino-like.pdf}}
-% \subfloat[]
-%  {\label{fig:domino-leave-athome}
-%  \includegraphics[height=5cm]{domino-athome.pdf}}
-%\caption[Acceptance of Ranger]{\small \textbf{Acceptance of Ranger}.}
-%  \label{fig:domino-acceptance}
-%\end{figure}
+\begin{figure}[!h]
+\centering
+ \subfloat[]
+  {\label{fig:domino-like}
+  \includegraphics[height=5cm]{domino-like.pdf}}
+ \subfloat[]
+  {\label{fig:domino-leave-athome}
+  \includegraphics[height=5cm]{domino-athome.pdf}}
+\caption[Acceptance of Ranger]{\small \textbf{Acceptance of Ranger}.}
+  \label{fig:domino-acceptance}
+\end{figure}
 

### 2014-09-04 paper.tex
Created a new, 'clean' paper. Started to add relevant parts

--- 2014-09-04 domino-study_hri15.tex
@@
 \end{abstract}
-
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{I.2.9}{Artificial Intelligence}{Robotics}[commercial robots and applications]
-
-%\terms{Theory}
-
-\keywords{anthropomorphism; children; engagement; human-robot interaction; mental models of robot behavior; wizard-of-oz}
-
-\section{Introduction}
-
-In the previous study, we investigated how children interact and relate to
-Ranger. We found that manipulating the robot's behavior (\textit{proactive vs.
-reactive}) can result in a different interaction style with the robot
-(\textit{playful vs. task-oriented}). Generally, the robot was able to motivate
-children to tidy up by putting their toys into the box.
-
-However, the observed engagement and motivation may be due to an initial
-fascination for the robot which is likely to fade out over time. Sustaining
-interaction beyond novelty in HRI is challenging, and in child-robot
-interaction, in particular. Also in the Roomba Study, we saw that initially,
-children were fascinated by Roomba and played with it (even though this robot is
-not made to encourage children to interact with it) but most of the children
-lost their fascination soon and engaged less in using or playing with the robot.
-Previous work comes to a similar conclusion. For instance, a study with the Pleo
-robot in family homes showed that children interacted less with the robot after
-some time \cite{fernaeus_how_2010}. We can expect a similar trend with Ranger.
-This makes it important to explore possibilities of how to sustain children's
-interaction with Ranger. The question is, how we can enhance children's interest
-in Ranger so that they still engage with it after some time, and still feel
-motivated by the robot to tidy up. Can we achieve this without increasing the
-complexity and cost of the robot too much, keeping in mind the affordability of
-the robot and its prospective deployment in a domestic environment?
-
-In this chapter, we present a study that explores possibilities of sustaining
-children's engagement with Ranger by manipulating the robot's behavior in such
-way that it appears \textit{unexpected} to the children. We examine how
-different variations of robot behavior impact children's interaction with Ranger
-and their perception of it (\eg in terms of attributing intention and cognitive
-abilities to the robot).
-
-Using a playful domino game as the interaction scenario, we refer to this study
-hereafter as the \textbf{``Domino Study''}.
-
-\section{Scope and Research Goals}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction: Towards Sustained Engagement}
 
@@
 
-\section{Related Work}
-
-\subsection{Motivation and Contributions}
-
-The overall motivation of this study is to explore ways of fostering engagement and sustaining children's interest in the robot.
-Ultimately, the robotic box Ranger aims to motivate children to tidy up, and engagement with the robot is a prerequisite for this: \textit{``Engagement is crucial, because it is typically a prerequisite for other system objectives: If a user stops interaction with a system, then it cannot have any further impact''} \cite[p.~648]{bickmore_maintaining_2010}.
-
-The question is how can we extend children's interest in the robot and sustain their engagement?
-This question is related to the \textit{novelty effect} which is commonly observed in human-robot interaction.
-Engagement beyond novelty is challenging to achieve, and optimally a long-term study should be used to investigate the interaction over time.
-With the current Ranger prototype which is operated by a human Wizard, a longitudinal study in a natural setting was not feasible at this point of time.\footnote{While we were planning this study, a second version of the Ranger prototype was under development.
-However, we wanted to take any opportunity to study children's interaction with the Ranger in more detail, and therefore set up another short-term study that would focus on a specific aspect of the interaction.} Although we see it as a limitation, most of the HRI studies that investigated engagement and attributions of intentionality to a robot were short-term studies but nevertheless produced relevant results that can encourage future research.
-Also the Domino Study is a short-term investigation and does not directly look at long-term usage but rather addresses the question of engagement with the robot, which in turn is a pre-requisite for long-term engagement.\\
-
-We studied the effect of three different types of unexpected robot behavior (sometimes also labeled as \textit{misbehavior}) by means of a short-term interaction study in a controlled lab-setting.
-
-If we are able to show that the robot's variation of behavior can improve short-term engagement, it is likely that this also leads to improvement in long-term engagement \cite{bickmore_maintaining_2010}.
-
-\begin{figure}[!h] 
-    \centering 
-    \includegraphics[width=0.5\columnwidth]{domino_header.png} 
-    \caption[How do Children Interact with a Robot that Behaves
-    Unexpectedly?]{\small \textbf{How do children perceive and interact with a
-    robot that behaves unexpectedly?} In an interaction study in the lab, 26
-    children aged 4-5 years played with a robot that behaved unexpectedly from time
-    to time. We studied children's engagement with the robot and their attributions
-    of intentionality to it.}
-
-    \label{fig:domino-header} 
-\end{figure}
+We present in this article a study that explores possibilities of sustaining
+children's engagement with the Ranger~\cite{mondada2014ranger} robot by
+manipulating the robot's behavior in such way that it appears
+\textit{unexpected} to the children. We examine how different variations of
+robot behavior impact children's interaction with Ranger and their perception of
+it (\eg in terms of attributing intention and cognitive abilities to the robot).
+
+Using a playful domino game as the interaction scenario, we refer to this study
+hereafter as the \textbf{``Domino Study''}.
 
@@
 In the Domino Study, we analyze child-robot interaction with a robot that shows
-unexpected behavior. In a playful scenario which was set up in a laboratory
-environment (Figure~\ref{fig:domino-setup}), 26 children aged 4-5 years were
-assembling a domino game together. Each group consisted of two children and the
-Ranger robot, which was used to transport domino tiles between the two children.
-
-Ranger usually behaved correctly (expected behavior), coming over to a child
+unexpected behaviour. In a playful scenario which was set up in a laboratory
+environment, 26 children aged 4-5 years were assembling a domino game together.
+Each group consisted of two children and the \emph{Ranger} robot, which was used
+to transport domino tiles between the two children.
+
+Ranger usually behaved correctly (expected behaviour), coming over to a child
 after being called and delivering the domino tile to the other child. However,
-in pre-defined rounds Ranger showed unexpected behavior, when a child called the
-robot. We defined three different types of \textit{misbehavior} that were tested
+in pre-defined rounds, Ranger showed unexpected behaviour when a child called the
+robot. We defined three different types of \textit{misbehaviour} that were tested
 in a between-subjects study design:
@@
     \item The robot makes a \textbf{mistake}: When called by the child to come
-        over, the robot goes wrong but recognizes its mistake and repairs. We
-        expect this to be perceived as \textit{``to err is human''}, and assume
-        increased attributions of human-likeness to the robot.\footnote{The
-        attribution of human-likeness to a robot is labeled as
+    over, the robot goes wrong but recognizes its mistake and repairs. We expect
+    this to be perceived (explicitly) as \textit{``to err is human''}, and
+    (implicitly) as the robot being endowed with a certain level of
+    introspective capabilities (it was able to recognize its own error). In this
+    condition, we assume increased attributions of human-likeness to the
+    robot.\footnote{The attribution of human-likeness to a robot is labeled as
     \textit{anthropomorphism}, and we will hereafter sometimes use ``attribute
@@
     wrong location. We expect this to be perceived as a bug or system error
-        which causes the robot to not work correctly, and assume few
+    which causes the robot to not work correctly, and hypothesize decreased
     attributions of human-likeness to the robot.
@@
     \item The robot \textbf{disobey}: When called by the child to come over, the
-        robot shows the intention to not obey by literally ``shaking its head'',
-        which should reflect the negative reply to the child's request. The
-        robot then goes to a wrong location and remains there while it continues
-        to shake its head (this cue is not used in the lost behavior). We expect
-        the disobey behavior to be perceived as the robot having an
-        \textit{``own will''}, and we assume this leads to increased
-        attributions of human-likeness (intention) to the robot.
+    robot shows it refuses to obey by literally ``shaking its head'' and
+    becoming red. The robot then goes to a wrong location and remains there
+    while it continues to shake its head. We expect the disobey behaviour to be
+    perceived as the robot having an \textit{``own will''}, and we assume this
+    leads to increased attributions of human-likeness (ascribing intentionality)
+    to the robot.
 
@@
 We analyzed children's reaction focusing on two main aspects. On one hand,
-children's \textbf{behavior} (their reactions) toward the unexpected robot
-behavior was studied in terms of \textbf{active engagement} with the robot. On
+children's \textbf{behaviour} (their reactions) toward the unexpected robot
+behaviour was studied in terms of \textbf{active engagement} with the robot. On
 the other hand, we analyzed children's \textbf{perception} of the robot in term
@@
 
-Our research questions deal with both children's observable behavior and their
+Our research questions deal with both children's observable behaviour and their
 perception of the robot. We would also like to explore the relation between
@@
 the robot. The motivation behind this is to find out whether
-\textit{anthropomorphism} cannot only be measured as a specific type of
-perception but also as an observable behavior in the interaction itself. Thus,
-we would like to take a first step in bringing things together and develop an
-\textbf{index of anthropomorphism} that considers both children's perception and
-interaction aspects (qualitatively). Previous work suggests that a social
-relation to a robot (we view anthropomorphism as a specific type of social
-relation) reflects an increased engagement and can be effective in sustaining
-interaction. Consequently, we hypothesize a positive correlation between the
-anthropomorphic perception of the robot and the amount of engagement in the
-interaction.
-
-%\subsection{Engagement}
-
-%\subsection{Unexpected Robot Behavior}
-
-\section{Method and Procedure}
-
-\subsection{Description of the Scenario}
+\textit{anthropomorphism} can not only be measured as a specific type of
+perception but also as an observable behaviour in the interaction itself. Thus,
+we would like to bridge things together and, relying on the concept of an
+\textbf{anthropomorphism index} introduced by~\cite{fink2014dynamics}, build a
+compound metric that considers both children's perception and interaction
+aspects (qualitatively). Previous work suggests that a social relation to a
+robot (we view anthropomorphism as a specific type of social relation) reflects
+an increased engagement and can be effective in sustaining interaction.
+Consequently, we formulate a third hypotesis:
+
+\begin{description}
+
+    \item[Hypothesis 3:] Anthropomorphic perception of the robot and the amount
+    of engagement in the interaction positively correlate.
+
+\end{description}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Scenario and Research Methodology}
+
+\subsection{The Ranger robot}
+
+We used the same prototype as in the previous study, and Ranger was again
+controlled by a human Wizard, who was in the same room (see
+Figure~\ref{fig:domino-setup}). This was to ensure that the Wizard could see
+children's interaction and hear their commands to the robot without any delay.
+
+\subsection{The Domino scenario}
+
+\subsubsection{Experimental setting}
+
+\begin{figure}[ht!] 
+    \centering 
+    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
+    \caption{\small The study took place in one of the rooms in the lab. One
+    child is located in a tent (referred to as \textit{the receiver}), while the
+    other (referred to as \textit{the searcher}) is asked to sit on one of the
+    three beanbags, behind which each 3 domino tiles are distributed (displayed
+    as black stars). A playground with a river drawn on it is used as an
+    imaginary barrier that only the robot is allowed to cross. The solid green
+    arrows, show the robot's path for the \textit{correct} behaviour. The blue
+    dashed arrow visualizes a possible \textit{lost} path, where the Ranger
+    stops and remains at a wrong stop (denoted by the blue cross). The yellow
+    arrows reflect a possible \textit{mistake} path, where the robot goes wrong
+    but then turns back and goes to the searcher child. The red dashed arrow
+    visualizes a possible \textit{disobey} path where the robot goes wrong, then
+    turns toward the child but remains at the wrong stop (red cross).}
+
+    \label{fig:domino-setup} 
+\end{figure}
 
@@
 We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
-pictures of comic farm animals: cow, sheep, hen, donkey, duck, pig, rabbit. The
+pictures of cartoon farm animals: cow, sheep, hen, donkey, duck, pig, rabbit. The
 pictures were taken from a commercially available domino game adapted to the age
@@
 
-\subsection{Manipulation of Robot Behavior}
-\label{sec:domino-manipulation}
-
-We used the same prototype as in the previous study, and Ranger was again
-controlled by a human Wizard, who was in the same room (see
-Figure~\ref{fig:domino-setup}). This was to ensure that the Wizard could see
-children's interaction and hear their commands to the robot without any delay.
-Following a pre-defined script, the robot showed a behavior as presented in the
-following list.
-
-\begin{figure}[!b] 
+\subsubsection{Course of the study}
+
+In our study, there were a total of 14 runs, and at each run, the robot exhibits
+one out of four possible behaviours: \emph{correct}, \emph{mistake}, \emph{lost}
+or \emph{disobey}.  The first 5 runs were used to set the baseline and the robot
+always behaved correctly. In the 9 remaining runs, the robot showed one of the
+misbehaviour (\emph{mistake}, \emph{lost} or \emph{disobey}) at the $3^{rd}$ and
+$4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run. The study is build as
+a between-subject study, and the type of misbehaviour was therefore always the
+same for a given group.
+
+Special attention has been paid to the distribution of misbehaving runs during
+the study. The five first correct runs aims at setting the children expectation
+regarding a consistent robot behaviour. When the robot then exhibits an
+unexpected behaviour, children are likely to be positively surprised. A similar
+effect has been observed in a study with a robot that was cheating from time to
+time~\cite{short_no_2010}.  Besides, to prevent the robot misbehaviours to be
+immediately interpreted as failures, we introduce these misbehaviour neither at
+the very beginning nor at very end of the interaction
+(\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
+failures negatively impact trust).
+
+\cite{short_no_2010} also adopted a similar pattern when introducing unexpected
+robot behaviour. In their study with a robot that cheated, from the 20 rounds of
+the rock-paper-scissors game, the robot cheated three times in the middle: on
+the 4th, 8th and 15th round. The authors adjusted the interaction length so that
+the spacing and timing of the cheating was preserved.
+
+\begin{figure}[!t]
     \centering
-    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
-    \caption[Study Setup of the Playroom in the Lab]{\small \textbf{Study setup
-    of the playroom in the lab (schematic top view)}. We configured one of the
-    rooms in the lab to a playroom with a children's tent from IKEA, in which one of
-    the children is located (referred to as \textit{the receiver} or ``the child in
-    the tent''). A play carpet with a river on it is used as an imaginary barrier
-    between the two children. The other child, referred to as \textit{the searcher}
-    (or ``the child on the beanbag'') is asked to remain ``on the other side of the
-    river'' in the area with the 3 beanbags, behind which each 3 domino tiles are
-    distributed (displayed as black stars). In the back of the room, there is a
-    camera to record the interaction scenario, and right next to it in the corner,
-    there is the Wizard control station: a table with a laptop computer. As some
-    parents stayed in the room during the interaction study, they are asked to sit
-    on the chairs placed in the back of the room. The board next to the door is not
-    used during the experiment, it is simply an accessory. The solid green arrows,
-    show the robot's path for the \textit{correct} behavior. The blue dashed arrow
-    visualizes a possible \textit{lost} path, where the Ranger stops and remains at
-    a wrong stop (denoted by the blue cross). The yellow arrows reflect a possible
-    \textit{mistake} path, where the robot goes wrong but then turns toward the
-    searcher child (U-turn), and then comes straight over to the searcher. The red
-    dashed arrow visualizes a possible \textit{disobey} path where the robot goes
-    wrong, then turns toward the child but remains at the wrong stop (red cross).
-    The different audio and visual cues that the robot uses during the different
-    paths are explained in the text.}
-
-    \label{fig:domino-setup} 
+    \subfloat[mistake]{
+        \label{fig:domino-mistake}
+        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
+    }
+    \subfloat[lost]{
+        \label{fig:domino-lost}
+        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
+    }
+    \subfloat[disobey]{
+        \label{fig:domino-disobey}
+        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
+    }
+    \caption{\small The three robot misbehaviours.}
+    \label{fig:domino-misbehaviour}
 \end{figure}
 
-The \textbf{correct} robot behavior:
+In the \emph{correct} robot behaviour (baseline behaviour) consists in the
+following states:
 
@@
     \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
-        and shows green light pattern (Figure~\ref{fig:domino-put},
-        page~\pageref{fig:domino-put}, the light pattern is still yellow here
-        indicating that Ranger ``reached'' the child; the green light pattern
-        was shown slightly after the putting was done)
+        and shows a green light pattern,
 
     \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
-        sound and shows green light pattern (Figure~\ref{fig:domino-remove},
-        page~\pageref{fig:domino-remove}).
-
-        %	\item \emph{Box is touched or petted:} Ranger ``blushes'' with pink
-        %	light around the area of the box's ``cheeks''
-
-        %	\item \emph{Box is kicked or mistreated:} Ranger makes a
-        %	``disturbance'' sound and the box moves backward
+        sound and shows a green light pattern,
 
@@
     children called the robot saying something like \textit{``Robot come
-        here!''}, the robot starts moving toward the child
-        (Figure~\ref{fig:domino-call}, page~\pageref{fig:domino-call}). Ranger
-        does not react to any other verbal commands.
+    here!''}, the robot starts moving toward the child (Ranger does not react to
+    any other verbal commands).
 
@@
     children who should either put or remove a domino tile, Ranger stops and
-        shows yellow light, if no reaction, Ranger also makes a wiggle-like move
-        (Figure~\ref{fig:domino-show}, page~\pageref{fig:domino-show}).
+    shows a pulsating yellow light pattern. If no reaction, Ranger also makes a
+    wiggle-like move.
 
@@
 
-\begin{figure*}[!b]
-  \centering
-
-  \subfloat[call]
-  {\label{fig:domino-call}
-  \includegraphics[height=4cm]{domino-call.png}} 
-  \subfloat[put]
-  {\label{fig:domino-put}
-  \includegraphics[height=4cm]{domino-put.png}}
-  \subfloat[remove]
-  {\label{fig:domino-remove}
-  \includegraphics[height=4cm]{domino-remove.png}}
-
-  \bigskip
-
-  \subfloat[explore]
-  {\label{fig:domino-explore}
-  \includegraphics[height=4cm]{domino-explore.png}}
-  \subfloat[gesture]
-  {\label{fig:domino-gesture}
-  \includegraphics[height=4cm]{domino-gesture.png}}
-  \subfloat[misuse]
-  {\label{fig:domino-misuse}
-  \includegraphics[height=4cm]{domino-misuse.png}}
-
-  \bigskip
-
-  \subfloat[show]
-  {\label{fig:domino-show}
-  \includegraphics[height=4cm]{domino-show.png}}
-  \subfloat[touch]
-  {\label{fig:domino-touch}
-  \includegraphics[height=4cm]{domino-touch.png}}   
-  \subfloat[look at experimenter]
-  {\label{fig:domino-look}
-  \includegraphics[height=4cm]{domino-look.png}}\\
-
-  \caption[Children's Interactions with the Robot and the Feedback of the
-  Robot]{\small \textbf{Children's interactions with the robot and the feedback
-  of the robot.} Apart from \textit{talking} to the robot, which is not
-  displayed here, there were nine main interactions, which are explained in the
-  respective paragraph on how children's behavior was coded in the videos
-  (page~\pageref{sec:domino-coding}). The robot showed feedback to some of the
-  children's actions: \textit{call, put} and \textit{remove} (top row), as
-  explained in the text.}
-
-  \label{fig:domino-actions}
-\end{figure*}
-
-Most of the time when the sender child (on one of the beanbags, see
-Figure~\ref{fig:domino-setup}, page~\pageref{fig:domino-setup}) calls the robot,
-it correctly goes right over to the beanbag where the child sits (bold green
-arrows in Figure~\ref{fig:domino-setup}). It starts from its starting position
-next to the tent, crosses the play carpet with the ``river'' and then goes to
-the respective beanbag. During some specific \textit{runs} however, the robot
-behaves unexpectedly (dashed arrows in Figure~\ref{fig:domino-setup}). There
-were three different \textbf{manipulations} of the robot behavior:
+During the misbehaving runs, the robot's behaviour is manipulated in three
+possible ways:
 
@@
     it is on the carpet, stops, turns, and goes wrong (see yellow path in
-        Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns
-        its ``face'' toward the sender child, and ``blushes'' red around its
-        ``cheeks'' (as if it recognizes its wrong position,
-        Figure~\ref{fig:domino-mistake}, page~\pageref{fig:domino-mistake}).
-        Then, Ranger goes correctly over to the sender child. The
-        \textit{mistake} behavior is \textit{robot-repaired}, as no
-        human-intervention is needed.
+    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
+    ``face'' toward the sender child, and ``blushes'' red around its ``cheeks''
+    (as if it recognizes its wrong position) and finally goes correctly over to
+    the sender child. The \textit{mistake} behaviour is \textit{robot-repaired},
+    as no human-intervention is needed.
 
@@
     Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
-        with its ``face'' turned away from the child, and it blinks in yellow
-        light (the same as when in front of a child) (see
-        Figure~\ref{fig:domino-lost}, page~\pageref{fig:domino-lost}). Ranger
-        remains waiting at the wrong position until the experimenter tells the
-        child to go over to the robot to put the domino tile. The \textit{lost}
-        behavior is \textit{human-repaired}, as it needs human-intervention.
+    with its ``face'' turned away from the child, and it blinks in yellow light,
+    as if it was in front of a child. Ranger remains waiting at the wrong
+    position until the experimenter tells the child to go over to the robot to
+    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
+    as it needs human-intervention.
 
     \item \textbf{Disobey:} After being called, Ranger goes until it is on the
-        carpet. Then, it shows \textit{disobeying} behavior: It stops, makes red
-        light all over its surface and produces a repeated ``disturbance''
-        sound. It turns, and goes to a wrong position (see red path in
-        Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its
-        ``face'' toward the sender child (Figure~\ref{fig:domino-disobey},
-        page~\pageref{fig:domino-disobey}). In addition to the red blinking,
-        Ranger makes a slow wiggle-like move, and remains waiting at the wrong
-        position until the experimenter tells the child to go over to the robot
-        to put the domino tile. Also the \textit{disobey} behavior is
-        \textit{human-repaired}.
+    carpet. It then stops, makes red
+    light all over its surface and produces a repeated ``disturbance'' sound. It
+    turns, and goes to a wrong position (see red path in
+    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
+    toward the sender child. In addition to the red blinking, Ranger
+    makes a slow wiggle-like move, and remains waiting at the wrong position
+    until the experimenter tells the child to go over to the robot to put the
+    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.
 
 \end{itemize}
-
-\begin{figure}[!t]
-  \centering
-\subfloat[mistake]
-  {\label{fig:domino-mistake}
-  \includegraphics[height=5cm]{domino-mistake.png}}
-  \subfloat[lost]
-  {\label{fig:domino-lost}
-  \includegraphics[height=5cm]{domino-lost.png}}
-  \subfloat[disobey]
-  {\label{fig:domino-disobey}
-  \includegraphics[height=5cm]{domino-disobey.png}}
-
-  \caption[The Three Robot Misbehaviors]{\small \textbf{The three robot
-  misbehaviors.}}
-
-  \label{fig:domino-misbehavior}
-\end{figure}
 
@@
 child has put a domino tile, Ranger automatically turns and goes over to the
-tent (the receiver child does not even need to call the robot).
-
-%\paragraph{Time points of robot misbehavior}
-
-After several correct runs, we assumed that children expect consistent robot
-behavior. When the robot then does something unexpected, children are likely to
-be positively surprised. A similar effect has been observed in a study with a
-robot that was cheating from time to time \cite{short_no_2010}.
-
-It may be that children interpret the unexpected robot behavior as a failure.
-But we do not want them to lose trust in the robot, contrary, the unexpected
-robot behavior should have a positive effect and promote engagement. We tried to
-avoid a negative influence by timing the robot misbehavior not at the very
-beginning and very end of the interaction, because it has been shown that early
-and late robot failures negatively impact trust
-\cite{desai_effects_2012,desai_impact_2013}. Desai et al. suggest that users
-should all start and end with a working system. Consequently, we placed several
-unexpected robot behaviors around the middle of the interaction, as shown in
-Table~\ref{tab:domino-second}.
-
-Also \cite{short_no_2010} decided to follow this pattern when introducing
-unexpected robot behavior. In their study with a robot that cheated, from the 20
-rounds of the rock-paper-scissors game, the robot cheated three times in the
-middle: on the 4th, 8th and 15th round. The authors adjusted the interaction
-length so that the spacing and timing of the cheating was preserved.
-
-In our study, there were 14 runs in total. 5 runs were used to set the baseline
-and in those 5 runs the robot always behaved correctly. Then, in the 9 remaining
-runs, the robot showed misbehavior at the $3^{rd}$ and $4^{th}$ run as well as
-at the $7^{th}$ and $8^{th}$ run (see Tables~\ref{tab:domino-first} and
-\ref{tab:domino-second} on page \pageref{tab:domino-first}).
-
-\subsubsection{Scenario Description}
-
-\subsubsection{Manipulation of Robot Behavior}
-
-\subsubsection{Semi-structured Interviews with Children}
+tent (the receiver child does not need to call the robot). The receiver child
+takes the tile and the robot moves to a waiting location until the next run
+starts.
 
@@
 
-Table~\ref{tab:domino-sample} (page~\pageref{tab:domino-sample}) gives an
-overview.
-
-\begin{table}[H]
-%\vspace{1 cm}
-\captionof{table}[Domino Study Participants]{\small \textbf{Overview of the 13 groups (n = 26 children) that participated in the Domino Study.} The \textit{scenario duration} is the time that children spent interacting with the robot.
-The time duration of the short interviews is not included here.
-The \textit{anthropomorphism index} is a score that we developed and which measures how far children anthropomorphize the robot during the interaction study and the interview (see Section~\ref{sec:domino-anth-score}).
-The last row of the table gives the overview of the sample including the Mean age (M), the average scenario duration and average anthropomorphism index.}
-\label{tab:domino-sample}       % Give a unique label
-\centering
-\footnotesize
-
-\begin{tabular}{lllll}
-\hline\noalign{\smallskip}
-	\multirow{3}{*}{\textbf{group}} & \multirow{3}{*}{\textbf{children (age)}} & \multirow{3}{*}{\textbf{relation}} & \textbf{scenario} & \textbf{anthropomorphism} \\
-	 & & & \textbf{duration} & \textbf{index} \\
-	 & & & (min:sec) & points / \% \\
-\noalign{\smallskip}\hline\hline\noalign{\smallskip}
-
-	mistake1 & boy (4) & friends & 19:01 & 5.75 / 36~\% \\ 
-	& boy (4) & & & \\ 
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	mistake2 & boy (5) & friends & 15:28 & 10 / 63~\% \\
-	& boy (4.5) & & & \\ 
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	mistake3 & boy (4) & family & 15:24 & 8 / 50~\% \\ 
-	& girl (4) & & & \\ 
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	mistake4 & boy (4.5) & friends & 13:23 & 8 / 50~\% \\ 
-	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \hline \noalign{\smallskip}
-
-	lost1 & boy (4.5) & family & 17:08 & 8.75 / 55~\% \\ 
-	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}
-
-	lost2 & boy (5) & friends & 16:43 & 8.75 / 55~\% \\
-	& boy (4.5) & & & \\  
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	lost3 & girl (4.5) & friends & 15:01 & 7.5 / 47~\% \\ 
-	& girl (4.5) & & &  \\ \noalign{\smallskip} \hline \noalign{\smallskip}
-
-	lost4 & boy (5) & friends & 13:04 & 8.25 / 52~\% \\
-	& girl (4) & & & \\ 
-\noalign{\smallskip} \hline \hline \noalign{\smallskip}
-
-	disobey1 & boy (4.5) & friends & 13:37 & 3.75 / 23~\% \\
-	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}
-
-	disobey2 & boy (4.5) & friends & 17:37 & 3.25 / 20~\% \\ 
-	& girl (4.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}
-
-	disobey3 & boy (5.5) & friends & 17:38 & 10.25 / 64~\% \\ 
-	& boy (5.5) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}
-
-	disobey4 & girl (4) & friends & 14:46 & 4.5 / 28~\% \\
-	& girl (4) & & & \\ \noalign{\smallskip} \hline \noalign{\smallskip}
-
-	disobey5 & boy (4) & friends & 16:25 & 10.75 / 67~\%  \\
-	& boy (4) & & & \\
-\noalign{\smallskip} \hline \hline \noalign{\smallskip}
-
-	13 groups & M age 4.46 & 2 family & 15:47 & M 7.5 / 47~\% \\ 
-	26 children & 16 boys, 10 girls & 11 friends & & (SD 2.5 points) \\	
-\noalign{\smallskip}\hline
-
-\end{tabular}
-\end{table}
-
-\subsubsection{Course of the Study}
-
-We recruited pairs of children (4-5 years old, who knew each other) to play a
-``collaborative domino game with a robot''. We distributed flyers in the campus
-kindergarten, sent out mails to pre-schools in town, and made a posting on an
-online-blog that targets parents in Lausanne.
-
-Participants were invited to come to our lab for a playful child-robot
-interaction study that would last 60 min at most. Parents (or guardians) brought
-their children and could either stay in the arranged play room or go to the
-cafeteria in the same building. During the study, two experimenters were
-present.
-
-\begin{itemize}
-
-    \item \textbf{Introduction and pre-interview ($\sim$5~min):} One of the
-        experimenters introduced the study to the parents and asked them to sign
-        a consent form. The other experimenter briefed children by explaining
-        them the domino game and conducting the pre-interview (questions about
-        previous experience with robots, and their expectations)\footnote{The
-        interview questions for all three short-interviews are given in
-        Table~\ref{tab:domino-questions} and the original French version can be
-        found in the Appendix (page~\pageref{apx:domino-interview}).}. At the end of the
-        pre-interview we introduced the Ranger box (first hidden under the wizard table)
-        and explained that it was there to transport the domino tiles between them.
-
-    \item \textbf{First interaction phase ($\sim$10~min):} In all 5 runs the
-        robot behaves correctly, as displayed in Table \ref{tab:domino-first}.
-        This first interaction phase was the same across all three conditions.
-        It serves to familiarize children with the situation, the robot, and the
-        game. We can assume that children expect consistent robot behavior
-        afterwards.
-
-\begin{table}[H]
-\captionof{table}[First Interaction Phase (5 Runs with Correct Robot Behavior)]{\small \textbf{First interaction phase.} The robot behaved correctly~(v) in all five runs.}
-\label{tab:domino-first}       % Give a unique label
-\centering
-\footnotesize
-\begin{tabular}{lccccc}
-\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
-	&  run 1.1 & run 1.2 & run 1.3 & run 1.4 & run 1.5  \\ 
-\noalign{\smallskip}\hline\hline
-	\textit{correct} & v & v & v & v & v  \\ 
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
-
-    \item \textbf{First short interview ($\sim$5~min):} In this interview we
-        asked children several questions to assess their first impression of
-        Ranger, and how far they ascribe cognitive abilities and mental states
-        to the correctly behaving robot. After this first interview, children
-        switched their roles (beanbag / tent), so to create a balance.
-
-    \item \textbf{Second interaction phase ($\sim$20~min):} In the 9 runs of the
-        second phase, the robot alternated between behaving correctly and
-        misbehaving, as displayed in Table \ref{tab:domino-second}.
-
-\begin{table}[H]
-\captionof{table}[Second Interaction Phase (9 Runs with Partly Robot Misbehavior)]{\small \textbf{Second interaction phase.} There are 9 runs in the second interaction phase.
-At some time points, namely runs 2.3, 2.4 and 2.7, 2.8., the robot showed the respective misbehavior~(x), according to the experimental group either \textit{mistake, lost} or \textit{disobey}.
-In the other runs, namely runs 2.1, 2.2.
-and 2.5, 2.6 and 2.9 the robot behaved correctly~(v).}
-\label{tab:domino-second}       % Give a unique label
-\centering
-\footnotesize
-\begin{tabular}{lccccccccc}
-\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
-	&  run 2.1 & run 2.2 & \textbf{run 2.3} & \textbf{run 2.4} & run 2.5 & run 2.6 & \textbf{run 2.7} & \textbf{run 2.8} & run 2.9 \\ 
-\noalign{\smallskip}\hline\hline
-	\textit{mistake} & v & v & \textbf{x} & \textbf{x} & v & v & \textbf{x} & \textbf{x} & v \\ 
-	\textit{lost} & v & v & \textbf{x} & \textbf{x} & v & v & \textbf{x} & \textbf{x} & v \\ 
-	\textit{disobey} & v & v & \textbf{x} & \textbf{x} & v & v & \textbf{x} & \textbf{x} & v \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
-
-    \item \textbf{Second short interview ($\sim$5~min):} After this phase of
-        interacting with the unexpectedly behaving robot, we conducted another
-        short interview and a debriefing with the children. We mostly asked
-        open-ended questions, concerning several topics, such as whether they
-        noticed anything unusual in the robot behavior (manipulation check), and
-        how far they ascribe cognitive abilities, mental states, and moral
-        standing to the robot after it had shown unexpected behavior.
-
-\end{itemize}
-
-In the end, we thanked parents and children and each child received a little
-gift (\eg a small puzzle or a coloring book). Some children made a drawing of
-the robot, which may be an interesting qualitative evaluation tool for future
-studies with young children.
-
-%	when there was enough time (we set a time limit of 60 min as duration for the entire experiment), we asked children to draw the Ranger robot with which they had just played.
-
-The study was set up as a between-subjects experiment with three conditions,
-corresponding to the three types of robot misbehavior. Thus, in one group the
-robot only showed one type of misbehavior during the second interaction phase.
-There were each 4 groups in the \textit{mistake} and \textit{lost} condition,
-and 5 groups in the \textit{disobey} condition (see
-Table~\ref{tab:domino-sample}). We did not have a control condition in which the
-robot always behaved correctly in all 14 runs. However, we consider the first 7
-runs as reference for \textit{expected behavior} (runs 1.1-2.2), to compare
-against the remaining 7 runs, reflecting \textit{unexpected behavior} (2.3-2.9,
-manipulation phase with the 3 conditions). As such, we can carry out a
-within-subjects analysis to investigate the difference between expected and
-unexpected robot behavior. All interactions and interviews were video and
-audio-recorded.
-
-\subsection{Semi-structured Interviews with the Children}
-
-It is not easy to interview young children. We have seen this in our previous
-study. Children have a short attention span, we (the experimenters) are
-strangers to them, and they are in an unfamiliar environment. The pre-interview
-served to ``break the ice'' and during the first playful interaction phase, most
-children familiarized themselves with the situation.
-
-Also, children do not articulate themselves and understand questions like
-adults. We tested our interview structure and the script in a pilot-study with
-three young children, and were assisted in formulating our questions by a
-pedagogue and father of four. This helped us adapting our language and
-question-style to the 4-5 year old participants. We set up the interviews like a
-casual conversation / discussion, so we did not separate the two children in
-order to keep the situation natural. We used casual and informal language
-adapted to the age of the children, and encouraged them to justify their answers
-and tell us more details by asking, for example, \textit{How do you know ... ?}
-or \textit{Tell me, what have you observed when ... ?}. We paid attention to not
-``put words in children's mouth''. Consequently, though we re-phrased and
-repeated some questions, we never forced children to give an answer, and
-accepted when they said they would not know or when they did not respond at all.
-
-\begin{table}[h]
-%\vspace{1 cm}
-\captionof{table}[Questions Used During the Interviews with Children]{\small \textbf{Questions used during the semi-structured interviews with children.} An ``X'' indicates if the question was used in the pre-interview (\textit{pre}), in the \textit{first} short interview (after the 5 runs in which the robot behaved correctly) or in the \textit{second} short interview (after the 9 runs in which the robot sometimes showed unexpected behavior).
-The Ranger robot toy box is abbreviated with ``R''.
-(The original French version of the interview script is in the Appendix, page~\pageref{apx:domino-interview}.)}
-\label{tab:domino-questions}       % Give a unique label
-\centering
-\footnotesize
-\begin{tabular}{lcccl}
-\hline\noalign{\smallskip}
-	\textbf{question} & \textbf{pre} & \textbf{first} & \textbf{second} & \textbf{construct} \\
-\noalign{\smallskip}\hline\hline\noalign{\smallskip}
-
-	How do you imagine a robot? & X & & & \multirow{3}{*}{expectation} \\
-	What could it look like? & X & & & \\
-	Have you ever seen a robot before? & X & & & \\
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	When you first saw R, what did you think? &  & X & & \multirow{4}{*}{impression} \\
-	Is R a robot? How do you know? & & X & & \\
-	Did you expect R would come over to you when you call it? & & X & & \\
-	What happened when you put the domino tile in the box? & & X & & \\
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	Do you think R could go out the door all by itself? & & X & & \multirow{4}{*}{ascribe intention} \\	
-	Does R always obey / come over to you? & & X & X & \\
-	Could R do something silly? & & X & X & \\
-	Why did R not come over to you when you called it? & & & X & \\
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	Here is a domino tile. Do you think R can see it? & & X & X & \multirow{2}{*}{ascribe cognitive abilities} \\
-	When I say \textit{``Hello R!''}, do you think R can hear it? & & X & X & \\	
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	Does R have feelings? Can R be happy or sad sometimes? & & & X & ascribe emotional state \\
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	Do you like R? Why (not)? & & & X & \multirow{3}{*}{social acceptance} \\
-	What do you (not) like about it? & & & X & \\
-	Would you like to have R at home? & & & X & \\	
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	Could R be your friend? Why (not)? & & & X & companionship\\
-\noalign{\smallskip} \hline \noalign{\smallskip}
-
-	Assume you go on a holiday for two weeks. Is it alright & & & \multirow{2}{*}{X} & \multirow{2}{*}{ascribe moral standing}\\
-	~~to leave R alone at home? Why (not)? & & &  & \\	
-\noalign{\smallskip}\hline
-
-\end{tabular}
-\end{table}
-
-We generally needed to keep the interviews as short as possible. In designing
-our interview script and selecting relevant questions, we took inspiration from
-previous work on child-robot interaction and children's perception of robots
-\cite{kahn_jr._robotic_2006,weiss_i_2009,leite_influence_2013}. For instance, we
-applied and adapted some of the ``constructs'' and example questions from the
-questionnaires used in \cite{kahn_jr._robotic_2006} and \cite{weiss_i_2009}. The
-authors evaluated children's perception of the robotic dog AIBO after the
-children had played with the robot. A ``construct'' addresses a specific factor
-(topic) that can be measured by several questions. For instance, the construct
-``cognitive abilities'' (called ``cognition'' in \cite{weiss_i_2009}) considers
-the robot's ability to hear and to see (perceptual skills), as attributed by the
-children. The construct ``moral standing'' and the respective question was taken
-from \cite{kahn_jr._robotic_2006}.\footnote{According to
-\cite{kahn_jr._robotic_2006}, \textit{moral} refers to considerations based on
-an artifact's physical or psychological welfare, and virtue (whether the
-artifact deserves care). An attribution of moral standing reflects, for
-instance, that the robot engenders moral regard, is morally responsible,
-blameworthy, has rights or deserves respect.}			Similarly, we grouped
-questions according to specific constructs that they evaluate (see
-Table~\ref{tab:domino-questions}). This was an adaption and extension of the
-questions and constructs used in previous work.\\
-
-With several recurring questions in the first and second interview, we wanted to
-see the differences in children's perception of the correctly behaving and
-unexpectedly behaving robot. We planned to use these two interviews as a
-within-subject measurement, however, this did not work out very well because
-children's responses were not always accurate, not comparable one by one, and
-children did not always give an answer.
-
-%	Even when children reply that they do not know, this is interesting. Then we either do not ask a good question or they are really uncertain about it.
-
-Similar to how we processed interviews in the previous studies, we qualitatively
-transcribed interviews, \ie we did not craft a full word-by-word transcript but
-noted down any statement that was useful and relevant. This was organized in a
-spreadsheet, so to obtain an overview of the different replies to a question.
-The interviews were analyzed in a qualitative manner.
-
-\subsubsection{Measurements, Coding and Data Analysis}
-
-We have obtained two main types of data. On one hand, as just described, we can
-analyze children's verbal statements concerning their \textbf{perception of the
-robot} (captured in the audio recorded interviews). On the other hand, what we
-describe in the following paragraphs, we can do a quantitative and qualitative
-analysis of \textbf{children's behavior toward the robot} (captured in the video
-recordings). Furthermore, we can investigate how far these two types of data can
-be used to understand children's engagement in the interaction and how far they
-anthropomorphize the robot. We would like to develop a toolkit that considers
-both children's perception and interaction, in order to measure anthropomorphism
-(as a special type of human-like engagement with the robot).
-
-\paragraph{Coding children's behavior in the videos}	
-\label{sec:domino-coding}
-
-Similar to the coding scheme we used in the Ranger study
-(Chapter~\ref{chap:Ranger-fieldstudy}), we annotated children's behavior in the
-videos. Snapshots of the actions, along with the robot's feedback are shown in
-Figure~\ref{fig:domino-actions}, page~\pageref{fig:domino-actions}. For the
-segmentation of behavior we also used the same method as in the Ranger study. We
-coded 10 different actions:
+\subsection{Data collection}
+\subsubsection{Action coding}
+
+We annotated children's behavior in the video records, and coded 10 different
+actions:
 
@@
         ``eye'', try to climb on or inside the box, drive / push the robot
-        around, stop the robot's wheels with a foot;\\
+        around, stop the robot's wheels with a foot;
 
@@
 \end{itemize}
+
+In total, we obtained 2354 distinct actions which summed up to a total
+annotation duration of 145 minutes. On average, one child accounted for 92
+actions (SD=23).
 
@@
 are spontaneous actions that were not requested but arose in the interaction.
-Hence, these actions are interesting to study, and they can further be used to
-analyze \textbf{engagement}.
-
-\subsubsection{Analyzing engagement with Ranger}
-
-%	\textbf{Engagement} is a key metric in social HRI. In general, there are two
-%	types of engagement: emotional and behavioral engagement.  efficacy of
-%	various social characteristics (emotion, dialogue, personality \etc) can be
-%	measured for capturing attention (acquisition time) and holding interest
-%	(duration) \citep{steinfeld_common_2006}.
-
-%	In a long-term interaction study with 8-9 year old children,
-%	\cite{leite_long-term_2013} was measuring engagement through video
-%	observations (by analyzing the amount of time that children spent looking at
-%	the robot), interviews, and questionnaires. The interviews were
-%	semi-structured, containing initial yes-or-no questions followed by
-%	open-ended questions that allowed children to justify and elaborate their
-%	answers.
-%We have chosen a similar approach: in video observations we coded the action
-%\textit{explore}, which includes carefully watching the robot. We also
-%conducted short-term interviews with the 4-5 year old children, however,
-%questionnaires were not feasible with this age group.
-
-There are different possibilities to measure engagement in HRI, depending on the
-specific research question and context. Metrics to measure behavioral engagement
-in the interaction include, for instance, conversation analysis (\eg used in
-\cite{short_no_2010}) or general attention analysis. These can be studied by
-analyzing interaction videos in terms of head movement, eye tracking and gesture
-/ body movement analysis (\eg in \cite{sidner_explorations_2005}).
-Post-measurements to measure emotional engagement can be questionnaires that try
-to assess constructs like the perceived presence and involvement in the
-interaction. An example is the \textit{Interactive Experience Questionnaire}
-(originally developed by \cite{lombard_measuring_2000}) of which adapted
-versions were used in
-\cite{kidd_effect_2004,bainbridge_effect_2008,short_no_2010}.
-
-A mix of several methods has been used in a long-term interaction study with 8-9
-year old children, \cite{leite_long-term_2013}. The author measured engagement
-through video observations (by analyzing the amount of time that children spent
-looking at the robot), interviews, and questionnaires. The interviews were
-semi-structured, containing initial yes-or-no questions followed by open-ended
-questions that allowed children to justify and elaborate their answers. We have
-chosen a similar approach that considers both children's behavioral and
-emotional engagement.
-
-%	: in video observations we coded several ``engagement actions
-%	\textit{explore}, which includes carefully watching the robot. We also
-%	conducted short-term interviews with the 4-5 year old children, however,
-%	questionnaires were not feasible with this age group.
-
-With 4-5 year old children, however, we cannot use rating scales to ask them
-about constructs as abstract as social presence or how much they felt involved
-in the interaction. Here, we rely mostly on video analysis to quantify
-engagement. Several of the aforementioned coded actions
-(Section~\ref{sec:domino-coding}) can reflect engagement: \textit{explore,
-misuse, gesture, touch, show,} and \textit{talk}. Also, \textit{look} at the
-experimenter can be considered as engagement in the interaction: We assume that
-children look at the experimenter when they are surprised and seek for help.
-This behavior reflects that they want to make sense of the robot's behavior and
-that they notice it as ``strange''. Further, we can take into account how they
-refer to Ranger and describe the robot (as well as their experience) in the
-interviews. We describe the combination of the two types of data in the next
-paragraphs.
-
-\paragraph{Engagement reflected in the perception of the robot}
-
-We assume that active reasoning about Ranger reflects engagement (or interest in
-the robot). But how do we identify whether children, 4-5 years old, reason about
-a robot, its cognitive abilities, intentions or mental states, rather than
-viewing it as a machine stepping through a task? As \cite{short_no_2010}
-mentioned: \textit{``It is not easy to measure the attribution of mental
-state.''} Asking \textit{``How much does the robot think?''} is not sufficient.
-Short et al. proposed to rely more on subtle cues in the participants' behavior
-and responses. The nature of participants' responses to open-ended question
-about the robot's behavior (whether they noticed anything unusual and what) can
-give insight into their attributions of mental state to the robot.
-
-%	In \cite{short_no_2010}, a speech analysis revealed that participants used
-%	more active voice verbs to describe the behavior of the cheating robot
-%	compared to the robot that behaved fairly at all times. The authors
-%	interpret that a use of active voice implies action in choice, and
-%	attributions of mental state to the robot.
-
-In terms of children's perception of Ranger, we used some of the questions
-presented in Table~\ref{tab:domino-questions} to assess how far they
-anthropomorphize the robot. As an indication for anthropomorphism we take
-questions in the constructs \textit{ascribe intention, ascribe cognitive
-abilities, ascribe emotional state}, and \textit{ascribe moral standing}.
-
-\paragraph{Engagement reflected in the interaction}
-
-As previously mentioned, from the 10 types of actions that were coded in the
-videos, we cannot consider all of them as reflecting engagement with Ranger.
-Since we asked children from our side to \textit{call} the robot, as well as to
-\textit{put} and \textit{remove} domino tiles, these three actions were
-excluded. Finally, we consider the following 7 actions as \textbf{engagement
-actions}: \textit{explore, misuse, gesture, touch, show, talk}.\footnote{In
-several figures of the ``engagement actions'' later on, \textit{explore} is
-excluded from the visualization because it was too prominent and differences in
-the other actions would not be observable. The huge proportion of
-\textit{explore} suggests that this category needs to be refined in future
-studies.}
+These actions reflect engagement, and are the only one we considered during the
+analysis (except otherwise indicated).
+
+\subsubsection{Semi-structured interviews}
 
 \paragraph{Anthropomorphism index}
-\label{sec:domino-anth-score}
-
-To account for the fact that anthropomorphism arises in an interaction, we try
-to bring both children's perception of the robot (post-measurement) and their
-behavior toward it (in-the-moment measurement) together. By doing so, we would
-like to obtain a qualitative \textbf{anthropomorphism index}. We quantify the
-index by giving 1 point for each anthropomorphic perception of the robot (max.
-13 points) and for specific kinds of human-like behavior toward the robot (max.
-3 points). The index included the following aspects:\\ \\
-
-\textbf{Perception: \textit{(max. 13 points)}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Findings}
+
+\subsection{General considerations}
+
+\subsubsection{Engagement}
+
+\subsubsection{Attribution of higher cognitive skills}
+\paragraph{Intentionality}
+\paragraph{Emotions}
+
+\subsubsection{Manipulation check: Negligable impact of the conditions}
+
+\subsection{Inter-subject and inter-group differences}
+
+\subsection{Anthropomorphic projections and social engagement}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Lessons Learned and Future Directions}
+
 \begin{itemize}
-	\item Ascribe \textbf{mental states / feelings} to Ranger: \textit{0-4 points}\\
-	(2 points for agreeing that Ranger can be happy or sad; 2 points for attributing Ranger with hunger or tiredness)
-	\item Ascribe \textbf{cognitive abilities / intention} to Ranger: \textit{0-4 points}\\ 
-	(each 0.5 points for ascribing seeing and hearing ability; 1 point for agreeing that Ranger can go out the door by itself; 1 point for disagreeing that Ranger always obeys; 1 point for agreeing that Ranger can do something silly)
-	\item Ascribe \textbf{sociality / companionship} to Ranger: \textit{1 point}\\ 
-	(1 point for agreeing that Ranger can be a friend)
-	\item Ascribe \textbf{moral standing} to Ranger: \textit{1 point}\\ (1 point for disagreeing that Ranger be left alone at home)
-	\item Other \textbf{anthropomorphic statements}: \textit{0-3 points}\\ 
-	(1 point for anthropomorphic reason for Ranger's misbehavior; 2 points for anthropomorphic reason for not leaving Ranger alone) 
+\item It’s a challenge to interview young children ... 
+\item Huge differences between the children and groups make it hard to draw general conclusions
+\item Children did not perceive the 3 different conditions as we did not perceive the 3 different conditions as we expected
+\item Coding scheme: “explore” category was not well defined
 \end{itemize}
 
-\textbf{Behavior: \textit{(max. 3 points)}}
-\begin{itemize}
-	\item Use of \textbf{direct speech} toward Ranger: \textit{1 point}\\
-	(\textit{calling} the robot to come over is not considered)
-	\item Use of \textbf{polite formulations} toward Ranger: \textit{1 point}\\ 
-	(\eg saying \textit{``thank you Ranger''} or \textit{``please Ranger ...''} or \textit{``goodbye''})
-	\item Use of \textbf{social or pointing gestures} toward Ranger: \textit{1 point}\\ 
-	(\eg waving at the robot, nodding)
-\end{itemize}
-
-There are certainly limitations to this scoring scheme. For instance, the
-balance between perception and behavior aspects is questionable (13 to 3
-points). Also, we did not consistently assign 1 point to each item, but assigned
-points between 0.5 and 2 points. We did this because we found that different
-items reflect a higher level of anthropomorphic perception of the robot than
-others (for instance, ascribing the ability to see an hear was suggested by our
-study setup, and we cannot be sure that it really reflects anthropomorphism).
-There are possibilities of refinement of this scoring scheme. For instance, a
-more systematic weighting procedure and the identification of all relevant
-factors would be an interesting future achievement. We could introduce a formula
-to calculate the anthropomorphism index \textit{$\alpha$} by taking the sum of
-the various items ($x_1, x_2, x_3...$) and different weights ($a, b, c ...$) to
-balance them: $\alpha$ \textit{=} $a x_1$ \textit{+} $b x_2$ \textit{+} $c x_3
-...$~. Machine learning techniques could be used to optimize such a calculation
-of the anthropomorphism index.
-
-\section{Findings}
-
-There are two main types of findings: 1) related to the interaction of the
-children with the robot and 2) related to the perception of the robot. This
-section is organized accordingly. We then bring both types of data together by
-building the \textit{anthropomorphism index}.
-
-\subsection{Interaction}
-
-\paragraph{Scenario and run duration}
-
-In total, there was more than 5~hours of video material obtained from the
-13~groups. The video material consisted of around 3.5~hours of the two
-interaction phases and 1.5~hours of interviews. The interaction analysis
-considers only the video parts that correspond to the \textit{scenario
-duration}, which starts when the receiver child in the tent asks the searcher
-child for the first domino tile, and it stops when the receiver child puts
-together the last domino to the chain. The scenario duration is split in two
-interaction phases, as described in Section \ref{sec:domino-course-study}, with
-a pause in the middle, that corresponds to the first interview. On average, the
-first interaction phase with 5 runs of the always correctly behaving robot
-lasted 5~min~34~sec. The second interaction phase with 9 runs and the partly
-misbehaving robot lasted on average 10~min~14~sec. Overall, the scenario
-duration (all 14 runs) varied between 13~min~04~sec and 19~min~01~sec (average
-15~min~47~sec, SD~=~1~min~50~sec). The condition had no significant impact on
-the scenario duration (F(2,23)=.18, p=.835).\\
-
-When looking at the average duration of each run, it is not a surprise that the
-runs in which the robot misbehaved (2.3-2.4 and 2.7-2.8) lasted longer
-(M~=~71~sec, SD~=~16~sec) than the runs in which the robot behaved correctly
-(M~=~54~sec, SD~=~16~sec). Overall, for the runs with the correctly behaving
-robot, there is a tendency that the average duration of the run decreases over
-time ($M_{run1.1}$~=~73~sec, $M_{run2.9}$~=~42~sec). This suggests that children
-familiarize themselves with the playful task and the robot and react more
-promptly to it.
-
-\paragraph{Interaction}
-
-\begin{figure}[!h]
-  \centering
-\subfloat[total number (count, \%)]    
-    {\label{fig:domino-action-count}\includegraphics[height=5cm]{domino_actions-pie.pdf}}
-%  \hspace{0.3cm}
-\subfloat[annotation duration, (\%)]    
-    {\label{fig:domino-action-time}\includegraphics[height=5cm]{domino_duration-pie.pdf}}
-
-  \caption[Total Number and Duration of Children's Actions with Ranger]{\small \textbf{Children's actions with Ranger.} (a) shows the total number of the counted actions that were annotated in the videos, (b) shows the total annotation duration percentage of these actions (the total duration of all coded actions are considered as 100\%, not the duration of the scenario).}
-  \label{fig:domino-actions-pie}
-\end{figure}
-
-After having coded children's actions in the video, we obtained 2354 distinct
-actions which summed up to a total annotation duration of 145 minutes. On
-average, one child accounted for 92 actions (SD=23). The average number of
-actions carried out per child was less in the \textit{disobey} condition
-(average 75 actions) than in the \textit{lost} (average 98 actions) and
-\textit{mistake} (average 102 actions) condition. The overall distribution of
-the count of actions and the duration of the total annotation time per action is
-shown in Figure~\ref{fig:domino-actions-pie}. We see that even more than in the
-previous study, \textbf{children explored the robot} (52~\% of the actions,
-making up 76~\% of the total annotation duration). Exploring includes carefully
-watching the robot or actively trying to find out how it works. For instance,
-one boy (4 years, group \texttt{lost1}) clapped his hands and waved in front of
-Ranger's eyes; then he told the experimenter \textit{``No, it cannot hear and it
-doesn't see me!''}.\\
-
-Overall, the interactions with the robot were less varied than in the previous
-study. We assume this was because the scenario was not as open but fairly well
-structured and probably even more constrained (compared to the previous study
-which was carried out in children's own rooms).
-
-%	Also, children were asked to remain in the tent and around the beanbag, so
-%	they could not freely interact with Ranger, as it was possible in the field
-%	study. This constraint is alright because the Domino Study does not openly
-%	explore interactions but focuses on children's reaction to the misbehaving
-%	robot.
-
-Besides \textit{explore}, children engage mostly in the actions required by the
-scenario (Figure~\ref{fig:domino-actions-pie}): \textit{call} (12~\%),
-\textit{put} (8~\%) and \textit{remove} (8~\%). Another 8~\% of the actions were
-\textit{look} at the experimenter, which suggests that children were seeking for
-help or reinforcement sometime. The remaining 12~\% of actions are attributed to
-\textit{touch} (5~\%), \textit{talk} (4~\%) and \textit{gesture} (3~\%).
-
-\begin{figure}[!b] 
-\centering 
-\includegraphics[width=0.99\columnwidth]{domino-time-all.pdf} 
-\caption[Number and Type of Actions for Each Run]{\small \textbf{Number and type of actions for each run} (average for one child per minute).
-Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9).
-The first 7 runs correspond to the \textit{expected phase}, the second 7 runs correspond to the \textit{unexpected phase}.
-Especially during run 2.3, the first time when the robot showed an unexpected behavior, children tended to \textit{look} more at the experimenter.
-During the unexpected phase, also \textit{talk} and \textit{gesture} seem to be increased.
-The specific values comparing the expected and unexpected phases overall are presented in Table \ref{tab:domino-conditions}, page~\pageref{tab:domino-conditions}.}
-\label{fig:domino-time-all} 
-\end{figure}
-
-When visualizing the average count of \textbf{actions for each run} (see
-Figure~\ref{fig:domino-time-all}), we can see that over time, the total number
-of actions does \textit{not} decrease. While interacting with the expected
-behaving robot, there is a peak in run 2.1 which may be due to the fact that
-children switched roles before that run. During the interaction with the
-unexpected behaving robot, there are peaks in runs 2.3, the first run in which
-the robot misbehaved, and a small peak in run 2.9, the very last run. This last
-peak may be due to the fact that we told children this was the last run, and as
-most children did not want to stop playing with the robot. Hence, they tended to
-show some extra engagement, by increasing their use of \textit{gestures} and
-\textit{talking} to the robot, for instance.
-
-The key question is: how was the interaction impacted by the three
-\textbf{different robot misbehaviors}?
-Figure~\ref{fig:domino-time-condition-one} shows how the number of actions
-evolved from run to run by condition. Overall, children tended to interact
-slightly less with the \textit{disobeying} robot (the actions are normalized,
-\ie they show an average per child per minute). This difference can be observed
-during all the runs (and has also been found concerning children's engagement
-with the robot, see next paragraphs). We are not sure how to interpret this. We
-have to assume that interaction differences between the groups and further
-individual differences between the children are the reason. We come back to
-individual differences in the interaction later.
-
-\begin{figure}[!h] 
-\centering 
-\includegraphics[width=0.9\columnwidth]{domino-actions-perrun.pdf} 
-\caption[Total Number of Actions for Each Run per Condition]{\small \textbf{Total number of actions for each run per condition} (average for one child per minute).
-Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9).
-Especially during run 2.3, the first time when the robot showed an unexpected behavior, children interact more with the robot, as well as during run 2.7 when the robot misbehaved again after two correct runs.
-Another increase of actions is during the very last run.}
-\label{fig:domino-time-condition-one} 
-\end{figure}
-
-When comparing children's interaction with the robot between the
-\textit{expected} phase and the \textit{unexpected} phase, the differences
-between the conditions and the effect of the robot's misbehavior in general,
-become clearer. Table~\ref{tab:domino-conditions} gives an overview. It compares
-the number of actions in the expected and unexpected phase for the different
-robot behaviors (average per child). The only two actions that were
-significantly impacted by the different robot manipulations were
-\textit{explore} and \textit{look}. As these two actions are considered to
-reflect engagement, we will come back to these differences in the next
-paragraphs on engagement with the robot. Overall, the values indicate that
-children interacted on average more with the robot in the \textit{lost} and
-\textit{mistake} condition. Also, in most cases, the values are higher in the
-unexpected phase than in the expected phase. Consequently, children interacted
-more during the phase with the misbehaving robot than during the phase when the
-robot always behaved correctly. (Statistical tests to compare the effect of the
-three different robot behaviors are provided in the following paragraphs,
-concerning the \textit{``engagement actions''}, which are subset of all the
-interactions.)
-
-\begin{table*}[H]
-\captionof{table}[Actions with the Three Robot Misbehaviors in Expected and Unexpected Phase.]{\small \textbf{Comparison of actions with the three robot misbehaviors in the expected and unexpected phase}.
-This table is based on n~=~2354 counted actions, and shows the average scores per child for the different actions by robot behavior condition.
-The first line in each double-row shows the values for the expected (exp) phase, in the second line are the values for the unexpected (unexp) phase.
-For instance, a value of 5.13 for \textit{call} in the expected phase, means that a child called the robot on average 5 times during the expected phase.
-Italic numbers indicate higher value when comparing the values of the expected and unexpected phase within the condition.
-Bold numbers indicate highest values when comparing the three different conditions.}
-\label{tab:domino-conditions}       % Give a unique label
-\centering
-\footnotesize
-\begin{tabular}{lcccccccccc}
-\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
-	 & \textbf{call} & \textbf{explore} & \textbf{gesture} & \textbf{look} & \textbf{misuse} & \textbf{put} & \textbf{remove} & \textbf{show} & \textbf{talk} & \textbf{touch} \\ 
-	 & exp & exp & exp & exp & exp & exp & exp & exp & exp & exp \\
-	 & unexp & unexp & unexp & unexp & unexp & unexp & unexp & unexp & unexp & unexp \\
-\noalign{\smallskip}\hline\hline
-
-	\textit{mistake} & \textbf{5.13} & \textbf{26.25} & 0.63 & 3.63 & 0.00 & \textit{\textbf{3.88}} & 3.00 & 0.00 & 0.50 & \textit{\textbf{3.00}} \\
-	(n=813) & \textit{6.50} & \textit{\textbf{31.75}} & \textit{\textbf{2.50}} & \textit{4.38} & \textit{0.25} & \textbf{3.50} & \textit{\textbf{3.63}} & \textit{\textbf{0.38}} & \textit{2.25} & \textbf{2.63} \vspace{0.2cm} \\
-
-	\textit{lost} & 3.63 & 25.00 & 0.63 & \textbf{3.88} & 0.00 & 3.50 & \textbf{3.50} & \textit{\textbf{0.50}} & 0.38 & 0.75 \\
-	 (n=787) & \textit{\textbf{6.88}} & \textit{31.38} & \textit{1.75} & \textit{\textbf{6.88}} & 0.00 & \textbf{3.50} & 3.50 & 0.00 & \textit{1.75} & \textit{1.00} \vspace{0.2cm} \\
-
-	\textit{disobey} & 5.00 & 12.00 & \textbf{1.30} & 1.20 & \textbf{0.10} & \textit{3.70} & \textit{\textbf{3.50}} & 0.10 & \textbf{2.50} & \textit{2.90} \\
-	(n=754) & \textit{6.70} & \textit{19.50} & \textit{1.40} & \textit{2.70} & \textit{\textbf{0.80}} & 3.40 & 3.40 & \textit{0.20} & \textit{\textbf{3.00}} & 2.00 \\
-
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table*}
-
-\paragraph{Engagement with the robot}	
-\label{sec:domino-engagement}
-
-In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
-here. As mentioned before, the findings here do not directly address the issues
-of long-term usage but concern short-term \textit{engagement}, which is a
-pre-requisite for long-term usage.
-
-The huge proportion of \textit{explore} actions (52~\% of all coded actions)
-already suggests that children were generally engaged in the interaction, and
-most of the time carefully observed what the robot did. When considering the
-actions \textit{explore, gesture, look, misuse, show, talk}, and \textit{touch}
-as \textbf{engagement actions}, 1699 of the 2354 actions reflected engagement
-(72~\%). This indicates that overall children were very engaged in the
-interaction with the robot. Furthermore, data suggests that the robot in the
-\textit{mistake} and \textit{lost} condition were more engaging for children
-(each 75~\% of the actions reflected engagement) than the robot in the
-\textit{disobey} condition (66~\% reflected engagement). The statistical
-analysis supports this: An ANOVA indicates that there was a significant effect
-of robot behavior on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
-\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
-indicate that the mean score for \textit{explore} in the \textit{disobey}
-condition is significantly different from the score in the \textit{mistake} and
-\textit{lost} condition. This suggests that children explored the disobeying
-robot less\footnote{It is surprising that the disobeying robot was explored
-less. One may assume that the disobeying robot might better attract children's
-attention because it faces the searcher child and uses fairly strong audio and
-light cues as compared to the other behaviors.} (for the average values, see
-Table~\ref{tab:domino-conditions}). For \textit{look}, the only significant
-difference is found between the mean scores of \textit{lost} and
-\textit{disobey}. Data suggests that when the robot is lost, children look more
-often at the experimenter than when the robot disobeys. The other actions were
-not found to differ significantly between the robot behavior conditions.
-
-Overall, was there an effect on engagement when the robot misbehaved? We compare
-children's engagement during the interaction phase with the expected robot
-behavior and during the interaction phase with the unexpectedly behaving robot.
-A statistical analysis revealed a significant difference between the average of
-engagement actions carried out during the first 7 runs (correct robot behavior)
-and during the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1,
-p=.03). Figure~\ref{fig:domino-engagement-condition} shows the values for
-engagement actions in the three conditions, comparing the expected and
-unexpected phase. In all three conditions, children carried out more engagement
-actions with the unexpectedly behaving robot. No interaction effect was found
-between the two phases of interaction (expected / unexpected) and condition
-(F(2,36)=1.2, p=.31). In general, this finding supports our first hypothesis:
-children show more engagement toward a robot that behaves unexpectedly from time
-to time compared to a robot that always behaves correctly.
-
-It is, however, unclear why children engaged less with the disobeying robot (as
-mentioned before), especially also in the \textit{expected} phase (see
-Figure~\ref{fig:domino-engagement-condition}). In this phase, the robot did not
-disobey but always behaved correctly as in the other two conditions. There were
-no robot behavior differences between the conditions. We have to assume that the
-effect is due to individual and group variations of children's behavior. These
-individual variations would probably be less observable in the data if the
-sample size would have been bigger.
-
-\begin{figure}[!t] 
-\centering 
-\includegraphics[width=0.5\columnwidth]{domino-engagement-condition.pdf} 
-\caption[Engagement Actions in Expected and Unexpected Phase]{\small \textbf{Average number of engagement actions in expected and unexpected phase.} In all three behavior conditions, children engage more in the unexpected phase.
-In general, the \textit{lost} and \textit{mistake} misbehavior are more engaging than the \textit{disobeying} behavior.}
-\label{fig:domino-engagement-condition} 
-\end{figure}
-
-Looking into detail, how did engagement change from run to run?
-Figure~\ref{fig:domino-time-active} shows the average engagement actions
-(without explore) for each run. How can we explain these variations? During the
-\textit{first interaction phase} with the \textit{expected behavior}, we observe
-small variations. Then, with the first \textit{unexpected robot behavior} in run
-2.3, there is a huge peak in the engagement actions, which can again be observed
-in run 2.5, slightly in run 2.7, and then again in the last run 2.9. These runs
-correspond exactly to when the robot changed its behavior form correct to
-incorrect and \textit{vice versa}. It appears that children are quite sensitive
-to these variations and spontaneously respond to it. But as mentioned before, we
-have to note that the huge peak of engagement actions in the last run may be due
-to the fact that children knew this was going to be the last round.
-
-\begin{figure}[!h] 
-\centering 
-\includegraphics[width=0.99\columnwidth]{domino-time-active.pdf} 
-\caption[Engagement Actions for Each Run]{\small \textbf{Engagement actions for each run} (without explore). Average for one child per minute.}
-\label{fig:domino-time-active} 
-\end{figure}
-
-The picture is unclear, when looking at how engagement evolved from run to run
-in the three different conditions (see Appendix
-Figure~\ref{fig:domino-time-condition},
-page~\pageref{fig:domino-time-condition}). Both within the respective conditions
-and when comparing them, there are variations that are difficult to make sense
-of and we cannot give a clear interpretation how these variances may be related
-to the respective robot misbehavior. We have to assume that the fairly small
-sample size of 8-10 children per condition and the huge differences in
-children's individual interaction style is the reason for these strange
-variations.
-
-Overall, our data suggest that the robot that gets lost and does a mistake
-engage in a similar way but that the disobeying robot elicits less engagement.
-This was verified by computing an average value for the \textit{engagement
-actions}. This average expresses how many engagement actions one child did per
-minute. The general engagement action values of the \textit{mistake} (5.66) and
-\textit{lost} (5.41) condition are higher than the value of the \textit{disobey}
-(3.48) condition. This shows again, that the disobeying robot was less engaging
-for the children. A possible interpretation of this result is, that the
-disobeying robot frustrated children or was perceived more negatively than the
-other two manipulations.
-
-\begin{figure}[!h]
-    \centering
-    \subfloat[disobey3, boy S15]    
-    {\label{fig:domino-diff-group1}\includegraphics[height=4cm]{domino-disobey3_S15.pdf}}
-    %  \hspace{0.3cm}
-    \subfloat[disobey3, boy S16]    
-    {\label{fig:domino-diff-group2}\includegraphics[height=4cm]{domino-disobey3_S16.pdf}}\\
-    %  \hspace{0.3cm}
-    \subfloat[mistake1, boy S5]    
-    {\label{fig:domino-same-group1}\includegraphics[height=4cm]{domino-mistake1_S5.pdf}}
-    %  \hspace{0.3cm}
-    \subfloat[mistake1, boy S6]    
-    {\label{fig:domino-same-group2}\includegraphics[height=4cm]{domino-mistake1_S6.pdf}}
-
-    \caption[Individual Differences in Interacting with the Robot]{\small
-        \textbf{Individual differences in interacting with the robot}. The top row
-        with figures a) and b) shows the group \texttt{disobey3} that consisted of two
-        boys. We consider this group as not aligned in their interaction with the
-        robot. While the boy S16 in figure b) talks a lot the robot and also touches
-        it frequently and uses gestures during the first runs, the other boy S15 in
-        figure a) does not do so at all. The bottom row with figures c) and d) shows
-        the group \texttt{mistake1} that also consisted of two boys. We consider this
-        group as fairly aligned in their interaction with the robot. Both children
-        tend to touch the robot and look at the experimenter.}
-
-    \label{fig:domino-individual-differences}
-\end{figure}
-
-\paragraph{Individual differences}
-
-In fact, we visualized engagement actions for each child (see examples in
-Figure~\ref{fig:domino-individual-differences}), and found very different
-interaction styles between them, both on a pair and on an individual level. In a
-few groups, children were ``aligned'' (homogeneous) in their behavior. For
-instance, if one child started to talk to the robot, the other child would do
-the same. Mimicking or mirroring the behavior of others is common among young
-children. We consider a group as aligned when they engaged with the robot in a
-similar way. This was the case in some of the groups. In some other groups,
-there were differences between the two children, for instance one child hardly
-showed engagement actions while the other one was more engaged. Or there was one
-child who dominated the interaction while the other may have had a more
-introvert personality.
-
-With a small sample size, individual differences have a quite strong impact in
-the data-set and it makes statements about the influence of the robot behavior
-as a variable difficult. For instance, we found more \textit{misuse} behavior in
-the \textit{disobeying} condition (Figure~\ref{fig:domino-time-disobey-active},
-page~\pageref{fig:domino-time-disobey-active}) than in the other conditions. One
-may assume that this is due to the robot's strong disobeying behavior. However,
-there were two boys who had a rough interaction style and reacted almost
-aggressively toward the disobeying robot. No other children showed this strong
-reaction.
-
-We did not find a statistically significant effect of gender on any of the
-actions. There are however some \textbf{qualitative gender differences} that are
-noteworthy. Boys generally seemed to interact more with the robot: they
-\textit{explored} it more (M=52.0, SD=16.0) than girls did (M=38.7, SD=17.8);
-boys \textit{talked} more (M=5.19, SD=9.0) to the robot than girls (M=1.0,
-SD=2.2); they \textit{called} the robot more often (M=12.75, SD=5.9) than girls
-(M=8.8, SD=5.9), used more \textit{gestures} toward the robot (M=3.6, SD=4.5)
-than girls (M=1.4, SD=2.0) and boys were they only ones who showed some few
-\textit{misuse} actions. Contrary, girls more often touched the robot (M=5.2,
-SD=6.0) than boys did (M=3.6, SD=3.5), and slightly more often looked to the
-experimenter (M=7.8, SD=7.4) than boys (M=6.8, SD=4.1). Interestingly, we had
-found similar but also non-significant gender differences in the Ranger Study
-(Chapter~\ref{chap:Ranger-fieldstudy}): boys had used more gestures toward the
-robot, while girls had more often touched the robot. Despite the fact that in
-both cases the differences are not significant, we can interpret that boys and
-girls interact differently with Ranger.
-
-\paragraph{Summary}
-
-It is not easy to draw a clear conclusion about children's interaction with the
-robot, especially not when comparing the three different conditions. There were
-huge variations in the data, due to children's different interaction styles and
-their individuality. Overall, the analysis showed that children were generally
-engaged in the interaction with Ranger. Most of the time, they explored the
-robot, by watching it carefully or trying to find out how it works, for
-instance. During the course of the experiment, the amount of actions did not
-decrease (over the whole experiment) but was sustained by the manipulation of
-robot behavior. Children were significantly more engaged in the interaction
-phase with the unexpected robot behavior, compared to the phase in which the
-robot behaved correctly. The increase of looking at the experimenter in run~2.3
-shows that children were surprised when they saw the robot doing something
-unexpected. Concerning the different robot misbehaviors, the \textit{mistake}
-and \textit{lost} robot behavior appear to be more effective to trigger (and
-possibly sustain) interaction than the \textit{disobey} behavior. Children's
-high engagement (increased use of gestures and direct speech to the robot) in
-the last run of the experiment may reflect their wish to continue playing with
-the robot.
-
-\subsection{Perception}
-
-In this section, we analyze how children perceived the robot. This may help
-understand why they tended to be less engaged with the disobeying robot. This
-section is organized along the different constructs that were assessed in the
-interviews with the children. An overview of the questions used during the
-interviews is given in Table~\ref{tab:domino-questions},
-page~\pageref{tab:domino-questions}.
-
-Overall, we gathered more than 1.5~hours of video- and audio-recorded interview
-material. The duration of both the first and second interview together varied
-between 5-11~min, with an average duration of 7~min~49~sec. The second interview
-(M=280~sec, SD=70~sec) usually lasted slightly longer than the first one
-(M=189~sec, SD=39~sec).
-
-%\hl{(probably check for gender differences in children's responses)}
-
-\paragraph{Expectations and robot-likeness}
-
-In the pre-interview, some of the children said that they had seen a robot
-before. This may be due to the fact that several participants (their parents)
-were recruited around the campus of our Institute of Technology. Some children
-mentioned they had seen a robot at EPFL's \textit{``robotic festival''}, a
-public event at which robots are demonstrated and robotic workshops are
-organized. We asked children how they imagine a robot and how a robot could look
-like (Figure~\ref{fig:domino-imagine}). 10 children did not respond to this
-question which can be explained by the fact that this was the very first
-question we asked them and the whole situation was still new to them. However,
-from the 16 children who provided an answer, 10 mentioned that for them, a robot
-has some human-like properties: it either looks like a human (has a body, arms,
-hands, legs, feet, or a head) or it can walk, grasp, search for things, or even
-set the table. 5 of the children had no clear concept of what a robot is.
-
-\begin{figure}[!h]
-    \centering
-    \subfloat[] {
-        \label{fig:domino-imagine}
-        \includegraphics[width=4.75cm]{domino-imagine.pdf}
-    }
-    %    \hspace{0.2cm}
-    \subfloat[] {
-        \label{fig:domino-robot}
-        \includegraphics[width=4.75cm]{domino-robot.pdf}
-    }
-    %	\hspace{0.2cm}
-    \subfloat[]	{
-        \label{fig:domino-ranger-how}
-        \includegraphics[width=4.75cm]{domino-ranger-how.pdf}
-    }
-    \caption[Expectations and Robot-likeness or Ranger]{\small
-    \textbf{Expectations of robots in general and robot-likeness of Ranger.}
-    When children had to justify why they thought Ranger is a robot (c), multiple
-    answers were possible, we received 21 answers from 12 children.}
-
-    \label{fig:domino-expectations}
-\end{figure}
-
-\paragraph{First impression of Ranger}
-
-Asked whether Ranger was a robot (see Figure~\ref{fig:domino-robot}), children
-were not sure how to reply, and some hesitated or did not provide an answer at
-all. In general, it was not easy for children to decide whether Ranger was a
-robot or not because only a few of them had a clear concept of a robot in mind.
-9 children did not give an answer at all. Some children mentioned they had had
-different expectations (those who had a human-like image of a robot). From those
-who replied, 5 children did not find that Ranger is a robot because it has no
-arms or legs and because its eyes are not real. However the majority of the
-respondents (12 of 17) was convinced of the opposite, namely that Ranger is a
-robot. According to them (see Figure~\ref{fig:domino-ranger-how}) Ranger is a
-robot because it is able to move by itself, it has eyes, it is able to transport
-things, and because it has feelings (expressed by the light and sound cues).
-
-\paragraph{Manipulation check}
-
-Before going into details about differences in the perception of the robot due
-to the different misbehaviors, we need to check whether children noticed the
-manipulations of the robot behavior, and how they interpreted them. Did they
-perceive and classify the different misbehaviors, \textit{mistake, lost} and
-\textit{disobey}, as we intended?  As stated in the beginning of the chapter, we
-had hypothesized that the \textit{disobey} behavior is perceived as the robot
-intentionally not doing what it should do. The \textit{mistake} behavior was
-intended to show that the robot can do a mistake but is aware of it and able to
-repair its mistake, which should also lead to some perception of intentionality.
-Contrary, we expected that the \textit{lost} condition is perceived as a
-malfunction or bug of the robot.  In the second interview, after the robot had
-misbehaved, we asked children whether the robot always did what they wanted it
-to do. Most children disagreed and said they noticed something strange. However,
-there were some children who gave a positive answer, suggesting that they found
-the robot always did what they wanted it to do. This was a surprise. Had they
-not noticed the robot's misbehavior? Why not? On one hand, we found that
-children sometimes gave contradictory replies when asked the same question
-twice. This is difficult to interpret. On the other hand, children may have a
-general tendency to please adults \cite{leite_long-term_2013}, and it could be
-the case that some were too shy to tell us that the robot did something strange.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[height=6cm]{domino-why-misbehavior.pdf}   
-    \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
-    to the question why the robot did not come over, and we received 37 answers.
-    This question shows that children did not necessarily interpret the misbehavior
-    in the way we had assumed.}
-
-    \label{fig:domino-why-misbehavior}
-\end{figure}
-
-We nevertheless asked children why they thought the robot had not always come
-over to them. 4 of the children did not reply. The remaining ones gave a variety
-of reasons (Figure~\ref{fig:domino-why-misbehavior}). The most common answer (9
-of 37 replies) was that the robot is somehow \textit{unpredictable} in what it
-is doing and that it could go \textit{no matter where}\footnote{We translated
-children's answers from French to English. For some expressions the meaning and
-connotation of an expression may not be the same. We understand \textit{``partir
-dans tous les senses''} as ``to go off in all possible directions'' and hence
-interpret this reflects viewing the robot as being unpredictable.} because
-\textit{``with robots you have these kind of problems, they do no matter what''}
-(boy (5), \texttt{lost4}). 8 replies concerned \textit{technical problems}
-(including \textit{broken parts}), suggesting that children perceived the
-misbehavior as unintended by the robot. 2 of the children who had interacted
-with the disobeying robot said Ranger was \textit{angry}, which none of the
-children in other conditions replied (these were not the two boys who reacted
-aggressively). Several children ascribed intentionality to Ranger explaining
-that it \textit{did not want to continue} carrying domino tiles or that it
-\textit{made a mistake / did something silly}\footnote{We understood
-\textit{``faire une bêtise''} as ``to do a silly thing'' in the sense of making
-a mistake.}.
-
-%\hl{(put some more quotes of the children, maybe even in French)}
-
-Overall, we can notice that not all children perceived the misbehavior of the
-robot as we had intended and we have to keep this in mind while interpreting the
-data. Also \cite{leite_long-term_2013} found in her study that when children did
-not understand an action of the robot, they tended to view it as a mistake,
-rather than interpreting the robot's behavior as a deliberative action.
-
-%	\textit{``the supportive behavior ``Play Bad Move'' was not completely
-%	understood as a deliberative action of the robot, but rather as a
-%	mistake''}.
-
-In our case, it is not easy to make a clear statement about how each of the
-manipulations was perceived by the children.  Similar to how people reacted to
-the cheating robot in the study of \cite{short_no_2010}, most children showed
-surprise, were amused, sometimes confused, or occasionally slightly angry (\eg
-two boys tended to shout to the robot after it had disobeyed). The
-\textit{disobeying} robot seemed to evoke the strongest reactions, partly with a
-negative implication: later three of the children in this condition stated they
-would not accept Ranger as a friend \textit{because it did not always come over
-when they asked it to come over}. \cite{short_no_2010} described a similar
-implication of the robot cheating behavior: participants made unfavorable
-character attributions to the cheating robot, so the robot's actions affected
-perceptions of the robot as ``fair'' and ``honest''.
-
-%	\cite{short_no_2010} found that participants often had an emotional reaction
-%	to the robot's behavior and made unfavorable character attributions to the
-%	cheating robot. The robot's actions affected perceptions of the robot as
-%	``fair'' and ``honest''. Qualitatively, the authors found that participants'
-%	reactions in the verbal cheat case tended more towards confusion, while
-%	their reactions to the action cheat were more exaggerated, showing surprise,
-%	amusement, and occasionally anger.
-
-%	\cite{short_no_2010} found that participants who saw the action cheat
-%	mentioned cheating, while the participants who saw the verbal cheat
-%	frequently described it as a mistake or malfunction, while only sometimes
-%	calling it cheating.
-
-\begin{figure}[!h]
-    \centering
-    \subfloat[]{
-        \label{fig:domino-hear}
-        \includegraphics[height=5.5cm]{domino-hear.pdf}
-    }
-    \subfloat[] {
-        \label{fig:domino-see}
-        \includegraphics[height=5.5cm]{domino-see.pdf}
-    }
-    \caption[Attribution of Cognitive Skills to Ranger]{\small
-    \textbf{Attribution of cognitive skills to Ranger.} These two questions were
-    asked both in the first interview, after children had interacted with the
-    correctly behaving robot, and in the second interview, after children had
-    interacted with the unexpectedly behaving robot (three conditions). A comparison
-    of the answers (first-second) can reveal to what extent the respective
-    misbehavior of the robot impacted children's attribution of cognitive abilities.
-    (Note that there were 10 participants in the disobey condition and each 8
-    participants in the mistake and lost condition. Consequently, here and in the
-    following visualizations, we need to be careful as the bars are based on
-    counting answers.) The three bars on the right side of each diagram are a
-    split-up of the \textit{``all''} bar of the second time children were asked.}
-
-    \label{fig:domino-cognition}
-\end{figure}
-
-\paragraph{Attributions of cognitive abilities (perceptual skills)}
-
-To assess how far children ascribed low-level cognitive abilities to the robot,
-we asked them whether they believed Ranger is able to hear and see
-(Figure~\ref{fig:domino-cognition}). Also these questions were asked both in the
-first and the second interview. First, the majority of children replied
-positively, saying that Ranger can hear (15) and can see (19). We asked them to
-justify their answer in both cases (\textit{``How do you know?''}). Those
-ascribing cognitive abilities answered, for instance: \textit{``It can see
-because it is looking right at me.''} (girl (4), \texttt{disobey4}) or
-\textit{``The only thing it can hear is when you say `come here'.''} (boy (5),
-\texttt{mistake2}). Those who answered negatively added, for instance:
-\textit{``It cannot see because the eyes are not real.''} (girl (4.5),
-\texttt{disobey1}); \textit{``It cannot hear because it doesn't have ears.''}
-(boy (4), \texttt{mistake4}); and surprisingly two 4-year old children mentioned
-that Ranger is not able to hear because it does not have a \textit{mouth}. It
-seems that for some younger children the concepts of speaking and hearing are
-both related to a mouth. From those two questions, we can summarize that after
-children had interacted with the \textbf{correctly behaving robot} the majority
-does \textbf{ascribe cognitive abilities} to the robot.\\
-
-After they had interacted with the misbehaving robot, some children responded
-differently. Now 11 children (first 15) answered Ranger can hear, and 15
-children (first 19) responded it can see. 2 children in the \textit{mistake}
-condition consistently changed their opinion for both hearing and seeing
-abilities. The other changes were not consistent for both senses and partly even
-contradicting. There was no clear tendency, and also we cannot say whether the
-different conditions had a different impact. We can note that also to the
-\textbf{unexpectedly behaving robot} children tend to \textbf{ascribe cognitive
-abilities} but slightly less than before. It seems that initially the
-attribution of cognitive abilities is due to the robot's physical design (\eg
-eyes) and that the manipulation of the robot's behavior does not substantially
-change this perception (only for few children).
-
-\begin{figure}[h]
-    \centering
-    \subfloat[] {
-        \label{fig:domino-obey}
-        \includegraphics[height=5.8cm]{domino-obey.pdf}
-    }
-    \subfloat[] {
-        \label{fig:domino-silly}
-        \includegraphics[height=5.8cm]{domino-silly.pdf}
-    }
-    \caption[Attribution of Intention to Ranger]{\small \textbf{Attribution of
-    intention to Ranger.} Similar as before, children were asked these questions
-    twice. Concerning question (a), there are no remarkable differences in
-    children's responses given in the \textit{first} and \textit{second} interview.
-    Children tend to think Ranger does always obey to them, even after it misbehaved
-    (\textit{second} part). There is however a small difference in the responses
-    visualized in graph (b). After the robot misbehaved, 8 children think the robot
-    could do something silly whereas first, only 3 children answered like this.}
-
-    \label{fig:domino-intention}
-\end{figure}
-
-\paragraph{Attributions of intention}
-
-One of the central points of this study was to investigate to what degree
-children attribute intention and cognitive abilities to the robot.  In the first
-interview after children had interacted with the correctly behaving robot we
-asked three questions to assess how far they ascribe \textbf{intention} to it
-(see questionnaire items in Table~\ref{tab:domino-questions},
-page~\pageref{tab:domino-questions}). One of these questions was whether they
-believed Ranger could go out the door by itself. They majority of 16 children
-answered negatively, which suggests that they initially do not ascribe intention
-to the robot. The two other questions were whether Ranger would always obey and
-whether Ranger could do a silly thing (Figure~\ref{fig:domino-intention}). These
-two questions were asked again later after children had interacted with the
-unexpectedly behaving robot.
-
-%	With these recurring questions we wanted to see whether children had changed
-%	their mind in terms of ascribing intention to Ranger (and whether the
-%	unexpected robot behavior had caused this effect). This comparison turned
-%	out to be difficult, however.
-
-Overall, in the first interview 12 of the 26 children believed Ranger does
-always obey to them. Asked whether Ranger could do something silly, the great
-majority of 21 children replied negatively. We can summarize that after children
-had interacted with the \textbf{correctly behaving robot} the majority does
-\textbf{not ascribe intention} to the robot.
-
-After they had interacted with the misbehaving robot, we asked children again.
-Now, still 11 children (previously 12) believed Ranger would always obey to
-them. When analyzing the answers of each child separately, there were 2 children
-in the \textit{disobey} condition that changed their answer from \textit{yes} to
-\textit{no}; however also 1 child in the \textit{lost} condition that switched
-their answer in the opposite way (strangely). There was a more remarkable change
-when asking children whether Ranger could do something silly. In the second
-interview, 8 children (previously~3) answered Ranger could do something silly. 1
-child in the \textit{disobey} condition had changed their answer, and each 2 in
-the \textit{mistake} and \textit{lost} condition.
-
-Overall, it it interesting to note that children tend to ascribe cognitive
-abilities to the robot, like the ability to see and hear but not intention. We
-interpret that children may perceive the robot as being able to process sensory
-information but that it is not able to make decisions on its own. We can
-summarize that even with the \textbf{unexpectedly behaving robot} children do
-\textbf{not necessarily ascribe intention} to the robot. The unexpected robot
-behavior impacted only some children's attributions of intention to the robot.
-It seemed that some children did not interpret the robot's misbehavior as
-intentional but more like a technical problem or mistake. For instance, even
-after the robot misbehaved by \textit{disobeying}, the majority of the children
-in this condition was still convinced that the robot could not do a silly thing
-(Figure~\ref{fig:domino-silly}).
-
-\paragraph{Attributions of emotional state and perceived companionship}
-
-We examined whether children attributed \textbf{feelings} to the robot by asking
-them (once at the end of the experiment) if they thought that Ranger can feel
-happy or sad sometimes (Figure~\ref{fig:domino-feelings}). The great majority of
-children (21 of 26) gave a positive answer. Only 2 children who had interacted
-with the \textit{disobeying} robot did not believe that Ranger has feelings and
-another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
-all. Overall, data suggests that \textbf{children attributed emotional states}
-to the robot. Asked for more details, several children answered that it is
-through its colors and sounds that the robot shows a feeling. Most children said
-that they could make the robot feel happy by playing with it and putting a
-domino tile inside the box. This may also be a reflection of their own feelings,
-projected on the robot.  More than half of the children (14 of 26) agreed Ranger
-can be their friend. We did not ask about what being a friend means to them but
-as children generally liked playing with the robot, this may be linked to each
-other. We can note that children \textbf{ascribe feelings to the robot and
-partly accept that it can be a ``friend''}.
-
-\begin{figure}[!h]
-    \centering
-    \subfloat[]
-    {   \label{fig:domino-feelings}
-        \includegraphics[height=5cm]{domino-feelings.pdf}}
-    \subfloat[]
-    {   \label{fig:domino-friend}
-        \includegraphics[height=5cm]{domino-friend.pdf}}
-    \caption[Attribution of Emotional State and Perceived Companionship]{\small
-    \textbf{Attributions of emotional state and perceived companionship}.}
-
-    \label{fig:domino-feelings-companion}
-\end{figure}
-
-\paragraph{Attributions of moral standing}
-
-Inspired from the questionnaire used by \cite{kahn_jr._robotic_2006}, we asked
-children if it would be alright to leave Ranger alone at home (\eg during two
-weeks when they go on a vacation) (Figure~\ref{fig:domino-leave}). The great
-majority of 20 children responded negatively. Asked why, children gave a variety
-of answers that we classified into 7 categories
-(Figure~\ref{fig:domino-leave-why}). With 5 replies, the most common answer was
-that the robot ``could do something silly''. Some other children simply answered
-they would like to take it with them. Others were afraid that the Ranger ``would
-not find its way'' or ``may be taken away by someone''. 2 children believed
-Ranger is sad when left alone and 1 child responded the robot would try to
-escape. This shows that some children really ascribed emotions or an ``own
-will'' to the robot.  We can summarize that children generally \textbf{ascribe
-moral standing to the robot}, meaning that it is an entity that deserves some
-kind of respect and care.
-
-\begin{figure}[!h]
-    \centering 
-    \subfloat[] {
-        \label{fig:domino-leave}
-        \includegraphics[height=5cm]{domino-leave.pdf}
-    } 
-    \subfloat[] {
-        \label{fig:domino-leave-why}
-        \includegraphics[height=5cm]{domino-leave-why.pdf}
-    } 
-    \caption[Attribution of Moral Standing]{\small \textbf{Attributions of moral
-        standing}. We asked children whether it was alright to leave Ranger
-        alone at home if they go on a 2-week vacation (a). Multiple answers
-        (open-ended) were allowed when asked to justify their answer (b).}
-
-    \label{fig:domino-leave-alone} 
-\end{figure}
-
-\paragraph{Acceptance of Ranger}
-
-It does not come as a surprise that children showed great fascination for the
-robot and the domino game (we cannot clearly separate these two things). Only
-those children whose expectations of the robot were not met, seemed to be
-skeptical. Asked if they like Ranger, 16 children gave a positive reply and
-there was no negative response, however 10 children did not answer this
-question. Also, 18 of the children answered they would like to have Ranger at
-home. Still 5 children gave a negative reply and 3 did not provide an answer at
-all.
-
-\begin{figure}[!h]
-\centering
- \subfloat[]
-  {\label{fig:domino-like}
-  \includegraphics[height=5cm]{domino-like.pdf}}
- \subfloat[]
-  {\label{fig:domino-leave-athome}
-  \includegraphics[height=5cm]{domino-athome.pdf}}
-\caption[Acceptance of Ranger]{\small \textbf{Acceptance of Ranger}.}
-  \label{fig:domino-acceptance}
-\end{figure}
-
-\paragraph{Summary}
-
-In general, children tended to associate a robot with some human-like design and
-characteristics, and they were hence not sure whether Ranger counts as a robot.
-According to the children, Ranger's ability to move and its moving eyes however
-suggest it is a robot.
-
-Their perception of Ranger shows that they commonly ascribed some human-like
-characteristics to the robot, such as emotional states or cognitive abilities,
-and that they also tend to view it as a social entity (\eg by ascribing moral
-standing, and accepting it as a friend). But children do not necessarily ascribe
-intention and own reasoning to the robot. This suggests that anthropomorphism is
-not something discrete being either \textit{there} or \textit{not there}; it may
-rather exist in several variations or levels. (We explore social engagement and
-anthropomorphism in more detail in the next section and come back to it in the
-Conclusions Chapter of this thesis.)
-
-Concerning the manipulation of the robot behavior, most (but not all) children
-recognized something strange and agreed that the robot did \textit{``no matter
-what''}. The different types of misbehavior were not clearly interpreted as we
-had intended. The robot's behavior was mostly perceived as
-\textit{``unpredictable''}. Qualitatively, it seemed that the
-\textit{disobeying} robot had a stronger impact on children's perception of the
-robot than the other two behaviors \textit{mistake} and \textit{lost}.
-Generally, children like Ranger and most said that they would like to play with
-it at home.\\
-
-%Also \cite{leite_long-term_2013} reported that when the iCat (the robot used in
-%the study) said something that children were not expecting, the most salient
-%affective expression was surprise.  6 out of the 16 children who took part in
-%the study talked to the robot from the first until the last week of
-%interaction. The most frequent words that children said to the robot were
-%``thank you''. (we also observed this in the Domino Study)
-
-\subsection{Anthropomorphism Index and Social Engagement with Ranger}
-
-The anthropomorphism index expresses to what extent children engaged with Ranger
-in a human-like way, both in terms of their behavior toward the robot and their
-perception of the robot. We mostly present findings on a pair (group) level but
-also look at differences between children in one group.
-
-As described in Section \ref{sec:domino-anth-score}
-(page~\pageref{sec:domino-anth-score}), the anthropomorphism index considers on
-one hand whether children behaved toward the robot in a human-like way. The
-behavioral aspects refer to a qualitative analysis of the interaction, and not
-to the counts of actions annotated in the video material. These qualitative
-aspects included use of direct speech toward the robot, use of social pointing
-gestures (\eg waving or nodding), and use of polite formulations. For instance,
-several children said \textit{``thank you''} when Ranger brought a domino tile
-to them or used a polite formulation when calling Ranger: \textit{``Robot,
-please come over!''}\footnote{These forms of politeness that children use when
-talking to a robot have also been observed by \cite{leite_long-term_2013}.}. If
-a child was using such formulations, he or she was assigned 1 point, and at the
-end, the sum of these points formed the anthropomorphism index. On the other
-hand, the anthropomorphism index considers to what degree children perceive the
-robot as human-like. These results have been mostly presented in the previous
-section (\eg attribution of feelings to the robot).
-
-To obtain the anthropomorphism index for a pair, we first calculated the index
-per child and then took the average of the two children in one group.  The group
-indexes varied between 3.25 and 10.75 points with an average of 7.5 points
-(SD~=~2.5), which is 47~\% of the maximum possible index of 16 points. Similar
-to the individually different interaction styles of the children, there were
-also variations in terms of to what extent they anthropmorphized Ranger. In 7 of
-the 13 groups, the anthropomorphism indexes for both children were similar
-(difference less than 1.5 points), which means that both children
-anthropomorphized the robot to a similar degree. This agreement among children
-happened for both higher and lower indexes. In 6 of the 13 groups, the
-anthropomorphism indexes varied in more than 2 points, which means that one of
-the children anthropomorphized the robot more than the other one. This is an
-interesting finding.
-
-On an overall average, Ranger was moderately anthropomorphized by the
-children.\footnote{However, as our developed anthropomorphism score is relative,
-we cannot really make a claim about what a difference of \textit{+} or \textit{-
-1} point means.} 8 of the 13 groups had an index of 8 or higher.
-Table~\ref{tab:domino-anth-score} shows that of those groups, 3 were in the
-\textit{mistake} condition, 3 in the \textit{lost} condition and 2 in the
-\textit{disobey} condition. Also, the mean index of anthropomorphism in the
-three conditions varied, with the \textit{mistake} and \textit{lost} condition
-leading to a higher index than the \textit{disobey} condition.	This finding
-suggests that the disobeying robot was less anthropomorphized than the other two
-robot behaviors, which speaks against our second hypothesis. We had expected
-that the disobeying behavior is perceived as an intentional action which we
-assumed would lead to increased anthropomorphism. This was not the case. The
-slight difference between the \textit{lost} and \textit{mistake} robot was also
-expected in the opposite direction. It could be that the robot's
-``helplessness'' led to this. With the lost robot, children looked more often at
-the experimenter than in the other condition (see
-Table~\ref{tab:domino-conditions}, page~\pageref{tab:domino-conditions}), which
-suggests that they could not fully make sense of the robot's behavior. The fact
-of not being able to understand (and hence predict) a robot's behavior is likely
-to increase anthropomorphism.\footnote{One of the cognitive / psychological
-explanations for anthropomorphism is that people want to make sense of something
-they do not understand and then tend to anthropomorphize this something (human
-traits are a good source of making attributions because this is what people
-understand best -- themselves and other humans). For more details the reader may
-refer to \cite{epley_seeing_2007}.}
-
-\begin{table}[ht!]
-\label{tab:domino-anth-score}       % Give a unique label
-\centering
-\footnotesize
-\begin{tabular}{lccc}
-\noalign{\smallskip}\noalign{\smallskip}\hline\noalign{\smallskip}
-	& \multirow{2}{*}{M} & \multirow{2}{*}{SD} & count of groups with \\ 
-	& & & with index above 8 \\
-\noalign{\smallskip}\hline\hline
-	\textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
-	\textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
-	\textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\caption{\textbf{Anthropomorphism index.} The maximum possible index was 16.
-The \textit{lost} robot elicits the highest index, which suggests that it is anthropomorphized more.
-Contrary to our hypothesis, data suggests that the \textit{disobeying} robot is anthropomorphized less but the \textit{lost} robot more.}
-\end{table}
-
-But to what extent is the human-like interaction related to perceiving the robot
-as human-like? Do children who interact a lot and are probably more engaged with
-the robot also perceive the robot as more human-like? This was what we
-hypothesized. Data suggests the opposite, however. As shown in
-Figure~\ref{fig:domino-anthropo-interaction}, we found a significant
-\textit{negative} correlation between the count of engagement actions (per
-group) and the qualitative anthropomorphism index (r(11)=-0.56, p=.05).
-
-%	(b=-.05, t(11)=-2.22, p=.048).
-
-The overall model with the count of engagement actions (per group) predicts a
-significant proportion of the qualitative anthropomorphism index (adjusted
-R$^2$=.25, F(1,11)=4.9, p=.05). This means that the more a group showed
-engagement in the interaction, the less they anthropomorphized the robot. This
-is a key results, which was against our initial assumption. How can we interpret
-this? It may be that children who interact more with the robot understand better
-how it works, they are more familiar with it, and as such the robot appears less
-``mystical'' to them, so there is not a big need to anthropomorphize it. On the
-contrary, the cluster of groups that do not interact much but anthropomorphize
-the robot more, is quite homogeneous. The negative correlation between the
-number of engagement actions and the anthropomorphism index suggests that
-children who interact more with the robot tend to anthropomorphize it less. This
-implies that anthropomorphism could fade out after some time (or rather after
-some interaction). This evokes the question how far anthropomorphism (as a
-special kind of social engagement) really helps in sustaining interaction. This
-is a critical point because most of the short-term investigations suggest that
-anthropomorphic design and human social cues emitted by a robot foster
-engagement and acceptance. What if this is not true for continued interaction,
-and thus for the long-term?  We have to be careful about our interpretation, due
-to the small sample size with which we obtained these findings. We suggest to
-investigate the aspect further in future research.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.8\columnwidth]{domino-correlation.pdf}
-
-    \caption[Correlation of Anthropomorphic Perception of the Robot and
-    Interaction]{\small \textbf{Correlation of anthropomorphic perception of the
-    robot and engagement actions.} A scatter plot of the count of engagement
-    actions (without explore) and the \textit{anthropomorphic perception} (score per
-    group) shows a negative correlation. The score for the anthropomorphic
-    perception (\textit{y-axis}) does not take into account the behavioral aspect of
-    the anthropomorphism index, as this is part of the interaction
-    (\textit{x-axis}).  There seem to be two clusters of groups: those who interact
-    more with the robot and anthropomorphize it less, and those who interact less
-    but anthropomorphize the robot more.}
-
-    \label{fig:domino-anthropo-interaction}
-\end{figure}
-
-Our data on the anthropomorphism index also suggest \textbf{qualitative gender
-differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
-SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
-SD=2.4). (Interestingly, as it was mentioned before, boys interacted slightly
-more with the robot than girls; though not significantly. This is
-counter-intuitive concerning the negative correlation between amount of
-interaction with the robot and anthropomorphism tendency.) It would be
-interesting to investigate in more detail whether boys are more prone to
-anthropomophize a robot than girls.\footnote{Findings presented in
-\cite{schermerhorn_robot_2008} suggested similar gender differences. In their
-study, males tended to think of the robot as more human-like and accordingly
-showed more ``social facilitation'' than females, who perceived the robot as
-more machine-like.}
-
-%	\hl{(is this consistent with previous work?)}
-
-\paragraph{Summary}
-
-The established \textit{anthropomorphism index} suggests that children tend to
-conditionally anthropomorphize the robot. Higher indexes of anthropomorphism
-were found in the \textit{lost} and \textit{mistake} condition which was against
-our hypothesis. Interestingly, data suggests a significant negative correlation
-of engagement and anthropomorphism index. It appears that groups who interacted
-more with the robot perceived it as less-humanlike. This raises the question to
-what extent anthropomorphic perceptions of a robot can last over time, and with
-increasing interaction experience.
-
-\section{Discussion}
-
-\subsection{Engagement and Anthropomorphism}
-
-\section{Conclusions}
-
-We found that in a playful scenario where 4-5 year old children play domino
-together with a robot, the robot seems to be more engaging when it shows some
-misbehavior compared to when it always behaves as expected.\footnote{However, we
-cannot say if this effect holds also after novelty has worn off.} Different
-types of misbehavior appear to have a different effect on children's interaction
-and their perception of human-likeness in the robot. A \textit{disobeying} robot
-may be perceived more negatively than a robot that makes a \textit{mistake} or
-gets \textit{lost}. This may lead to attributions of negative personality to the
-robot and children may be less motivated to continue interacting. Such effect
-would be against our idea to promote long-term engagement. A similar conclusion
-was drawn by \cite{short_no_2010}, in their study of a cheating robot:
-Participants sympathized with a robot that \textit{verbally} cheated but they
-behaved punitively towards a robot that cheated \textit{in its actions}.  Thus,
-the effect depends on the type of misbehavior that the robot shows. With some
-``lighter'' misbehavior, children may show helping-behavior and increase their
-engagement, whereas using some ``stronger'' misbehavior, may lead children to
-see the robot as being unpredictable and they could lose trust in it.
-
-In general, any difference in robot behavior may have a strong effect on
-children's perception of the robot, and can powerfully shape how they relate to
-it: \textit{``The attribution of mental state to a robotic partner has dramatic
-consequences for the relationship between robot and human. A friend has mental
-state, a vacuum cleaner does not''} \cite[p.~225]{short_no_2010}.  From what we
-have seen in the Domino Study, we have a rough estimate of how children react
-and relate to a robot that behaves unexpectedly from time to time. They are
-mostly surprised, laugh at the robot, and they tend to be more engaged and
-playful. However, they are also confused and cannot really make sense of the
-robot's strange behavior. We also cannot clearly say whether children perceived
-the unexpected robot behavior entirely as a malfunction (something that happens
-to a machine) or as being intended and based on a motivation (something related
-to a social entity). Children stated both, when asked why the robot had
-misbehaved. Some referred to \textit{``a technical problem''} while others said
-the robot \textit{``is tired''} or it \textit{``doesn't want to carry domino
-tiles any more but rather go on a tour outside''}. Maybe our manipulations were
-not as clearly designed as we expected. There is always some freedom in how
-things are interpreted -- especially with young children.  Certainly more work
-needs to be done to investigate which robot behavior is most beneficial for
-young children and can promote their engagement and motivation to interact with
-Ranger over extended periods of time.
-
-%	Whereas a cheating opponent is acting out of a desire to win the game, a
-%	malfunction, on the other hand, is entirely accidental, and could be the
-%	fault of physical design or faulty programming, and can even occur entirely
-%	without involvement on the part of the robot. \textit{``A malfunction is
-%	something that happens to a machine, while a social entity that can cheat
-%	has motivations and desires.'' Short et al.}
-
-\subsection{Limitations}
-
-This study and the results have several limitations.  First, we did not have a
-real control group in which the robot always behaved correctly. Instead, we took
-the first interaction phase as a reference for how children interact with the
-correctly behaving robot.  Also, the sample size of 13 groups was small. There
-were  variations in the data due to the individual differences of children. More
-data could have allowed for a better comparison between the conditions.  With
-the manipulation of the robot behavior we were able to surprise children.
-However, it is questionable how often the same type of behavior manipulation
-leads to surprise. Moreover, our experiment was a short-term interaction study
-while we try to make statements about how to sustain long-term engagement. This
-is critical but not unusual. Long-term HRI studies with young children are
-extremely rare as they are difficult to set up as well as time and resource
-consuming \cite{leite_long-term_2013}. Nevertheless, we could have probably
-improved our study by setting up several short interaction sessions spreading
-over several weeks. At the end of each session we could have asked whether
-children want to play again with the robot. Such a study could have helped to
-investigate the long-term interaction with the robot and the impact of the
-behavioral variances.
-
-\subsection{Lessons Learned}
-
-One of the lessons learned is that it is difficult to set up a controlled lab
-study with young children. Children are not like adults who patiently
-participate in a 45-minutes experiment and then get some reward in the end. On
-one hand, an experiment with children should not be boring for them, but on the
-other hand, you would like to seriously collect some data. A lot of the
-challenges we experienced are also described in \cite{ros_child-robot_2011}. One
-of the most difficult parts turned out to be the interviews with the children.
-We need to be careful to not over interpret some of their answers. Some children
-seem to not have a clear opinion and partly contradict themselves. These answers
-are not easy to interpret. An interview script including the questions need to
-be designed very carefully, and should definitely be tested beforehand with the
-respective age group.
-
-Overall, it appears that when trying to study something in more detail, such as
-the manipulation of robot behavior, 4-5 year old children may be too young. But
-when trying to evaluate a more general approach, the design of a prototype, or
-an interaction scenario, children are a very good choice. They say things as
-they are and react very naturally, when compared to adults, who may reply more
-socially desired.
-
-\paragraph{Summary}
-
-In this study, we investigated the effect of unexpected robot behavior on
-children's engagement in interacting with Ranger and on their perception of the
-robot.  Our first hypothesis finds support: children show more engagement toward
-a robot that behaves unexpectedly from time to time. Further, different types of
-unexpected behavior may have a different effect, and therefore the behavior
-manipulation needs to be designed with care.
-We did not find support for our second hypothesis which stated that children
-perceive a robot showing intention or cognitive abilities as more human-like
-than a robot that appears to have a system error. This may be due to the study
-setup and the fact that children did not interpret the robot misbehavior in the
-conceived way. Our findings seem to suggest the contrary to our hypothesis. A
-robot that appeared to do a \textit{mistake} or to be \textit{lost} was more
-anthropomorphized than a robot that \textit{disobeyed}. But again, as children
-may have misinterpreted these robot behaviors we cannot be sure about this
-result.
-
-Another outcome of this study is the initial development and first tryout of an
-\textbf{anthropomorphism index}. This index considers both behavioral and
-perception aspects and is able to indicate lower and higher levels of
-anthropomorphism along this continuous index. At the moment, there is no such
-index available that quantifies anthropomorphism along a scale and there is no
-technique that combines behavior and perception. We may raise a discussion about
-this in Chapter~\ref{chap:conclusion}.  In the future, we will need to refine
-and improve this scale. For instance, we need to identify the specific factors
-that should be included as measurement points in such a scale, for both aspects
-(behavior and perception). Also, we need to think about how to balance the two
-aspects appropriately. Probably, also characteristics of the person, the robot,
-and the situation need to be considered.
-
-\nocite{johnson_detecting_2003}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Acknowledgments}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{abbrv}

### 2014-09-08 paper.tex
Work on data collection + findings

@@
 \graphicspath{{figures/}}
-\usepackage{multirow}
+
+\usepackage{booktabs}
 
@@
 \subsection{Data collection}
-\subsubsection{Action coding}
+
+We have obtained and analysed two types of data. The \textbf{children's
+behaviours toward the robot} (\ie the child-robot interactions) have been
+captured in the video recordings by annotating a set of actions, described
+below. The children's \textbf{perception of the
+robot} has been captured through audio-recorded semi-structured interviews.
+
+\subsubsection{Interaction: Action coding}
 
@@
 annotation duration of 145 minutes. On average, one child accounted for 92
-actions (SD=23).
+actions (SD=23). Figure~\ref{fig:domino-time-all} shows the distribution of
+actions over the different runs, in any condition.
+
+\begin{figure*}[ht!] 
+    \centering 
+    \includegraphics[width=0.8\linewidth]{domino-time-all.pdf} 
+    \caption{\small \textbf{Number and type of actions for each run} (average for
+    one child per minute). Generally, the number of actions does not decrease over
+    time (from run 1.1 to run 2.9). The first 7 runs correspond to the
+    \textit{expected phase}, the second 7 runs correspond to the \textit{unexpected
+    phase}. Especially during run 2.3, the first time when the robot showed an
+    unexpected behavior, children tended to \textit{look} more at the experimenter.
+    During the unexpected phase, also \textit{talk} and \textit{gesture} seem to be
+    increased.}
+
+    \label{fig:domino-time-all} 
+\end{figure*}
 
@@
 
-\subsubsection{Semi-structured interviews}
+\subsubsection{Perception: semi-structured interviews}
 
-\paragraph{Anthropomorphism index}
+It is not easy to interview young children: they have a short attention span, we
+(the experimenters) are strangers to them, and they are in an unfamiliar
+environment. The pre-interview served to ``break the ice'' and during the first
+playful interaction phase, most children familiarized themselves with the
+situation.
+
+Also, children do not articulate themselves and understand questions like
+adults. We tested our interview structure and the script in a pilot-study with
+three young children, and were assisted in formulating our questions by a
+pedagogue and father of four. This helped us adapting our language and
+question-style to the 4-5 year old participants. We set up the interviews like a
+casual conversation / discussion, so we did not separate the two children in
+order to keep the situation natural. We used casual and informal language
+adapted to the age of the children, and encouraged them to justify their answers
+and tell us more details by asking, for example, \textit{How do you know ... ?}
+or \textit{Tell me, what have you observed when ... ?}. We paid attention to not
+``put words in children's mouth''. Consequently, though we re-phrased and
+repeated some questions, we never forced children to give an answer, and
+accepted when they said they would not know or when they did not respond at all.
+
+\begin{table}[h]
+\centering
+\footnotesize
+\begin{tabular}{p{0.9\linewidth}}
+    \toprule
+    \textbf{Construct \emph{expectation}} \\
+    \midrule
+
+    \emph{How do you imagine a robot?} \\
+    \emph{What could it look like?} \\
+    \emph{Have you ever seen a robot before?} \\
+
+    %%
+    \toprule
+    \textbf{Construct \emph{impression}} \\
+    \midrule
+
+    \emph{When you first saw R, what did you think?} \\
+    \emph{Is R a robot? How do you know?} \\
+    \emph{Did you expect R would come over to you when you call it?} \\
+    \emph{What happened when you put the domino tile in the box?} \\
+
+    %%
+    \toprule
+    \textbf{Ascribe intention} \\
+    \midrule
+
+    \emph{Do you think R could go out the door all by itself?} \\	
+    \emph{Does R always obey / come over to you?} \\
+    \emph{Could R do something silly?} \\
+    \emph{Why did R not come over to you when you called it?} \\
+
+    %%
+    \toprule
+    \textbf{Ascribe cognitive abilities} \\
+    \midrule
+
+    \emph{Here is a domino tile. Do you think R can see it?} \\ 
+    \emph{When I say \textit{``Hello R!''}, do you think R can hear it?} \\
+
+    %%
+    \toprule
+    \textbf{Ascribe emotional state} \\
+    \midrule
+
+    \emph{Does R have feelings? Can R be happy or sad sometimes?} \\
+
+    %%
+    \toprule
+    \textbf{Social acceptance} \\
+    \midrule
+
+    \emph{Do you like R? Why (not)?} \\
+    \emph{What do you (not) like about it?} \\
+    \emph{Would you like to have R at home?} \\
+
+    %%
+    \toprule
+    \textbf{Companionship} \\
+    \midrule
+
+    \emph{Could R be your friend? Why (not)?}\\
+
+    %%
+    \toprule
+    \textbf{Ascribe moral standing} \\
+    \midrule
+
+    \emph{Assume you go on a holiday for two weeks. Is it alright to leave R
+    alone at home? Why (not)?} \\
+
+    \bottomrule
+
+\end{tabular}
+
+    \caption{\small Questions used during the semi-structured interviews
+    with children. The Ranger robot toy box is abbreviated with ``R''.}
+
+    \label{tab:domino-questions}
+
+\end{table}
+
+We generally needed to keep the interviews as short as possible. In designing
+our interview script and selecting relevant questions, we took inspiration from
+previous work on child-robot interaction and children's perception of robots
+\cite{kahn_jr._robotic_2006,weiss_i_2009,leite_influence_2013}. For instance, we
+applied and adapted some of the ``constructs'' and example questions from the
+questionnaires used in \cite{kahn_jr._robotic_2006} and \cite{weiss_i_2009}. The
+authors evaluated children's perception of the robotic dog AIBO after the
+children had played with the robot. A ``construct'' addresses a specific factor
+(topic) that can be measured by several questions. For instance, the construct
+``cognitive abilities'' (called ``cognition'' in \cite{weiss_i_2009}) considers
+the robot's ability to hear and to see (perceptual skills), as attributed by the
+children. The construct ``moral standing'' and the respective question was taken
+from \cite{kahn_jr._robotic_2006}.\footnote{According to
+\cite{kahn_jr._robotic_2006}, \textit{moral} refers to considerations based on
+an artifact's physical or psychological welfare, and virtue (whether the
+artifact deserves care). An attribution of moral standing reflects, for
+instance, that the robot engenders moral regard, is morally responsible,
+blameworthy, has rights or deserves respect.}			Similarly, we grouped
+questions according to specific constructs that they evaluate (see
+Table~\ref{tab:domino-questions}). This was an adaption and extension of the
+questions and constructs used in previous work.\\
+
+With several recurring questions in the first and second interview, we wanted to
+see the differences in children's perception of the correctly behaving and
+unexpectedly behaving robot. We planned to use these two interviews as a
+within-subject measurement, however, this did not work out very well because
+children's responses were not always accurate, not comparable one by one, and
+children did not always give an answer.
+
+%	Even when children reply that they do not know, this is interesting. Then we either do not ask a good question or they are really uncertain about it.
+
+Similar to how we processed interviews in the previous studies, we qualitatively
+transcribed interviews, \ie we did not craft a full word-by-word transcript but
+noted down any statement that was useful and relevant. This was organized in a
+spreadsheet, so to obtain an overview of the different replies to a question.
+The interviews were analyzed in a qualitative manner.
+
+\subsubsection{Engagement and anthropomorphism index}
+
+we can investigate how far these two types of data can
+be used to understand children's engagement in the interaction and how far they
+anthropomorphize the robot. We would like to develop a toolkit that considers
+both children's perception and interaction, in order to measure anthropomorphism
+(as a special type of human-like engagement with the robot).
+
+There are different possibilities to measure engagement in HRI, depending on the
+specific research question and context. Metrics to measure behavioral engagement
+in the interaction include, for instance, conversation analysis (\eg used in
+\cite{short_no_2010}) or general attention analysis. These can be studied by
+analyzing interaction videos in terms of head movement, eye tracking and gesture
+/ body movement analysis (\eg in \cite{sidner_explorations_2005}).
+Post-measurements to measure emotional engagement can be questionnaires that try
+to assess constructs like the perceived presence and involvement in the
+interaction. An example is the \textit{Interactive Experience Questionnaire}
+(originally developed by \cite{lombard_measuring_2000}) of which adapted
+versions were used in
+\cite{kidd_effect_2004,bainbridge_effect_2008,short_no_2010}.
+
+A mix of several methods has been used in a long-term interaction study with 8-9
+year old children, \cite{leite_long-term_2013}. The author measured engagement
+through video observations (by analyzing the amount of time that children spent
+looking at the robot), interviews, and questionnaires. The interviews were
+semi-structured, containing initial yes-or-no questions followed by open-ended
+questions that allowed children to justify and elaborate their answers. We have
+chosen a similar approach that considers both children's behavioral and
+emotional engagement.
+
+With 4-5 year old children, however, we cannot use rating scales to ask them
+about constructs as abstract as social presence or how much they felt involved
+in the interaction. Therefore we have attempted to combine \emph{interaction}
+data with the results of the semi-structured interviews.  Several of the
+aforementioned coded actions can reflect engagement: \textit{explore, misuse,
+gesture, touch, show,} and \textit{talk}. Also, \textit{look} at the
+experimenter can be considered as engagement in the interaction: We assume that
+children look at the experimenter when they are surprised and seek for help.
+This behavior reflects that they want to make sense of the robot's behavior and
+that they notice it as ``strange''. Further, we can take into account how they
+refer to Ranger and describe the robot (as well as their experience) in the
+interviews.  Specifically, we used the constructs \textit{ascribe intention,
+    ascribe cognitive abilities, ascribe emotional state}, and \textit{ascribe
+    moral standing} (Table~\ref{tab:domino-questions}) to assess how far they
+    anthropomorphize the robot.
+
+To account for the fact that anthropomorphism arises in an interaction, we try
+to bring both children's perception of the robot (post-measurement) and their
+behavior toward it (in-the-moment measurement) together. By doing so, we would
+like to obtain a qualitative \textbf{anthropomorphism
+index}~\cite{fink2014dynamics}. We quantify the index by giving 1 point for each
+anthropomorphic perception of the robot (max.  13 points) and for specific kinds
+of human-like behavior toward the robot (max.  3 points). The index included the
+following aspects:\\
+
+\textbf{Perception: \textit{(max. 13 points)}}
+\begin{itemize}
+	\item Ascribe \textbf{mental states / feelings} to Ranger: \textit{0-4 points}\\
+	(2 points for agreeing that Ranger can be happy or sad; 2 points for attributing Ranger with hunger or tiredness)
+	\item Ascribe \textbf{cognitive abilities / intention} to Ranger: \textit{0-4 points}\\ 
+	(each 0.5 points for ascribing seeing and hearing ability; 1 point for agreeing that Ranger can go out the door by itself; 1 point for disagreeing that Ranger always obeys; 1 point for agreeing that Ranger can do something silly)
+	\item Ascribe \textbf{sociality / companionship} to Ranger: \textit{1 point}\\ 
+	(1 point for agreeing that Ranger can be a friend)
+	\item Ascribe \textbf{moral standing} to Ranger: \textit{1 point}\\ (1 point for disagreeing that Ranger be left alone at home)
+	\item Other \textbf{anthropomorphic statements}: \textit{0-3 points}\\ 
+	(1 point for anthropomorphic reason for Ranger's misbehavior; 2 points for anthropomorphic reason for not leaving Ranger alone) 
+\end{itemize}
+
+\textbf{Behavior: \textit{(max. 3 points)}}
+\begin{itemize}
+	\item Use of \textbf{direct speech} toward Ranger: \textit{1 point}\\
+	(\textit{calling} the robot to come over is not considered)
+	\item Use of \textbf{polite formulations} toward Ranger: \textit{1 point}\\ 
+	(\eg saying \textit{``thank you Ranger''} or \textit{``please Ranger ...''} or \textit{``goodbye''})
+	\item Use of \textbf{social or pointing gestures} toward Ranger: \textit{1 point}\\ 
+	(\eg waving at the robot, nodding)
+\end{itemize}
+
+There are certainly limitations to this scoring scheme. For instance, the
+balance between perception and behavior aspects is questionable (13 to 3
+points). Also, we did not consistently assign 1 point to each item, but assigned
+points between 0.5 and 2 points. We did this because we found that different
+items reflect a higher level of anthropomorphic perception of the robot than
+others (for instance, ascribing the ability to see an hear was suggested by our
+study setup, and we cannot be sure that it really reflects anthropomorphism).
+There are possibilities of refinement of this scoring scheme. For instance, a
+more systematic weighting procedure and the identification of all relevant
+factors would be an interesting future achievement. We could introduce a formula
+to calculate the anthropomorphism index \textit{$\alpha$} by taking the sum of
+the various items ($x_1, x_2, x_3...$) and different weights ($a, b, c ...$) to
+balance them: $\alpha$ \textit{=} $a x_1$ \textit{+} $b x_2$ \textit{+} $c x_3
+...$~. Machine learning techniques could be used to optimize such a calculation
+of the anthropomorphism index.
 
@@
 
-\subsubsection{Manipulation check: Negligable impact of the conditions}
+\paragraph{Moral standing}
+
+Inspired from the questionnaire used by \cite{kahn_jr._robotic_2006}, we asked
+children if it would be alright to leave Ranger alone at home (\eg during two
+weeks when they go on a vacation) (Figure~\ref{fig:domino-leave-alone}). The great
+majority of 20 children responded negatively. Asked why, children gave a variety
+of answers that we classified into 7 categories. With 5 replies, the most common answer was
+that the robot ``could do something silly'' (\emph{``faire une bêtise''}). Some
+other children simply answered they would like to take it with them. Others
+were afraid that the Ranger ``would not find its way'' or ``may be taken
+away by someone''. 2 children believed Ranger is sad when left alone and 1
+child responded the robot would try to escape. Interestingly, and while we
+intuitively expected many children to fear that the robot would be sad if
+left alone, only 2 expressed a moral position, while most of the others
+actually expressed several forms of distrust towards the robot: \emph{it's
+not alright to leave the robot alone, not because it is morally incorrect,
+but because we do not trust the robot to remain still}. This shows that things
+must be put into perspective and even young children do not consider our robot
+as an intentional agent, not to say a social agent.
+
+\begin{figure}[!h]
+    \centering 
+    \includegraphics[width=0.9\linewidth]{domino-leave-why.pdf}
+    \caption{\small Attributions of moral
+        standing: we asked children whether it was alright to leave Ranger
+        alone at home if they go on a 2-week vacation. Multiple answers
+        (open-ended) were allowed when asked to justify their answer.}
+
+    \label{fig:domino-leave-alone} 
+\end{figure}
+
+\subsection{Manipulation check: Negligable impact of the conditions}
 

### 2014-09-15 paper.tex
First pass on the whole article. 11 pages for now

@@
 \title{\LARGE \bf
-How Children Perceive and Interact with a Robot that Behaves Unexpectedly - The Domino Experiment
+How Children Perceive and Interact with a Robot that Behaves Unexpectedly -- The Domino Experiment
 }
@@
 \textbf{Engagement} is a metric that has been extensively used and studied both
-in HRI and interactions with other agent-like systems. It has been defined from
-several perspectives. For example \cite{sidner_where_2004} define engagement as
-\textit{``the process by which two (or more) participants establish, maintain
-and end their perceived connections''}. A definition of long-term engagement is
-proposed by \cite{bickmore_maintaining_2010}: \textit{``the degree of
-involvement a user chooses to have with a system over time''}.
+in HRI and during interactions with other agent-like systems. It has been
+defined from several perspectives. For example \cite{sidner_where_2004} define
+engagement as \textit{``the process by which two (or more) participants
+establish, maintain and end their perceived connections''}. A definition of
+long-term engagement is proposed by \cite{bickmore_maintaining_2010}:
+\textit{``the degree of involvement a user chooses to have with a system over
+time''}.
 
@@
 of research has moved toward creating sophisticated emotional models which cause
-complex robot behavior. Some other work
+complex robot behaviour. \cite{leite_long-term_2013} studied the long-term
+engagement of children with a chess playing robot that adapted its behaviour to
+the children and showed empathy toward them. She found that empathetic robots
+are more likely to engage users in the long-term and they proposed several
+guidelines for designing such artificial companions. Some other work
 \cite{bickmore_maintaining_2010,short_no_2010} has shown that there can be much
@@
 manipulations that make the agent more life-like and human. For instance, when
-the agent showed variations in its behavior, participants were more engaged and
+the agent showed variations in its behaviour, participants were more engaged and
 reported a desire to continue interacting with the agent.
@@
 Similarly, more looking at short-term engagement, \cite{short_no_2010} found
-that a simple manipulation of the robot's behavior can lead to greater
+that a simple manipulation of the robot's behaviour can lead to greater
 engagement. The authors let participants play several rounds of the
@@
 they were interacting with the robot. The mechanism behind the cheating action
-that the robot showed, was that participants did not expect this behavior from
+that the robot showed, was that participants did not expect this behaviour from
 the robot. The authors suggest that \textit{``any deviation from expected
@@
 \textit{``many interactions can be improved by the introduction of such simple
-behaviors, and that this should be exploited by designers in HRI. Bringing human
-and robot together to perform a simple, repetitive, familiar task and then
-having the robot behave unexpectedly can increase engagement and mental state
-attribution without complex behavioral or mechanical additions.''}
-\cite{leite_long-term_2013} studied the long-term engagement of children with a
-chess playing robot that adapted its behavior to the children and showed empathy
-toward them. She found that empathetic robots are more likely to engage users in
-the long-term and they proposed several guidelines for designing such artificial
-companions. Our aim for the ``Domino Study'' is however less ambitious than
-creating a long-term robot companion. We are still at an early stage of the
-development and are using a remote controlled prototype as we did in the
-previous study. What we would like to achieve in this study is to find out how
+    behaviours, and that this should be exploited by designers in HRI. Bringing
+    human and robot together to perform a simple, repetitive, familiar task and
+then having the robot behave unexpectedly can increase engagement and mental
+state attribution without complex behavioural or mechanical additions.''}.
+In their model of the dynamics of anthropomorphism, Fink et
+al.~\cite{fink2014dynamics} also suggest that \emph{disruptive behaviours}
+may lead to increased anthropomorphic projections and possibly engagement.
+
+Based on these previous researches, we would like to find out in this study how
 we can enhance children's experience with the robot so that they do not find it
-repetitive and boring to interact with Ranger. In general, repetitiveness is
-likely to decrease a user's motivation to continue using a system
-\cite{bickmore_establishing_2005}.
+repetitive and boring, and ultimately keep interacting with the robot (as
+repetitiveness is likely to decrease a user's motivation to continue using a
+system~\cite{bickmore_establishing_2005}).
 
 We present in this article a study that explores possibilities of sustaining
-children's engagement with the Ranger~\cite{mondada2014ranger} robot by
-manipulating the robot's behavior in such way that it appears
+children's engagement with the \emph{Ranger}~\cite{mondada2014ranger} robot by
+manipulating the robot's behaviour in such way that it appears
 \textit{unexpected} to the children. We examine how different variations of
-robot behavior impact children's interaction with Ranger and their perception of
+robot behaviour impact children's interaction with Ranger and their perception of
 it (\eg in terms of attributing intention and cognitive abilities to the robot).
@@
 hereafter as the \textbf{``Domino Study''}.
+
+This study also aims at applying to an actual study and assessing the usefulness
+of the \emph{anthropomorphic index} proposed by Fink et
+al.~\cite{fink2014dynamics} as a compound (behavioural and phenomenological)
+metric for the attribution of human-like features to robot. We are especially
+interested in investigating how this indicator predicts and/or reflects actual
+\emph{engagement} into the interaction.
 
@@
     \item The robot makes a \textbf{mistake}: When called by the child to come
-    over, the robot goes wrong but recognizes its mistake and repairs. We expect
-    this to be perceived (explicitly) as \textit{``to err is human''}, and
-    (implicitly) as the robot being endowed with a certain level of
-    introspective capabilities (it was able to recognize its own error). In this
-    condition, we assume increased attributions of human-likeness to the
-    robot.\footnote{The attribution of human-likeness to a robot is labeled as
-    \textit{anthropomorphism}, and we will hereafter sometimes use ``attribute
-    intention'' and ``anthropomorphize'' synonymously.}
+        over, the robot goes wrong but recognizes its mistake and repairs. We
+        expect this to be perceived (explicitly) as \textit{``to err is
+        human''}, and (implicitly) as the robot being endowed with a certain
+        level of introspective capabilities (it was able to recognize its own
+        error). In this condition, we assume increased attributions of
+        human-likeness to the robot.\footnote{The attribution of human-likeness
+            to a robot is hereafter labeled as \textit{anthropomorphic
+        projections}.}
 
@@
 in general a robot that behaves unexpectedly from time to time can promote
-engagement and lead children to attribute intention to it. \cite{short_no_2010}
-found that participants anthropomorphize a cheating robot more than a robot that
-always behaves fairly, and also evaluate the interaction as more engaging. Based
+engagement and lead children to attribute intention to it. Based
 on the related work we formulate the following two hypotheses:
@@
 
-    \item[Hypothesis 2:] Children perceive a robot that shows intention or
-        cognitive abilities as more human-like than a robot that appears to have
-        a system error, \ie the disobeying robot and the robot that makes a
-        mistake will be more anthropomorphized than the robot that gets lost
-        (between subjects variable).
+    \item[Hypothesis 2:] Children perceive a robot that (tentatively) displays
+        intention or cognitive abilities as more human-like than a robot that
+        appears to have a system error, \ie the disobeying robot and the robot
+        that makes a mistake will be more anthropomorphized than the robot that
+        gets lost (between subjects variable).
 
@@
 we would like to bridge things together and, relying on the concept of an
-\textbf{anthropomorphism index} introduced by~\cite{fink2014dynamics}, build a
+\textbf{anthropomorphism index}, build a
 compound metric that considers both children's perception and interaction
@@
 \subsection{The Ranger robot}
-
-We used the same prototype as in the previous study, and Ranger was again
-controlled by a human Wizard, who was in the same room (see
-Figure~\ref{fig:domino-setup}). This was to ensure that the Wizard could see
-children's interaction and hear their commands to the robot without any delay.
 
@@
 
-The basic idea of the interaction scenario was that there are two children who
-play domino together, with the help of the robotic box Ranger. The scenario
-setup is displayed in Figure~\ref{fig:domino-setup}. The challenge is that the
-tiles of the domino are distributed in the room, hidden behind three beanbags,
-and while one child -- \textit{the searcher} -- searches for the right tile, the
-other child -- \textit{the receiver} -- is asked to stay in a play tent. There
-is a ``river'' (play carpet) in between the two children that we told them they
-cannot cross and therefore they need the robot to transport the domino tiles
-between them.
+The interaction scenario consisted in two children who play domino together,
+with the help of the robotic box Ranger. The scenario setup is displayed in
+Figure~\ref{fig:domino-setup}. The challenge is that the tiles of the domino are
+distributed in the room, hidden behind three beanbags, and while one child --
+\textit{the searcher} -- searches for the right tile, the other child --
+\textit{the receiver} -- is asked to stay in a play tent. There is a ``river''
+(play carpet) in between the two children that we told them they cannot cross
+and therefore they need the robot to transport the domino tiles between them.
+
+The robot was controlled by a human wizard, who was in the same room (see
+Figure~\ref{fig:domino-setup}). This was to ensure that the wizard could see
+children's interaction and hear their commands to the robot without any delay.
+Only one group asked at the beginning of the experiment if the wizard was the
+one actually controlling the robot. This did not seem to subsequently influence
+their behaviour.
 
 We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
-pictures of cartoon farm animals: cow, sheep, hen, donkey, duck, pig, rabbit. The
-pictures were taken from a commercially available domino game adapted to the age
-of the children (produced by Djeco, advised age 3+).
+pictures of cartoon farm animals: cow, sheep, hen, donkey, duck, pig, rabbit.
+The pictures were taken from a commercially available domino game adapted to the
+age of the children (produced by Djeco, advised age 3+).
 
-To start the game (divided in several \textit{runs} that correspond each to the
+To start the game (divided in several \emph{runs} that correspond each to the
 delivery and assembling of one domino tile), there is already one domino tile in
-front of the tent, where \textit{the receiver} child stays and assembles the
-domino chain. \textit{The receiver} child asks \textit{the searcher} child for a
-specific tile, \eg a tile with a donkey, \textit{the searcher} searches for the
-respective tile, sits down on the next beanbag, and asks the robot to come over.
-The Ranger robot is first located next to the tent, then, when called by the
-\textit{searcher} it starts moving, crosses the river carpet, and comes over to
-the \textit{searcher} on the beanbag. The \textit{searcher} child puts the
-domino tile into the robotic box, and the robot then goes back to \textit{the
-receiver} child in the tent. Then, \textit{the receiver} takes out the domino
-tile from the robot, and puts the two tiles together. The first \textit{run} is
-over, and a new \textit{run} starts, when \textit{the receiver} asks \textit{the
-searcher} for the next domino tile.
+front of the tent, where the receiver child stays and assembles the domino
+chain. The receiver child asks the searcher child for a specific tile, \eg a
+tile with a donkey, the searcher searches for the respective tile, sits down on
+the next beanbag, and asks the robot to come over.  The Ranger robot is first
+located next to the tent, then, when called by the searcher it starts moving,
+crosses the river carpet, and comes over to the searcher on the beanbag. The
+searcher child puts the domino tile into the robotic box, and the robot then
+goes back to the receiver child in the tent. Then, the receiver takes out the
+domino tile from the robot, and puts the two tiles together. The first
+\emph{run} is over, and a new \emph{run} starts, when the receiver asks the
+searcher for the next domino tile.
 
@@
 one out of four possible behaviours: \emph{correct}, \emph{mistake}, \emph{lost}
-or \emph{disobey}.  The first 5 runs were used to set the baseline and the robot
-always behaved correctly. In the 9 remaining runs, the robot showed one of the
-misbehaviour (\emph{mistake}, \emph{lost} or \emph{disobey}) at the $3^{rd}$ and
-$4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run. The study is build as
-a between-subject study, and the type of misbehaviour was therefore always the
+or \emph{disobey}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
+the baseline and the robot always behaved correctly. The children then switched
+the roles and in the 9 remaining runs (\emph{2.1} to \emph{2.9}), the robot
+showed one of the misbehaviour (\emph{mistake}, \emph{lost} or \emph{disobey})
+at the $3^{rd}$ and $4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run
+(see Figure~\ref{fig:domino-time-active}). The study is build as a
+between-subject study, and the type of misbehaviour was therefore always the
 same for a given group.
@@
 (\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
-failures negatively impact trust).
-
-\cite{short_no_2010} also adopted a similar pattern when introducing unexpected
-robot behaviour. In their study with a robot that cheated, from the 20 rounds of
-the rock-paper-scissors game, the robot cheated three times in the middle: on
-the 4th, 8th and 15th round. The authors adjusted the interaction length so that
-the spacing and timing of the cheating was preserved.
+failures negatively impact trust). \cite{short_no_2010} also adopted a similar
+pattern when introducing unexpected robot behaviour. In their study with a robot
+that cheated, from the 20 rounds of the rock-paper-scissors game, the robot
+cheated three times in the middle: on the 4th, 8th and 15th round. The authors
+adjusted the interaction length so that the spacing and timing of the cheating
+was preserved.
 
@@
 
-In the \emph{correct} robot behaviour (baseline behaviour) consists in the
+The \emph{correct} robot behaviour (baseline behaviour) consists in the
 following states:
@@
 
+In the human-repaired conditions, the experimenter instructs the searcher child
+(after ~10 sec) to bring him/herself the domino tile to the robot.
+
 On its way back to the tent, Ranger always goes correctly. After the sender
@@
 Overall, there were 13 pairs of children (n=26) participating in the interaction
-study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45). In 11 of the
-pairs, children were friends who knew each other from kindergarten, nursery
-school or because they lived in the same neighborhood. 2 of the pairs were
-composed of brother and sister.
+study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
+French-speaking. In 11 of the pairs, children were friends who knew each other
+from kindergarten, nursery school or because they lived in the same
+neighborhood. 2 of the pairs were composed of brother and sister.
 
@@
 captured in the video recordings by annotating a set of actions, described
-below. The children's \textbf{perception of the
-robot} has been captured through audio-recorded semi-structured interviews.
+below. The children's \textbf{phenomenological perception of the robot} has been
+captured through audio-recorded semi-structured interviews which took place
+between run \emph{1.5} and \emph{2.1} and at the end of the 14 runs.
 
@@
 
-We annotated children's behavior in the video records, and coded 10 different
+We annotated children's behaviour in the video records, and coded 10 different
 actions:
@@
 annotation duration of 145 minutes. On average, one child accounted for 92
-actions (SD=23). Figure~\ref{fig:domino-time-all} shows the distribution of
-actions over the different runs, in any condition.
+actions (SD=23).
 
@@
     \centering 
-    \includegraphics[width=0.8\linewidth]{domino-time-all.pdf} 
-    \caption{\small \textbf{Number and type of actions for each run} (average for
-    one child per minute). Generally, the number of actions does not decrease over
-    time (from run 1.1 to run 2.9). The first 7 runs correspond to the
-    \textit{expected phase}, the second 7 runs correspond to the \textit{unexpected
-    phase}. Especially during run 2.3, the first time when the robot showed an
-    unexpected behavior, children tended to \textit{look} more at the experimenter.
-    During the unexpected phase, also \textit{talk} and \textit{gesture} seem to be
+    \includegraphics[width=0.9\linewidth]{domino-time-active.pdf} 
+    \caption{\small \textbf{Number and type of actions for each run} (n=480,
+        spontaneous actions, excluding \emph{explore}). Generally, the number of
+        actions does not decrease over time (from run 1.1 to run 2.9).  The
+        first 7 runs correspond to the \textit{expected phase}, the second 7
+        runs correspond to the \textit{unexpected phase}. Especially during run
+        2.3, the first time when the robot showed an unexpected behaviour,
+        children tended to \textit{look} more at the experimenter. During the
+        unexpected phase, also \textit{talk} and \textit{gesture} seem to be
         increased.}
 
-    \label{fig:domino-time-all} 
+    \label{fig:domino-time-active} 
 \end{figure*}
@@
 are spontaneous actions that were not requested but arose in the interaction.
-These actions reflect engagement, and are the only one we considered during the
-analysis (except otherwise indicated).
+These actions reflect engagement, and are the one we considered during the
+analysis. Figure~\ref{fig:domino-time-active} shows the distribution of these
+actions over the different runs, in any condition.
 
@@
 
-It is not easy to interview young children: they have a short attention span, we
-(the experimenters) are strangers to them, and they are in an unfamiliar
-environment. The pre-interview served to ``break the ice'' and during the first
-playful interaction phase, most children familiarized themselves with the
-situation.
-
-Also, children do not articulate themselves and understand questions like
-adults. We tested our interview structure and the script in a pilot-study with
-three young children, and were assisted in formulating our questions by a
-pedagogue and father of four. This helped us adapting our language and
-question-style to the 4-5 year old participants. We set up the interviews like a
+One pre-interview and two interviews (between run \emph{1.5} and \emph{2.1} and
+at the end) were conducted with the children.  We set up the interviews like a
 casual conversation / discussion, so we did not separate the two children in
@@
     \toprule
-    \textbf{Construct \emph{expectation}} \\
+    \textbf{Construct \emph{expectations}} \\
     \midrule
@@
     \toprule
-    \textbf{Ascribe cognitive abilities} \\
+    \textbf{Ascribe cognitive connections} \\
     \midrule
@@
 
-    \caption{\small Questions used during the semi-structured interviews
-    with children. The Ranger robot toy box is abbreviated with ``R''.}
+    \caption{\small Constructs and questions used during the semi-structured interviews
+    with children. The Ranger robot toy box is abbreviated with ``R''. Questions
+    related to the construct \emph{expectations} were asked during the
+    pre-interview.}
 
@@
 
-We generally needed to keep the interviews as short as possible. In designing
-our interview script and selecting relevant questions, we took inspiration from
-previous work on child-robot interaction and children's perception of robots
+In designing our interview script and selecting relevant questions, we took
+inspiration from previous work on child-robot interaction and children's
+perception of robots
 \cite{kahn_jr._robotic_2006,weiss_i_2009,leite_influence_2013}. For instance, we
-applied and adapted some of the ``constructs'' and example questions from the
-questionnaires used in \cite{kahn_jr._robotic_2006} and \cite{weiss_i_2009}. The
-authors evaluated children's perception of the robotic dog AIBO after the
-children had played with the robot. A ``construct'' addresses a specific factor
-(topic) that can be measured by several questions. For instance, the construct
-``cognitive abilities'' (called ``cognition'' in \cite{weiss_i_2009}) considers
-the robot's ability to hear and to see (perceptual skills), as attributed by the
-children. The construct ``moral standing'' and the respective question was taken
-from \cite{kahn_jr._robotic_2006}.\footnote{According to
-\cite{kahn_jr._robotic_2006}, \textit{moral} refers to considerations based on
-an artifact's physical or psychological welfare, and virtue (whether the
+applied and adapted some of the \emph{constructs} and example questions from the
+questionnaires used in \cite{kahn_jr._robotic_2006} and \cite{weiss_i_2009}. A
+\emph{construct} addresses a specific factor (topic) that can be measured by
+several questions. For instance, the construct ``cognitive connections'' (using
+Flavell's terminology~\cite{flavell1988development}) considers the robot's
+ability to hear and to see (perceptual skills), as attributed by the children.
+The construct ``moral standing'' and the respective question was taken from
+\cite{kahn_jr._robotic_2006}.\footnote{According to
+\cite{kahn_jr._robotic_2006}, \textit{moral} refers to considerations based
+on an artifact's physical or psychological welfare, and virtue (whether the
 artifact deserves care). An attribution of moral standing reflects, for
@@
 questions according to specific constructs that they evaluate (see
-Table~\ref{tab:domino-questions}). This was an adaption and extension of the
-questions and constructs used in previous work.\\
+Table~\ref{tab:domino-questions}).
 
@@
 
-Similar to how we processed interviews in the previous studies, we qualitatively
+The interviews were analyzed in a qualitative manner (we qualitatively
 transcribed interviews, \ie we did not craft a full word-by-word transcript but
-noted down any statement that was useful and relevant. This was organized in a
-spreadsheet, so to obtain an overview of the different replies to a question.
-The interviews were analyzed in a qualitative manner.
+noted down any statement that was useful and relevant) and used to compute the
+anthropomorphism index presented below.
 
@@
 
-we can investigate how far these two types of data can
-be used to understand children's engagement in the interaction and how far they
-anthropomorphize the robot. We would like to develop a toolkit that considers
-both children's perception and interaction, in order to measure anthropomorphism
-(as a special type of human-like engagement with the robot).
-
 There are different possibilities to measure engagement in HRI, depending on the
-specific research question and context. Metrics to measure behavioral engagement
+specific research question and context. Metrics to measure behavioural engagement
 in the interaction include, for instance, conversation analysis (\eg used in
@@
 questions that allowed children to justify and elaborate their answers. We have
-chosen a similar approach that considers both children's behavioral and
+chosen a similar approach that considers both children's behavioural and
 emotional engagement.
@@
 children look at the experimenter when they are surprised and seek for help.
-This behavior reflects that they want to make sense of the robot's behavior and
+This behaviour reflects that they want to make sense of the robot's behaviour and
 that they notice it as ``strange''. Further, we can take into account how they
@@
 to bring both children's perception of the robot (post-measurement) and their
-behavior toward it (in-the-moment measurement) together. By doing so, we would
+behaviour toward it (in-the-moment measurement) together. By doing so, we would
 like to obtain a qualitative \textbf{anthropomorphism
-index}~\cite{fink2014dynamics}. We quantify the index by giving 1 point for each
-anthropomorphic perception of the robot (max.  13 points) and for specific kinds
-of human-like behavior toward the robot (max.  3 points). The index included the
+index}~\cite{fink2014dynamics}. We quantify the index by attributing points for each
+anthropomorphic \emph{perception} of the robot (max.  13 points) and for specific kinds
+of human-like \emph{behaviour} toward the robot (max.  3 points). The index included the
 following aspects:\\
@@
 	\item Other \textbf{anthropomorphic statements}: \textit{0-3 points}\\ 
-	(1 point for anthropomorphic reason for Ranger's misbehavior; 2 points for anthropomorphic reason for not leaving Ranger alone) 
+	(1 point for anthropomorphic reason for Ranger's misbehaviour; 2 points for anthropomorphic reason for not leaving Ranger alone) 
 \end{itemize}
 
-\textbf{Behavior: \textit{(max. 3 points)}}
+\textbf{behaviour: \textit{(max. 3 points)}}
 \begin{itemize}
@@
 There are certainly limitations to this scoring scheme. For instance, the
-balance between perception and behavior aspects is questionable (13 to 3
+balance between perception and behaviour aspects is questionable (13 to 3
 points). Also, we did not consistently assign 1 point to each item, but assigned
@@
 items reflect a higher level of anthropomorphic perception of the robot than
-others (for instance, ascribing the ability to see an hear was suggested by our
+others (for instance, ascribing the ability to see and hear was suggested by our
 study setup, and we cannot be sure that it really reflects anthropomorphism).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Findings}
+\section{Main Findings}
 
-\subsection{General considerations}
+\subsection{Manipulation check: Negligible impact of the conditions}
 
-\subsubsection{Engagement}
+As stated in the introduction, we had hypothesized that the \textit{disobey}
+behaviour is perceived as the robot intentionally not doing what it should do.
+The \textit{mistake} behaviour was intended to show that the robot can do a
+mistake but is aware of it and able to repair its mistake, which should also
+lead to some perception of intentionality.  Contrary, we expected that the
+\textit{lost} condition is perceived as a malfunction or bug of the robot.  In
+the second interview, after the robot had misbehaved, we asked children whether
+the robot always did what they wanted it to do. Most children disagreed and said
+they noticed something strange. However, there were some children who gave a
+positive answer, suggesting that they found the robot always did what they
+wanted it to do. This was a surprise. Had they not noticed the robot's
+misbehaviour? Why not? On one hand, we found that children sometimes gave
+contradictory replies when asked the same question twice. This is difficult to
+interpret. On the other hand, children may have a general tendency to please
+adults \cite{leite_long-term_2013}, and it could be the case that some were too
+shy to tell us that the robot did something strange.
 
-\subsubsection{Attribution of higher cognitive skills}
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1.0\linewidth]{domino-why-misbehavior.pdf}   
+    \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
+    to the question why the robot did not come over, and we received 37 answers.
+    This question shows that children did not necessarily interpret the misbehaviour
+    in the way we had assumed.}
+
+    \label{fig:domino-why-misbehaviour}
+\end{figure}
+
+We nevertheless asked children why they thought the robot had not always come
+over to them. 4 of the children did not reply. The remaining ones gave a variety
+of reasons (Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9
+of 37 replies) was that the robot is somehow \textit{unpredictable} in what it
+is doing and that it could go \textit{no matter where}\footnote{We translated
+children's answers from French to English. For some expressions the meaning
+and connotation of an expression may not be the same. We understand
+\textit{``partir dans tous les sens''} as ``to go off in all possible
+directions'' and hence interpret this reflects viewing the robot as being
+unpredictable.} because \textit{``with robots you have these kind of problems,
+they do no matter what''}. 8 replies concerned \textit{technical problems}
+(including \textit{broken parts}), suggesting that children perceived the
+misbehaviour as unintended by the robot. 2 of the children who had interacted
+with the disobeying robot said Ranger was \textit{angry}, which none of the
+children in other conditions replied. Several children ascribed intentionality
+to Ranger explaining that it \textit{did not want to continue} carrying domino
+tiles or that it \textit{made a mistake / did something silly}\footnote{We
+understood \textit{``faire une bêtise''} as ``to do a silly thing'' in the sense
+of making a mistake.}.
+
+Overall, we can notice that not all children perceived the misbehaviour of the
+robot as we had intended and we have to keep this in mind while interpreting the
+data. Also \cite{leite_long-term_2013} found in her study that when children did
+not understand an action of the robot, they tended to view it as a mistake,
+rather than interpreting the robot's behaviour as a deliberative action.
+
+%	\textit{``the supportive behaviour ``Play Bad Move'' was not completely
+%	understood as a deliberative action of the robot, but rather as a
+%	mistake''}.
+
+In our case, it is not easy to make a clear statement about how each of the
+manipulations was perceived by the children.  Similar to how people reacted to
+the cheating robot in the study of \cite{short_no_2010}, most children showed
+surprise, were amused, sometimes confused, or occasionally slightly angry (\eg
+two boys tended to shout to the robot after it had disobeyed). The
+\textit{disobeying} robot seemed to evoke the strongest reactions, partly with a
+negative implication: later three of the children in this condition stated they
+would not accept Ranger as a friend \textit{because it did not always come over
+when they asked it to come over}. \cite{short_no_2010} described a similar
+implication of the robot cheating behaviour: participants made unfavorable
+character attributions to the cheating robot, so the robot's actions affected
+perceptions of the robot as ``fair'' and ``honest''.
+
+%	\cite{short_no_2010} found that participants often had an emotional reaction
+%	to the robot's behaviour and made unfavorable character attributions to the
+%	cheating robot. The robot's actions affected perceptions of the robot as
+%	``fair'' and ``honest''. Qualitatively, the authors found that participants'
+%	reactions in the verbal cheat case tended more towards confusion, while
+%	their reactions to the action cheat were more exaggerated, showing surprise,
+%	amusement, and occasionally anger.
+
+%	\cite{short_no_2010} found that participants who saw the action cheat
+%	mentioned cheating, while the participants who saw the verbal cheat
+%	frequently described it as a mistake or malfunction, while only sometimes
+%	calling it cheating.
+
+\subsection{Engagement}
+
+In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
+here. As mentioned before, the findings here do not directly address the issues
+of long-term usage but concern short-term \textit{engagement}, which is a
+pre-requisite for long-term usage.
+
+The huge proportion of \textit{explore} actions (52~\% of all coded actions)
+already suggests that children were generally engaged in the interaction, and
+most of the time carefully observed what the robot did. When considering the
+actions \textit{explore, gesture, look, misuse, show, talk}, and \textit{touch}
+as \textbf{engagement actions}, 1699 of the 2354 actions reflected engagement
+(72~\%). This indicates that overall children were very engaged in the
+interaction with the robot. Furthermore, data suggests that the robot in the
+\textit{mistake} and \textit{lost} condition were more engaging for children
+(each 75~\% of the actions reflected engagement) than the robot in the
+\textit{disobey} condition (66~\% reflected engagement). The statistical
+analysis supports this: An ANOVA indicates that there was a significant effect
+of robot behaviour on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
+\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
+indicate that the mean score for \textit{explore} in the \textit{disobey}
+condition is significantly different from the score in the \textit{mistake} and
+\textit{lost} condition. This suggests that children explored the disobeying
+robot less\footnote{It is surprising that the disobeying robot was explored
+less. One may expect that the disobeying robot might better attract
+children's attention because it faces the searcher child and uses fairly
+strong audio and light cues as compared to the other behaviours.}. For
+\textit{look}, the only significant difference is found between the mean
+scores of \textit{lost} and \textit{disobey}. Data suggests that when the
+robot is lost, children look more often at the experimenter than when the
+robot disobeys. The other actions were not found to differ significantly
+between the robot behaviour conditions.
+
+Overall, was there an effect on engagement when the robot misbehaved? We compare
+children's engagement during the interaction phase with the expected robot
+behaviour and during the interaction phase with the unexpectedly behaving robot.
+A statistical analysis revealed a significant difference between the average of
+engagement actions carried out during the first 7 runs (correct robot behaviour)
+and during the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1,
+p=.03). In all three conditions, children carried out more engagement
+actions with the unexpectedly behaving robot. No interaction effect was found
+between the two phases of interaction (expected / unexpected) and condition
+(F(2,36)=1.2, p=.31). In general, this finding supports our first hypothesis:
+children show more engagement toward a robot that behaves unexpectedly from time
+to time compared to a robot that always behaves correctly.
+
+\subsection{Attribution of higher cognitive skills}
+
 \paragraph{Intentionality}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\linewidth]{domino-intention.pdf}
+    \caption{\small \textbf{Attribution of
+        intention to Ranger.} Children were asked these
+        questions at both interviews. Concerning question (a), there are no remarkable
+        differences in children's responses given in the \textit{first} and
+        \textit{second} interview.  Children tend to think Ranger does always
+        obey to them, even after it misbehaved (\textit{second} part). There is
+        however a small difference in the responses to question (b).
+        After the robot misbehaved, 8 children think the robot could do
+        something silly whereas first, only 3 children answered like this.}
+
+    \label{fig:domino-intention}
+
+\end{figure}
+
+One of the central points of this study was to investigate to what degree
+children attribute intention and cognitive abilities to the robot.  In the first
+interview after children had interacted with the correctly behaving robot we
+asked three questions to assess how far they ascribe \textbf{intention} to it
+(see questionnaire items in Table~\ref{tab:domino-questions},
+page~\pageref{tab:domino-questions}). One of these questions was whether they
+believed Ranger could go out the door by itself. They majority of 16 children
+answered negatively, which suggests that they initially do not ascribe intention
+to the robot. The two other questions were whether Ranger would always obey and
+whether Ranger could do a silly thing (Figure~\ref{fig:domino-intention}). These
+two questions were asked again later after children had interacted with the
+unexpectedly behaving robot.
+
+%	With these recurring questions we wanted to see whether children had changed
+%	their mind in terms of ascribing intention to Ranger (and whether the
+%	unexpected robot behaviour had caused this effect). This comparison turned
+%	out to be difficult, however.
+
+Overall, in the first interview 12 of the 26 children believed Ranger does
+always obey to them. Asked whether Ranger could do something silly, the great
+majority of 21 children replied negatively. We can summarize that after children
+had interacted with the \textbf{correctly behaving robot} the majority does
+\textbf{not ascribe intention} to the robot.
+
+After they had interacted with the misbehaving robot, we asked children again.
+Now, still 11 children (previously 12) believed Ranger would always obey to
+them. When analyzing the answers of each child separately, there were 2 children
+in the \textit{disobey} condition that changed their answer from \textit{yes} to
+\textit{no}; however also 1 child in the \textit{lost} condition that switched
+their answer in the opposite way (strangely). There was a more remarkable change
+when asking children whether Ranger could do something silly. In the second
+interview, 8 children (previously~3) answered Ranger could do something silly. 1
+child in the \textit{disobey} condition had changed their answer, and each 2 in
+the \textit{mistake} and \textit{lost} condition.
+
+We can summarize that even with the \textbf{unexpectedly behaving robot}
+children do \textbf{not necessarily ascribe intention} to the robot. The
+unexpected robot behaviour impacted only some children's attributions of
+intention to the robot.  It seemed that some children did not interpret the
+robot's misbehaviour as intentional but more like a technical problem or
+mistake. For instance, even after the robot misbehaved by \textit{disobeying},
+the majority of the children in this condition was still convinced that the
+robot could not do a silly thing.  It it interesting to note that children tend
+to ascribe cognitive abilities to the robot, like the ability to see and hear
+but not intention. We interpret that children may perceive the robot as being
+able to process sensory information but that it is not able to make decisions on
+its own.
+
 \paragraph{Emotions}
+
+We examined whether children attributed \textbf{feelings} to the robot by asking
+them (once at the end of the experiment) if they thought that Ranger can feel
+happy or sad sometimes. The great majority of
+children (21 of 26) gave a positive answer. Only 2 children who had interacted
+with the \textit{disobeying} robot did not believe that Ranger has feelings and
+another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
+all. Overall, data suggests that \textbf{children attributed emotional states}
+to the robot. Asked for more details, several children answered that it is
+through its colors and sounds that the robot shows a feeling. Most children said
+that they could make the robot feel happy by playing with it and putting a
+domino tile inside the box. This may also be a reflection of their own feelings,
+projected on the robot.  More than half of the children (14 of 26) agreed Ranger
+can be their friend. We did not ask about what being a friend means to them but
+as children generally liked playing with the robot, this may be linked to each
+other. We can note that children \textbf{ascribe feelings to the robot and
+partly accept that it can be a ``friend''}.
 
@@
 children if it would be alright to leave Ranger alone at home (\eg during two
-weeks when they go on a vacation) (Figure~\ref{fig:domino-leave-alone}). The great
-majority of 20 children responded negatively. Asked why, children gave a variety
-of answers that we classified into 7 categories. With 5 replies, the most common answer was
-that the robot ``could do something silly'' (\emph{``faire une bêtise''}). Some
-other children simply answered they would like to take it with them. Others
-were afraid that the Ranger ``would not find its way'' or ``may be taken
-away by someone''. 2 children believed Ranger is sad when left alone and 1
-child responded the robot would try to escape. Interestingly, and while we
-intuitively expected many children to fear that the robot would be sad if
-left alone, only 2 expressed a moral position, while most of the others
-actually expressed several forms of distrust towards the robot: \emph{it's
-not alright to leave the robot alone, not because it is morally incorrect,
-but because we do not trust the robot to remain still}. This shows that things
-must be put into perspective and even young children do not consider our robot
-as an intentional agent, not to say a social agent.
+weeks when they go on a vacation) (Figure~\ref{fig:domino-leave-alone}). The
+great majority of 20 children responded negatively. Asked why, children gave a
+variety of answers that we classified into 7 categories. With 5 replies, the
+most common answer was that the robot ``could do something silly''. Some other
+children simply answered they would like to take it with them. Others were
+afraid that the Ranger ``would not find its way'' or ``may be taken away by
+someone''. 2 children believed Ranger is sad when left alone and 1 child
+responded the robot would try to escape. Interestingly, and while we intuitively
+expected many children to fear that the robot would be sad if left alone, only 2
+expressed a moral position, while most of the others actually expressed several
+forms of distrust towards the robot, that could be phrase like: it is not
+alright to leave the robot alone, not because it is morally incorrect, but
+because we do not trust the robot to remain still. This shows that things must
+be put into perspective and even young children do not automatically consider a
+so-called social robot as an actual social agent.
 
@@
     \centering 
-    \includegraphics[width=0.9\linewidth]{domino-leave-why.pdf}
+    \includegraphics[width=1.0\linewidth]{domino-leave-why.pdf}
     \caption{\small Attributions of moral
@@
 
-\subsection{Manipulation check: Negligable impact of the conditions}
+\subsection{Anthropomorphic projections and social engagement}
 
-\subsection{Inter-subject and inter-group differences}
+The anthropomorphism index expresses to what extent children engaged with Ranger
+in a human-like way, both in terms of their behaviour toward the robot and their
+perception of the robot. We present here findings on a pair (group) level.
 
-\subsection{Anthropomorphic projections and social engagement}
+To obtain the anthropomorphism index for a pair, we first calculated the index
+per child and then took the average of the two children in one group.  The group
+indexes varied between 3.25 and 10.75 points with an average of 7.5 points
+(SD~=~2.5), which is 47~\% of the maximum possible index of 16 points.
+Intra-group variations were interesting: In 7 of the 13 groups, the
+anthropomorphism indexes for both children were similar (difference less than
+1.5 points), which means that both children anthropomorphized the robot to a
+similar degree. This agreement among children happened for both higher and lower
+indexes. In 6 of the 13 groups, the anthropomorphism indexes varied in more than
+2 points, which means that one of the children anthropomorphized the robot more
+than the other one.
+
+On average, Ranger was moderately anthropomorphized by the
+children.\footnote{However, as our developed anthropomorphism score is relative,
+we cannot really make a claim about what a difference of \textit{+} or \textit{-
+1} point means.} 8 of the 13 groups had an index of 8 or higher, evenly spread
+over the three conditions (Table~\ref{tab:domino-anth-score}). However, the mean
+index of anthropomorphism in the three conditions varied, with the
+\textit{mistake} and \textit{lost} condition leading to a higher index than the
+\textit{disobey} condition. This finding suggests that the disobeying robot was
+less anthropomorphized than the other two robot behaviours, which speaks against
+our second hypothesis. We had expected that the disobeying behaviour is
+perceived as an intentional action which we assumed would lead to increased
+anthropomorphism. This was not the case. The slight difference between the
+\textit{lost} and \textit{mistake} robot was also expected in the opposite
+direction. It could be that the robot's ``helplessness'' led to this. With the
+lost robot, children looked more often at the experimenter than in the other
+condition, which suggests that they could not fully make sense of the robot's
+behaviour. The fact of not being able to understand (and hence predict) a
+robot's behaviour is likely to increase anthropomorphism.\footnote{One of the
+cognitive / psychological explanations for anthropomorphism is that people
+want to make sense of something they do not understand and then tend to
+anthropomorphize this something (human traits are a good source of making
+attributions because this is what people understand best -- themselves and
+other humans). For more details the reader may refer to
+\cite{epley_seeing_2007}.}
+
+\begin{table}[ht!]
+    \centering
+    \footnotesize
+    \begin{tabular}{lccc}
+        \toprule
+        & M & SD & groups with index > 8 \\
+        \midrule
+
+        \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
+        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
+        \textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
+        \bottomrule
+    \end{tabular}
+    \caption{\textbf{Anthropomorphism index.} The maximum possible index was 16. The
+    \textit{lost} robot elicits the highest index, which suggests that it is
+    anthropomorphized more. Contrary to our hypothesis, data suggests that the
+    \textit{disobeying} robot is anthropomorphized less but the \textit{lost} robot
+    more.}
+
+    \label{tab:domino-anth-score}       % Give a unique label
+\end{table}
+
+But to what extent is the human-like interaction related to perceiving the robot
+as human-like? Do children who interact a lot and are probably more engaged with
+the robot also perceive the robot as more human-like? This was what we
+hypothesized. Data suggests the opposite, however. As shown in
+Figure~\ref{fig:domino-anthropo-interaction}, we found a significant
+\textit{negative} correlation between the count of engagement actions (per
+group) and the qualitative anthropomorphism index (r(11)=-0.56, p=.05).
+
+%	(b=-.05, t(11)=-2.22, p=.048).
+
+The overall model with the count of engagement actions (per group) predicts a
+significant proportion of the qualitative anthropomorphism index (adjusted
+R$^2$=.25, F(1,11)=4.9, p=.05). This means that the more a group showed
+engagement in the interaction, the less they anthropomorphized the robot. This
+is a key results, which was against our initial assumption. How can we interpret
+this? It may be that children who interact more with the robot understand better
+how it works, they are more familiar with it, and as such the robot appears less
+``mystical'' to them, so there is not a big need to anthropomorphize it. On the
+contrary, the cluster of groups that do not interact much but anthropomorphize
+the robot more, is quite homogeneous. The negative correlation between the
+number of engagement actions and the anthropomorphism index suggests that
+children who interact more with the robot tend to anthropomorphize it less. This
+implies that anthropomorphism could fade out after some time (or rather after
+some interaction). This evokes the question how far anthropomorphism (as a
+special kind of social engagement) really helps in sustaining interaction. This
+is a critical point because most of the short-term investigations suggest that
+anthropomorphic design and human social cues emitted by a robot foster
+engagement and acceptance. What if this is not true for continued interaction,
+and thus for the long-term?  We have to be careful about our interpretation, due
+to the small sample size with which we obtained these findings. We suggest to
+investigate the aspect further in future research.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.8\columnwidth]{domino-correlation.pdf}
+
+    \caption[Correlation of Anthropomorphic Perception of the Robot and
+    Interaction]{\small \textbf{Correlation of anthropomorphic perception of the
+    robot and engagement actions.} A scatter plot of the count of engagement
+    actions (without explore) and the \textit{anthropomorphic perception} (score per
+    group) shows a negative correlation. The score for the anthropomorphic
+    perception (\textit{y-axis}) does not take into account the behavioural aspect of
+    the anthropomorphism index, as this is part of the interaction
+    (\textit{x-axis}).  There seem to be two clusters of groups: those who interact
+    more with the robot and anthropomorphize it less, and those who interact less
+    but anthropomorphize the robot more.}
+
+    \label{fig:domino-anthropo-interaction}
+\end{figure}
+
+Our data on the anthropomorphism index also suggest \textbf{qualitative gender
+differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
+SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
+SD=2.4). (Interestingly, as it was mentioned before, boys interacted slightly
+more with the robot than girls; though not significantly. This is
+counter-intuitive concerning the negative correlation between amount of
+interaction with the robot and anthropomorphism tendency.) It would be
+interesting to investigate in more detail whether boys are more prone to
+anthropomophize a robot than girls.\footnote{Findings presented in
+\cite{schermerhorn_robot_2008} suggested similar gender differences. In their
+study, males tended to think of the robot as more human-like and accordingly
+showed more ``social facilitation'' than females, who perceived the robot as
+more machine-like.}
+
+\paragraph{Summary}
+
+The established \textit{anthropomorphism index} suggests that children tend to
+conditionally anthropomorphize the robot. Higher indexes of anthropomorphism
+were found in the \textit{lost} and \textit{mistake} condition which was against
+our hypothesis. Interestingly, data suggests a significant negative correlation
+of engagement and anthropomorphism index. It appears that groups who interacted
+more with the robot perceived it as less-humanlike. This raises the question to
+what extent anthropomorphic perceptions of a robot can last over time, and with
+increasing interaction experience.
 
@@
 
-\begin{itemize}
-\item It’s a challenge to interview young children ... 
-\item Huge differences between the children and groups make it hard to draw general conclusions
-\item Children did not perceive the 3 different conditions as we did not perceive the 3 different conditions as we expected
-\item Coding scheme: “explore” category was not well defined
-\end{itemize}
+We found that in a playful scenario where 4-5 year old children play domino
+together with a robot, the robot seems to be more engaging when it shows some
+misbehaviour compared to when it always behaves as expected. However, we
+cannot say if this effect holds also after novelty has worn off.
+
+From what we
+have seen in the Domino Study, we have a rough estimate of how children react
+and relate to a robot that behaves unexpectedly from time to time. They are
+mostly surprised, laugh at the robot, and they tend to be more engaged and
+playful. However, they are also confused and cannot really make sense of the
+robot's strange behaviour. We also cannot conclusively tell apart whether children perceived
+the unexpected robot behaviour entirely as a malfunction (something that happens
+to a machine) or as being intended and based on a motivation (something related
+to a social entity). Children stated both, when asked why the robot had
+misbehaved. Some referred to \textit{``a technical problem''} while others said
+the robot \textit{``is tired''} or it \textit{``doesn't want to carry domino
+tiles any more but rather go on a tour outside''}. Maybe our manipulations were
+not as clearly designed as we expected. There is always some freedom in how
+things are interpreted -- especially with young children.  Certainly more work
+needs to be done to investigate which robot behaviour is most beneficial for
+young children and can promote their engagement and motivation to interact with
+Ranger over extended periods of time.
+
+%	Whereas a cheating opponent is acting out of a desire to win the game, a
+%	malfunction, on the other hand, is entirely accidental, and could be the
+%	fault of physical design or faulty programming, and can even occur entirely
+%	without involvement on the part of the robot. \textit{``A malfunction is
+%	something that happens to a machine, while a social entity that can cheat
+%	has motivations and desires.'' Short et al.}
+
+\subsection{Limitations}
+
+This study and the results have several limitations.  First, we did not have a
+real control group in which the robot always behaved correctly. Instead, we took
+the first interaction phase as a reference for how children interact with the
+correctly behaving robot.  Also, the sample size of 13 groups was small. There
+were  variations in the data due to the individual differences of children. More
+data could have allowed for a better comparison between the conditions.
+
+With the manipulation of the robot behaviour we were able to surprise children.
+However, it is questionable how often the same type of behaviour manipulation
+leads to surprise. Moreover, our experiment was a short-term interaction study
+while we try to make statements about how to sustain long-term engagement. This
+is critical but not unusual. Long-term HRI studies with young children are
+extremely rare as they are difficult to set up as well as time and resource
+consuming \cite{leite_long-term_2013}. Nevertheless, we could have probably
+improved our study by setting up several short interaction sessions spreading
+over several weeks. At the end of each session we could have asked whether
+children want to play again with the robot. Such a study could have helped to
+investigate the long-term interaction with the robot and the impact of the
+behavioural variances.
+
+\subsection{Lessons Learned}
+
+One of the lessons learned is that it is difficult to set up a controlled lab
+study with young children. Children are not like adults who patiently
+participate in a 45-minutes experiment and then get some reward in the end. On
+one hand, an experiment with children should not be boring for them, but on the
+other hand, you would like to seriously collect some data. A lot of the
+challenges we experienced are also described in \cite{ros_child-robot_2011}. One
+of the most difficult parts turned out to be the interviews with the children.
+We need to be careful to not over interpret some of their answers. Some children
+seem to not have a clear opinion and partly contradict themselves. These answers
+are not easy to interpret. An interview script including the questions need to
+be designed very carefully, and should definitely be tested beforehand with the
+respective age group.
+
+Overall, it appears that when trying to study something in more detail, such as
+the manipulation of robot behaviour, 4-5 year old children may be too young. But
+when trying to evaluate a more general approach, the design of a prototype, or
+an interaction scenario, children are a very good choice. They say things as
+they are and react very naturally, when compared to adults, who may reply more
+socially desired.
+
+\paragraph{Summary}
+
+In this study, we investigated the effect of unexpected robot behaviour on
+children's engagement in interacting with Ranger and on their perception of the
+robot.  Our first hypothesis finds support: children show more engagement toward
+a robot that behaves unexpectedly from time to time. Further, different types of
+unexpected behaviour may have a different effect, and therefore the behaviour
+manipulation needs to be designed with care.
+We did not find support for our second hypothesis which stated that children
+perceive a robot showing intention or cognitive abilities as more human-like
+than a robot that appears to have a system error. This may be due to the study
+setup and the fact that children did not interpret the robot misbehaviour in the
+conceived way. Our findings seem to suggest the contrary to our hypothesis. A
+robot that appeared to do a \textit{mistake} or to be \textit{lost} was more
+anthropomorphized than a robot that \textit{disobeyed}. But again, as children
+may have misinterpreted these robot behaviours we cannot be sure about this
+result.
+
+Another outcome of this study is the initial development and first tryout of an
+\textbf{anthropomorphism index}. This index considers both behavioural and
+perception aspects and is able to indicate lower and higher levels of
+anthropomorphism along this continuous index. At the moment, there is no such
+index available that quantifies anthropomorphism along a scale and there is no
+technique that combines behaviour and perception. In the future, we will need to refine
+and improve this scale. For instance, we need to identify the specific factors
+that should be included as measurement points in such a scale, for both aspects
+(behaviour and perception). Also, we need to think about how to balance the two
+aspects appropriately. Probably, also characteristics of the person, the robot,
+and the situation need to be considered.
 

### 2014-09-16 paper.tex
Added abstract + layout changes

@@
 
+Presented is a study on the impact of unexpected robot behaviours on the
+perception of a robot by children and their subsequent engagement in a playful interaction.
+We propose an original analysis methodology which blends behavioural cues and
+reported phenomenological perceptions into a compound \emph{index}.
+
+While we found only a limited recognition of the different misbehaviours of the
+robot that we attribute to the age of the subject (M=4.46), interesting findings
+include a sustained engagement level, an unexpectedly low level of attribution
+of higher cognitive abilities and a \emph{negative} correlation between
+anthropomorphic projections and actual behavioural engagement.
+
+Besides, this study operationalizes for the first time the
+\emph{anthropomorphism index} proposed by~\cite{fink2014dynamics}, which proves a
+valuable tool to assess qualitative psycho-behavioural episodes occurring during
+human-robot interaction.
+
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction: Towards Sustained Engagement}
+\section{Introduction}
+\subsection{Towards Sustained Engagement}
 
@@
 
-\subsection{The Ranger robot}
-
 \subsection{The Domino scenario}
@@
 searcher for the next domino tile.
+
+\subsubsection{The Ranger robot}
 
@@
 
-We annotated children's behaviour in the video records, and coded 10 different
-actions:
-
-\begin{itemize}
-
-    \item \textbf{Explore (ex)}: when children actively try to find out what the
-        robot is doing (\eg by looking under the box); attentively watch or
-        observe the robot (\eg attentively waiting for the box to show a
-        reaction); experiment with the robot to figure out how it works (\eg put
-        hands in front or inside of the box to see what happens);
-
-    \item \textbf{Misuse (mis)}: when children kick the robot, poke it in its
-        ``eye'', try to climb on or inside the box, drive / push the robot
-        around, stop the robot's wheels with a foot;
-
-    \item \textbf{Put domino (put)}: when a domino tile is put inside the box;
-
-    \item \textbf{Remove domino (rem)}: when a domino tile is removed from the
-        box;
-
-    \item \textbf{Gesture (ges)}: when gestures are used to communicate /
-        interact with the robot (\eg pointing gestures, waving at the robot);
-
-    \item \textbf{Touch (touch)}: when the box is touched (\eg petted or
-        caressed);
-
-    \item \textbf{Show (show)}: when a child shows something to the robot (\eg
-        by holding a domino tile in front of its eyes);
-
-    \item \textbf{Call (call)}: when a child calls the robot to come over;
-
-    \item \textbf{Talk (talk)}: when a child directly talks to the robot (using
-        direct speech) besides calling the robot;
-
-    \item \textbf{Look (look)}:	when a child looks at the experimenter due to
-        confusion caused by the robot; look is not coded when the experimenter
-        asks a question to the child;
-
-\end{itemize}
-
-In total, we obtained 2354 distinct actions which summed up to a total
-annotation duration of 145 minutes. On average, one child accounted for 92
-actions (SD=23).
-
 \begin{figure*}[ht!] 
@@
 
+We annotated children's behaviour in the video records, and coded 10 different
+actions:
+
+\begin{itemize}
+
+    \item \textbf{Explore (ex)}: when children actively try to find out what the
+        robot is doing (\eg by looking under the box); attentively watch or
+        observe the robot (\eg attentively waiting for the box to show a
+        reaction); experiment with the robot to figure out how it works (\eg put
+        hands in front or inside of the box to see what happens);
+
+    \item \textbf{Misuse (mis)}: when children kick the robot, poke it in its
+        ``eye'', try to climb on or inside the box, drive / push the robot
+        around, stop the robot's wheels with a foot;
+
+    \item \textbf{Put domino (put)}: when a domino tile is put inside the box;
+
+    \item \textbf{Remove domino (rem)}: when a domino tile is removed from the
+        box;
+
+    \item \textbf{Gesture (ges)}: when gestures are used to communicate /
+        interact with the robot (\eg pointing gestures, waving at the robot);
+
+    \item \textbf{Touch (touch)}: when the box is touched (\eg petted or
+        caressed);
+
+    \item \textbf{Show (show)}: when a child shows something to the robot (\eg
+        by holding a domino tile in front of its eyes);
+
+    \item \textbf{Call (call)}: when a child calls the robot to come over;
+
+    \item \textbf{Talk (talk)}: when a child directly talks to the robot (using
+        direct speech) besides calling the robot;
+
+    \item \textbf{Look (look)}:	when a child looks at the experimenter due to
+        confusion caused by the robot; look is not coded when the experimenter
+        asks a question to the child;
+
+\end{itemize}
+
+In total, we obtained 2354 distinct actions which summed up to a total
+annotation duration of 145 minutes. On average, one child accounted for 92
+actions (SD=23).
+
 The actions \textit{put, remove} and \textit{call} were ``requested'' actions
@@
 
-\begin{table}[h]
+\begin{table}[h!t]
 \centering

### 2014-09-16 paper.tex
2nd pass

@@
 
-\textbf{Engagement} is a metric that has been extensively used and studied both
+\emph{Engagement} is a metric that has been extensively used and studied both
 in HRI and during interactions with other agent-like systems. It has been
@@
 
+    \item The robot gets \textbf{lost}: When called by the child to come over,
+        the robot goes wrong, without any observable reason, and remains at the
+        wrong location. We expect this to be perceived as a mechanical
+        malfunction (a bug or system error which causes the robot to not work
+        correctly), and hypothesize decreased attributions of human-likeness to
+        the robot.
+
+    \item The robot \textbf{disobey}: When called by the child to come over, the
+        robot shows it refuses to obey by literally ``shaking its head'' and
+        becoming red. The robot then goes to a wrong location and remains there
+        while it continues to shake its head. We expect the disobey behaviour to
+        be perceived as the robot having an explicit \textit{``own will''}, and
+        we assume this leads to increased attributions of human-likeness
+        (ascribing intentionality) to the robot.
+
     \item The robot makes a \textbf{mistake}: When called by the child to come
@@
         projections}.}
-
-    \item The robot gets \textbf{lost}: When called by the child to come over,
-    the robot goes wrong, without any observable reason, and remains at the
-    wrong location. We expect this to be perceived as a bug or system error
-    which causes the robot to not work correctly, and hypothesize decreased
-    attributions of human-likeness to the robot.
-
-    \item The robot \textbf{disobey}: When called by the child to come over, the
-    robot shows it refuses to obey by literally ``shaking its head'' and
-    becoming red. The robot then goes to a wrong location and remains there
-    while it continues to shake its head. We expect the disobey behaviour to be
-    perceived as the robot having an \textit{``own will''}, and we assume this
-    leads to increased attributions of human-likeness (ascribing intentionality)
-    to the robot.
 
@@
 
-The robot was controlled by a human wizard, who was in the same room (see
-Figure~\ref{fig:domino-setup}). This was to ensure that the wizard could see
-children's interaction and hear their commands to the robot without any delay.
-Only one group asked at the beginning of the experiment if the wizard was the
-one actually controlling the robot. This did not seem to subsequently influence
-their behaviour.
+The Ranger~\cite{mondada2014ranger} is a wheeled box (27 x 37 x 37 cm) with
+partial wooden surface. Being remote controlled, it can move around a flat
+surface, move its eyes and eyebrows, display colors (LEDs) and light patterns,
+and play sounds through Bluetooth speakers.  The robot was controlled by a human
+wizard, who was in the same room (see Figure~\ref{fig:domino-setup}). This was
+to ensure that the wizard could see children's interaction and hear their
+commands to the robot without any delay.  Only one group asked at the beginning
+of the experiment if the wizard was the one actually controlling the robot. This
+did not seem to subsequently influence their behaviour.
 
@@
 
-\subsubsection{The Ranger robot}
-
 \subsubsection{Course of the study}
@@
 In our study, there were a total of 14 runs, and at each run, the robot exhibits
-one out of four possible behaviours: \emph{correct}, \emph{mistake}, \emph{lost}
-or \emph{disobey}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
+one out of four possible behaviours: \emph{correct}, \emph{lost}
+\emph{disobey} or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
 the baseline and the robot always behaved correctly. The children then switched
 the roles and in the 9 remaining runs (\emph{2.1} to \emph{2.9}), the robot
-showed one of the misbehaviour (\emph{mistake}, \emph{lost} or \emph{disobey})
+showed one of the misbehaviour (\emph{lost}, \emph{disobey} or \emph{mistake})
 at the $3^{rd}$ and $4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run
@@
     \centering
-    \subfloat[mistake]{
-        \label{fig:domino-mistake}
-        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
-    }
     \subfloat[lost]{
@@
     }
+    \subfloat[mistake]{
+        \label{fig:domino-mistake}
+        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
+    }
     \caption{\small The three robot misbehaviours.}
@@
 During the misbehaving runs, the robot's behaviour is manipulated in three
-possible ways:
+possible ways (Figure~\ref{fig:domino-misbehaviour}):
 
 \begin{itemize}
-
-    \item \textbf{Mistake:} The sender child calls Ranger. The robot goes until
-    it is on the carpet, stops, turns, and goes wrong (see yellow path in
-    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
-    ``face'' toward the sender child, and ``blushes'' red around its ``cheeks''
-    (as if it recognizes its wrong position) and finally goes correctly over to
-    the sender child. The \textit{mistake} behaviour is \textit{robot-repaired},
-    as no human-intervention is needed.
 
@@
     domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.
+
+    \item \textbf{Mistake:} The sender child calls Ranger. The robot goes until
+    it is on the carpet, stops, turns, and goes wrong (see yellow path in
+    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
+    ``face'' toward the sender child, and ``blushes'' red around its ``cheeks''
+    (as if it recognizes its wrong position) and finally goes correctly over to
+    the sender child. The \textit{mistake} behaviour is \textit{robot-repaired},
+    as no human-intervention is needed.
 
@@
 
-\subsubsection{Perception: semi-structured interviews}
+\subsubsection{Phenomenological perception: semi-structured interviews}
 
@@
 
-\subsection{Manipulation check: Negligible impact of the conditions}
+\subsection{Misbehaviour recognition and engagement}
 
@@
 mistake but is aware of it and able to repair its mistake, which should also
-lead to some perception of intentionality.  Contrary, we expected that the
+lead to the perception of intentionality and introspective skills.  Contrary, we expected that the
 \textit{lost} condition is perceived as a malfunction or bug of the robot.  In
@@
 the robot always did what they wanted it to do. Most children disagreed and said
-they noticed something strange. However, there were some children who gave a
-positive answer, suggesting that they found the robot always did what they
-wanted it to do. This was a surprise. Had they not noticed the robot's
-misbehaviour? Why not? On one hand, we found that children sometimes gave
-contradictory replies when asked the same question twice. This is difficult to
-interpret. On the other hand, children may have a general tendency to please
-adults \cite{leite_long-term_2013}, and it could be the case that some were too
-shy to tell us that the robot did something strange.
+they noticed something strange.
+%However, there were some children who gave a
+%positive answer, suggesting that they found the robot always did what they
+%wanted it to do. This was a surprise. Had they not noticed the robot's
+%misbehaviour? Why not? On one hand, we found that children sometimes gave
+%contradictory replies when asked the same question twice. This is difficult to
+%interpret. On the other hand, children may have a general tendency to please
+%adults \cite{leite_long-term_2013}, and it could be the case that some were too
+%shy to tell us that the robot did something strange.
 
@@
 
-We nevertheless asked children why they thought the robot had not always come
-over to them. 4 of the children did not reply. The remaining ones gave a variety
+When asked why they thought the robot had not always come
+over to them, 4 of the children did not reply. The remaining ones gave a variety
 of reasons (Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9
@@
 unpredictable.} because \textit{``with robots you have these kind of problems,
-they do no matter what''}. 8 replies concerned \textit{technical problems}
+they do no matter what''}. 8 replies related to \textit{technical problems}
 (including \textit{broken parts}), suggesting that children perceived the
@@
 
-In our case, it is not easy to make a clear statement about how each of the
-manipulations was perceived by the children.  Similar to how people reacted to
-the cheating robot in the study of \cite{short_no_2010}, most children showed
-surprise, were amused, sometimes confused, or occasionally slightly angry (\eg
-two boys tended to shout to the robot after it had disobeyed). The
-\textit{disobeying} robot seemed to evoke the strongest reactions, partly with a
-negative implication: later three of the children in this condition stated they
-would not accept Ranger as a friend \textit{because it did not always come over
-when they asked it to come over}. \cite{short_no_2010} described a similar
-implication of the robot cheating behaviour: participants made unfavorable
-character attributions to the cheating robot, so the robot's actions affected
-perceptions of the robot as ``fair'' and ``honest''.
+%In our case, it is not easy to make a clear statement about how each of the
+%manipulations was perceived by the children.  Similar to how people reacted to
+%the cheating robot in the study of \cite{short_no_2010}, most children showed
+%surprise, were amused, sometimes confused, or occasionally slightly angry (\eg
+%two boys tended to shout to the robot after it had disobeyed). The
+%\textit{disobeying} robot seemed to evoke the strongest reactions, partly with a
+%negative implication: later three of the children in this condition stated they
+%would not accept Ranger as a friend \textit{because it did not always come over
+%when they asked it to come over}. \cite{short_no_2010} described a similar
+%implication of the robot cheating behaviour: participants made unfavorable
+%character attributions to the cheating robot, so the robot's actions affected
+%perceptions of the robot as ``fair'' and ``honest''.
 
@@
 %	calling it cheating.
-
-\subsection{Engagement}
 
@@
 
-Overall, was there an effect on engagement when the robot misbehaved? We compare
-children's engagement during the interaction phase with the expected robot
-behaviour and during the interaction phase with the unexpectedly behaving robot.
-A statistical analysis revealed a significant difference between the average of
-engagement actions carried out during the first 7 runs (correct robot behaviour)
-and during the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1,
-p=.03). In all three conditions, children carried out more engagement
-actions with the unexpectedly behaving robot. No interaction effect was found
-between the two phases of interaction (expected / unexpected) and condition
-(F(2,36)=1.2, p=.31). In general, this finding supports our first hypothesis:
-children show more engagement toward a robot that behaves unexpectedly from time
-to time compared to a robot that always behaves correctly.
+Overall, we found a significant difference between the average of engagement
+actions carried out during the first 7 runs (correct robot behaviour) and during
+the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1, p=.03). In
+all three conditions, children carried out more engagement actions with the
+unexpectedly behaving robot. No interaction effect was found between the two
+phases of interaction (expected / unexpected) and condition (F(2,36)=1.2,
+p=.31). In general, this finding supports our first hypothesis: children show
+more engagement toward a robot that behaves unexpectedly from time to time
+compared to a robot that always behaves correctly.
 
@@
 
-        \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
         \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
         \textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
+        \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
         \bottomrule
@@
 
-Our data on the anthropomorphism index also suggest \textbf{qualitative gender
-differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
-SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
-SD=2.4). (Interestingly, as it was mentioned before, boys interacted slightly
-more with the robot than girls; though not significantly. This is
-counter-intuitive concerning the negative correlation between amount of
-interaction with the robot and anthropomorphism tendency.) It would be
-interesting to investigate in more detail whether boys are more prone to
-anthropomophize a robot than girls.\footnote{Findings presented in
-\cite{schermerhorn_robot_2008} suggested similar gender differences. In their
-study, males tended to think of the robot as more human-like and accordingly
-showed more ``social facilitation'' than females, who perceived the robot as
-more machine-like.}
-
-\paragraph{Summary}
-
-The established \textit{anthropomorphism index} suggests that children tend to
-conditionally anthropomorphize the robot. Higher indexes of anthropomorphism
-were found in the \textit{lost} and \textit{mistake} condition which was against
-our hypothesis. Interestingly, data suggests a significant negative correlation
-of engagement and anthropomorphism index. It appears that groups who interacted
-more with the robot perceived it as less-humanlike. This raises the question to
-what extent anthropomorphic perceptions of a robot can last over time, and with
-increasing interaction experience.
+%Our data on the anthropomorphism index also suggest \textbf{qualitative gender
+%differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
+%SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
+%SD=2.4). (Interestingly, as it was mentioned before, boys interacted slightly
+%more with the robot than girls; though not significantly. This is
+%counter-intuitive concerning the negative correlation between amount of
+%interaction with the robot and anthropomorphism tendency.) It would be
+%interesting to investigate in more detail whether boys are more prone to
+%anthropomophize a robot than girls.\footnote{Findings presented in
+%\cite{schermerhorn_robot_2008} suggested similar gender differences. In their
+%study, males tended to think of the robot as more human-like and accordingly
+%showed more ``social facilitation'' than females, who perceived the robot as
+%more machine-like.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Lessons Learned and Future Directions}
-
-We found that in a playful scenario where 4-5 year old children play domino
-together with a robot, the robot seems to be more engaging when it shows some
-misbehaviour compared to when it always behaves as expected. However, we
-cannot say if this effect holds also after novelty has worn off.
-
-From what we
-have seen in the Domino Study, we have a rough estimate of how children react
-and relate to a robot that behaves unexpectedly from time to time. They are
-mostly surprised, laugh at the robot, and they tend to be more engaged and
-playful. However, they are also confused and cannot really make sense of the
-robot's strange behaviour. We also cannot conclusively tell apart whether children perceived
-the unexpected robot behaviour entirely as a malfunction (something that happens
-to a machine) or as being intended and based on a motivation (something related
-to a social entity). Children stated both, when asked why the robot had
-misbehaved. Some referred to \textit{``a technical problem''} while others said
-the robot \textit{``is tired''} or it \textit{``doesn't want to carry domino
-tiles any more but rather go on a tour outside''}. Maybe our manipulations were
-not as clearly designed as we expected. There is always some freedom in how
-things are interpreted -- especially with young children.  Certainly more work
-needs to be done to investigate which robot behaviour is most beneficial for
-young children and can promote their engagement and motivation to interact with
-Ranger over extended periods of time.
+\section{Conclusions and Future Directions}
+
+As hypothesised, we found that in a playful scenario where 4-5 year old children
+play domino together with a robot, the robot seems to be more engaging when it
+shows some misbehaviour compared to when it always behaves as expected
+(notwithstanding the likely impact of a novelty effect).
+
+Regarding the design of our three conditions (\emph{lost},
+\emph{disobey}, \emph{mistake}), we cannot conclusively affirm whether children perceived the
+unexpected robot behaviour as a malfunction (something that happens to a
+machine) or as being intended and based on a motivation (something related to a
+social entity). Children stated both, when asked why the robot had misbehaved.
+Some referred to \textit{``a technical problem''} while others said the robot
+\textit{``is tired''} or it \textit{``doesn't want to carry domino tiles any
+more but rather go on a tour outside''}. While our manipulations were not as
+clearly designed as we expected for the age range of the subjects, we still
+believe these three conditions (mechanical malfunction -- the \emph{lost}
+condition, vs. explicit intentionality -- the \emph{disobey} condition, vs.
+implicit intentionality -- the \emph{mistake} condition) are relevant and we
+suggest to replicate a similar study with slightly older children.
+
+%It also appears
+%From what we
+%have seen in the Domino Study, we have a rough estimate of how children react
+%and relate to a robot that behaves unexpectedly from time to time. They are
+%mostly surprised, laugh at the robot, and they tend to be more engaged and
+%playful. However, they are also confused and cannot really make sense of the
+%robot's strange behaviour. We also cannot conclusively tell apart whether children perceived
+%the unexpected robot behaviour entirely as a malfunction (something that happens
+%to a machine) or as being intended and based on a motivation (something related
+%to a social entity). Children stated both, when asked why the robot had
+%misbehaved. Some referred to \textit{``a technical problem''} while others said
+%the robot \textit{``is tired''} or it \textit{``doesn't want to carry domino
+%tiles any more but rather go on a tour outside''}. Maybe our manipulations were
+%not as clearly designed as we expected. There is always some freedom in how
+%things are interpreted -- especially with young children.  Certainly more work
+%needs to be done to investigate which robot behaviour is most beneficial for
+%young children and can promote their engagement and motivation to interact with
+%Ranger over extended periods of time.
 
@@
 
-\subsection{Limitations}
-
-This study and the results have several limitations.  First, we did not have a
-real control group in which the robot always behaved correctly. Instead, we took
-the first interaction phase as a reference for how children interact with the
-correctly behaving robot.  Also, the sample size of 13 groups was small. There
-were  variations in the data due to the individual differences of children. More
-data could have allowed for a better comparison between the conditions.
-
-With the manipulation of the robot behaviour we were able to surprise children.
-However, it is questionable how often the same type of behaviour manipulation
-leads to surprise. Moreover, our experiment was a short-term interaction study
-while we try to make statements about how to sustain long-term engagement. This
-is critical but not unusual. Long-term HRI studies with young children are
-extremely rare as they are difficult to set up as well as time and resource
-consuming \cite{leite_long-term_2013}. Nevertheless, we could have probably
-improved our study by setting up several short interaction sessions spreading
-over several weeks. At the end of each session we could have asked whether
-children want to play again with the robot. Such a study could have helped to
-investigate the long-term interaction with the robot and the impact of the
-behavioural variances.
-
-\subsection{Lessons Learned}
-
-One of the lessons learned is that it is difficult to set up a controlled lab
-study with young children. Children are not like adults who patiently
-participate in a 45-minutes experiment and then get some reward in the end. On
-one hand, an experiment with children should not be boring for them, but on the
-other hand, you would like to seriously collect some data. A lot of the
-challenges we experienced are also described in \cite{ros_child-robot_2011}. One
-of the most difficult parts turned out to be the interviews with the children.
-We need to be careful to not over interpret some of their answers. Some children
-seem to not have a clear opinion and partly contradict themselves. These answers
-are not easy to interpret. An interview script including the questions need to
-be designed very carefully, and should definitely be tested beforehand with the
-respective age group.
-
-Overall, it appears that when trying to study something in more detail, such as
-the manipulation of robot behaviour, 4-5 year old children may be too young. But
-when trying to evaluate a more general approach, the design of a prototype, or
-an interaction scenario, children are a very good choice. They say things as
-they are and react very naturally, when compared to adults, who may reply more
-socially desired.
-
-\paragraph{Summary}
-
-In this study, we investigated the effect of unexpected robot behaviour on
-children's engagement in interacting with Ranger and on their perception of the
-robot.  Our first hypothesis finds support: children show more engagement toward
-a robot that behaves unexpectedly from time to time. Further, different types of
-unexpected behaviour may have a different effect, and therefore the behaviour
-manipulation needs to be designed with care.
-We did not find support for our second hypothesis which stated that children
+%\subsection{Limitations}
+%
+%This study and the results have several limitations.  First, we did not have a
+%real control group in which the robot always behaved correctly. Instead, we took
+%the first interaction phase as a reference for how children interact with the
+%correctly behaving robot.  Also, the sample size of 13 groups was small. There
+%were  variations in the data due to the individual differences of children. More
+%data could have allowed for a better comparison between the conditions.
+%
+%With the manipulation of the robot behaviour we were able to surprise children.
+%However, it is questionable how often the same type of behaviour manipulation
+%leads to surprise. Moreover, our experiment was a short-term interaction study
+%while we try to make statements about how to sustain long-term engagement. This
+%is critical but not unusual. Long-term HRI studies with young children are
+%extremely rare as they are difficult to set up as well as time and resource
+%consuming \cite{leite_long-term_2013}. Nevertheless, we could have probably
+%improved our study by setting up several short interaction sessions spreading
+%over several weeks. At the end of each session we could have asked whether
+%children want to play again with the robot. Such a study could have helped to
+%investigate the long-term interaction with the robot and the impact of the
+%behavioural variances.
+%
+%\subsection{Lessons Learned}
+%
+%One of the lessons learned is that it is difficult to set up a controlled lab
+%study with young children. Children are not like adults who patiently
+%participate in a 45-minutes experiment and then get some reward in the end. On
+%one hand, an experiment with children should not be boring for them, but on the
+%other hand, you would like to seriously collect some data. A lot of the
+%challenges we experienced are also described in \cite{ros_child-robot_2011}. One
+%of the most difficult parts turned out to be the interviews with the children.
+%We need to be careful to not over interpret some of their answers. Some children
+%seem to not have a clear opinion and partly contradict themselves. These answers
+%are not easy to interpret. An interview script including the questions need to
+%be designed very carefully, and should definitely be tested beforehand with the
+%respective age group.
+%
+%Overall, it appears that when trying to study something in more detail, such as
+%the manipulation of robot behaviour, 4-5 year old children may be too young. But
+%when trying to evaluate a more general approach, the design of a prototype, or
+%an interaction scenario, children are a very good choice. They say things as
+%they are and react very naturally, when compared to adults, who may reply more
+%socially desired. 
+%
+%
+%\paragraph{Summary}
+
+%In this study, we investigated the effect of unexpected robot behaviour on
+%children's engagement in interacting with Ranger and on their perception of the
+%robot.  Our first hypothesis finds support: children show more engagement toward
+%a robot that behaves unexpectedly from time to time. Further, different types of
+%unexpected behaviour may have a different effect, and therefore the behaviour
+%manipulation needs to be designed with care.
+
+Still, we did not find support for our second hypothesis which stated that children
 perceive a robot showing intention or cognitive abilities as more human-like
-than a robot that appears to have a system error. This may be due to the study
+than a robot that appears to have a system error. While this may be due to the study
 setup and the fact that children did not interpret the robot misbehaviour in the
-conceived way. Our findings seem to suggest the contrary to our hypothesis. A
+conceived way, our findings seem to suggest the contrary to our hypothesis. A
 robot that appeared to do a \textit{mistake} or to be \textit{lost} was more
-anthropomorphized than a robot that \textit{disobeyed}. But again, as children
-may have misinterpreted these robot behaviours we cannot be sure about this
-result.
-
-Another outcome of this study is the initial development and first tryout of an
-\textbf{anthropomorphism index}. This index considers both behavioural and
-perception aspects and is able to indicate lower and higher levels of
-anthropomorphism along this continuous index. At the moment, there is no such
-index available that quantifies anthropomorphism along a scale and there is no
-technique that combines behaviour and perception. In the future, we will need to refine
-and improve this scale. For instance, we need to identify the specific factors
-that should be included as measurement points in such a scale, for both aspects
-(behaviour and perception). Also, we need to think about how to balance the two
-aspects appropriately. Probably, also characteristics of the person, the robot,
-and the situation need to be considered.
+anthropomorphized than a robot that \textit{disobeyed}.
+
+Another outcome of this study is the initial application of an
+anthropomorphism index to a child-robot interaction study. This index
+considers both behavioural and phenomenological aspects and is able to indicate
+lower and higher levels of anthropomorphism along this continuous index.  Our
+experience with this index suggests that children tend to conditionally
+anthropomorphize the robot. Higher indexes of anthropomorphism were found in the
+\textit{lost} and \textit{mistake} condition which was against our hypothesis.
+
+Interestingly, data suggests a significant negative correlation of engagement
+and anthropomorphism index. It appears that groups who interacted more with the
+robot perceived it as less-humanlike. This raises an important question for the
+human-robot interaction community: to what extent anthropomorphic perceptions
+impact the interaction experience. Our findings here go against the intuition.
 

### 2014-09-29 paper.tex
Full proof-read. Still 10p. :-(

@@
 We propose an original analysis methodology which blends behavioural cues and
-reported phenomenological perceptions into a compound \emph{index}.
+reported phenomenological perceptions into a compound index.
 
@@
 are more likely to engage users in the long-term and they proposed several
-guidelines for designing such artificial companions. Some other work
-\cite{bickmore_maintaining_2010,short_no_2010} has shown that there can be much
-simpler ways to enhance engagement.
+guidelines for designing such artificial companions. Other works
+\cite{bickmore_maintaining_2010,short_no_2010} have shown that simpler ways to
+enhance engagement may as well be effective.
 
@@
 
-Similarly, more looking at short-term engagement, \cite{short_no_2010} found
-that a simple manipulation of the robot's behaviour can lead to greater
-engagement. The authors let participants play several rounds of the
-rock-paper-scissors game with the robot (the playfulness of the scenario seems
-important). When the robot was cheating from time to time, participants tended
-to ascribe intention to the robot what in turn led to greater engagement in how
-they were interacting with the robot. The mechanism behind the cheating action
-that the robot showed, was that participants did not expect this behaviour from
-the robot. The authors suggest that \textit{``any deviation from expected
+Similarly, looking at short-term engagement, \cite{short_no_2010} found that a
+simple manipulation of the robot's behaviour can lead to greater engagement. The
+authors let participants play several rounds of the rock-paper-scissors game
+with the robot (the playfulness of the scenario seems important). When the robot
+was cheating from time to time, participants tended to ascribe intention to the
+robot what in turn led to greater engagement in how they were interacting with
+the robot. The authors observe that \textit{``any deviation from expected
 operation is sufficient to create a greater degree of engagement in the
-interaction.''} Moreover, \cite[p.~225]{short_no_2010} proposed that
-\textit{``many interactions can be improved by the introduction of such simple
-    behaviours, and that this should be exploited by designers in HRI. Bringing
-    human and robot together to perform a simple, repetitive, familiar task and
-then having the robot behave unexpectedly can increase engagement and mental
-state attribution without complex behavioural or mechanical additions.''}.
-In their model of the dynamics of anthropomorphism, Fink et
-al.~\cite{fink2014dynamics} also suggest that \emph{disruptive behaviours}
-may lead to increased anthropomorphic projections and possibly engagement.
+interaction.''} Besides, they suggest that \textit{``many interactions can be
+improved by the introduction of such simple behaviours, and that this should
+be exploited by designers in HRI. Bringing human and robot together to
+perform a simple, repetitive, familiar task and then having the robot behave
+unexpectedly can increase engagement and mental state attribution without
+complex behavioural or mechanical additions.''}.  Along those lines, Fink
+\etal\cite{fink2014dynamics} also suggest in their model of the dynamics of
+anthropomorphism, that \emph{disruptive behaviours} may lead to increased
+anthropomorphic projections and possibly engagement.
 
@@
 We present in this article a study that explores possibilities of sustaining
-children's engagement with the \emph{Ranger}~\cite{mondada2014ranger} robot by
+children's engagement with the \emph{Ranger} robot~\cite{mondada2014ranger} by
 manipulating the robot's behaviour in such way that it appears
@@
 robot behaviour impact children's interaction with Ranger and their perception of
-it (\eg in terms of attributing intention and cognitive abilities to the robot).
+it (in terms of attributing intention and cognitive abilities to the robot).
 
@@
 
-This study also aims at applying to an actual study and assessing the usefulness
-of the \emph{anthropomorphic index} proposed by Fink et
-al.~\cite{fink2014dynamics} as a compound (behavioural and phenomenological)
-metric for the attribution of human-like features to robot. We are especially
-interested in investigating how this indicator predicts and/or reflects actual
-\emph{engagement} into the interaction.
-
-\subsection{Research Questions and Hypotheses}
+This study also aims at assessing the effectiveness of the \emph{anthropomorphic
+index} proposed by Fink \etal\cite{fink2014dynamics} as a compound (behavioural
+and phenomenological) metric for the attribution of human-like features to
+robot. We are especially interested in investigating how this indicator predicts
+and/or reflects actual \emph{engagement} into the interaction.
+
+\subsection{Design and Hypotheses}
 
@@
 unexpected behaviour. In a playful scenario which was set up in a laboratory
-environment, 26 children aged 4-5 years were assembling a domino game together.
+environment, 26 children aged 4-5 years (MD=4.46) were assembling a domino game together.
 Each group consisted of two children and the \emph{Ranger} robot, which was used
@@
         correctly), and hypothesize decreased attributions of human-likeness to
-        the robot.
+        the robot.\footnote{We use interchangeably \textit{attribution of
+            human-likeness} and \textit{anthropomorphic projections} in the
+        remaining of the article.}
 
@@
         error). In this condition, we assume increased attributions of
-        human-likeness to the robot.\footnote{The attribution of human-likeness
-            to a robot is hereafter labeled as \textit{anthropomorphic
-        projections}.}
+        human-likeness to the robot.
 
@@
 perception but also as an observable behaviour in the interaction itself. Thus,
-we would like to bridge things together and, relying on the concept of an
-\textbf{anthropomorphism index}, build a
-compound metric that considers both children's perception and interaction
-aspects (qualitatively). Previous work suggests that a social relation to a
-robot (we view anthropomorphism as a specific type of social relation) reflects
-an increased engagement and can be effective in sustaining interaction.
-Consequently, we formulate a third hypotesis:
+we would like to bridge things together and, relying on the concept of
+anthropomorphism index~\cite{fink2014dynamics}, build a compound metric that
+considers both children's perception and interaction aspects (qualitatively).
+Previous work suggests that a social relation to a robot (we view
+anthropomorphism as a specific type of social relation) reflects an increased
+engagement and can be effective in sustaining interaction.  Consequently, we
+formulate a third hypothesis:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Scenario and Research Methodology}
-
-\subsection{The Domino scenario}
+\section{The Domino study}
+
+\subsection{Scenario and course of the study}
 
@@
 \textit{the receiver} -- is asked to stay in a play tent. There is a ``river''
-(play carpet) in between the two children that we told them they cannot cross
+(playground) in between the two children that we told them they cannot cross
 and therefore they need the robot to transport the domino tiles between them.
@@
 The Ranger~\cite{mondada2014ranger} is a wheeled box (27 x 37 x 37 cm) with
-partial wooden surface. Being remote controlled, it can move around a flat
+partial wooden surface. It is remotely controlled, it can move around a flat
 surface, move its eyes and eyebrows, display colors (LEDs) and light patterns,
 and play sounds through Bluetooth speakers.  The robot was controlled by a human
-wizard, who was in the same room (see Figure~\ref{fig:domino-setup}). This was
-to ensure that the wizard could see children's interaction and hear their
-commands to the robot without any delay.  Only one group asked at the beginning
-of the experiment if the wizard was the one actually controlling the robot. This
-did not seem to subsequently influence their behaviour.
+wizard, who was in the same room (see Figure~\ref{fig:domino-setup} -- only one
+group asked at the beginning of the experiment if the wizard was the one
+actually controlling the robot. This did not seem to subsequently influence
+their behaviour).
 
 We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
-pictures of cartoon farm animals: cow, sheep, hen, donkey, duck, pig, rabbit.
-The pictures were taken from a commercially available domino game adapted to the
-age of the children (produced by Djeco, advised age 3+).
-
-To start the game (divided in several \emph{runs} that correspond each to the
-delivery and assembling of one domino tile), there is already one domino tile in
-front of the tent, where the receiver child stays and assembles the domino
-chain. The receiver child asks the searcher child for a specific tile, \eg a
-tile with a donkey, the searcher searches for the respective tile, sits down on
-the next beanbag, and asks the robot to come over.  The Ranger robot is first
-located next to the tent, then, when called by the searcher it starts moving,
-crosses the river carpet, and comes over to the searcher on the beanbag. The
-searcher child puts the domino tile into the robotic box, and the robot then
-goes back to the receiver child in the tent. Then, the receiver takes out the
-domino tile from the robot, and puts the two tiles together. The first
-\emph{run} is over, and a new \emph{run} starts, when the receiver asks the
-searcher for the next domino tile.
+pictures of cartoon farm animals (taken from a commercially available domino
+game manufactured by Djeco and adapted to the age of the children).
+
+The game (divided in several \emph{runs} that correspond each to the delivery
+and assembling of one domino tile) starts with one domino tile in front of the
+tent, where the receiver child stays and assembles the domino chain. The
+receiver child asks the searcher child for a specific tile, \eg a tile with a
+donkey, the searcher searches for the respective tile, sits down on the next
+beanbag, and asks the robot to come over.  The Ranger robot is first located
+next to the tent, then, when called by the searcher (\textit{``Robot, come
+here!''}), it starts moving, crosses the river carpet, and comes over to the
+searcher on the beanbag. The searcher child puts the domino tile into the
+robotic box, and the robot then goes back to the receiver child in the tent.
+Then, the receiver takes out the domino tile from the robot, and puts the two
+tiles together. The first \emph{run} is over, and a new \emph{run} starts, when
+the receiver asks the searcher for the next domino tile.
+
+\subsubsection{Participants}
+
+Overall, there were 13 pairs of children (n=26) participating in the interaction
+study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
+French-speaking. In 11 of the pairs, children were friends who knew each other
+from kindergarten, nursery school or because they lived in the same
+neighborhood. 2 of the pairs were composed of brother and sister.
 
@@
 regarding a consistent robot behaviour. When the robot then exhibits an
-unexpected behaviour, children are likely to be positively surprised. A similar
+unexpected behaviour, children are likely to be positively surprised (a similar
 effect has been observed in a study with a robot that was cheating from time to
-time~\cite{short_no_2010}.  Besides, to prevent the robot misbehaviours to be
+time~\cite{short_no_2010}).  Besides, to prevent the robot misbehaviours to be
 immediately interpreted as failures, we introduce these misbehaviour neither at
@@
 (\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
-failures negatively impact trust). \cite{short_no_2010} also adopted a similar
-pattern when introducing unexpected robot behaviour. In their study with a robot
-that cheated, from the 20 rounds of the rock-paper-scissors game, the robot
-cheated three times in the middle: on the 4th, 8th and 15th round. The authors
-adjusted the interaction length so that the spacing and timing of the cheating
-was preserved.
+failures negatively impact trust. \cite{short_no_2010} also adopted a similar
+pattern when introducing unexpected robot behaviour).
 
@@
 
-The \emph{correct} robot behaviour (baseline behaviour) consists in the
-following states:
-
-\begin{itemize}
-
-    \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
-        and shows a green light pattern,
-
-    \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
-        sound and shows a green light pattern,
-
-    \item \emph{Robot is called by one of the children:} When one of the
-    children called the robot saying something like \textit{``Robot come
-    here!''}, the robot starts moving toward the child (Ranger does not react to
-    any other verbal commands).
-
-    \item \emph{Robot reaches one of the children:} When in front of one of the
-    children who should either put or remove a domino tile, Ranger stops and
-    shows a pulsating yellow light pattern. If no reaction, Ranger also makes a
-    wiggle-like move.
-
-\end{itemize}
-
+%The \emph{correct} robot behaviour (baseline behaviour) consists in the
+%following states:
+%
+%\begin{itemize}
+%
+%    \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
+%        and shows a green light pattern,
+%
+%    \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
+%        sound and shows a green light pattern,
+%
+%    \item \emph{Robot is called by one of the children:} When one of the
+%    children called the robot saying something like \textit{``Robot come
+%    here!''}, the robot starts moving toward the child (Ranger does not react to
+%    any other verbal commands).
+%
+%    \item \emph{Robot reaches one of the children:} When in front of one of the
+%    children who should either put or remove a domino tile, Ranger stops and
+%    shows a pulsating yellow light pattern. If no reaction, Ranger also makes a
+%    wiggle-like move.
+%
+%\end{itemize}
+%
 During the misbehaving runs, the robot's behaviour is manipulated in three
@@
 
-\subsubsection{Participants}
-
-Overall, there were 13 pairs of children (n=26) participating in the interaction
-study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
-French-speaking. In 11 of the pairs, children were friends who knew each other
-from kindergarten, nursery school or because they lived in the same
-neighborhood. 2 of the pairs were composed of brother and sister.
-
 \subsection{Data collection}
@@
 below. The children's \textbf{phenomenological perception of the robot} has been
-captured through audio-recorded semi-structured interviews which took place
+captured through two audio-recorded semi-structured interviews which took place
 between run \emph{1.5} and \emph{2.1} and at the end of the 14 runs.
@@
 
-    \item \textbf{Explore (ex)}: when children actively try to find out what the
+    \item \textbf{Explore}: when children actively try to find out what the
         robot is doing (\eg by looking under the box); attentively watch or
@@
 
-    \item \textbf{Misuse (mis)}: when children kick the robot, poke it in its
+    \item \textbf{Misuse}: when children kick the robot, poke it in its
         ``eye'', try to climb on or inside the box, drive / push the robot
@@
 
-    \item \textbf{Put domino (put)}: when a domino tile is put inside the box;
+    \item \textbf{Put domino}: when a domino tile is put inside the box;
 
@@
 
-    \item \textbf{Gesture (ges)}: when gestures are used to communicate /
+    \item \textbf{Gesture}: when gestures are used to communicate /
         interact with the robot (\eg pointing gestures, waving at the robot);
 
-    \item \textbf{Touch (touch)}: when the box is touched (\eg petted or
+    \item \textbf{Touch}: when the box is touched (\eg petted or
         caressed);
 
-    \item \textbf{Show (show)}: when a child shows something to the robot (\eg
+    \item \textbf{Show}: when a child shows something to the robot (\eg
         by holding a domino tile in front of its eyes);
 
-    \item \textbf{Call (call)}: when a child calls the robot to come over;
-
-    \item \textbf{Talk (talk)}: when a child directly talks to the robot (using
+    \item \textbf{Call}: when a child calls the robot to come over;
+
+    \item \textbf{Talk}: when a child directly talks to the robot (using
         direct speech) besides calling the robot;
 
-    \item \textbf{Look (look)}:	when a child looks at the experimenter due to
+    \item \textbf{Look}: when a child looks at the experimenter due to
         confusion caused by the robot; look is not coded when the experimenter
@@
 The actions \textit{put, remove} and \textit{call} were ``requested'' actions
-because the scenario required them and children were asked to carry them out.
-Hence, these actions are not relevant to be analyzed quantitatively. The other
-actions \textit{explore, misuse, gesture, touch, show, talk} and \textit{look}
-are spontaneous actions that were not requested but arose in the interaction.
-These actions reflect engagement, and are the one we considered during the
-analysis. Figure~\ref{fig:domino-time-active} shows the distribution of these
-actions over the different runs, in any condition.
+that the children had to perform in the scenario. On the contrary,
+\textit{explore, misuse, gesture, touch, show, talk} and \textit{look} are
+spontaneous actions that were not requested but arose in the interaction.  These
+actions reflect engagement, and are the one we considered during the analysis.
+Figure~\ref{fig:domino-time-active} shows the distribution of these actions over
+the different runs, in summed over the three condition.
 
@@
     \toprule
-    \textbf{Construct \emph{expectations}} \\
+    \textbf{Expectations} \\
     \midrule
@@
     \toprule
-    \textbf{Construct \emph{impression}} \\
+    \textbf{Impression} \\
     \midrule
@@
 ability to hear and to see (perceptual skills), as attributed by the children.
-The construct ``moral standing'' and the respective question was taken from
+The construct ``moral standing'' and the related question was taken from
 \cite{kahn_jr._robotic_2006}.\footnote{According to
@@
 unexpectedly behaving robot. We planned to use these two interviews as a
-within-subject measurement, however, this did not work out very well because
+within-subject measurement, however, this did not fully work out because
 children's responses were not always accurate, not comparable one by one, and
@@
 
-\subsubsection{Engagement and anthropomorphism index}
-
-There are different possibilities to measure engagement in HRI, depending on the
-specific research question and context. Metrics to measure behavioural engagement
-in the interaction include, for instance, conversation analysis (\eg used in
-\cite{short_no_2010}) or general attention analysis. These can be studied by
-analyzing interaction videos in terms of head movement, eye tracking and gesture
-/ body movement analysis (\eg in \cite{sidner_explorations_2005}).
-Post-measurements to measure emotional engagement can be questionnaires that try
-to assess constructs like the perceived presence and involvement in the
-interaction. An example is the \textit{Interactive Experience Questionnaire}
-(originally developed by \cite{lombard_measuring_2000}) of which adapted
-versions were used in
-\cite{kidd_effect_2004,bainbridge_effect_2008,short_no_2010}.
-
-A mix of several methods has been used in a long-term interaction study with 8-9
-year old children, \cite{leite_long-term_2013}. The author measured engagement
-through video observations (by analyzing the amount of time that children spent
-looking at the robot), interviews, and questionnaires. The interviews were
-semi-structured, containing initial yes-or-no questions followed by open-ended
-questions that allowed children to justify and elaborate their answers. We have
-chosen a similar approach that considers both children's behavioural and
-emotional engagement.
-
-With 4-5 year old children, however, we cannot use rating scales to ask them
-about constructs as abstract as social presence or how much they felt involved
-in the interaction. Therefore we have attempted to combine \emph{interaction}
+\subsubsection{Engagement}
+
+%There are different possibilities to measure engagement in HRI, depending on the
+%specific research question and context. Metrics to measure behavioural engagement
+%in the interaction include, for instance, conversation analysis (\eg used in
+%\cite{short_no_2010}) or general attention analysis. These can be studied by
+%analyzing interaction videos in terms of head movement, eye tracking and gesture
+%/ body movement analysis (\eg in \cite{sidner_explorations_2005}).
+%Post-measurements to measure emotional engagement can be questionnaires that try
+%to assess constructs like the perceived presence and involvement in the
+%interaction. An example is the \textit{Interactive Experience Questionnaire}
+%(originally developed by \cite{lombard_measuring_2000}) of which adapted
+%versions were used in
+%\cite{kidd_effect_2004,bainbridge_effect_2008,short_no_2010}.
+%
+%A mix of several methods has been used in a long-term interaction study with 8-9
+%year old children, \cite{leite_long-term_2013}. The author measured engagement
+%through video observations (by analyzing the amount of time that children spent
+%looking at the robot), interviews, and questionnaires. The interviews were
+%semi-structured, containing initial yes-or-no questions followed by open-ended
+%questions that allowed children to justify and elaborate their answers. We have
+%chosen a similar approach that considers both children's behavioural and
+%emotional engagement.
+%
+%With 4-5 year old children, however, we cannot use rating scales to ask them
+%about constructs as abstract as social presence or how much they felt involved
+%in the interaction.
+
+We have measured engagement by combining \emph{interaction}
 data with the results of the semi-structured interviews.  Several of the
@@
 moral standing} (Table~\ref{tab:domino-questions}) to assess how far they
-    anthropomorphize the robot.
-
-To account for the fact that anthropomorphism arises in an interaction, we try
+engaged with the robot.
+
+To account for the fact that anthropomorphism arises in an interaction, we tried
 to bring both children's perception of the robot (post-measurement) and their
-behaviour toward it (in-the-moment measurement) together. By doing so, we would
-like to obtain a qualitative \textbf{anthropomorphism
-index}~\cite{fink2014dynamics}. We quantify the index by attributing points for each
-anthropomorphic \emph{perception} of the robot (max.  13 points) and for specific kinds
-of human-like \emph{behaviour} toward the robot (max.  3 points). The index included the
-following aspects:\\
+behaviour toward it (in-the-moment measurement) together. We did so by building
+a qualitative anthropomorphism index~\cite{fink2014dynamics}. We quantify the
+index by attributing points for each anthropomorphic \emph{perception} of the
+robot (max.  13 points) and for specific kinds of human-like \emph{behaviour}
+toward the robot (max.  3 points). The index included the following aspects:\\
 
@@
 study setup, and we cannot be sure that it really reflects anthropomorphism).
-There are possibilities of refinement of this scoring scheme. For instance, a
-more systematic weighting procedure and the identification of all relevant
-factors would be an interesting future achievement. We could introduce a formula
-to calculate the anthropomorphism index \textit{$\alpha$} by taking the sum of
-the various items ($x_1, x_2, x_3...$) and different weights ($a, b, c ...$) to
-balance them: $\alpha$ \textit{=} $a x_1$ \textit{+} $b x_2$ \textit{+} $c x_3
-...$~. Machine learning techniques could be used to optimize such a calculation
-of the anthropomorphism index.
 
@@
 In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
-here. As mentioned before, the findings here do not directly address the issues
+here. The findings here do not directly address the issues
 of long-term usage but concern short-term \textit{engagement}, which is a
@@
 children's attention because it faces the searcher child and uses fairly
-strong audio and light cues as compared to the other behaviours.}. For
-\textit{look}, the only significant difference is found between the mean
-scores of \textit{lost} and \textit{disobey}. Data suggests that when the
-robot is lost, children look more often at the experimenter than when the
-robot disobeys. The other actions were not found to differ significantly
-between the robot behaviour conditions.
+strong audio and light cues as compared to the other behaviours.}.
 
@@
 all three conditions, children carried out more engagement actions with the
-unexpectedly behaving robot. No interaction effect was found between the two
-phases of interaction (expected / unexpected) and condition (F(2,36)=1.2,
-p=.31). In general, this finding supports our first hypothesis: children show
-more engagement toward a robot that behaves unexpectedly from time to time
-compared to a robot that always behaves correctly.
+unexpectedly behaving robot (Figure~\ref{fig:domino-time-active}). No
+interaction effect was found between the two phases of interaction (expected /
+unexpected) and condition (F(2,36)=1.2, p=.31). In general, this finding
+supports our first hypothesis: children show more engagement toward a robot that
+behaves unexpectedly from time to time compared to a robot that always behaves
+correctly.
 
@@
     \includegraphics[width=0.7\linewidth]{domino-intention.pdf}
-    \caption{\small \textbf{Attribution of
-        intention to Ranger.} Children were asked these
-        questions at both interviews. Concerning question (a), there are no remarkable
-        differences in children's responses given in the \textit{first} and
-        \textit{second} interview.  Children tend to think Ranger does always
-        obey to them, even after it misbehaved (\textit{second} part). There is
-        however a small difference in the responses to question (b).
-        After the robot misbehaved, 8 children think the robot could do
-        something silly whereas first, only 3 children answered like this.}
+    \caption{\small \textbf{Attribution of intention to Ranger.} Children were
+        asked these questions at both interviews. Concerning question (a), there
+        are no remarkable differences in children's responses given in the
+        \textit{first} and \textit{second} interview.  Children tend to think
+        Ranger does always obey to them, even after it misbehaved. There is
+        however a small difference in the responses to question (b).  After the
+        robot misbehaved, 8 children think the robot could do something silly whereas
+        first, only 3 children answered like this.}
 
@@
 asked three questions to assess how far they ascribe \textbf{intention} to it
-(see questionnaire items in Table~\ref{tab:domino-questions},
-page~\pageref{tab:domino-questions}). One of these questions was whether they
-believed Ranger could go out the door by itself. They majority of 16 children
-answered negatively, which suggests that they initially do not ascribe intention
-to the robot. The two other questions were whether Ranger would always obey and
-whether Ranger could do a silly thing (Figure~\ref{fig:domino-intention}). These
-two questions were asked again later after children had interacted with the
-unexpectedly behaving robot.
+(see questionnaire items in Table~\ref{tab:domino-questions}). One of these
+questions was whether they believed Ranger could go out the door by itself. The
+majority of 16 children answered negatively, which suggests that they initially
+do not ascribe intention to the robot. The two other questions were whether
+Ranger would always obey and whether Ranger could do a silly thing
+(Figure~\ref{fig:domino-intention}). These two questions were asked again later
+after children had interacted with the unexpectedly behaving robot.
 
@@
 them (once at the end of the experiment) if they thought that Ranger can feel
-happy or sad sometimes. The great majority of
+happy or sad sometimes. The majority of
 children (21 of 26) gave a positive answer. Only 2 children who had interacted
@@
 domino tile inside the box. This may also be a reflection of their own feelings,
-projected on the robot.  More than half of the children (14 of 26) agreed Ranger
+projected on the robot. About half of the children (14 of 26) agreed that Ranger
 can be their friend. We did not ask about what being a friend means to them but
@@
 children if it would be alright to leave Ranger alone at home (\eg during two
-weeks when they go on a vacation) (Figure~\ref{fig:domino-leave-alone}). The
-great majority of 20 children responded negatively. Asked why, children gave a
+weeks when they go on a vacation) (Figure~\ref{fig:domino-leave-alone}). 
+20 out of 26 children responded negatively. Asked why, children gave a
 variety of answers that we classified into 7 categories. With 5 replies, the
@@
 expressed a moral position, while most of the others actually expressed several
-forms of distrust towards the robot, that could be phrase like: it is not
-alright to leave the robot alone, not because it is morally incorrect, but
-because we do not trust the robot to remain still. This shows that things must
+forms of distrust towards the robot. This shows that things must
 be put into perspective and even young children do not automatically consider a
@@
 On average, Ranger was moderately anthropomorphized by the
-children.\footnote{However, as our developed anthropomorphism score is relative,
-we cannot really make a claim about what a difference of \textit{+} or \textit{-
-1} point means.} 8 of the 13 groups had an index of 8 or higher, evenly spread
+children. 8 of the 13 groups had an index of 8 or higher, evenly spread
 over the three conditions (Table~\ref{tab:domino-anth-score}). However, the mean
@@
 condition, which suggests that they could not fully make sense of the robot's
-behaviour. The fact of not being able to understand (and hence predict) a
+behaviour, and the fact of not being able to understand (and hence predict) a
 robot's behaviour is likely to increase anthropomorphism.\footnote{One of the
@@
 
-But to what extent is the human-like interaction related to perceiving the robot
-as human-like? Do children who interact a lot and are probably more engaged with
-the robot also perceive the robot as more human-like? This was what we
-hypothesized. Data suggests the opposite, however. As shown in
-Figure~\ref{fig:domino-anthropo-interaction}, we found a significant
-\textit{negative} correlation between the count of engagement actions (per
-group) and the qualitative anthropomorphism index (r(11)=-0.56, p=.05).
+We hypothesized that children who interact a lot and are probably more engaged
+with the robot also perceive the robot as more human-like. Data suggests the
+opposite, however. As shown in Figure~\ref{fig:domino-anthropo-interaction}, we
+found a significant \textit{negative} correlation between the count of
+engagement actions (per group) and the qualitative anthropomorphism index
+(r(11)=-0.56, p=.05).
 
@@
 engagement in the interaction, the less they anthropomorphized the robot. This
-is a key results, which was against our initial assumption. How can we interpret
-this? It may be that children who interact more with the robot understand better
+is a key results, which was against our initial assumption. A possible
+interpretation is that children who interact more with the robot understand better
 how it works, they are more familiar with it, and as such the robot appears less
@@
 and anthropomorphism index. It appears that groups who interacted more with the
-robot perceived it as less-humanlike. This raises an important question for the
+robot perceived it as less human-like. This raises an important question for the
 human-robot interaction community: to what extent anthropomorphic perceptions

### 2014-09-29 paper.tex
Formatting: down to 8.75 pages

@@
     \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
-    \caption{\small The study took place in one of the rooms in the lab. One
-    child is located in a tent (referred to as \textit{the receiver}), while the
-    other (referred to as \textit{the searcher}) is asked to sit on one of the
-    three beanbags, behind which each 3 domino tiles are distributed (displayed
-    as black stars). A playground with a river drawn on it is used as an
-    imaginary barrier that only the robot is allowed to cross. The solid green
-    arrows, show the robot's path for the \textit{correct} behaviour. The blue
+    \caption{\small \textbf{Experimental setting} One child is located in a
+        tent, while the other is asked to sit on one of the three beanbags,
+        behind each of which 3 domino tiles are distributed (displayed as black
+        stars). A playground with a river drawn on it is used as an imaginary
+        barrier that only the robot is allowed to cross. The solid green arrows
+        show the robot's path for the \textit{correct} behaviour. The blue
         dashed arrow visualizes a possible \textit{lost} path, where the Ranger
-    stops and remains at a wrong stop (denoted by the blue cross). The yellow
-    arrows reflect a possible \textit{mistake} path, where the robot goes wrong
-    but then turns back and goes to the searcher child. The red dashed arrow
-    visualizes a possible \textit{disobey} path where the robot goes wrong, then
-    turns toward the child but remains at the wrong stop (red cross).}
+        stops and remains at a wrong stop. The yellow arrows reflect a possible
+        \textit{mistake} path, where the robot goes wrong but then turns back
+        and goes to the child. The red dashed arrow visualizes a possible
+        \textit{disobey} path where the robot goes wrong, then turns toward the
+        child but stays at a wrong position.}
 
@@
 We annotated children's behaviour in the video records, and coded 10 different
-actions:
-
-\begin{itemize}
-
-    \item \textbf{Explore}: when children actively try to find out what the
-        robot is doing (\eg by looking under the box); attentively watch or
-        observe the robot (\eg attentively waiting for the box to show a
-        reaction); experiment with the robot to figure out how it works (\eg put
-        hands in front or inside of the box to see what happens);
-
-    \item \textbf{Misuse}: when children kick the robot, poke it in its
-        ``eye'', try to climb on or inside the box, drive / push the robot
-        around, stop the robot's wheels with a foot;
-
-    \item \textbf{Put domino}: when a domino tile is put inside the box;
-
-    \item \textbf{Remove domino (rem)}: when a domino tile is removed from the
-        box;
-
-    \item \textbf{Gesture}: when gestures are used to communicate /
-        interact with the robot (\eg pointing gestures, waving at the robot);
-
-    \item \textbf{Touch}: when the box is touched (\eg petted or
-        caressed);
-
-    \item \textbf{Show}: when a child shows something to the robot (\eg
-        by holding a domino tile in front of its eyes);
-
-    \item \textbf{Call}: when a child calls the robot to come over;
-
-    \item \textbf{Talk}: when a child directly talks to the robot (using
-        direct speech) besides calling the robot;
-
-    \item \textbf{Look}: when a child looks at the experimenter due to
-        confusion caused by the robot; look is not coded when the experimenter
-        asks a question to the child;
-
-\end{itemize}
+actions: \textbf{explore} (actively try to find out what the robot is doing, \eg
+by looking under the box; attentively watch or observe the robot; experiment
+with the robot to figure out how it works); \textbf{misuse} (kick the robot,
+poke it in its ``eye'', try to climb on or inside the box, drive/push the robot
+around, stop the robot's wheels with a foot); \textbf{put} (a domino tile is put
+inside the box); \textbf{remove} (a domino tile is removed from the box);
+\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
+pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
+petted or caressed); \textbf{show} (show something to the robot; \textbf{call}
+(call the robot to come over); \textbf{talk} (all the other case of direct
+verbal interaction); \textbf{look} (when a child looks \emph{at the
+experimenter} due to confusion caused by the robot; look is not coded when the
+experimenter asks a question to the child);
 
@@
 \footnotesize
-\begin{tabular}{p{0.9\linewidth}}
+\begin{tabular}{p{1\linewidth}}
     \toprule
@@
 
-\textbf{Perception: \textit{(max. 13 points)}}
+\textbf{Perception}: \textit{(max. 13 points)}
+
 \begin{itemize}
-	\item Ascribe \textbf{mental states / feelings} to Ranger: \textit{0-4 points}\\
-	(2 points for agreeing that Ranger can be happy or sad; 2 points for attributing Ranger with hunger or tiredness)
-	\item Ascribe \textbf{cognitive abilities / intention} to Ranger: \textit{0-4 points}\\ 
-	(each 0.5 points for ascribing seeing and hearing ability; 1 point for agreeing that Ranger can go out the door by itself; 1 point for disagreeing that Ranger always obeys; 1 point for agreeing that Ranger can do something silly)
-	\item Ascribe \textbf{sociality / companionship} to Ranger: \textit{1 point}\\ 
-	(1 point for agreeing that Ranger can be a friend)
-	\item Ascribe \textbf{moral standing} to Ranger: \textit{1 point}\\ (1 point for disagreeing that Ranger be left alone at home)
-	\item Other \textbf{anthropomorphic statements}: \textit{0-3 points}\\ 
-	(1 point for anthropomorphic reason for Ranger's misbehaviour; 2 points for anthropomorphic reason for not leaving Ranger alone) 
+    \item Ascription of \textbf{mental states / feelings}: \textit{2 points} for agreeing
+            that Ranger can be happy or sad; \textit{2 points} for attributing Ranger with
+        hunger or tiredness.
+
+    \item Ascription of \textbf{cognitive abilities / intention}: each \textit{0.5
+        points} for ascribing seeing and hearing ability; \textit{1 point} for agreeing
+            that Ranger can go out the door by itself; \textit{1 point} for disagreeing that
+            Ranger always obeys; \textit{1 point} for agreeing that Ranger can do something
+        silly.
+
+    \item Ascription of \textbf{sociality / companionship}: \textit{1 point} for agreeing
+        that Ranger can be a friend.
+
+    \item Ascription of \textbf{moral standing}: \textit{1 point} for disagreeing that
+        Ranger be left alone at home.
+
+    \item Other \textbf{anthropomorphic statements}: \textit{1 point} for anthropomorphic
+        reason for Ranger's misbehaviour; \textit{2 points} for anthropomorphic reason
+        for not leaving Ranger alone.
+
 \end{itemize}
 
-\textbf{behaviour: \textit{(max. 3 points)}}
+\textbf{Behaviour}: \textit{(max. 3 points)}
 \begin{itemize}
-	\item Use of \textbf{direct speech} toward Ranger: \textit{1 point}\\
-	(\textit{calling} the robot to come over is not considered)
-	\item Use of \textbf{polite formulations} toward Ranger: \textit{1 point}\\ 
-	(\eg saying \textit{``thank you Ranger''} or \textit{``please Ranger ...''} or \textit{``goodbye''})
-	\item Use of \textbf{social or pointing gestures} toward Ranger: \textit{1 point}\\ 
-	(\eg waving at the robot, nodding)
+    \item Use of \textbf{direct speech}: \textit{1 point} (not considering
+        \textit{calling} the robot to come over).
+
+    \item Use of \textbf{polite formulations}: \textit{1 point} (\eg
+        \textit{``thank you Ranger''} or \textit{``please Ranger ...''}).
+
+    \item Use of \textbf{social or pointing gestures}: \textit{1 point} (\eg
+        waving at the robot).
+
 \end{itemize}
@@
     \centering
-    \includegraphics[width=1.0\linewidth]{domino-why-misbehavior.pdf}   
+    \includegraphics[width=0.8\linewidth]{domino-why-misbehavior.pdf}   
     \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
@@
     \centering
-    \includegraphics[width=0.7\linewidth]{domino-intention.pdf}
+    \includegraphics[width=0.75\linewidth]{domino-intention.pdf}
     \caption{\small \textbf{Attribution of intention to Ranger.} Children were
@@
     \centering
-    \includegraphics[width=0.8\columnwidth]{domino-correlation.pdf}
+    \includegraphics[width=0.7\columnwidth]{domino-correlation.pdf}
 

### 2014-10-01 paper.tex
British english

@@
 and phenomenological) metric for the attribution of human-like features to
-robot. We are especially interested in investigating how this indicator predicts
-and/or reflects actual \emph{engagement} into the interaction.
+a robot. We are especially interested in investigating how this indicator predicts
+and/or reflects actual \emph{engagement} in the interaction.
 
@@
 
-In the Domino Study, we analyze child-robot interaction with a robot that shows
+In the Domino Study, we analyse child-robot interaction with a robot that shows
 unexpected behaviour. In a playful scenario which was set up in a laboratory
@@
 
-We analyzed children's reaction focusing on two main aspects. On one hand,
+We analysed children's reaction focusing on two main aspects. On one hand,
 children's \textbf{behaviour} (their reactions) toward the unexpected robot
 behaviour was studied in terms of \textbf{active engagement} with the robot. On
-the other hand, we analyzed children's \textbf{perception} of the robot in term
+the other hand, we analysed children's \textbf{perception} of the robot in term
 of \textbf{anthropomorphism} -- the attribution of human-like characteristics,
@@
 partial wooden surface. It is remotely controlled, it can move around a flat
-surface, move its eyes and eyebrows, display colors (LEDs) and light patterns,
+surface, move its eyes and eyebrows, display colours (LEDs) and light patterns,
 and play sounds through Bluetooth speakers.  The robot was controlled by a human
@@
 from kindergarten, nursery school or because they lived in the same
-neighborhood. 2 of the pairs were composed of brother and sister.
+neighbourhood. 2 of the pairs were composed of brother and sister.
 
@@
 
-The interviews were analyzed in a qualitative manner (we qualitatively
+The interviews were analysed in a qualitative manner (we qualitatively
 transcribed interviews, \ie we did not craft a full word-by-word transcript but
@@
 Now, still 11 children (previously 12) believed Ranger would always obey to
-them. When analyzing the answers of each child separately, there were 2 children
+them. When analysing the answers of each child separately, there were 2 children
 in the \textit{disobey} condition that changed their answer from \textit{yes} to
@@
 to the robot. Asked for more details, several children answered that it is
-through its colors and sounds that the robot shows a feeling. Most children said
+through its colours and sounds that the robot shows a feeling. Most children said
 that they could make the robot feel happy by playing with it and putting a

### 2014-10-01 paper.tex
Integrated most of Julia 'little things' + a few from Pierre

@@
 \title{\LARGE \bf
-How Children Perceive and Interact with a Robot that Behaves Unexpectedly -- The Domino Experiment
+How Children Perceive and Interact with a Robot that Behaves Unexpectedly
 }
@@
 \begin{document}
+\sloppy % prevent margin overflow
 \maketitle
@@
 While we found only a limited recognition of the different misbehaviours of the
-robot that we attribute to the age of the subject (M=4.46), interesting findings
-include a sustained engagement level, an unexpectedly low level of attribution
-of higher cognitive abilities and a \emph{negative} correlation between
-anthropomorphic projections and actual behavioural engagement.
+robot that we attribute to the age of the child participants (M=4.46),
+interesting findings include a sustained engagement level, an unexpectedly low
+level of attribution of higher cognitive abilities and a \emph{negative}
+correlation between anthropomorphic projections and actual behavioural
+engagement.
 
 Besides, this study operationalizes for the first time the
-\emph{anthropomorphism index} proposed by~\cite{fink2014dynamics}, which proves a
-valuable tool to assess qualitative psycho-behavioural episodes occurring during
-human-robot interaction.
+\emph{anthropomorphism index} proposed by~\cite{fink2014dynamics}, which can be
+considered as an effective tool to assess qualitative psycho-behavioural
+episodes occurring during human-robot interaction.
 
@@
 \section{Introduction}
-\subsection{Towards Sustained Engagement}
+\subsection{Towards Engagement}
 
@@
 engagement of children with a chess playing robot that adapted its behaviour to
-the children and showed empathy toward them. She found that empathetic robots
+the children and showed empathy toward them. The authors found that empathetic robots
 are more likely to engage users in the long-term and they proposed several
@@
 unexpectedly can increase engagement and mental state attribution without
-complex behavioural or mechanical additions.''}.  Along those lines, Fink
+complex behavioural or mechanical additions.''}  Along those lines, Fink
 \etal\cite{fink2014dynamics} also suggest in their model of the dynamics of
-anthropomorphism, that \emph{disruptive behaviours} may lead to increased
+anthropomorphism in HRI, that \emph{disruptive behaviours} may lead to increased
 anthropomorphic projections and possibly engagement.
 
-Based on these previous researches, we would like to find out in this study how
+Based on this previous research, we would like to explore in this study how
 we can enhance children's experience with the robot so that they do not find it
@@
         malfunction (a bug or system error which causes the robot to not work
-        correctly), and hypothesize decreased attributions of human-likeness to
+        correctly), and hypothesise decreased attributions of human-likeness to
         the robot.\footnote{We use interchangeably \textit{attribution of
@@
 
-    \item The robot \textbf{disobey}: When called by the child to come over, the
-        robot shows it refuses to obey by literally ``shaking its head'' and
+    \item The robot \textbf{disobeys}: When called by the child to come over, the
+        robot shows that it refuses to obey by literally ``shaking its head'' and
         becoming red. The robot then goes to a wrong location and remains there
@@
     \item The robot makes a \textbf{mistake}: When called by the child to come
-        over, the robot goes wrong but recognizes its mistake and repairs. We
+        over, the robot goes wrong but recognises its mistake and repairs. We
         expect this to be perceived (explicitly) as \textit{``to err is
         human''}, and (implicitly) as the robot being endowed with a certain
-        level of introspective capabilities (it was able to recognize its own
+        level of introspective capabilities (it was able to recognise its own
         error). In this condition, we assume increased attributions of
@@
         appears to have a system error, \ie the disobeying robot and the robot
-        that makes a mistake will be more anthropomorphized than the robot that
+        that makes a mistake will be more anthropomorphised than the robot that
         gets lost (between subjects variable).
@@
 perception but also as an observable behaviour in the interaction itself. Thus,
-we would like to bridge things together and, relying on the concept of
+we would like to bring things together and, relying on the concept of
 anthropomorphism index~\cite{fink2014dynamics}, build a compound metric that
@@
 
-\subsection{Scenario and course of the study}
-
-\subsubsection{Experimental setting}
+\subsection{Scenario and Course of the Study}
+
+\subsubsection{Experimental Setting}
 
@@
         behind each of which 3 domino tiles are distributed (displayed as black
-        stars). A playground with a river drawn on it is used as an imaginary
+        stars). A play mat with a river drawn on it is used as an imaginary
         barrier that only the robot is allowed to cross. The solid green arrows
         show the robot's path for the \textit{correct} behaviour. The blue
-        dashed arrow visualizes a possible \textit{lost} path, where the Ranger
-        stops and remains at a wrong stop. The yellow arrows reflect a possible
+        dashed arrow visualises a possible \textit{lost} path, where the Ranger
+        stops and remains at a wrong spot. The yellow arrows reflect a possible
         \textit{mistake} path, where the robot goes wrong but then turns back
-        and goes to the child. The red dashed arrow visualizes a possible
+        and goes to the child. The red dashed arrow visualises a possible
         \textit{disobey} path where the robot goes wrong, then turns toward the
@@
 \textit{the receiver} -- is asked to stay in a play tent. There is a ``river''
-(playground) in between the two children that we told them they cannot cross
+(play mat) in between the two children that we told them they cannot cross
 and therefore they need the robot to transport the domino tiles between them.
@@
 receiver child asks the searcher child for a specific tile, \eg a tile with a
-donkey, the searcher searches for the respective tile, sits down on the next
+donkey, the searcher child searches for the respective tile, sits down on the next
 beanbag, and asks the robot to come over.  The Ranger robot is first located
@@
 study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
-French-speaking. In 11 of the pairs, children were friends who knew each other
+French-speaking. We based our age range choice on a previous study ``in the
+wild''~\cite{fink2014which} that suggested that younger children (4-6 years)
+interacted more effectively with the Ranger robot.
+
+In 11 of the pairs, children were friends who knew each other
 from kindergarten, nursery school or because they lived in the same
-neighbourhood. 2 of the pairs were composed of brother and sister.
-
-\subsubsection{Course of the study}
+neighbourhood. 2 of the pairs were composed of brother and sister. One parent
+would generally attend, sit on a chair behind the children.
+
+\subsubsection{Course of the Study}
 
 In our study, there were a total of 14 runs, and at each run, the robot exhibits
-one out of four possible behaviours: \emph{correct}, \emph{lost}
-\emph{disobey} or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
+one out of four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey}
+or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
 the baseline and the robot always behaved correctly. The children then switched
-the roles and in the 9 remaining runs (\emph{2.1} to \emph{2.9}), the robot
-showed one of the misbehaviour (\emph{lost}, \emph{disobey} or \emph{mistake})
-at the $3^{rd}$ and $4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run
-(see Figure~\ref{fig:domino-time-active}). The study is build as a
-between-subject study, and the type of misbehaviour was therefore always the
-same for a given group.
+the roles receiver/searcher and in the 9 remaining runs (\emph{2.1} to
+\emph{2.9}), the robot showed one of the misbehaviours (\emph{lost},
+\emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
+the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}). The
+study is built as a between-subject study, and the type of misbehaviour was
+therefore always the same for a given group.
 
 Special attention has been paid to the distribution of misbehaving runs during
-the study. The five first correct runs aims at setting the children expectation
+the study. The five first correct runs aim at setting the children's expectation
 regarding a consistent robot behaviour. When the robot then exhibits an
@@
 time~\cite{short_no_2010}).  Besides, to prevent the robot misbehaviours to be
-immediately interpreted as failures, we introduce these misbehaviour neither at
-the very beginning nor at very end of the interaction
-(\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
+immediately interpreted as failures, we introduce these misbehaviours neither at
+the very beginning nor at the very end of the interaction.
+\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
 failures negatively impact trust. \cite{short_no_2010} also adopted a similar
-pattern when introducing unexpected robot behaviour).
+pattern when introducing unexpected robot behaviour.
+
+%
+%\begin{figure}[!t]
+%    \centering
+%    \subfloat[lost]{
+%        \label{fig:domino-lost}
+%        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
+%    }
+%    \subfloat[disobey]{
+%        \label{fig:domino-disobey}
+%        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
+%    }
+%    \subfloat[mistake]{
+%        \label{fig:domino-mistake}
+%        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
+%    }
+%    \caption{\small The three robot misbehaviours.}
+%    \label{fig:domino-misbehaviour}
+%\end{figure}
 
@@
     \centering
-    \subfloat[lost]{
-        \label{fig:domino-lost}
-        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
-    }
-    \subfloat[disobey]{
-        \label{fig:domino-disobey}
-        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
-    }
-    \subfloat[mistake]{
-        \label{fig:domino-mistake}
-        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
-    }
-    \caption{\small The three robot misbehaviours.}
+    \includegraphics[width=0.6\columnwidth]{domino-disobey.png}
+    \caption{\small The experimental setup, here in the \emph{disobey} condition.}
     \label{fig:domino-misbehaviour}
@@
     with its ``face'' turned away from the child, and it blinks in yellow light,
-    as if it was in front of a child. Ranger remains waiting at the wrong
+    as it would only do when in front of a child. Ranger remains waiting at the wrong
     position until the experimenter tells the child to go over to the robot to
@@
     Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
-    toward the sender child. In addition to the red blinking, Ranger
+    toward the searcher child. In addition to the red blinking, Ranger
     makes a slow wiggle-like move, and remains waiting at the wrong position
@@
 
-    \item \textbf{Mistake:} The sender child calls Ranger. The robot goes until
+    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
     it is on the carpet, stops, turns, and goes wrong (see yellow path in
     Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
-    ``face'' toward the sender child, and ``blushes'' red around its ``cheeks''
-    (as if it recognizes its wrong position) and finally goes correctly over to
-    the sender child. The \textit{mistake} behaviour is \textit{robot-repaired},
+    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
+    (as if it recognises its wrong position) and finally goes correctly over to
+    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
     as no human-intervention is needed.
@@
 
-On its way back to the tent, Ranger always goes correctly. After the sender
+On its way back to the tent, Ranger always goes correctly. After the searcher
 child has put a domino tile, Ranger automatically turns and goes over to the
@@
 
-\subsection{Data collection}
+\subsection{Data Collection}
 
 We have obtained and analysed two types of data. The \textbf{children's
-behaviours toward the robot} (\ie the child-robot interactions) have been
+behaviour toward the robot} (\ie the child-robot interactions) have been
 captured in the video recordings by annotating a set of actions, described
-below. The children's \textbf{phenomenological perception of the robot} has been
+below. Children's \textbf{phenomenological perception of the robot} has been
 captured through two audio-recorded semi-structured interviews which took place
-between run \emph{1.5} and \emph{2.1} and at the end of the 14 runs.
-
-\subsubsection{Interaction: Action coding}
+between run \emph{1.5} and \emph{2.1} and at the end of the experiment. A
+short preliminary interview was also conducted to explain the game and assess
+the expectations of the children toward the robot.
+
+\subsubsection{Interaction: Action Coding}
 
@@
 We annotated children's behaviour in the video records, and coded 10 different
-actions: \textbf{explore} (actively try to find out what the robot is doing, \eg
-by looking under the box; attentively watch or observe the robot; experiment
-with the robot to figure out how it works); \textbf{misuse} (kick the robot,
-poke it in its ``eye'', try to climb on or inside the box, drive/push the robot
-around, stop the robot's wheels with a foot); \textbf{put} (a domino tile is put
-inside the box); \textbf{remove} (a domino tile is removed from the box);
+actions (the coding scheme has been inspired from~\cite{fink2014which}):
+\textbf{explore} (actively try to find out what the robot is doing, \eg by
+looking under the box; attentively watch or observe the robot; experiment with
+the robot to figure out how it works); \textbf{misuse} (kick the robot, poke it
+in its ``eye'', try to climb on or inside the box, drive/push the robot around,
+stop the robot's wheels with a foot); \textbf{put} (a domino tile is put inside
+the box); \textbf{remove} (a domino tile is removed from the box);
 \textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
 pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
-petted or caressed); \textbf{show} (show something to the robot; \textbf{call}
-(call the robot to come over); \textbf{talk} (all the other case of direct
+petted or caressed); \textbf{show} (show something to the robot); \textbf{call}
+(call the robot to come over); \textbf{talk} (all the other cases of direct
 verbal interaction); \textbf{look} (when a child looks \emph{at the
@@
 
-The actions \textit{put, remove} and \textit{call} were ``requested'' actions
+The actions \textit{put, remove} and \textit{call} are ``requested'' actions
 that the children had to perform in the scenario. On the contrary,
@@
 Figure~\ref{fig:domino-time-active} shows the distribution of these actions over
-the different runs, in summed over the three condition.
-
-\subsubsection{Phenomenological perception: semi-structured interviews}
-
-One pre-interview and two interviews (between run \emph{1.5} and \emph{2.1} and
-at the end) were conducted with the children.  We set up the interviews like a
-casual conversation / discussion, so we did not separate the two children in
-order to keep the situation natural. We used casual and informal language
-adapted to the age of the children, and encouraged them to justify their answers
-and tell us more details by asking, for example, \textit{How do you know ... ?}
-or \textit{Tell me, what have you observed when ... ?}. We paid attention to not
-``put words in children's mouth''. Consequently, though we re-phrased and
-repeated some questions, we never forced children to give an answer, and
-accepted when they said they would not know or when they did not respond at all.
+the different runs, over the three condition.
+
+\subsubsection{Perception: Semi-Structured Interviews}
+
+One pre-interview and two interviews were conducted with the children.  We set
+up the interviews like a casual conversation / discussion, so we did not
+separate the two children in order to keep the situation natural. We used casual
+and informal language adapted to the age of the children, and encouraged them to
+justify their answers and tell us more details by asking, for example,
+\textit{How do you know ... ?} or \textit{Tell me, what have you observed when
+... ?}. We paid attention to not ``put words in children's mouth''.
+Consequently, though we re-phrased and repeated some questions, we never forced
+children to give an answer, and accepted when they said they would not know or
+when they did not respond at all.
 
@@
 perception of robots
-\cite{kahn_jr._robotic_2006,weiss_i_2009,leite_influence_2013}. For instance, we
+\cite{kahn_jr._robotic_2006,leite_influence_2013,weiss_i_2009}. For instance, we
 applied and adapted some of the \emph{constructs} and example questions from the
@@
         reason for Ranger's misbehaviour; \textit{2 points} for anthropomorphic reason
-        for not leaving Ranger alone.
+        for not leaving Ranger alone (\eg \textit{``It would be sad''}).
 
@@
 
-\subsection{Misbehaviour recognition and engagement}
-
-As stated in the introduction, we had hypothesized that the \textit{disobey}
+\subsection{Misbehaviour Recognition and Interaction Engagement}
+
+\paragraph{Misbehaviour Recognition}
+
+As stated in the introduction, we had hypothesised that the \textit{disobey}
 behaviour is perceived as the robot intentionally not doing what it should do.
@@
 
-When asked why they thought the robot had not always come
-over to them, 4 of the children did not reply. The remaining ones gave a variety
-of reasons (Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9
-of 37 replies) was that the robot is somehow \textit{unpredictable} in what it
-is doing and that it could go \textit{no matter where}\footnote{We translated
+When asked why they thought the robot had not always come over to them, 4 of the
+children did not reply. The remaining ones gave a variety of reasons
+(Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9 of 37
+replies) was that the robot is somehow \textit{unpredictable} in what it is
+doing and that it could go \textit{``no matter where''}\footnote{We translated
 children's answers from French to English. For some expressions the meaning
@@
 (including \textit{broken parts}), suggesting that children perceived the
-misbehaviour as unintended by the robot. 2 of the children who had interacted
+misbehaviour as unintended by the robot. Two of the children who had interacted
 with the disobeying robot said Ranger was \textit{angry}, which none of the
-children in other conditions replied. Several children ascribed intentionality
-to Ranger explaining that it \textit{did not want to continue} carrying domino
-tiles or that it \textit{made a mistake / did something silly}\footnote{We
-understood \textit{``faire une bêtise''} as ``to do a silly thing'' in the sense
-of making a mistake.}.
+children in other conditions replied. 13 out of 26 children appeared to ascribe
+intentionality precursors to Ranger explaining that it \textit{did not want to
+continue} carrying domino tiles or that it \textit{``did something
+silly''}\footnote{We understood \textit{``faire une bêtise''} as ``to do a silly
+thing'' in the sense of making a mistake.}.
 
@@
 
+\paragraph{Engagement}
 In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
@@
 interaction with the robot. Furthermore, data suggests that the robot in the
-\textit{mistake} and \textit{lost} condition were more engaging for children
+\textit{mistake} and \textit{lost} condition was more engaging for children
 (each 75~\% of the actions reflected engagement) than the robot in the
@@
 all three conditions, children carried out more engagement actions with the
-unexpectedly behaving robot (Figure~\ref{fig:domino-time-active}). No
-interaction effect was found between the two phases of interaction (expected /
-unexpected) and condition (F(2,36)=1.2, p=.31). In general, this finding
-supports our first hypothesis: children show more engagement toward a robot that
-behaves unexpectedly from time to time compared to a robot that always behaves
-correctly.
-
-\subsection{Attribution of higher cognitive skills}
+unexpectedly behaving robot. No interaction effect was found between the two
+phases of interaction (expected / unexpected) and condition (F(2,36)=1.2,
+p=.31). In general, this finding supports our first hypothesis: children show
+more engagement toward a robot that behaves unexpectedly from time to time
+compared to a robot that always behaves correctly.
+
+\subsection{Attribution of Higher Cognitive Skills}
 
 \paragraph{Intentionality}
+
+One of the central points of this study was to investigate to what degree
+children attribute intention and cognitive abilities to the robot.  In the first
+interview after children had interacted with the correctly behaving robot we
+asked three questions to assess how far they ascribe \textbf{intention} to it
+(see questionnaire items in Table~\ref{tab:domino-questions}). One of these
+questions was whether they believed Ranger could go out the door by itself. The
+majority of 16 children answered negatively, which suggests that they initially
+do not ascribe intention to the robot. The two other questions were whether
+Ranger would always obey and whether Ranger could do a silly thing
+(Figure~\ref{fig:domino-intention}). These two questions were asked again later
+after children had interacted with the unexpectedly behaving robot.
+
+%	With these recurring questions we wanted to see whether children had changed
+%	their mind in terms of ascribing intention to Ranger (and whether the
+%	unexpected robot behaviour had caused this effect). This comparison turned
+%	out to be difficult, however.
 
@@
 
-One of the central points of this study was to investigate to what degree
-children attribute intention and cognitive abilities to the robot.  In the first
-interview after children had interacted with the correctly behaving robot we
-asked three questions to assess how far they ascribe \textbf{intention} to it
-(see questionnaire items in Table~\ref{tab:domino-questions}). One of these
-questions was whether they believed Ranger could go out the door by itself. The
-majority of 16 children answered negatively, which suggests that they initially
-do not ascribe intention to the robot. The two other questions were whether
-Ranger would always obey and whether Ranger could do a silly thing
-(Figure~\ref{fig:domino-intention}). These two questions were asked again later
-after children had interacted with the unexpectedly behaving robot.
-
-%	With these recurring questions we wanted to see whether children had changed
-%	their mind in terms of ascribing intention to Ranger (and whether the
-%	unexpected robot behaviour had caused this effect). This comparison turned
-%	out to be difficult, however.
-
 Overall, in the first interview 12 of the 26 children believed Ranger does
 always obey to them. Asked whether Ranger could do something silly, the great
-majority of 21 children replied negatively. We can summarize that after children
+majority of 21 children replied negatively. We can summarise that after children
 had interacted with the \textbf{correctly behaving robot} the majority does
@@
 
-We can summarize that even with the \textbf{unexpectedly behaving robot}
+We can summarise that even with the \textbf{unexpectedly behaving robot}
 children do \textbf{not necessarily ascribe intention} to the robot. The
@@
 
-\paragraph{Emotions}
-
-We examined whether children attributed \textbf{feelings} to the robot by asking
+\paragraph{Emotions and Companionship}
+
+We examined whether children attribute \textbf{feelings} to the robot by asking
 them (once at the end of the experiment) if they thought that Ranger can feel
@@
 another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
-all. Overall, data suggests that \textbf{children attributed emotional states}
+all. Overall, data suggests that \textbf{children attribute emotional states}
 to the robot. Asked for more details, several children answered that it is
@@
 20 out of 26 children responded negatively. Asked why, children gave a
-variety of answers that we classified into 7 categories. With 5 replies, the
+variety of answers that we classified into 6 categories. With 5 replies, the
 most common answer was that the robot ``could do something silly''. Some other
@@
 be put into perspective and even young children do not automatically consider a
-so-called social robot as an actual social agent.
+so-called social robot as an actual social agent that deserves care.
 
@@
 
-\subsection{Anthropomorphic projections and social engagement}
+\subsection{Anthropomorphic Projections and Social Engagement}
 
@@
 
-On average, Ranger was moderately anthropomorphized by the
-children. 8 of the 13 groups had an index of 8 or higher, evenly spread
-over the three conditions (Table~\ref{tab:domino-anth-score}). However, the mean
-index of anthropomorphism in the three conditions varied, with the
-\textit{mistake} and \textit{lost} condition leading to a higher index than the
-\textit{disobey} condition. This finding suggests that the disobeying robot was
-less anthropomorphized than the other two robot behaviours, which speaks against
-our second hypothesis. We had expected that the disobeying behaviour is
-perceived as an intentional action which we assumed would lead to increased
-anthropomorphism. This was not the case. The slight difference between the
-\textit{lost} and \textit{mistake} robot was also expected in the opposite
-direction. It could be that the robot's ``helplessness'' led to this. With the
-lost robot, children looked more often at the experimenter than in the other
-condition, which suggests that they could not fully make sense of the robot's
-behaviour, and the fact of not being able to understand (and hence predict) a
-robot's behaviour is likely to increase anthropomorphism.\footnote{One of the
-cognitive / psychological explanations for anthropomorphism is that people
-want to make sense of something they do not understand and then tend to
-anthropomorphize this something (human traits are a good source of making
-attributions because this is what people understand best -- themselves and
-other humans). For more details the reader may refer to
-\cite{epley_seeing_2007}.}
+On average, Ranger was moderately anthropomorphized by the children. 8 of the 13
+groups had an index of 8 or higher, evenly spread over the three conditions
+(Table~\ref{tab:domino-anth-score}). However, the mean index of anthropomorphism
+in the three conditions varied, with the \textit{mistake} and \textit{lost}
+condition leading to a higher index than the \textit{disobey} condition. This
+finding suggests that the disobeying robot was less anthropomorphized than the
+other two robot behaviours, which speaks against our second hypothesis. We had
+expected that the disobeying behaviour is perceived as an intentional action
+which we assumed would lead to increased anthropomorphism. This was not the
+case. The slight difference between the \textit{lost} and \textit{mistake} robot
+was also expected in the opposite direction. It could be that the robot's
+``helplessness'' led to this. This is also reflected in children's behaviour:
+with the lost robot, children looked more often at the experimenter than in the
+other condition, which suggests that they could not fully make sense of the
+robot's behaviour, and the fact of not being able to understand (and hence
+predict) a robot's behaviour is likely to increase
+anthropomorphism.\footnote{One of the cognitive / psychological explanations for
+anthropomorphism is that people want to make sense of something they do not
+understand and then tend to anthropomorphize this something (human traits
+are a good source of making attributions because this is what people
+understand best -- themselves and other humans). For more details the reader may
+refer to \cite{epley_seeing_2007}.}
 
@@
 
-We hypothesized that children who interact a lot and are probably more engaged
+We hypothesised that children who interact a lot and are probably more engaged
 with the robot also perceive the robot as more human-like. Data suggests the
@@
     Interaction]{\small \textbf{Correlation of anthropomorphic perception of the
-    robot and engagement actions.} A scatter plot of the count of engagement
-    actions (without explore) and the \textit{anthropomorphic perception} (score per
+    robot and engagement actions per group.} A scatter plot of the count of engagement
+    actions (without \emph{explore}) and the \textit{anthropomorphic perception} (score per
     group) shows a negative correlation. The score for the anthropomorphic
@@
 more but rather go on a tour outside''}. While our manipulations were not as
-clearly designed as we expected for the age range of the subjects, we still
+clearly perceived as we expected for the age range of the subjects, we still
 believe these three conditions (mechanical malfunction -- the \emph{lost}
@@
 robot perceived it as less human-like. This raises an important question for the
-human-robot interaction community: to what extent anthropomorphic perceptions
-impact the interaction experience. Our findings here go against the intuition.
+human-robot interaction community: to what extent do anthropomorphic perceptions
+impact the interaction experience? Our findings here go against the intuition.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgments}
-
-This research was supported by the Swiss National Science Foundation through the
-National Centre of Competence in Research Robotics.
+% double blind review
+%\section*{Acknowledgements}
+%
+%This research was supported by the Swiss National Science Foundation through the
+%National Centre of Competence in Research Robotics.
 

### 2014-10-01 paper.tex
Implemented most of Pierre's comments

@@
 
-Using a playful domino game as the interaction scenario, we refer to this study
-hereafter as the \textbf{``Domino Study''}.
-
 This study also aims at assessing the effectiveness of the \emph{anthropomorphic
@@
 
-In the Domino Study, we analyse child-robot interaction with a robot that shows
-unexpected behaviour. In a playful scenario which was set up in a laboratory
-environment, 26 children aged 4-5 years (MD=4.46) were assembling a domino game together.
-Each group consisted of two children and the \emph{Ranger} robot, which was used
-to transport domino tiles between the two children.
+We analyse child-robot interaction with a robot that shows unexpected behaviour.
+In a playful scenario which was set up in a laboratory environment, 26 children
+aged 4-5 years (MD=4.46) were assembling a domino game together. Each group
+consisted of two children and the \emph{Ranger} robot, which was used to
+transport domino tiles between the two children.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Domino study}
+\section{Research Methodology}
 
@@
 
-The interviews were analysed in a qualitative manner (we qualitatively
-transcribed interviews, \ie we did not craft a full word-by-word transcript but
+We did not craft a full word-by-word transcript but
 noted down any statement that was useful and relevant) and used to compute the
@@
 
-We have measured engagement by combining \emph{interaction}
-data with the results of the semi-structured interviews.  Several of the
-aforementioned coded actions can reflect engagement: \textit{explore, misuse,
-gesture, touch, show,} and \textit{talk}. Also, \textit{look} at the
-experimenter can be considered as engagement in the interaction: We assume that
-children look at the experimenter when they are surprised and seek for help.
-This behaviour reflects that they want to make sense of the robot's behaviour and
-that they notice it as ``strange''. Further, we can take into account how they
-refer to Ranger and describe the robot (as well as their experience) in the
-interviews.  Specifically, we used the constructs \textit{ascribe intention,
-ascribe cognitive abilities, ascribe emotional state}, and \textit{ascribe
-moral standing} (Table~\ref{tab:domino-questions}) to assess how far they
-engaged with the robot.
-
-To account for the fact that anthropomorphism arises in an interaction, we tried
-to bring both children's perception of the robot (post-measurement) and their
-behaviour toward it (in-the-moment measurement) together. We did so by building
-a qualitative anthropomorphism index~\cite{fink2014dynamics}. We quantify the
+We have measured engagement by combining \emph{interaction} data with the
+results of the semi-structured interviews.  Several of the aforementioned coded
+actions can reflect engagement: \textit{explore, misuse, gesture, touch, show,}
+and \textit{talk}. Also, \textit{look} at the experimenter can be considered as
+engagement in the interaction: We assume that children look at the experimenter
+when they are surprised and seek for help.  This behaviour reflects that they
+want to make sense of the robot's behaviour. Further, we can take into account
+how they refer to Ranger and describe the robot (as well as their experience) in
+the interviews.  Specifically, we used the constructs \textit{ascribe intention,
+ascribe cognitive abilities, ascribe emotional state}, and \textit{ascribe moral
+standing} (Table~\ref{tab:domino-questions}) to assess how far they engaged with
+the robot.
+
+To account for the fact that anthropomorphism arises in an interaction, we bring
+both children's perception of the robot (post-measurement) and their behaviour
+toward it (in-the-moment measurement) together. We did so by building a
+anthropomorphism index~\cite{fink2014dynamics}. We quantify the
 index by attributing points for each anthropomorphic \emph{perception} of the
@@
 There are certainly limitations to this scoring scheme. For instance, the
-balance between perception and behaviour aspects is questionable (13 to 3
-points). Also, we did not consistently assign 1 point to each item, but assigned
-points between 0.5 and 2 points. We did this because we found that different
-items reflect a higher level of anthropomorphic perception of the robot than
-others (for instance, ascribing the ability to see and hear was suggested by our
-study setup, and we cannot be sure that it really reflects anthropomorphism).
+balance between perception and behaviour aspects is questionable and the
+weighting of each item can be discussed: we did not consistently assign 1 point
+to each item, but assigned points between 0.5 and 2 points depending on our
+perception of how a given item reflect on a higher level of anthropomorphic
+perception of the robot (for instance, ascribing the ability to see and hear was
+suggested by our study setup, and we cannot be sure that it really reflects
+anthropomorphism). We believe however that the approach remains valid,
+considering that the anthropomorphism index is primarily a \emph{comparison}
+metric and not an absolute value.
 
@@
 
-Overall, we can notice that not all children perceived the misbehaviour of the
-robot as we had intended and we have to keep this in mind while interpreting the
-data. Also \cite{leite_long-term_2013} found in her study that when children did
-not understand an action of the robot, they tended to view it as a mistake,
-rather than interpreting the robot's behaviour as a deliberative action.
+Not all children perceived the misbehaviour of the robot as we had intended and
+we have to keep this in mind while interpreting the data. Also
+\cite{leite_long-term_2013} found in her study that when children did not
+understand an action of the robot, they tended to view it as a mistake, rather
+than interpreting the robot's behaviour as a deliberative action.
 
@@
 In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
-here. The findings here do not directly address the issues
+here. The findings do not directly address the issues
 of long-term usage but concern short-term \textit{engagement}, which is a
@@
 After they had interacted with the misbehaving robot, we asked children again.
-Now, still 11 children (previously 12) believed Ranger would always obey to
-them. When analysing the answers of each child separately, there were 2 children
-in the \textit{disobey} condition that changed their answer from \textit{yes} to
-\textit{no}; however also 1 child in the \textit{lost} condition that switched
-their answer in the opposite way (strangely). There was a more remarkable change
-when asking children whether Ranger could do something silly. In the second
-interview, 8 children (previously~3) answered Ranger could do something silly. 1
-child in the \textit{disobey} condition had changed their answer, and each 2 in
-the \textit{mistake} and \textit{lost} condition.
+Still 11 children believed Ranger would always obey to them. There was a
+more remarkable change when asking children whether Ranger could do something
+silly. In the second interview, 8 children (previously~3) answered Ranger could
+do something silly. 1 child in the \textit{disobey} condition had changed their
+answer, and each 2 in the \textit{mistake} and \textit{lost} condition.
 
@@
 the majority of the children in this condition was still convinced that the
-robot could not do a silly thing.  It it interesting to note that children tend
+robot could not do a silly thing.  It is however interesting to note that children tend
 to ascribe cognitive abilities to the robot, like the ability to see and hear
@@
 anthropomorphism indexes for both children were similar (difference less than
-1.5 points), which means that both children anthropomorphized the robot to a
-similar degree. This agreement among children happened for both higher and lower
+1.5 points). This agreement among children happened for both higher and lower
 indexes. In 6 of the 13 groups, the anthropomorphism indexes varied in more than
@@
 with the robot also perceive the robot as more human-like. Data suggests the
-opposite, however. As shown in Figure~\ref{fig:domino-anthropo-interaction}, we
-found a significant \textit{negative} correlation between the count of
-engagement actions (per group) and the qualitative anthropomorphism index
-(r(11)=-0.56, p=.05).
-
-%	(b=-.05, t(11)=-2.22, p=.048).
-
-The overall model with the count of engagement actions (per group) predicts a
-significant proportion of the qualitative anthropomorphism index (adjusted
-R$^2$=.25, F(1,11)=4.9, p=.05). This means that the more a group showed
-engagement in the interaction, the less they anthropomorphized the robot. This
-is a key results, which was against our initial assumption. A possible
-interpretation is that children who interact more with the robot understand better
-how it works, they are more familiar with it, and as such the robot appears less
-``mystical'' to them, so there is not a big need to anthropomorphize it. On the
-contrary, the cluster of groups that do not interact much but anthropomorphize
-the robot more, is quite homogeneous. The negative correlation between the
-number of engagement actions and the anthropomorphism index suggests that
-children who interact more with the robot tend to anthropomorphize it less. This
-implies that anthropomorphism could fade out after some time (or rather after
-some interaction). This evokes the question how far anthropomorphism (as a
-special kind of social engagement) really helps in sustaining interaction. This
-is a critical point because most of the short-term investigations suggest that
-anthropomorphic design and human social cues emitted by a robot foster
-engagement and acceptance. What if this is not true for continued interaction,
-and thus for the long-term?  We have to be careful about our interpretation, due
-to the small sample size with which we obtained these findings. We suggest to
-investigate the aspect further in future research.
+opposite, however. As shown in Figure~\ref{fig:domino-anthropo-interaction}, 
+%(we even found a significant \textit{negative} correlation between the count of
+%engagement actions (per group) and the qualitative anthropomorphism index --
+%r(11)=-0.56, p=.05 -- but the sample size is too small to report it).  (b=-.05,
+%t(11)=-2.22, p=.048).  The overall model with the count of engagement actions
+%(per group) predicts a significant proportion of the qualitative
+%anthropomorphism index (adjusted R$^2$=.25, F(1,11)=4.9, p=.05). This means
+%that 
+the more a group showed engagement in the interaction, the less they
+anthropomorphized the robot. This is a key result, which was against our
+initial assumption. A possible interpretation is that children who interact more
+with the robot understand better how it works, they are more familiar with it,
+and as such the robot appears less ``mystical'' to them, so there is not a big
+need to anthropomorphize it. On the contrary, the cluster of groups that do not
+interact much but anthropomorphize the robot more, is quite homogeneous, and may
+reflect a certain fear of interacting with a robot that would look to them to
+human-like.
+%The negative correlation between the number of engagement actions and the
+%anthropomorphism index suggests that children who interact more with the robot
+%tend to anthropomorphize it less. This implies that anthropomorphism could fade
+%out after some time (or rather after some interaction).
+This raises the question how far anthropomorphism (as a special kind of social
+engagement) really helps in sustaining interaction. This is a critical point
+because most of the short-term investigations suggest that anthropomorphic
+design and human social cues emitted by a robot foster engagement and
+acceptance. What if this is not true for continued interaction, and thus for the
+long-term? We need to remain modest here: while we found a significant
+\emph{negative} correlation between engagement and anthropomorphism in the data
+pictured on Figure~\ref{fig:domino-anthropo-interaction} (r(11)=-0.56, p=.05),
+we have to be careful about our interpretation, due to the small sample size (13
+pairs), and we suggest to investigate the aspect further in future research.
 
@@
 
-    \caption[Correlation of Anthropomorphic Perception of the Robot and
-    Interaction]{\small \textbf{Correlation of anthropomorphic perception of the
-    robot and engagement actions per group.} A scatter plot of the count of engagement
-    actions (without \emph{explore}) and the \textit{anthropomorphic perception} (score per
-    group) shows a negative correlation. The score for the anthropomorphic
-    perception (\textit{y-axis}) does not take into account the behavioural aspect of
-    the anthropomorphism index, as this is part of the interaction
-    (\textit{x-axis}).  There seem to be two clusters of groups: those who interact
-    more with the robot and anthropomorphize it less, and those who interact less
-    but anthropomorphize the robot more.}
+    \caption{\small \textbf{Anthropomorphic perception of the robot versus
+        engagement actions per pairs.} A scatter plot of the count of engagement
+        actions (without \emph{explore}) and the \textit{anthropomorphic
+        perception} (score per group) evidence one cluster of
+        high-anthropomorphizers/low-interactors and a another group of pairs who
+        interact more with the robot and anthropomorphize it less. The score for
+        the anthropomorphic perception (\textit{y-axis}) does not take into
+        account the behavioural aspect of the anthropomorphism index, as this is
+        part of the interaction (\textit{x-axis}).}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgements}
+%
 % double blind review
-%\section*{Acknowledgements}
-%
 %This research was supported by the Swiss National Science Foundation through the
 %National Centre of Competence in Research Robotics.
+We would like to thank all the families who participated to the study.
 

### 2014-10-01 paper.tex
Down to 8 pages

@@
 \section{Introduction}
-\subsection{Towards Engagement}
+\subsection{Towards Sustained Engagement}
 
@@
         behaves unexpectedly from time to time compared to a robot that always
-        behaves correctly (within subjects variable).
+        behaves correctly.
 
@@
         appears to have a system error, \ie the disobeying robot and the robot
-        that makes a mistake will be more anthropomorphised than the robot that
-        gets lost (between subjects variable).
+        that makes a mistake will be more anthropomorphized than the robot that
+        gets lost.
 
@@
 
-\subsection{Scenario and Course of the Study}
-
-\subsubsection{Experimental Setting}
+\subsection{Experimental Setting}
 
@@
     \centering 
-    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
+    \includegraphics[width=0.8\columnwidth]{domino-setup.pdf} 
     \caption{\small \textbf{Experimental setting} One child is located in a
         tent, while the other is asked to sit on one of the three beanbags,
-        behind each of which 3 domino tiles are distributed (displayed as black
-        stars). A play mat with a river drawn on it is used as an imaginary
-        barrier that only the robot is allowed to cross. The solid green arrows
-        show the robot's path for the \textit{correct} behaviour. The blue
-        dashed arrow visualises a possible \textit{lost} path, where the Ranger
-        stops and remains at a wrong spot. The yellow arrows reflect a possible
-        \textit{mistake} path, where the robot goes wrong but then turns back
-        and goes to the child. The red dashed arrow visualises a possible
-        \textit{disobey} path where the robot goes wrong, then turns toward the
-        child but stays at a wrong position.}
+        behind each of which 3 domino tiles are distributed. A play mat with a
+        river drawn on it is used as an imaginary barrier that only the robot is
+        allowed to cross. The solid green arrows show the robot's path for the
+        \textit{correct} behaviour. The blue arrow visualises a possible
+        \textit{lost} path, where the Ranger stops and remains at a wrong spot.
+        The yellow arrows reflect a possible \textit{mistake} path, where the
+        robot goes wrong but then turns back and goes to the child. The red
+        arrow visualises a possible \textit{disobey} path where the robot goes
+        wrong, then turns toward the child but stays at a wrong position.}
 
@@
 
-We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
-pictures of cartoon farm animals (taken from a commercially available domino
-game manufactured by Djeco and adapted to the age of the children).
-
-The game (divided in several \emph{runs} that correspond each to the delivery
-and assembling of one domino tile) starts with one domino tile in front of the
-tent, where the receiver child stays and assembles the domino chain. The
-receiver child asks the searcher child for a specific tile, \eg a tile with a
-donkey, the searcher child searches for the respective tile, sits down on the next
-beanbag, and asks the robot to come over.  The Ranger robot is first located
-next to the tent, then, when called by the searcher (\textit{``Robot, come
-here!''}), it starts moving, crosses the river carpet, and comes over to the
-searcher on the beanbag. The searcher child puts the domino tile into the
-robotic box, and the robot then goes back to the receiver child in the tent.
-Then, the receiver takes out the domino tile from the robot, and puts the two
-tiles together. The first \emph{run} is over, and a new \emph{run} starts, when
-the receiver asks the searcher for the next domino tile.
-
-\subsubsection{Participants}
+%We used a self-made domino consisting of 10 wooden tiles (10~x~20~x~1.5~cm) with
+%pictures of cartoon farm animals (taken from a commercially available domino
+%game manufactured by Djeco and adapted to the age of the children).
 
@@
 
-In 11 of the pairs, children were friends who knew each other
-from kindergarten, nursery school or because they lived in the same
-neighbourhood. 2 of the pairs were composed of brother and sister. One parent
-would generally attend, sit on a chair behind the children.
-
-\subsubsection{Course of the Study}
-
-In our study, there were a total of 14 runs, and at each run, the robot exhibits
-one out of four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey}
-or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
+%In 11 of the pairs, children were friends who knew each other
+%from kindergarten, nursery school or because they lived in the same
+%neighbourhood. 2 of the pairs were composed of brother and sister. One parent
+%would generally attend, sit on a chair behind the children.
+
+\subsection{Course of the Study}
+
+The game was divided in a total of 14 runs that correspond each to the delivery
+and assembling of one domino tile. At each run, the robot exhibits one out of
+four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey} or
+\emph{mistake}.  The game starts with one domino tile in front of the tent,
+where the receiver child stays and assembles the domino chain. The receiver
+child asks the searcher child for a specific tile, \eg a tile with a donkey, the
+searcher child searches for the respective tile and sits down on the next
+beanbag. When called by the searcher (\textit{``Robot, come here!''}), the robot
+starts moving, crosses the river carpet, and comes over to the searcher on the
+beanbag. The searcher child puts the domino tile into the robotic box, and the
+robot then goes back to the receiver child in the tent which takes the tile and
+assembles it. The \emph{run} is over, and a new \emph{run} starts when the
+receiver asks the searcher for the next domino tile.
+
+The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
 the baseline and the robot always behaved correctly. The children then switched
@@
 \emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
-the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}). The
-study is built as a between-subject study, and the type of misbehaviour was
-therefore always the same for a given group.
+the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}).
+%The
+%study is built as a between-subject study, and the type of misbehaviour was
+%therefore always the same for a given group.
 
@@
 During the misbehaving runs, the robot's behaviour is manipulated in three
-possible ways (Figure~\ref{fig:domino-misbehaviour}):
-
-\begin{itemize}
-
-    \item \textbf{Lost:} After being called, Ranger goes until it is on the
-    carpet. There, it stops, turns, and goes wrong (see blue path in
-    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
-    with its ``face'' turned away from the child, and it blinks in yellow light,
-    as it would only do when in front of a child. Ranger remains waiting at the wrong
-    position until the experimenter tells the child to go over to the robot to
-    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
-    as it needs human-intervention.
-
-    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
-    carpet. It then stops, makes red
-    light all over its surface and produces a repeated ``disturbance'' sound. It
-    turns, and goes to a wrong position (see red path in
-    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
-    toward the searcher child. In addition to the red blinking, Ranger
-    makes a slow wiggle-like move, and remains waiting at the wrong position
-    until the experimenter tells the child to go over to the robot to put the
-    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.
-
-    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
-    it is on the carpet, stops, turns, and goes wrong (see yellow path in
-    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
-    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
-    (as if it recognises its wrong position) and finally goes correctly over to
-    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
-    as no human-intervention is needed.
-
-\end{itemize}
-
-In the human-repaired conditions, the experimenter instructs the searcher child
-(after ~10 sec) to bring him/herself the domino tile to the robot.
+possible ways, represented on Figure~\ref{fig:domino-setup}.
+In the \textbf{lost} condition, goes to a wrong position, and remains here,
+behaving (yellow light pattern) as if it were correctly in front of the child.
+In the \textbf{disobey} condition, the robot stops mid-way, displays a red
+pattern and produces a repeated ``annoyed'' sound. It finally moves toward a
+wrong position and remains there, facing the child. In the \textbf{mistake}
+condition, the robot starts like for the \emph{lost} behaviour, but after a few
+seconds, turns back, blushes and finally reach the correct position, in front of
+the child.
+
+%\begin{itemize}	
+%
+%    \item \textbf{Lost:} After being called, Ranger goes until it is on the
+%    carpet. There, it stops, turns, and goes wrong (see blue path in
+%    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
+%    with its ``face'' turned away from the child, and it blinks in yellow light,
+%    as it would only do when in front of a child. Ranger remains waiting at the wrong
+%    position until the experimenter tells the child to go over to the robot to
+%    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
+%    as it needs human-intervention.
+%
+%    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
+%    carpet. It then stops, makes red
+%    light all over its surface and produces a repeated ``disturbance'' sound. It
+%    turns, and goes to a wrong position (see red path in
+%    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
+%    toward the searcher child. In addition to the red blinking, Ranger
+%    makes a slow wiggle-like move, and remains waiting at the wrong position
+%    until the experimenter tells the child to go over to the robot to put the
+%    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.
+%
+%    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
+%    it is on the carpet, stops, turns, and goes wrong (see yellow path in
+%    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
+%    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
+%    (as if it recognises its wrong position) and finally goes correctly over to
+%    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
+%    as no human-intervention is needed.
+%
+%\end{itemize}
+
+Both the \textit{lost} and \emph{disobey} behaviours are
+\textit{human-repaired}, while the \emph{mistake} condition is
+\emph{robot-repaired}. In the human-repaired conditions, the experimenter
+instructs the searcher child (after ~10 sec) to bring him/herself the domino
+tile to the robot.
 
@@
     \centering 
-    \includegraphics[width=0.9\linewidth]{domino-time-active.pdf} 
+    \includegraphics[width=0.8\linewidth]{domino-time-active.pdf} 
     \caption{\small \textbf{Number and type of actions for each run} (n=480,
@@
 
-We annotated children's behaviour in the video records, and coded 10 different
+One coder annotated children's behaviour in the video records, and coded 10 different
 actions (the coding scheme has been inspired from~\cite{fink2014which}):
@@
 
-\subsubsection{Engagement}
+\subsubsection{Anthropomorphism Index}
 
@@
 
-We have measured engagement by combining \emph{interaction} data with the
-results of the semi-structured interviews.  Several of the aforementioned coded
-actions can reflect engagement: \textit{explore, misuse, gesture, touch, show,}
-and \textit{talk}. Also, \textit{look} at the experimenter can be considered as
-engagement in the interaction: We assume that children look at the experimenter
-when they are surprised and seek for help.  This behaviour reflects that they
-want to make sense of the robot's behaviour. Further, we can take into account
-how they refer to Ranger and describe the robot (as well as their experience) in
-the interviews.  Specifically, we used the constructs \textit{ascribe intention,
-ascribe cognitive abilities, ascribe emotional state}, and \textit{ascribe moral
-standing} (Table~\ref{tab:domino-questions}) to assess how far they engaged with
-the robot.
-
+%We have measured engagement by combining \emph{interaction} data with the
+%results of the semi-structured interviews.  Several of the aforementioned coded
+%actions can reflect engagement: \textit{explore, misuse, gesture, touch, show,}
+%and \textit{talk}. Also, \textit{look} at the experimenter can be considered as
+%engagement in the interaction: We assume that children look at the experimenter
+%when they are surprised and seek for help.  This behaviour reflects that they
+%want to make sense of the robot's behaviour. Further, we can take into account
+%how they refer to Ranger and describe the robot (as well as their experience) in
+%the interviews.  Specifically, we used the constructs \textit{ascribe intention,
+%ascribe cognitive abilities, ascribe emotional state}, and \textit{ascribe moral
+%standing} (Table~\ref{tab:domino-questions}) to assess how far they engaged with
+%the robot.
+%
 To account for the fact that anthropomorphism arises in an interaction, we bring
@@
 index by attributing points for each anthropomorphic \emph{perception} of the
-robot (max.  13 points) and for specific kinds of human-like \emph{behaviour}
-toward the robot (max.  3 points). The index included the following aspects:\\
+robot and for specific kinds of human-like \emph{behaviour}
+toward the robot. The index included the following aspects:\\
 
@@
 
-\subsection{Misbehaviour Recognition and Interaction Engagement}
-
-\paragraph{Misbehaviour Recognition}
+\subsection{Misbehaviour Recognition, Engagement}
+
+%\paragraph{Misbehaviour Recognition}
 
@@
 
-\paragraph{Engagement}
+%\paragraph{Engagement}
 In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
@@
 (72~\%). This indicates that overall children were very engaged in the
-interaction with the robot. Furthermore, data suggests that the robot in the
-\textit{mistake} and \textit{lost} condition was more engaging for children
-(each 75~\% of the actions reflected engagement) than the robot in the
-\textit{disobey} condition (66~\% reflected engagement). The statistical
-analysis supports this: An ANOVA indicates that there was a significant effect
-of robot behaviour on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
-\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
-indicate that the mean score for \textit{explore} in the \textit{disobey}
-condition is significantly different from the score in the \textit{mistake} and
-\textit{lost} condition. This suggests that children explored the disobeying
-robot less\footnote{It is surprising that the disobeying robot was explored
-less. One may expect that the disobeying robot might better attract
-children's attention because it faces the searcher child and uses fairly
-strong audio and light cues as compared to the other behaviours.}.
-
-Overall, we found a significant difference between the average of engagement
+interaction with the robot.
+%Furthermore, data suggests that the robot in the
+%\textit{mistake} and \textit{lost} condition was more engaging for children
+%(each 75~\% of the actions reflected engagement) than the robot in the
+%\textit{disobey} condition (66~\% reflected engagement). The statistical
+%analysis supports this: An ANOVA indicates that there was a significant effect
+%of robot behaviour on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
+%\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
+%indicate that the mean score for \textit{explore} in the \textit{disobey}
+%condition is significantly different from the score in the \textit{mistake} and
+%\textit{lost} condition. This suggests that children explored the disobeying
+%robot less\footnote{It is surprising that the disobeying robot was explored
+%less. One may expect that the disobeying robot might better attract
+%children's attention because it faces the searcher child and uses fairly
+%strong audio and light cues as compared to the other behaviours.}.
+
+We found a significant difference between the average of engagement
 actions carried out during the first 7 runs (correct robot behaviour) and during
@@
 
-To obtain the anthropomorphism index for a pair, we first calculated the index
-per child and then took the average of the two children in one group.  The group
-indexes varied between 3.25 and 10.75 points with an average of 7.5 points
-(SD~=~2.5), which is 47~\% of the maximum possible index of 16 points.
-Intra-group variations were interesting: In 7 of the 13 groups, the
-anthropomorphism indexes for both children were similar (difference less than
-1.5 points). This agreement among children happened for both higher and lower
-indexes. In 6 of the 13 groups, the anthropomorphism indexes varied in more than
-2 points, which means that one of the children anthropomorphized the robot more
-than the other one.
+%To obtain the anthropomorphism index for a pair, we first calculated the index
+%per child and then took the average of the two children in one group.  The group
+%indexes varied between 3.25 and 10.75 points with an average of 7.5 points
+%(SD~=~2.5), which is 47~\% of the maximum possible index of 16 points.
+%Intra-group variations were interesting: In 7 of the 13 groups, the
+%anthropomorphism indexes for both children were similar (difference less than
+%1.5 points). This agreement among children happened for both higher and lower
+%indexes. In 6 of the 13 groups, the anthropomorphism indexes varied in more than
+%2 points, which means that one of the children anthropomorphized the robot more
+%than the other one.
 
 On average, Ranger was moderately anthropomorphized by the children. 8 of the 13
-groups had an index of 8 or higher, evenly spread over the three conditions
-(Table~\ref{tab:domino-anth-score}). However, the mean index of anthropomorphism
-in the three conditions varied, with the \textit{mistake} and \textit{lost}
-condition leading to a higher index than the \textit{disobey} condition. This
-finding suggests that the disobeying robot was less anthropomorphized than the
-other two robot behaviours, which speaks against our second hypothesis. We had
-expected that the disobeying behaviour is perceived as an intentional action
-which we assumed would lead to increased anthropomorphism. This was not the
-case. The slight difference between the \textit{lost} and \textit{mistake} robot
-was also expected in the opposite direction. It could be that the robot's
-``helplessness'' led to this. This is also reflected in children's behaviour:
-with the lost robot, children looked more often at the experimenter than in the
-other condition, which suggests that they could not fully make sense of the
-robot's behaviour, and the fact of not being able to understand (and hence
-predict) a robot's behaviour is likely to increase
-anthropomorphism.\footnote{One of the cognitive / psychological explanations for
-anthropomorphism is that people want to make sense of something they do not
-understand and then tend to anthropomorphize this something (human traits
-are a good source of making attributions because this is what people
-understand best -- themselves and other humans). For more details the reader may
-refer to \cite{epley_seeing_2007}.}
-
-\begin{table}[ht!]
-    \centering
-    \footnotesize
-    \begin{tabular}{lccc}
-        \toprule
-        & M & SD & groups with index > 8 \\
-        \midrule
-
-        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
-        \textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
-        \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
-        \bottomrule
-    \end{tabular}
-    \caption{\textbf{Anthropomorphism index.} The maximum possible index was 16. The
-    \textit{lost} robot elicits the highest index, which suggests that it is
-    anthropomorphized more. Contrary to our hypothesis, data suggests that the
-    \textit{disobeying} robot is anthropomorphized less but the \textit{lost} robot
-    more.}
-
-    \label{tab:domino-anth-score}       % Give a unique label
-\end{table}
+groups had an index of 8 or higher, evenly spread over the three conditions.
+However, the mean index of anthropomorphism in the three conditions varied, with
+the \textit{mistake} and \textit{lost} condition leading to a higher index than
+the \textit{disobey} condition. This finding suggests that the disobeying robot
+was less anthropomorphized than the other two robot behaviours, which speaks
+against our second hypothesis. We had expected that the disobeying behaviour is
+perceived as an intentional action which we assumed would lead to increased
+anthropomorphism. This was not the case. The slight difference between the
+\textit{lost} and \textit{mistake} robot was also expected in the opposite
+direction. It could be that the robot's ``helplessness'' led to this. This is
+also reflected in children's behaviour: with the lost robot, children looked
+more often at the experimenter than in the other condition, which suggests that
+they could not fully make sense of the robot's behaviour, and the fact of not
+being able to understand (and hence predict) a robot's behaviour is likely to
+increase anthropomorphism.\footnote{One of the cognitive / psychological
+explanations for anthropomorphism is that people want to make sense of
+something they do not understand and then tend to anthropomorphize this
+something (human traits are a good source of making attributions because
+this is what people understand best -- themselves and other humans). For
+more details the reader may refer to~\cite{epley_seeing_2007}.}
+%
+%\begin{table}[ht!] \centering \footnotesize \begin{tabular}{lccc} \toprule & M
+%& SD & groups with index > 8 \\ \midrule
+%
+%        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ \textit{disobey} & 6.5
+%        & 3.68 & 2 of 5 \\ \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\
+%        \bottomrule \end{tabular} \caption{\small \textbf{Anthropomorphism
+%        index.} The maximum possible index was 16. The \textit{lost} robot
+%        elicits the highest index, which suggests that it is anthropomorphized
+%        more. Contrary to our hypothesis, data suggests that the
+%        \textit{disobeying} robot is anthropomorphized less but the
+%        \textit{lost} robot more.}
+%
+%    \label{tab:domino-anth-score}       % Give a unique label
+%\end{table}
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{domino-correlation.pdf}
+    \includegraphics[width=0.6\columnwidth]{domino-correlation.pdf}
 
@@
 
-Interestingly, data suggests a significant negative correlation of engagement
-and anthropomorphism index. It appears that groups who interacted more with the
-robot perceived it as less human-like. This raises an important question for the
-human-robot interaction community: to what extent do anthropomorphic perceptions
-impact the interaction experience? Our findings here go against the intuition.
+Interestingly, data suggests that anthropomorphic perception does not
+automatically elicit  engagement, on the contrary. It appears that groups who
+interacted more with the robot perceived it as less human-like. This raises an
+important question for the human-robot interaction community: to what extent do
+anthropomorphic perceptions impact the interaction experience? Our findings here
+go against the intuition.
 

### 2014-10-03 paper.tex
Lastest minor fixes, reported by Julia

@@
 While we found only a limited recognition of the different misbehaviours of the
-robot that we attribute to the age of the child participants (M=4.46),
+robot that we attribute to the age of the child participants (4-5 years old),
 interesting findings include a sustained engagement level, an unexpectedly low
@@
 This study also aims at assessing the effectiveness of the \emph{anthropomorphic
-index} proposed by Fink \etal\cite{fink2014dynamics} as a compound (behavioural
+index} proposed in~\cite{fink2014dynamics} as a compound (behavioural
 and phenomenological) metric for the attribution of human-like features to
@@
 In a playful scenario which was set up in a laboratory environment, 26 children
-aged 4-5 years (MD=4.46) were assembling a domino game together. Each group
+aged 4-5 years (M=4.46) were assembling a domino game together. Each group
 consisted of two children and the \emph{Ranger} robot, which was used to
@@
 
+\vspace{1em}
 \paragraph{Moral standing}

### 2015-02-27 paper.tex
Turned the paper into an IROS paper. Implemented a few of the HRI reviewer comments

@@
-\documentclass{sig-alternate}
+\documentclass[letterpaper, 10pt, conference]{ieeeconf}
+\overrideIEEEmargins
 
@@
 
-%
-% --- Author Metadata here ---
-\conferenceinfo{10th ACM/IEEE International Conference on Human-Robot Interaction}{2015 Portland, USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
-
 \title{\LARGE \bf
-How Children Perceive and Interact with a Robot that Behaves Unexpectedly
+Unexpected Behaviors: Impact on Child-Robot Interaction
 }
 
-%%% HRI 2015 -> double-blind review process
-
-%\numberofauthors{1} 
-%\author{
-%\alignauthor
-%Julia Fink, S\'{e}verin Lemaignan, Pierre Dillenbourg\\
-%%\titlenote{Dr.~Trovato insisted his name be first.}
-%       \affaddr{Computer-Human Interaction in Learning and Instruction Lab (CHILI)}\\
-%       \affaddr{Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL)}\\
-%       \affaddr{CH-1015 Lausanne}\\
-%       \affaddr{Switzerland}\\
-%       \email{firstname.lastname@epfl.ch}
-%}
-%
-%\additionalauthors{Additional authors: 
-%Francesco Mondada, LSRO, EPFL, francesco.mondada@epfl.ch 
-%}
-%
+\author{
+    S\'{e}verin Lemaignan$^{1,2}$, Julia Fink$^{1}$, Francesco Mondada$^{2}$, Pierre
+    Dillenbourg$^{1}$\\
+$^{1}$Computer-Human Interaction in Learning and Instruction Lab (CHILI) \\
+$^{2}$Laboratoire de Systèmes Robotiques (LSRO) \\
+École Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\
+CH-1015 Lausanne, Switzerland \\
+{\tt\small firstname.last@epfl.ch}
+}
 
@@
 
-Presented is a study on the impact of unexpected robot behaviours on the
-perception of a robot by children and their subsequent engagement in a playful interaction.
+We present a study on the impact of unexpected robot behaviours on the
+perception of a robot by children and their subsequent engagement in a playful
+interaction based on a novel "domino" task.
 We propose an original analysis methodology which blends behavioural cues and
@@
 engagement.
-
-Besides, this study operationalizes for the first time the
-\emph{anthropomorphism index} proposed by~\cite{fink2014dynamics}, which can be
-considered as an effective tool to assess qualitative psycho-behavioural
-episodes occurring during human-robot interaction.
 
@@
 unexpectedly can increase engagement and mental state attribution without
-complex behavioural or mechanical additions.''}  Along those lines, Fink
-\etal\cite{fink2014dynamics} also suggest in their model of the dynamics of
-anthropomorphism in HRI, that \emph{disruptive behaviours} may lead to increased
-anthropomorphic projections and possibly engagement.
+complex behavioural or mechanical additions.''}  Along those lines, we also
+suggested in our model of the dynamics of anthropomorphism in
+HRI~\cite{lemaignan2014dynamics} that \emph{disruptive behaviours} may lead to
+increased anthropomorphic projections and possibly increased engagement.
 
@@
 
-This study also aims at assessing the effectiveness of the \emph{anthropomorphic
-index} proposed in~\cite{fink2014dynamics} as a compound (behavioural
-and phenomenological) metric for the attribution of human-like features to
-a robot. We are especially interested in investigating how this indicator predicts
-and/or reflects actual \emph{engagement} in the interaction.
+The main outcomes of this research, detailed hereafter, can be summarized as:
+
+\begin{enumerate}
+    \item an actionable approach (introduction of mis-behaviours) to support
+        child-robot engagement,
+    \item a mixed technique, blending behavioural cues and reported
+        phenomenological perceptions, to assess the robot perception in terms of
+        both engagement and human-likeliness,
+
+    \item a new experimental protocol that compares three types of
+        mis-behaviours, with different cognitive correlates,
+
+    \item and a first experimental cue that anthropomorphic perceptions do not
+        necessarily correlate with actual engagement.
+\end{enumerate}
 
@@
 
-\begin{description}
-
-    \item[Hypothesis 1:] Children show more engagement toward a robot that
+\begin{itemize}
+
+    \item {\bf Hypothesis 1}: Children show more engagement toward a robot that
         behaves unexpectedly from time to time compared to a robot that always
@@
 
-    \item[Hypothesis 2:] Children perceive a robot that (tentatively) displays
+    \item {\bf Hypothesis 2}: Children perceive a robot that (tentatively) displays
         intention or cognitive abilities as more human-like than a robot that
@@
 
-\end{description}
+\end{itemize}
 
@@
 perception but also as an observable behaviour in the interaction itself. Thus,
-we would like to bring things together and, relying on the concept of
-anthropomorphism index~\cite{fink2014dynamics}, build a compound metric that
+we would like to bring things together and propose a compound metric that
 considers both children's perception and interaction aspects (qualitatively).
@@
 
-\begin{description}
-
-    \item[Hypothesis 3:] Anthropomorphic perception of the robot and the amount
+\begin{itemize}
+
+\item {\bf Hypothesis 3}: Anthropomorphic perception of the robot and the amount
     of engagement in the interaction positively correlate.
 
-\end{description}
+\end{itemize}
 
@@
 
-In total, we obtained 2354 distinct actions which summed up to a total
-annotation duration of 145 minutes. On average, one child accounted for 92
-actions (SD=23).
+In total, we obtained 2354 distinct actions. On average, interactions lasted
+13min 43sec, and one child accounted for 90.53 actions (SD=23).
 
@@
 toward it (in-the-moment measurement) together. We did so by building a
-anthropomorphism index~\cite{fink2014dynamics}. We quantify the
+so-called \emph{anthropomorphism index}. We quantify the
 index by attributing points for each anthropomorphic \emph{perception} of the
@@
 suggested by our study setup, and we cannot be sure that it really reflects
-anthropomorphism). We believe however that the approach remains valid,
-considering that the anthropomorphism index is primarily a \emph{comparison}
-metric and not an absolute value.
+anthropomorphism). Note that these issues are mitigated by using the
+anthropomorphism index as a \emph{relative} metric (comparison between
+conditions) and not an absolute value.
 
@@
 
-\paragraph{Emotions and Companionship}
-
-We examined whether children attribute \textbf{feelings} to the robot by asking
-them (once at the end of the experiment) if they thought that Ranger can feel
-happy or sad sometimes. The majority of
-children (21 of 26) gave a positive answer. Only 2 children who had interacted
-with the \textit{disobeying} robot did not believe that Ranger has feelings and
-another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
-all. Overall, data suggests that \textbf{children attribute emotional states}
-to the robot. Asked for more details, several children answered that it is
-through its colours and sounds that the robot shows a feeling. Most children said
-that they could make the robot feel happy by playing with it and putting a
-domino tile inside the box. This may also be a reflection of their own feelings,
-projected on the robot. About half of the children (14 of 26) agreed that Ranger
-can be their friend. We did not ask about what being a friend means to them but
-as children generally liked playing with the robot, this may be linked to each
-other. We can note that children \textbf{ascribe feelings to the robot and
-partly accept that it can be a ``friend''}.
+%\paragraph{Emotions and Companionship}
+%
+%We examined whether children attribute \textbf{feelings} to the robot by asking
+%them (once at the end of the experiment) if they thought that Ranger can feel
+%happy or sad sometimes. The majority of
+%children (21 of 26) gave a positive answer. Only 2 children who had interacted
+%with the \textit{disobeying} robot did not believe that Ranger has feelings and
+%another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
+%all. Overall, data suggests that \textbf{children attribute emotional states}
+%to the robot. Asked for more details, several children answered that it is
+%through its colours and sounds that the robot shows a feeling. Most children said
+%that they could make the robot feel happy by playing with it and putting a
+%domino tile inside the box. This may also be a reflection of their own feelings,
+%projected on the robot. About half of the children (14 of 26) agreed that Ranger
+%can be their friend. We did not ask about what being a friend means to them but
+%as children generally liked playing with the robot, this may be linked to each
+%other. We can note that children \textbf{ascribe feelings to the robot and
+%partly accept that it can be a ``friend''}.
 
@@
 interact much but anthropomorphize the robot more, is quite homogeneous, and may
-reflect a certain fear of interacting with a robot that would look to them to
+reflect a certain fear of interacting with a robot that would look to them too
 human-like.
@@
 shows some misbehaviour compared to when it always behaves as expected
-(notwithstanding the likely impact of a novelty effect).
+(notwithstanding the impact of a novelty effect).
 
@@
 \section*{Acknowledgements}
-%
-% double blind review
-%This research was supported by the Swiss National Science Foundation through the
-%National Centre of Competence in Research Robotics.
+
 We would like to thank all the families who participated to the study.
+This research was supported by the Swiss National Science Foundation through the
+National Centre of Competence in Research Robotics.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{abbrv}
+\bibliographystyle{IEEEtran}
 \bibliography{domino}
 
-\balancecolumns
-
 \end{document}

### 2015-03-03 paper.tex
Large proof-reading/style fixing/article reorganization

@@
 \title{\LARGE \bf
-Unexpected Behaviors: Impact on Child-Robot Interaction
+Unexpected Behaviors: Studying their Impact on Child-Robot Interaction
 }
@@
 
-We present a study on the impact of unexpected robot behaviours on the
+We present a study on the impact of unexpected robot behaviors on the
 perception of a robot by children and their subsequent engagement in a playful
 interaction based on a novel "domino" task.
-We propose an original analysis methodology which blends behavioural cues and
+We propose an original analysis methodology which blends behavioral cues and
 reported phenomenological perceptions into a compound index.
 
-While we found only a limited recognition of the different misbehaviours of the
+While we found only a limited recognition of the different misbehaviors of the
 robot that we attribute to the age of the child participants (4-5 years old),
@@
 level of attribution of higher cognitive abilities and a \emph{negative}
-correlation between anthropomorphic projections and actual behavioural
+correlation between anthropomorphic projections and actual behavioral
 engagement.
@@
 of research has moved toward creating sophisticated emotional models which cause
-complex robot behaviour. \cite{leite_long-term_2013} studied the long-term
-engagement of children with a chess playing robot that adapted its behaviour to
+complex robot behavior. \cite{leite_long-term_2013} studied the long-term
+engagement of children with a chess playing robot that adapted its behavior to
 the children and showed empathy toward them. The authors found that empathetic robots
@@
 \cite{bickmore_maintaining_2010,short_no_2010} have shown that simpler ways to
-enhance engagement may as well be effective.
-
-\cite{bickmore_maintaining_2010} describe a series of longitudinal studies on
-engagement with an agent-like system. They demonstrated that user engagement
-with an interface agent can be increased using relatively simple techniques and
-manipulations that make the agent more life-like and human. For instance, when
-the agent showed variations in its behaviour, participants were more engaged and
-reported a desire to continue interacting with the agent.
+enhance engagement may as well be effective: \cite{bickmore_maintaining_2010}
+describe a series of longitudinal studies on engagement with an agent-like
+system. They demonstrated that user engagement with an interface agent can be
+increased using relatively simple techniques and manipulations that make the
+agent more life-like and human. For instance, when the agent showed variations
+in its behavior, participants were more engaged and reported a desire to
+continue interacting with the agent.
 
 Similarly, looking at short-term engagement, \cite{short_no_2010} found that a
-simple manipulation of the robot's behaviour can lead to greater engagement. The
+simple manipulation of the robot's behavior can lead to greater engagement. The
 authors let participants play several rounds of the rock-paper-scissors game
@@
 interaction.''} Besides, they suggest that \textit{``many interactions can be
-improved by the introduction of such simple behaviours, and that this should
+improved by the introduction of such simple behaviors, and that this should
 be exploited by designers in HRI. Bringing human and robot together to
@@
 unexpectedly can increase engagement and mental state attribution without
-complex behavioural or mechanical additions.''}  Along those lines, we also
+complex behavioral or mechanical additions.''}  Along those lines, we also
 suggested in our model of the dynamics of anthropomorphism in
-HRI~\cite{lemaignan2014dynamics} that \emph{disruptive behaviours} may lead to
+HRI~\cite{lemaignan2014dynamics} that \emph{disruptive behaviors} may lead to
 increased anthropomorphic projections and possibly increased engagement.
 
-Based on this previous research, we would like to explore in this study how
-we can enhance children's experience with the robot so that they do not find it
-repetitive and boring, and ultimately keep interacting with the robot (as
-repetitiveness is likely to decrease a user's motivation to continue using a
-system~\cite{bickmore_establishing_2005}).
-
-We present in this article a study that explores possibilities of sustaining
-children's engagement with the \emph{Ranger} robot~\cite{mondada2014ranger} by
-manipulating the robot's behaviour in such way that it appears
-\textit{unexpected} to the children. We examine how different variations of
-robot behaviour impact children's interaction with Ranger and their perception of
-it (in terms of attributing intention and cognitive abilities to the robot).
+Based on this previous research, we explore in this study how to
+sustain children's engagement with the \emph{Ranger}
+robot~\cite{mondada2014ranger} by manipulating the behavior of the robot so
+that it appears \textit{unexpected} to the children. We examine how different
+variations of robot behavior impact children's interaction with \emph{Ranger}
+and their perception of it, in terms of attributing intention and cognitive
+abilities to the robot.
 
@@
 \begin{enumerate}
-    \item an actionable approach (introduction of mis-behaviours) to support
-        child-robot engagement,
-    \item a mixed technique, blending behavioural cues and reported
+    \item a new experimental task that suggests and contrasts three types of
+        mis-behaviors, with different cognitive correlates,
+    \item a mixed technique, blending behavioral cues and reported
         phenomenological perceptions, to assess the robot perception in terms of
         both engagement and human-likeliness,
-
-    \item a new experimental protocol that compares three types of
-        mis-behaviours, with different cognitive correlates,
-
+    \item an actionable approach based on the introduction of mis-behaviors to support
+        child-robot engagement,
     \item and a first experimental cue that anthropomorphic perceptions do not
@@
 
-We analyse child-robot interaction with a robot that shows unexpected behaviour.
+We analyse child-robot interaction with a robot that shows unexpected behavior.
 In a playful scenario which was set up in a laboratory environment, 26 children
@@
 
-Ranger usually behaved correctly (expected behaviour), coming over to a child
+Ranger usually behaved correctly (expected behavior), coming over to a child
 after being called and delivering the domino tile to the other child. However,
-in pre-defined rounds, Ranger showed unexpected behaviour when a child called the
-robot. We defined three different types of \textit{misbehaviour} that were tested
+in pre-defined rounds, \emph{Ranger} showed unexpected behavior when a child called the
+robot. We defined three different types of \textit{misbehavior} that were tested
 in a between-subjects study design:
@@
         becoming red. The robot then goes to a wrong location and remains there
-        while it continues to shake its head. We expect the disobey behaviour to
+        while it continues to shake its head. We expect the disobey behavior to
         be perceived as the robot having an explicit \textit{``own will''}, and
@@
 We analysed children's reaction focusing on two main aspects. On one hand,
-children's \textbf{behaviour} (their reactions) toward the unexpected robot
-behaviour was studied in terms of \textbf{active engagement} with the robot. On
+children's \textbf{behavior} (their reactions) toward the unexpected robot
+behavior was studied in terms of \textbf{active engagement} with the robot. On
 the other hand, we analysed children's \textbf{perception} of the robot in term
@@
 
-Our research questions deal with both children's observable behaviour and their
-perception of the robot. We would also like to explore the relation between
-these two aspects, related to the attribution of human-like characteristics to
-the robot. The motivation behind this is to find out whether
-\textit{anthropomorphism} can not only be measured as a specific type of
-perception but also as an observable behaviour in the interaction itself. Thus,
-we would like to bring things together and propose a compound metric that
-considers both children's perception and interaction aspects (qualitatively).
-Previous work suggests that a social relation to a robot (we view
-anthropomorphism as a specific type of social relation) reflects an increased
-engagement and can be effective in sustaining interaction.  Consequently, we
-formulate a third hypothesis:
+Our research questions deal with both children's observable behavior and their
+perception of the robot. We propose to consider a novel combination of these two
+aspects into a synthetic \emph{compound index} that measure
+\emph{anthropomorphic projections} (\ie the attribution of human-like
+characteristics) to the robot by the children.
+
+Based on literature suggesting that a social relation to a robot
+(anthropomorphism is a specific type of social relation) reflects an increased
+engagement and can be effective in sustaining interaction, we formulate
+therefore a third hypothesis:
 
@@
 
-\item {\bf Hypothesis 3}: Anthropomorphic perception of the robot and the amount
-    of engagement in the interaction positively correlate.
-
+\item {\bf Hypothesis 3}: Anthropomorphic perception of the robot positively
+    correlates with the level of engagement in the interaction.
 \end{itemize}
@@
     \centering 
-    \includegraphics[width=0.8\columnwidth]{domino-setup.pdf} 
+    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
     \caption{\small \textbf{Experimental setting} One child is located in a
@@
         allowed to cross. The solid green arrows show the robot's path for the
-        \textit{correct} behaviour. The blue arrow visualises a possible
-        \textit{lost} path, where the Ranger stops and remains at a wrong spot.
+        \textit{correct} behavior. The blue arrow visualises a possible
+        \textit{lost} path, where the \emph{Ranger} stops and remains at a wrong spot.
         The yellow arrows reflect a possible \textit{mistake} path, where the
@@
 
-The interaction scenario consisted in two children who play domino together,
-with the help of the robotic box Ranger. The scenario setup is displayed in
-Figure~\ref{fig:domino-setup}. The challenge is that the tiles of the domino are
-distributed in the room, hidden behind three beanbags, and while one child --
-\textit{the searcher} -- searches for the right tile, the other child --
-\textit{the receiver} -- is asked to stay in a play tent. There is a ``river''
-(play mat) in between the two children that we told them they cannot cross
-and therefore they need the robot to transport the domino tiles between them.
-
-The Ranger~\cite{mondada2014ranger} is a wheeled box (27 x 37 x 37 cm) with
-partial wooden surface. It is remotely controlled, it can move around a flat
-surface, move its eyes and eyebrows, display colours (LEDs) and light patterns,
+The interaction scenario consisted in two children who play the dominos
+together, with the help of a remotely controlled robot (Wizard-of-Oz setup). We
+build to this end a large domino tiles based on a commercially available domino
+game representing animals.  Figure~\ref{fig:domino-setup} pictures the
+experimental setup.
+
+The challenge for the children consists in collecting domino tiles spread over
+the room, hidden behind beanbags (task of the \emph{searcher} child), getting
+the robot to carry to the second child, and finally assemble the tiles and
+decide for the next tile to fetch (tasks of the \emph{receiver} child).
+
+The \emph{Ranger}~\cite{mondada2014ranger} is a wheeled box (27 x 37 x 37 cm) with
+partial wooden surface. It can drive on a flat
+surface, move its eyes and eyebrows, display colours (LED arrays) and light patterns,
 and play sounds through Bluetooth speakers.  The robot was controlled by a human
@@
 actually controlling the robot. This did not seem to subsequently influence
-their behaviour).
+their behavior).
 
@@
 wild''~\cite{fink2014which} that suggested that younger children (4-6 years)
-interacted more effectively with the Ranger robot.
+interacted more effectively with the \emph{Ranger} robot.
 
@@
 
-The game was divided in a total of 14 runs that correspond each to the delivery
-and assembling of one domino tile. At each run, the robot exhibits one out of
-four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey} or
+The game (that lasted in average 13min 43sec per group of children) was divided
+in a total of 14 runs that correspond each to the delivery and assembling of one
+domino tile. At each run, the robot exhibits one out of the four possible
+behaviors previously presented: \emph{correct}, \emph{lost}, \emph{disobey} or
 \emph{mistake}.  The game starts with one domino tile in front of the tent,
@@
 child asks the searcher child for a specific tile, \eg a tile with a donkey, the
-searcher child searches for the respective tile and sits down on the next
+searcher child looks for the corresponding tile and sits down on the closest
 beanbag. When called by the searcher (\textit{``Robot, come here!''}), the robot
@@
 the roles receiver/searcher and in the 9 remaining runs (\emph{2.1} to
-\emph{2.9}), the robot showed one of the misbehaviours (\emph{lost},
+\emph{2.9}), the robot showed one of the misbehaviors (\emph{lost},
 \emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
-the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}).
+the $7^{th}$ and $8^{th}$ run (see axis $x$ of Figure~\ref{fig:domino-time-active}).
 %The
-%study is built as a between-subject study, and the type of misbehaviour was
+%study is built as a between-subject study, and the type of misbehavior was
 %therefore always the same for a given group.
@@
 the study. The five first correct runs aim at setting the children's expectation
-regarding a consistent robot behaviour. When the robot then exhibits an
-unexpected behaviour, children are likely to be positively surprised (a similar
-effect has been observed in a study with a robot that was cheating from time to
-time~\cite{short_no_2010}). Besides, to prevent the robot misbehaviours to be
-immediately interpreted as failures, we introduce these misbehaviours neither at
-the very beginning nor at the very end of the interaction.
-\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
-failures negatively impact trust. \cite{short_no_2010} also adopted a similar
-pattern when introducing unexpected robot behaviour.
+regarding a consistent robot behavior. When the robot then exhibits an
+unexpected behavior, children are likely to be positively surprised (a similar
+effect has been observed in a study with the robot that was cheating from time
+to time~\cite{short_no_2010}). Besides, to prevent the robot misbehaviors to be
+immediately interpreted as failures, we introduce these misbehaviors neither at
+the very beginning nor at the very end of the interaction
+(\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
+failures negatively impact trust. Besides \cite{short_no_2010} also adopted a
+similar pattern when introducing unexpected robot behavior).
 
@@
 %    }
-%    \caption{\small The three robot misbehaviours.}
-%    \label{fig:domino-misbehaviour}
+%    \caption{\small The three robot misbehaviors.}
+%    \label{fig:domino-misbehavior}
 %\end{figure}
@@
     \caption{\small The experimental setup, here in the \emph{disobey} condition.}
-    \label{fig:domino-misbehaviour}
+    \label{fig:domino-misbehavior}
 \end{figure}
 
-%The \emph{correct} robot behaviour (baseline behaviour) consists in the
+%The \emph{correct} robot behavior (baseline behavior) consists in the
 %following states:
@@
 %
-%    \item \emph{Domino tile put in robot:} Ranger makes a ``rewarding'' sound
+%    \item \emph{Domino tile put in robot:} \emph{Ranger} makes a ``rewarding'' sound
 %        and shows a green light pattern,
 %
-%    \item \emph{Domino tile removed from robot:} Ranger makes an ``emptying''
+%    \item \emph{Domino tile removed from robot:} \emph{Ranger} makes an ``emptying''
 %        sound and shows a green light pattern,
@@
 %    \item \emph{Robot reaches one of the children:} When in front of one of the
-%    children who should either put or remove a domino tile, Ranger stops and
-%    shows a pulsating yellow light pattern. If no reaction, Ranger also makes a
+%    children who should either put or remove a domino tile, \emph{Ranger} stops and
+%    shows a pulsating yellow light pattern. If no reaction, \emph{Ranger} also makes a
 %    wiggle-like move.
@@
 %
-During the misbehaving runs, the robot's behaviour is manipulated in three
+During the misbehaving runs, the behavior of the robot is manipulated in three
 possible ways, represented on Figure~\ref{fig:domino-setup}.
-In the \textbf{lost} condition, goes to a wrong position, and remains here,
+In the \textbf{lost} condition, the robot goes to a wrong position and remains here,
 behaving (yellow light pattern) as if it were correctly in front of the child.
@@
 wrong position and remains there, facing the child. In the \textbf{mistake}
-condition, the robot starts like for the \emph{lost} behaviour, but after a few
+condition, the robot starts like for the \emph{lost} behavior, but after a few
 seconds, turns back, blushes and finally reach the correct position, in front of
@@
 %
-%    \item \textbf{Lost:} After being called, Ranger goes until it is on the
+%    \item \textbf{Lost:} After being called, \emph{Ranger} goes until it is on the
 %    carpet. There, it stops, turns, and goes wrong (see blue path in
-%    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
+%    Figure~\ref{fig:domino-setup}). Once at the wrong position, \emph{Ranger} waits
 %    with its ``face'' turned away from the child, and it blinks in yellow light,
-%    as it would only do when in front of a child. Ranger remains waiting at the wrong
+%    as it would only do when in front of a child. \emph{Ranger} remains waiting at the wrong
 %    position until the experimenter tells the child to go over to the robot to
-%    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
+%    put the domino tile. The \textit{lost} behavior is \textit{human-repaired},
 %    as it needs human-intervention.
 %
-%    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
+%    \item \textbf{Disobey:} After being called, \emph{Ranger} goes until it is on the
 %    carpet. It then stops, makes red
@@
 %    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
-%    toward the searcher child. In addition to the red blinking, Ranger
+%    toward the searcher child. In addition to the red blinking, \emph{Ranger}
 %    makes a slow wiggle-like move, and remains waiting at the wrong position
 %    until the experimenter tells the child to go over to the robot to put the
-%    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.
-%
-%    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
+%    domino tile. The \textit{disobey} behavior is also \textit{human-repaired}.
+%
+%    \item \textbf{Mistake:} The searcher child calls \emph{Ranger}. The robot goes until
 %    it is on the carpet, stops, turns, and goes wrong (see yellow path in
-%    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
+%    Figure~\ref{fig:domino-setup}). Then, \emph{Ranger} waits ($\sim$2~sec), turns its
 %    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
 %    (as if it recognises its wrong position) and finally goes correctly over to
-%    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
+%    the searcher child. The \textit{mistake} behavior is \textit{robot-repaired},
 %    as no human-intervention is needed.
@@
 
-Both the \textit{lost} and \emph{disobey} behaviours are
-\textit{human-repaired}, while the \emph{mistake} condition is
-\emph{robot-repaired}. In the human-repaired conditions, the experimenter
-instructs the searcher child (after ~10 sec) to bring him/herself the domino
-tile to the robot.
-
-On its way back to the tent, Ranger always goes correctly. After the searcher
-child has put a domino tile, Ranger automatically turns and goes over to the
-tent (the receiver child does not need to call the robot). The receiver child
-takes the tile and the robot moves to a waiting location until the next run
-starts.
+Both the \textit{lost} and \emph{disobey} behaviors are \textit{human-repaired},
+while the \emph{mistake} condition is \emph{robot-repaired}. In the
+human-repaired conditions, the experimenter instructs the searcher child (after
+about 10 sec) to bring him/herself the domino tile to the robot.
+
+On its way back to the tent, \emph{Ranger} always behaves expectedly. After the
+searcher child has put a domino tile, \emph{Ranger} automatically turns and
+drives over to the tent (the receiver child does not need to call the robot).
+The receiver child takes the tile and the robot moves to a waiting location
+until the next run starts.
 
@@
 
-We have obtained and analysed two types of data. The \textbf{children's
-behaviour toward the robot} (\ie the child-robot interactions) have been
-captured in the video recordings by annotating a set of actions, described
-below. Children's \textbf{phenomenological perception of the robot} has been
-captured through two audio-recorded semi-structured interviews which took place
-between run \emph{1.5} and \emph{2.1} and at the end of the experiment. A
-short preliminary interview was also conducted to explain the game and assess
-the expectations of the children toward the robot.
-
-\subsubsection{Interaction: Action Coding}
-
-\begin{figure*}[ht!] 
-    \centering 
-    \includegraphics[width=0.8\linewidth]{domino-time-active.pdf} 
-    \caption{\small \textbf{Number and type of actions for each run} (n=480,
-        spontaneous actions, excluding \emph{explore}). Generally, the number of
-        actions does not decrease over time (from run 1.1 to run 2.9).  The
-        first 7 runs correspond to the \textit{expected phase}, the second 7
-        runs correspond to the \textit{unexpected phase}. Especially during run
-        2.3, the first time when the robot showed an unexpected behaviour,
-        children tended to \textit{look} more at the experimenter. During the
-        unexpected phase, also \textit{talk} and \textit{gesture} seem to be
-        increased.}
-
-    \label{fig:domino-time-active} 
-\end{figure*}
-
-One coder annotated children's behaviour in the video records, and coded 10 different
-actions (the coding scheme has been inspired from~\cite{fink2014which}):
-\textbf{explore} (actively try to find out what the robot is doing, \eg by
-looking under the box; attentively watch or observe the robot; experiment with
-the robot to figure out how it works); \textbf{misuse} (kick the robot, poke it
-in its ``eye'', try to climb on or inside the box, drive/push the robot around,
-stop the robot's wheels with a foot); \textbf{put} (a domino tile is put inside
-the box); \textbf{remove} (a domino tile is removed from the box);
-\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
-pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
-petted or caressed); \textbf{show} (show something to the robot); \textbf{call}
-(call the robot to come over); \textbf{talk} (all the other cases of direct
-verbal interaction); \textbf{look} (when a child looks \emph{at the
-experimenter} due to confusion caused by the robot; look is not coded when the
-experimenter asks a question to the child);
-
-In total, we obtained 2354 distinct actions. On average, interactions lasted
-13min 43sec, and one child accounted for 90.53 actions (SD=23).
-
-The actions \textit{put, remove} and \textit{call} are ``requested'' actions
-that the children had to perform in the scenario. On the contrary,
-\textit{explore, misuse, gesture, touch, show, talk} and \textit{look} are
-spontaneous actions that were not requested but arose in the interaction.  These
-actions reflect engagement, and are the one we considered during the analysis.
-Figure~\ref{fig:domino-time-active} shows the distribution of these actions over
-the different runs, over the three condition.
-
-\subsubsection{Perception: Semi-Structured Interviews}
-
-One pre-interview and two interviews were conducted with the children.  We set
-up the interviews like a casual conversation / discussion, so we did not
-separate the two children in order to keep the situation natural. We used casual
-and informal language adapted to the age of the children, and encouraged them to
-justify their answers and tell us more details by asking, for example,
-\textit{How do you know ... ?} or \textit{Tell me, what have you observed when
-... ?}. We paid attention to not ``put words in children's mouth''.
-Consequently, though we re-phrased and repeated some questions, we never forced
-children to give an answer, and accepted when they said they would not know or
-when they did not respond at all.
+We have collected and analysed two types of data. The \textbf{perception of the
+robot} by the children has been captured through two audio-recorded
+semi-structured interviews which took place between run \emph{1.5} and
+\emph{2.1} and at the end of the experiment (a short preliminary interview was
+also conducted to explain the game and assess the expectations of the children
+toward the robot).  Then, the \textbf{children's behavior toward the robot} (\ie
+the child-robot interaction) has been captured in the video recordings by
+annotating a set of actions, described below.
+
+\subsubsection{Perception -- Semi-Structured Interviews}
+
+One pre-interview and two interviews were conducted with the children. Due to
+the age of the participants, we set up the interviews like a casual conversation
+and we did not separate the two children. We paid attention to not ``put words
+in children's mouth''.  Consequently, though we re-phrased and repeated some
+questions, we accepted when they said they would not know or when they did not
+respond at all.
 
@@
     \toprule
-    \textbf{Expectations} \\
-    \midrule
-
+    \textbf{Expectations} (asked during the pre-interview) \\
     \emph{How do you imagine a robot?} \\
@@
     %%
-    \toprule
+    \vspace{0.2em}
     \textbf{Impression} \\
-    \midrule
 
@@
     %%
-    \toprule
+    \vspace{0.2em}
     \textbf{Ascribe intention} \\
-    \midrule
 
@@
     %%
-    \toprule
+    \vspace{0.2em}
     \textbf{Ascribe cognitive connections} \\
-    \midrule
 
@@
     %%
-    \toprule
+    \vspace{0.2em}
     \textbf{Ascribe emotional state} \\
-    \midrule
 
@@
     %%
-    \toprule
+    \vspace{0.2em}
     \textbf{Social acceptance} \\
-    \midrule
 
@@
     %%
-    \toprule
+    \vspace{0.2em}
     \textbf{Companionship} \\
-    \midrule
 
@@
     %%
-    \toprule
+    \vspace{0.2em}
     \textbf{Ascribe moral standing} \\
-    \midrule
 
@@
     \caption{\small Constructs and questions used during the semi-structured interviews
-    with children. The Ranger robot toy box is abbreviated with ``R''. Questions
+    with children. The \emph{Ranger} robot toy box is abbreviated with ``R''. Questions
     related to the construct \emph{expectations} were asked during the
@@
 perception of robots
-\cite{kahn_jr._robotic_2006,leite_influence_2013,weiss_i_2009}. For instance, we
+(\cite{kahn_jr._robotic_2006,leite_influence_2013,weiss_i_2009}). For instance, we
 applied and adapted some of the \emph{constructs} and example questions from the
@@
 blameworthy, has rights or deserves respect.} Similarly, we grouped
-questions according to specific constructs that they evaluate (see
+questions according to the specific constructs that they evaluate (see
 Table~\ref{tab:domino-questions}).
@@
 children's responses were not always accurate, not comparable one by one, and
-children did not always give an answer.
-
-%	Even when children reply that they do not know, this is interesting. Then we either do not ask a good question or they are really uncertain about it.
-
-We did not craft a full word-by-word transcript but
-noted down any statement that was useful and relevant) and used to compute the
-anthropomorphism index presented below.
-
-\subsubsection{Anthropomorphism Index}
+children did not always give an answer. Hence, we did not craft a full
+word-by-word transcript but instead we isolated the key statements that were
+relevant and used them to build the compound index presented below
+(section~\ref{compound_idx}).
+
+%%%%%%%%%%%%%%%
+\subsubsection{Interaction -- Action Coding}
+
+\begin{figure*}[ht!] 
+    \centering 
+    \includegraphics[width=0.8\linewidth]{domino-time-active.pdf} 
+    \caption{\small \textbf{Number and type of actions for each run} (n=480,
+        spontaneous actions). Generally, the number of
+        actions does not decrease over time (from run 1.1 to run 2.9).  The
+        first 7 runs correspond to the \textit{expected phase}, the second 7
+        runs correspond to the \textit{unexpected phase}. Especially during run
+        2.3, the first time when the robot showed an unexpected behavior,
+        children tended to \textit{look} more at the experimenter. During the
+        unexpected phase, also \textit{talk} and \textit{gesture} seem to be
+        increased.}
+    \label{fig:domino-time-active} 
+\end{figure*}
+
+We annotated the behaviors of the children in the video records, and coded the
+salient actions that reflected engagement toward the robot (the coding scheme has
+been inspired from~\cite{fink2014which}): \textbf{touch} (the box is touched,
+\eg petted or caressed); \textbf{talk} (all direct verbal interactions, except
+for calling it to come and pick a domino tile, since children were requested to
+perform this action anyway); \textbf{show} (show something to the robot);
+\textbf{misuse} (kick the robot, poke it in its ``eye'', try to climb on or
+inside the box, drive/push the robot around, stop the robot's wheels with a
+foot); \textbf{look} (when a child looks \emph{at the experimenter} due to
+confusion caused by the robot; look is not coded when the experimenter asks a
+question to the child); \textbf{gesture} (gestures are used to
+communicate/interact with the robot, \eg pointing gestures, waving at the
+robot). Figure~\ref{fig:domino-time-active} shows the distribution of these
+actions over the different runs, summed over the three condition.
+
+\subsubsection{Compound Index of Anthropomorphism}
+\label{compound_idx}
 
 %There are different possibilities to measure engagement in HRI, depending on the
-%specific research question and context. Metrics to measure behavioural engagement
+%specific research question and context. Metrics to measure behavioral engagement
 %in the interaction include, for instance, conversation analysis (\eg used in
@@
 %questions that allowed children to justify and elaborate their answers. We have
-%chosen a similar approach that considers both children's behavioural and
+%chosen a similar approach that considers both children's behavioral and
 %emotional engagement.
@@
 %engagement in the interaction: We assume that children look at the experimenter
-%when they are surprised and seek for help.  This behaviour reflects that they
-%want to make sense of the robot's behaviour. Further, we can take into account
-%how they refer to Ranger and describe the robot (as well as their experience) in
+%when they are surprised and seek for help.  This behavior reflects that they
+%want to make sense of the robot's behavior. Further, we can take into account
+%how they refer to \emph{Ranger} and describe the robot (as well as their experience) in
 %the interviews.  Specifically, we used the constructs \textit{ascribe intention,
@@
 %
-To account for the fact that anthropomorphism arises in an interaction, we bring
-both children's perception of the robot (post-measurement) and their behaviour
-toward it (in-the-moment measurement) together. We did so by building a
-so-called \emph{anthropomorphism index}. We quantify the
-index by attributing points for each anthropomorphic \emph{perception} of the
-robot and for specific kinds of human-like \emph{behaviour}
-toward the robot. The index included the following aspects:\\
-
-\textbf{Perception}: \textit{(max. 13 points)}
+Because the tendency to anthropomorphize manifests itself both in terms of
+perception and behavior, we propose to build a compound index that brings both
+children's perception of the robot (post-measurement) and their behavior toward
+it (in-the-moment measurement) together. We build the index by attributing
+points for each anthropomorphic \emph{perception} of the robot and for specific
+kinds of human-like \emph{behavior} toward the robot, using the following
+grading scheme:
+
+\vspace{0.5em}
+\textbf{Perception}
 
@@
     \item Ascription of \textbf{mental states / feelings}: \textit{2 points} for agreeing
-            that Ranger can be happy or sad; \textit{2 points} for attributing Ranger with
+            that \emph{Ranger} can be happy or sad; \textit{2 points} for attributing \emph{Ranger} with
         hunger or tiredness.
@@
         points} for ascribing seeing and hearing ability; \textit{1 point} for agreeing
-            that Ranger can go out the door by itself; \textit{1 point} for disagreeing that
-            Ranger always obeys; \textit{1 point} for agreeing that Ranger can do something
+            that \emph{Ranger} can go out the door by itself; \textit{1 point} for disagreeing that
+            \emph{Ranger} always obeys; \textit{1 point} for agreeing that \emph{Ranger} can do something
         silly.
@@
     \item Ascription of \textbf{sociality / companionship}: \textit{1 point} for agreeing
-        that Ranger can be a friend.
+        that \emph{Ranger} can be a friend.
 
     \item Ascription of \textbf{moral standing}: \textit{1 point} for disagreeing that
-        Ranger be left alone at home.
+        \emph{Ranger} be left alone at home.
 
     \item Other \textbf{anthropomorphic statements}: \textit{1 point} for anthropomorphic
-        reason for Ranger's misbehaviour; \textit{2 points} for anthropomorphic reason
-        for not leaving Ranger alone (\eg \textit{``It would be sad''}).
+        reason for \emph{Ranger}'s misbehavior; \textit{2 points} for anthropomorphic reason
+        for not leaving \emph{Ranger} alone (\eg \textit{``It would be sad''}).
 
@@
 
-\textbf{Behaviour}: \textit{(max. 3 points)}
+\textbf{Behavior}
+
 \begin{itemize}
@@
     \item Use of \textbf{polite formulations}: \textit{1 point} (\eg
-        \textit{``thank you Ranger''} or \textit{``please Ranger ...''}).
+        \textit{``thank you \emph{Ranger}''} or \textit{``please \emph{Ranger} ...''}).
 
@@
 
-There are certainly limitations to this scoring scheme. For instance, the
-balance between perception and behaviour aspects is questionable and the
-weighting of each item can be discussed: we did not consistently assign 1 point
-to each item, but assigned points between 0.5 and 2 points depending on our
-perception of how a given item reflect on a higher level of anthropomorphic
-perception of the robot (for instance, ascribing the ability to see and hear was
-suggested by our study setup, and we cannot be sure that it really reflects
-anthropomorphism). Note that these issues are mitigated by using the
-anthropomorphism index as a \emph{relative} metric (comparison between
-conditions) and not an absolute value.
+The balance of the grading scheme is open to debate: for instance, we did not
+consistently assign 1 point to each item, but assigned points between 0.5 and 2
+points depending on our perception of how a given item reflect a higher level of
+anthropomorphic perception of the robot (for instance, ascribing the ability to
+see and hear was suggested by the design of the study, and we cannot assert it
+really reflects the explicit projection of cognitive skills). This issue is
+however mitigated by our use of this compound index as a \emph{relative} metric
+(comparison between conditions) and not an absolute value.
 
@@
 
-\subsection{Misbehaviour Recognition, Engagement}
-
-%\paragraph{Misbehaviour Recognition}
+This section present our main findings, interleaving the analysis of perceptions
+(interviews) with behavioral data (action annotations).
+
+The analysis of interviews provides us with insights on the recognition of the
+different misbehaviors of the robot by the children (manipulation check,
+section~\ref{reco}), as well as a picture of the higher cognitive skills that
+they project onto the robot (section~\ref{higher_cognition}).
+
+On the other hand, the amount of actions performed in interaction with the robot
+gives an estimate of the actual engagement of children
+(section~\ref{engagement}).
+
+Finally, analyzing the interaction between perception and behaviors lead to 
+two remarkable clusters of children, adopting very different attitudes toward the
+robot (section~\ref{antidx}).
+
+\subsection{Misbehavior Recognition}
+\label{reco}
+
+%\paragraph{Misbehavior Recognition}
 
 As stated in the introduction, we had hypothesised that the \textit{disobey}
-behaviour is perceived as the robot intentionally not doing what it should do.
-The \textit{mistake} behaviour was intended to show that the robot can do a
+behavior is perceived as the robot intentionally not doing what it should do.
+The \textit{mistake} behavior was intended to show that the robot can do a
 mistake but is aware of it and able to repair its mistake, which should also
@@
 %wanted it to do. This was a surprise. Had they not noticed the robot's
-%misbehaviour? Why not? On one hand, we found that children sometimes gave
+%misbehavior? Why not? On one hand, we found that children sometimes gave
 %contradictory replies when asked the same question twice. This is difficult to
@@
     \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
-    to the question why the robot did not come over, and we received 37 answers.
-    This question shows that children did not necessarily interpret the misbehaviour
-    in the way we had assumed.}
-
-    \label{fig:domino-why-misbehaviour}
+    to the question why the robot did not come over, and we received 37 answers.}
+
+    \label{fig:domino-why-misbehavior}
 \end{figure}
@@
 children did not reply. The remaining ones gave a variety of reasons
-(Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9 of 37
+(Figure~\ref{fig:domino-why-misbehavior}). The most common answer (9 of 37
 replies) was that the robot is somehow \textit{unpredictable} in what it is
@@
 (including \textit{broken parts}), suggesting that children perceived the
-misbehaviour as unintended by the robot. Two of the children who had interacted
-with the disobeying robot said Ranger was \textit{angry}, which none of the
-children in other conditions replied. 13 out of 26 children appeared to ascribe
-intentionality precursors to Ranger explaining that it \textit{did not want to
-continue} carrying domino tiles or that it \textit{``did something
-silly''}\footnote{We understood \textit{``faire une bêtise''} as ``to do a silly
-thing'' in the sense of making a mistake.}.
-
-Not all children perceived the misbehaviour of the robot as we had intended and
-we have to keep this in mind while interpreting the data. Also
-\cite{leite_long-term_2013} found in her study that when children did not
-understand an action of the robot, they tended to view it as a mistake, rather
-than interpreting the robot's behaviour as a deliberative action.
-
-%	\textit{``the supportive behaviour ``Play Bad Move'' was not completely
+misbehavior as unintended by the robot. Two of the children who had interacted
+with the disobeying robot said \emph{Ranger} was \textit{angry}, which none of
+the children in other conditions replied. 13 out of 26 children appeared to
+ascribe intentionality precursors to \emph{Ranger} explaining that it
+\textit{did not want to continue} carrying domino tiles or that it \textit{``did
+something silly''}\footnote{We understood \textit{``faire une bêtise''} as ``to
+do a silly thing'' in the sense of making a mistake.}.
+
+%	\textit{``the supportive behavior ``Play Bad Move'' was not completely
 %	understood as a deliberative action of the robot, but rather as a
@@
 %negative implication: later three of the children in this condition stated they
-%would not accept Ranger as a friend \textit{because it did not always come over
+%would not accept \emph{Ranger} as a friend \textit{because it did not always come over
 %when they asked it to come over}. \cite{short_no_2010} described a similar
-%implication of the robot cheating behaviour: participants made unfavorable
+%implication of the robot cheating behavior: participants made unfavorable
 %character attributions to the cheating robot, so the robot's actions affected
@@
 %	\cite{short_no_2010} found that participants often had an emotional reaction
-%	to the robot's behaviour and made unfavorable character attributions to the
+%	to the robot's behavior and made unfavorable character attributions to the
 %	cheating robot. The robot's actions affected perceptions of the robot as
@@
 
-%\paragraph{Engagement}
-In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
-here. The findings do not directly address the issues
-of long-term usage but concern short-term \textit{engagement}, which is a
-pre-requisite for long-term usage.
-
-The huge proportion of \textit{explore} actions (52~\% of all coded actions)
-already suggests that children were generally engaged in the interaction, and
-most of the time carefully observed what the robot did. When considering the
-actions \textit{explore, gesture, look, misuse, show, talk}, and \textit{touch}
-as \textbf{engagement actions}, 1699 of the 2354 actions reflected engagement
-(72~\%). This indicates that overall children were very engaged in the
-interaction with the robot.
+\subsection{Attribution of Higher Cognitive Skills}
+\label{higher_cognition}
+
+\paragraph{Intentionality}
+
+One of the central points of this study was to investigate to what degree
+children attribute intention and cognitive abilities to the robot.  In the first
+interview after children had interacted with the correctly behaving robot we
+asked three questions to assess how far they ascribe \textbf{intention} to it
+(see questionnaire items in Table~\ref{tab:domino-questions}). One of these
+questions was whether they believed \emph{Ranger} could go out the door by
+itself. A majority of 16 children answered negatively, which suggests that
+they initially do not ascribe intention to the robot. The two other questions
+were whether Ranger would always obey and whether \emph{Ranger} could do a silly
+thing (Figure~\ref{fig:domino-intention}). These two questions were asked again
+later after children had interacted with the unexpectedly behaving robot.
+
+%	With these recurring questions we wanted to see whether children had changed
+%	their mind in terms of ascribing intention to \emph{Ranger} (and whether the
+%	unexpected robot behavior had caused this effect). This comparison turned
+%	out to be difficult, however.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.75\linewidth]{domino-intention.pdf}
+    \caption{\small \textbf{Attribution of intention to \emph{Ranger}.} Children were
+        asked these questions at both interviews. Concerning question (a), there
+        are no remarkable differences in children's responses given in the
+        \textit{first} and \textit{second} interview.  Children tend to think
+        \emph{Ranger} does always obey to them, even after it misbehaved. There is
+        however a small difference in the responses to question (b).  After the
+        robot misbehaved, 8 children think the robot could do something silly whereas
+        first, only 3 children answered like this.}
+
+    \label{fig:domino-intention}
+
+\end{figure}
+
+In the first interview, 12 out of the 15 children who provided an answer
+believed that \emph{Ranger} does always obey to them. Asked whether the robot
+could do something silly, a large majority of 21 children out of 24 replied
+negatively: it appears that after children the first round of interaction (with
+the \textbf{correctly behaving robot}) the children does \textbf{not} generally
+\textbf{ascribe intention} to the robot.
+
+After interacting with the misbehaving robot (second interview), most of the
+children still believed that \emph{Ranger} always obeys to them.  However, 8
+children (previously~3) think that \emph{Ranger} could do something silly. One
+child in the \textit{disobey} condition had changed his answer, and two in each
+the \textit{mistake} and \textit{lost} conditions: even with an
+\textbf{unexpectedly behaving robot} children do \textbf{not necessarily ascribe
+intention} to the robot.  It seems that some children did not interpret the
+misbehavior of the robot as intentional but more like a technical problem or
+mistake. For instance, even after the robot misbehaved by \textit{disobeying},
+the majority of the children in this condition was still convinced that the
+robot could not do a silly thing.  It is however interesting to note that
+children tend to ascribe cognitive abilities to the robot, like the ability to
+see and hear but not intention. We interpret this as children perceiving the
+robot as being able to process sensory information but not being able to make
+decisions on its own.
+
+%\paragraph{Emotions and Companionship}
+%
+%We examined whether children attribute \textbf{feelings} to the robot by asking
+%them (once at the end of the experiment) if they thought that \emph{Ranger} can feel
+%happy or sad sometimes. The majority of
+%children (21 of 26) gave a positive answer. Only 2 children who had interacted
+%with the \textit{disobeying} robot did not believe that \emph{Ranger} has feelings and
+%another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
+%all. Overall, data suggests that \textbf{children attribute emotional states}
+%to the robot. Asked for more details, several children answered that it is
+%through its colours and sounds that the robot shows a feeling. Most children said
+%that they could make the robot feel happy by playing with it and putting a
+%domino tile inside the box. This may also be a reflection of their own feelings,
+%projected on the robot. About half of the children (14 of 26) agreed that \emph{Ranger}
+%can be their friend. We did not ask about what being a friend means to them but
+%as children generally liked playing with the robot, this may be linked to each
+%other. We can note that children \textbf{ascribe feelings to the robot and
+%partly accept that it can be a ``friend''}.
+
+\vspace{1em}
+\paragraph{Moral standing}
+
+Inspired from the questionnaire used by \cite{kahn_jr._robotic_2006}, we asked
+children if it would be alright to leave \emph{Ranger} alone at home (\eg during two
+weeks when they go on a vacation) (Figure~\ref{fig:domino-leave-alone}). 
+20 out of 26 children responded negatively. Asked why, children gave a
+variety of answers that we classified into 6 categories. With 5 replies, the
+most common answer was that the robot ``could do something silly''. Some other
+children simply answered they would like to take it with them. Others were
+afraid that the \emph{Ranger} ``would not find its way'' or ``may be taken away by
+someone''. 2 children believed \emph{Ranger} is sad when left alone and 1 child
+responded the robot would try to escape. Interestingly, and while we intuitively
+expected many children to fear that the robot would be sad if left alone, only 2
+expressed a moral position, while most of the others actually expressed several
+forms of distrust towards the robot. This shows that things must
+be put into perspective and even young children do not automatically consider a
+so-called social robot as an actual social agent that deserves care.
+
+\begin{figure}[!h]
+    \centering 
+    \includegraphics[width=1.0\linewidth]{domino-leave-why.pdf}
+    \caption{\small Attributions of moral
+        standing: we asked children whether it was alright to leave \emph{Ranger}
+        alone at home if they go on a 2-week vacation. Multiple answers
+        (open-ended) were allowed when asked to justify their answer.}
+
+    \label{fig:domino-leave-alone} 
+\end{figure}
+
+\subsection{Engagement}
+\label{engagement}
+
+%The huge proportion of \textit{explore} actions (52~\% of all coded actions)
+%already suggests that children were generally engaged in the interaction, and
+%most of the time carefully observed what the robot did. When considering the
+%actions \textit{explore, gesture, look, misuse, show, talk}, and \textit{touch}
+%as \textbf{engagement actions}, 1699 of the 2354 actions reflected engagement
+%(72~\%). This indicates that overall children were very engaged in the
+%interaction with the robot.
+%
+%
 %Furthermore, data suggests that the robot in the
@@
 %analysis supports this: An ANOVA indicates that there was a significant effect
-%of robot behaviour on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
+%of robot behavior on the actions \textit{explore} (F(2,23)=11.31, p<.001) and
 %\textit{look} (F(2,23)=4.6, p=.021). Post-hoc comparisons using the Tukey's test
@@
 %children's attention because it faces the searcher child and uses fairly
-%strong audio and light cues as compared to the other behaviours.}.
-
-We found a significant difference between the average of engagement
-actions carried out during the first 7 runs (correct robot behaviour) and during
-the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1, p=.03). In
-all three conditions, children carried out more engagement actions with the
-unexpectedly behaving robot. No interaction effect was found between the two
-phases of interaction (expected / unexpected) and condition (F(2,36)=1.2,
-p=.31). In general, this finding supports our first hypothesis: children show
+%strong audio and light cues as compared to the other behaviors.}.
+
+We found a significant difference between the average of engagement actions
+(Figure~\ref{fig:domino-time-active}) carried out during the first 7 runs
+(correct robot behavior) and during the second 7 runs, when the robot behaved
+unexpectedly (F(1,36)=5.1, p=.03). In all three conditions, children carried out
+more engagement actions with the unexpectedly behaving robot.  Importantly, no
+interaction effect was found between the two phases of interaction (expected /
+unexpected) and condition (F(2,36)=1.2, p=.31): the robot's failure mode does
+not seem to impact the level of engagement.
+
+In general, this finding \textbf{supports our first hypothesis}: children show
 more engagement toward a robot that behaves unexpectedly from time to time
@@
 
-\subsection{Attribution of Higher Cognitive Skills}
-
-\paragraph{Intentionality}
-
-One of the central points of this study was to investigate to what degree
-children attribute intention and cognitive abilities to the robot.  In the first
-interview after children had interacted with the correctly behaving robot we
-asked three questions to assess how far they ascribe \textbf{intention} to it
-(see questionnaire items in Table~\ref{tab:domino-questions}). One of these
-questions was whether they believed Ranger could go out the door by itself. The
-majority of 16 children answered negatively, which suggests that they initially
-do not ascribe intention to the robot. The two other questions were whether
-Ranger would always obey and whether Ranger could do a silly thing
-(Figure~\ref{fig:domino-intention}). These two questions were asked again later
-after children had interacted with the unexpectedly behaving robot.
-
-%	With these recurring questions we wanted to see whether children had changed
-%	their mind in terms of ascribing intention to Ranger (and whether the
-%	unexpected robot behaviour had caused this effect). This comparison turned
-%	out to be difficult, however.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.75\linewidth]{domino-intention.pdf}
-    \caption{\small \textbf{Attribution of intention to Ranger.} Children were
-        asked these questions at both interviews. Concerning question (a), there
-        are no remarkable differences in children's responses given in the
-        \textit{first} and \textit{second} interview.  Children tend to think
-        Ranger does always obey to them, even after it misbehaved. There is
-        however a small difference in the responses to question (b).  After the
-        robot misbehaved, 8 children think the robot could do something silly whereas
-        first, only 3 children answered like this.}
-
-    \label{fig:domino-intention}
-
-\end{figure}
-
-Overall, in the first interview 12 of the 26 children believed Ranger does
-always obey to them. Asked whether Ranger could do something silly, the great
-majority of 21 children replied negatively. We can summarise that after children
-had interacted with the \textbf{correctly behaving robot} the majority does
-\textbf{not ascribe intention} to the robot.
-
-After they had interacted with the misbehaving robot, we asked children again.
-Still 11 children believed Ranger would always obey to them. There was a
-more remarkable change when asking children whether Ranger could do something
-silly. In the second interview, 8 children (previously~3) answered Ranger could
-do something silly. 1 child in the \textit{disobey} condition had changed their
-answer, and each 2 in the \textit{mistake} and \textit{lost} condition.
-
-We can summarise that even with the \textbf{unexpectedly behaving robot}
-children do \textbf{not necessarily ascribe intention} to the robot. The
-unexpected robot behaviour impacted only some children's attributions of
-intention to the robot.  It seemed that some children did not interpret the
-robot's misbehaviour as intentional but more like a technical problem or
-mistake. For instance, even after the robot misbehaved by \textit{disobeying},
-the majority of the children in this condition was still convinced that the
-robot could not do a silly thing.  It is however interesting to note that children tend
-to ascribe cognitive abilities to the robot, like the ability to see and hear
-but not intention. We interpret that children may perceive the robot as being
-able to process sensory information but that it is not able to make decisions on
-its own.
-
-%\paragraph{Emotions and Companionship}
-%
-%We examined whether children attribute \textbf{feelings} to the robot by asking
-%them (once at the end of the experiment) if they thought that Ranger can feel
-%happy or sad sometimes. The majority of
-%children (21 of 26) gave a positive answer. Only 2 children who had interacted
-%with the \textit{disobeying} robot did not believe that Ranger has feelings and
-%another 3 children (2 \textit{disobey} and 1 \textit{lost}) did not reply at
-%all. Overall, data suggests that \textbf{children attribute emotional states}
-%to the robot. Asked for more details, several children answered that it is
-%through its colours and sounds that the robot shows a feeling. Most children said
-%that they could make the robot feel happy by playing with it and putting a
-%domino tile inside the box. This may also be a reflection of their own feelings,
-%projected on the robot. About half of the children (14 of 26) agreed that Ranger
-%can be their friend. We did not ask about what being a friend means to them but
-%as children generally liked playing with the robot, this may be linked to each
-%other. We can note that children \textbf{ascribe feelings to the robot and
-%partly accept that it can be a ``friend''}.
-
-\vspace{1em}
-\paragraph{Moral standing}
-
-Inspired from the questionnaire used by \cite{kahn_jr._robotic_2006}, we asked
-children if it would be alright to leave Ranger alone at home (\eg during two
-weeks when they go on a vacation) (Figure~\ref{fig:domino-leave-alone}). 
-20 out of 26 children responded negatively. Asked why, children gave a
-variety of answers that we classified into 6 categories. With 5 replies, the
-most common answer was that the robot ``could do something silly''. Some other
-children simply answered they would like to take it with them. Others were
-afraid that the Ranger ``would not find its way'' or ``may be taken away by
-someone''. 2 children believed Ranger is sad when left alone and 1 child
-responded the robot would try to escape. Interestingly, and while we intuitively
-expected many children to fear that the robot would be sad if left alone, only 2
-expressed a moral position, while most of the others actually expressed several
-forms of distrust towards the robot. This shows that things must
-be put into perspective and even young children do not automatically consider a
-so-called social robot as an actual social agent that deserves care.
-
-\begin{figure}[!h]
-    \centering 
-    \includegraphics[width=1.0\linewidth]{domino-leave-why.pdf}
-    \caption{\small Attributions of moral
-        standing: we asked children whether it was alright to leave Ranger
-        alone at home if they go on a 2-week vacation. Multiple answers
-        (open-ended) were allowed when asked to justify their answer.}
-
-    \label{fig:domino-leave-alone} 
-\end{figure}
-
-\subsection{Anthropomorphic Projections and Social Engagement}
-
-The anthropomorphism index expresses to what extent children engaged with Ranger
-in a human-like way, both in terms of their behaviour toward the robot and their
-perception of the robot. We present here findings on a pair (group) level.
+It must be noted that the novelty of the robot plays an important role. Our
+findings do not directly address the issues of long-term usage and are
+effectively focused on short-term \textit{engagement}, which is a pre-requisite
+for long-term usage.
+
+\subsection{Anthropomorphic Projections}
+\label{antidx}
+
+The compound index of anthropomorphism, presented at section~\ref{antidx},
+expresses to what extent children engaged with \emph{Ranger} in a human-like
+way, both in terms of their behavior toward the robot and their perception of
+the robot (the findings presented hereafter are at pair (group) level).
 
@@
 
-On average, Ranger was moderately anthropomorphized by the children. 8 of the 13
-groups had an index of 8 or higher, evenly spread over the three conditions.
-However, the mean index of anthropomorphism in the three conditions varied, with
-the \textit{mistake} and \textit{lost} condition leading to a higher index than
-the \textit{disobey} condition. This finding suggests that the disobeying robot
-was less anthropomorphized than the other two robot behaviours, which speaks
-against our second hypothesis. We had expected that the disobeying behaviour is
-perceived as an intentional action which we assumed would lead to increased
-anthropomorphism. This was not the case. The slight difference between the
-\textit{lost} and \textit{mistake} robot was also expected in the opposite
-direction. It could be that the robot's ``helplessness'' led to this. This is
-also reflected in children's behaviour: with the lost robot, children looked
-more often at the experimenter than in the other condition, which suggests that
-they could not fully make sense of the robot's behaviour, and the fact of not
-being able to understand (and hence predict) a robot's behaviour is likely to
-increase anthropomorphism.\footnote{One of the cognitive / psychological
-explanations for anthropomorphism is that people want to make sense of
-something they do not understand and then tend to anthropomorphize this
-something (human traits are a good source of making attributions because
-this is what people understand best -- themselves and other humans). For
-more details the reader may refer to~\cite{epley_seeing_2007}.}
-%
-%\begin{table}[ht!] \centering \footnotesize \begin{tabular}{lccc} \toprule & M
-%& SD & groups with index > 8 \\ \midrule
-%
-%        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ \textit{disobey} & 6.5
-%        & 3.68 & 2 of 5 \\ \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\
-%        \bottomrule \end{tabular} \caption{\small \textbf{Anthropomorphism
-%        index.} The maximum possible index was 16. The \textit{lost} robot
-%        elicits the highest index, which suggests that it is anthropomorphized
-%        more. Contrary to our hypothesis, data suggests that the
-%        \textit{disobeying} robot is anthropomorphized less but the
-%        \textit{lost} robot more.}
-%
-%    \label{tab:domino-anth-score}       % Give a unique label
-%\end{table}
+On average, \emph{Ranger} was moderately anthropomorphized by the children. 8 of
+the 13 groups had an index of 8 or higher, evenly spread over the three
+conditions (table~\ref{tab:domino-anth-score}).  However, the mean index of
+anthropomorphism in the three conditions varied, with the \textit{mistake} and
+\textit{lost} condition leading to a higher index than the \textit{disobey}
+condition. This finding suggests that the disobeying robot was \emph{less}
+anthropomorphized than the other two robot behaviors, which speaks
+\textbf{against our second hypothesis}. We had expected that the disobeying
+behavior is perceived as an intentional action which we assumed would lead to
+increased anthropomorphism. This was not the case. The slight difference between
+the \textit{lost} and \textit{mistake} robot was also expected in the opposite
+direction and the \textit{lost} robot was overall the one eliciting the highest
+level of anthropomorphism (the robot's ``helplessness'' may have lead to this). This is
+also reflected in children's behavior: with the lost robot, children looked more
+often at the experimenter than in the other condition, which suggests that they
+could not fully make sense of the robot's behavior, and the fact of not being
+able to understand (and hence predict) a robot's behavior is likely to increase
+anthropomorphism.\footnote{One of the cognitive / psychological explanations for
+anthropomorphism is that people want to make sense of something they do not
+understand and then tend to anthropomorphize this something (human traits
+are a good source of making attributions because this is what people
+understand best -- themselves and other humans). For more details the reader
+may refer to~\cite{epley_seeing_2007}.}
+
+\begin{table}[ht!] \centering \footnotesize \begin{tabular}{lccc} \toprule & M
+& SD & groups with index $> 8$ \\ \midrule
+
+        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ \textit{disobey} & 6.5
+        & 3.68 & 2 of 5 \\ \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\
+        \bottomrule \end{tabular} \caption{\small \textbf{Anthropomorphism
+        index.} The maximum possible index was 16. The \textit{lost} robot
+        elicits the highest index, which suggests that it is anthropomorphized
+        more. Contrary to our hypothesis, data suggests that the
+        \textit{disobeying} robot is anthropomorphized less but the
+        \textit{lost} robot more.}
+
+    \label{tab:domino-anth-score}       % Give a unique label
+\end{table}
 
@@
 %that 
-the more a group showed engagement in the interaction, the less they
-anthropomorphized the robot. This is a key result, which was against our
+\textbf{the more a group showed engagement in the interaction, the less they
+anthropomorphized the robot}. This is a key result, which was against our
 initial assumption. A possible interpretation is that children who interact more
 with the robot understand better how it works, they are more familiar with it,
-and as such the robot appears less ``mystical'' to them, so there is not a big
+and as such the robot appears less ``mystical'' to them, and they hence do not
 need to anthropomorphize it. On the contrary, the cluster of groups that do not
@@
         engagement actions per pairs.} A scatter plot of the count of engagement
-        actions (without \emph{explore}) and the \textit{anthropomorphic
+        actions and the \textit{anthropomorphic
         perception} (score per group) evidence one cluster of
@@
         the anthropomorphic perception (\textit{y-axis}) does not take into
-        account the behavioural aspect of the anthropomorphism index, as this is
+        account the behavioral aspect of the anthropomorphism index, as this is
         part of the interaction (\textit{x-axis}).}
@@
 %Our data on the anthropomorphism index also suggest \textbf{qualitative gender
-%differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
+%differences} in children's tendency to anthropomorphize \emph{Ranger}. Boys (M=8.2,
 %SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
@@
 play domino together with a robot, the robot seems to be more engaging when it
-shows some misbehaviour compared to when it always behaves as expected
+shows some misbehavior compared to when it always behaves as expected
 (notwithstanding the impact of a novelty effect).
 
-Regarding the design of our three conditions (\emph{lost},
-\emph{disobey}, \emph{mistake}), we cannot conclusively affirm whether children perceived the
-unexpected robot behaviour as a malfunction (something that happens to a
-machine) or as being intended and based on a motivation (something related to a
-social entity). Children stated both, when asked why the robot had misbehaved.
-Some referred to \textit{``a technical problem''} while others said the robot
+Regarding the design of our three conditions (\emph{lost}, \emph{disobey},
+\emph{mistake}), we cannot conclusively affirm whether children perceived the
+unexpected robot behavior as a malfunction (something that happens to a machine)
+or as being intended and based on a motivation (something related to a social
+entity). Children stated both, when asked why the robot had misbehaved.  Some
+referred to \textit{``a technical problem''} while others said the robot
 \textit{``is tired''} or it \textit{``doesn't want to carry domino tiles any
@@
 %playful. However, they are also confused and cannot really make sense of the
-%robot's strange behaviour. We also cannot conclusively tell apart whether children perceived
-%the unexpected robot behaviour entirely as a malfunction (something that happens
+%robot's strange behavior. We also cannot conclusively tell apart whether children perceived
+%the unexpected robot behavior entirely as a malfunction (something that happens
 %to a machine) or as being intended and based on a motivation (something related
@@
 %things are interpreted -- especially with young children.  Certainly more work
-%needs to be done to investigate which robot behaviour is most beneficial for
+%needs to be done to investigate which robot behavior is most beneficial for
 %young children and can promote their engagement and motivation to interact with
@@
 %
-%With the manipulation of the robot behaviour we were able to surprise children.
-%However, it is questionable how often the same type of behaviour manipulation
+%With the manipulation of the robot behavior we were able to surprise children.
+%However, it is questionable how often the same type of behavior manipulation
 %leads to surprise. Moreover, our experiment was a short-term interaction study
@@
 %investigate the long-term interaction with the robot and the impact of the
-%behavioural variances.
+%behavioral variances.
 %
@@
 %Overall, it appears that when trying to study something in more detail, such as
-%the manipulation of robot behaviour, 4-5 year old children may be too young. But
+%the manipulation of robot behavior, 4-5 year old children may be too young. But
 %when trying to evaluate a more general approach, the design of a prototype, or
@@
 
-%In this study, we investigated the effect of unexpected robot behaviour on
-%children's engagement in interacting with Ranger and on their perception of the
+%In this study, we investigated the effect of unexpected robot behavior on
+%children's engagement in interacting with \emph{Ranger} and on their perception of the
 %robot.  Our first hypothesis finds support: children show more engagement toward
 %a robot that behaves unexpectedly from time to time. Further, different types of
-%unexpected behaviour may have a different effect, and therefore the behaviour
+%unexpected behavior may have a different effect, and therefore the behavior
 %manipulation needs to be designed with care.
 
-Still, we did not find support for our second hypothesis which stated that children
-perceive a robot showing intention or cognitive abilities as more human-like
-than a robot that appears to have a system error. While this may be due to the study
-setup and the fact that children did not interpret the robot misbehaviour in the
-conceived way, our findings seem to suggest the contrary to our hypothesis. A
-robot that appeared to do a \textit{mistake} or to be \textit{lost} was more
-anthropomorphized than a robot that \textit{disobeyed}.
-
-Another outcome of this study is the initial application of an
-anthropomorphism index to a child-robot interaction study. This index
-considers both behavioural and phenomenological aspects and is able to indicate
-lower and higher levels of anthropomorphism along this continuous index.  Our
-experience with this index suggests that children tend to conditionally
+Still, we did not find support for our second hypothesis which stated that
+children perceive a robot showing intention or cognitive abilities as more
+human-like than a robot that appears to have a system error. While this may be
+due to the study setup and the fact that children did not interpret the robot
+misbehavior in the conceived way, our findings seem to suggest the contrary to
+our hypothesis. A robot that appeared to do a \textit{mistake} or to be
+\textit{lost} was more anthropomorphized than a robot that \textit{disobeyed}.
+
+Another outcome of this study is the initial application of an compound index of
+anthropomorphism to assess children's anthropomorphic projection onto robots.
+This index considers both behavioral and phenomenological aspects, and it
+suggests, in our experiment, that children tend to conditionally
 anthropomorphize the robot. Higher indexes of anthropomorphism were found in the
